---
title: "Chin_Subj_Analysis_Stage2_V1"
author: "Lei Yue"
date: "2024-01-01"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Loading the data and Precossing the data
First, we load our first data sourse, namely, the five Chinese journals of coding data. Our coding scheme include three stage: pre-codding stage, coding stage and proofreading  coding stage. The coding data was producted in last two stages. We combine each coding data respectively becasuse these data was coded by different coding group.


### Loading the data of coding stage 
```{r message=FALSE, warning=FALSE}
library(openxlsx)
library(dplyr)
library(tidyverse)

file_list <- list.files(
  "C:\\Users\\yuelei\\Desktop\\chin-subj\\Stage_2_Code_Data",
  pattern = ".xlsx",
  full.names = TRUE, recursive = TRUE)

df <- setNames(
  lapply(file_list, function(file) read.xlsx(file)),
  sapply(file_list, basename))

rm(file_list)
names(df) <- paste0("[", seq_along(df), "] ", names(df))

df <- lapply(df, function(df) {  
  df[] <- lapply(df, as.character)  
  return(df)  
})  
```


### Combining the two stages' data (Group2,3,4,5,6, and 7)
```{r}
Group24567_1 <- dplyr::bind_rows(df[[3]],df[[6]],df[[7]],df[[8]],df[[9]]) %>% 
  dplyr::filter(Coder == "final") %>% 
  dplyr::select(-c(8,9,14:18,27,28,37,38)) %>% 
  dplyr::select(-31)

Group24567_2 <- dplyr::bind_rows(df[[11]],df[[13]],df[[14]],df[[15]],df[[16]]) %>% 
  dplyr::filter(Coder == "final") %>%
  dplyr::rename_at(vars(1:4,7), ~paste0(., "_N")) %>%
  dplyr::select(-20)
  
Group24567_bind <-  cbind(Group24567_1,Group24567_2) %>% 
  dplyr::select(1,31,2,32,8,33,11,34,3:7,9,10,12:30,35:49)

Group24567_bind_equal <- Group24567_bind %>%
  dplyr::select(3:8) %>% 
  dplyr::filter(!(Article_IDs == Article_IDs_N &
                    Study_Number == Study_Number_N &
                    Subjects_Group == Subjects_Group_N)) %>% 
  dplyr::mutate(Remark = ifelse(!(Article_IDs == Article_IDs_N), "Article_IDs", ifelse(!(Study_Number == Study_Number_N), "Study_Number", ifelse(!(Subjects_Group == Subjects_Group_N), "Subjects_Group", NA_character_))))

## The Articles_IDs, Study_Number, and Subject_Group of groups 2,4,5,6 and 7 are different in two coding stages (see Gourp24567_bind_equal) and now  we go back to the paper for modification.

Group24567_bind$Subjects_Group[125] <- Group24567_bind$Subjects_Group_N[125]

Group24567_bind$Subjects_Group[126] <- Group24567_bind$Subjects_Group_N[126]

Group24567_bind$Subjects_Group[127] <- Group24567_bind$Subjects_Group_N[127]
  
Group24567_bind$Subjects_Group[377] <- "传统识字教学组"
  
Group24567_bind$Subjects_Group[383] <- "健康对照组"

Group24567_bind$Subjects_Group[858] <- Group24567_bind$Subjects_Group_N[858]

Group24567_bind$Subjects_Group[859] <- Group24567_bind$Subjects_Group_N[859]

Group24567_bind$Subjects_Group[880] <- Group24567_bind$Subjects_Group_N[880]

Group24567_bind$Subjects_Group[881] <- Group24567_bind$Subjects_Group_N[881]

Group24567_bind$Subjects_Group[882] <- Group24567_bind$Subjects_Group_N[882]
  
Group24567_bind$Study_Number_N[975] <- 1
  
Group24567_bind$Study_Number_N[976] <- 2
  
Group24567_bind$Article_IDs[1057] <- 20181078
  
Group24567_bind$Subjects_Group_N[1076] <- "快乐经历"
  
Group24567_bind$Study_Number[1081] <- 0.1
  
Group24567_bind$Study_Number_N[1081] <- 0.1
  
Group24567_bind$Study_Number_N[1082] <- 0.2
  
Group24567_bind$Subjects_Group[1112] <- "控制组"
  
Group24567_bind$Study_Number_N[1176] <- 2

## run Group24567_bind_equal again and find this data.frame is not data available, thus we rm this data frame

rm(Group24567_bind_equal)
```


### Finding the distinct Ids in suppl documents
```{r }
Suppl_ID <- dplyr::bind_rows(df[[2]],df[[5]]) %>% 
  dplyr::filter(Coder == "final") %>%
  dplyr::distinct(Article_IDs)
```


### Loading the Group 1 data (include suppl)
```{r}
Group1_1 <- df[[1]] %>% 
  dplyr::filter(Coder == "final") %>% 
  dplyr::filter(!Article_IDs %in% Suppl_ID$Article_IDs) %>% 
  dplyr::select(-c(8,9,14:18,27,28,37,38)) %>% 
  dplyr::select(-30)

Group1_suppl <- df[[2]] %>% 
  dplyr::filter(Coder == "final") %>% 
  dplyr::rename_at(vars(8,9,14:18,27,28,37,38), ~paste0(., "_N"))

Group1_2 <- df[[10]] %>% 
  dplyr::filter(Coder == "final") %>%
  dplyr::filter(!Article_IDs %in% Suppl_ID$Article_IDs) %>%
  dplyr::rename_at(vars(1:4,7), ~paste0(., "_N"))

Group1_bind <- cbind(Group1_1,Group1_2) %>%
  dplyr::select(1,30,2,31,8,32,11,33,3:7,9,10,12:29,34:48)

Group1_bind_equal <- Group1_bind %>%
  dplyr::select(3:8) %>% 
  dplyr::filter(!(Article_IDs == Article_IDs_N &
                    Study_Number == Study_Number_N &
                    Subjects_Group == Subjects_Group_N)) %>% 
  dplyr::mutate(Remark = ifelse(!(Article_IDs == Article_IDs_N), "Article_IDs", ifelse(!(Study_Number == Study_Number_N), "Study_Number", ifelse(!(Subjects_Group == Subjects_Group_N), "Subjects_Group", NA_character_))))

Group1_bind <- bind_rows(Group1_bind,Group1_suppl)

## The Articles_IDs, Study_Number, and Subject_Group are different in two coding stages (see Gourp1_bind_equal) and now  we go back to the paper for modification.

Group1_bind$Study_Number[170] <- Group1_bind$Study_Number_N[170]

Group1_bind$Study_Number[171] <- Group1_bind$Study_Number_N[171] 

Group1_bind$Study_Number[172] <- Group1_bind$Study_Number_N[172] 

Group1_bind$Study_Number[173] <- Group1_bind$Study_Number_N[173] 

## run Group1_bind_equal again and find this data.frame is not data available, thus we rm this data frame

rm(Group1_bind_equal)
```


### Loading the Group 3 data (include suppl)
```{r}
Group3_1 <- df[[4]] %>% 
  dplyr::filter(Coder == "final") %>% 
  dplyr::filter(!Article_IDs %in% Suppl_ID$Article_IDs) %>% 
  dplyr::select(-c(8,9,14:18,27,28,37,38)) #%>% 
  #dplyr::select(-30)

Group3_suppl <- df[[5]] %>% 
  dplyr::filter(Coder == "final") %>% 
  dplyr::rename_at(vars(8,9,14:18,27,28,37,38), ~paste0(., "_N"))

Group3_2 <- df[[12]] %>% 
  dplyr::filter(Coder == "final") %>%
  dplyr::filter(!Article_IDs %in% Suppl_ID$Article_IDs) %>%
  dplyr::rename_at(vars(1:4,7), ~paste0(., "_N"))

Group3_bind <- cbind(Group3_1,Group3_2) %>%
  dplyr::select(1,30,2,31,8,32,11,33,3:7,9,10,12:29,34:48)

##20213137校对编码漏编，Group3_1中编码为20211037，IDs错误

Group3_bind_equal <- Group3_bind %>%
  dplyr::select(3:8) %>% 
  dplyr::filter(!(Article_IDs == Article_IDs_N &
                    Study_Number == Study_Number_N &
                    Subjects_Group == Subjects_Group_N)) %>% 
  dplyr::mutate(Remark = ifelse(!(Article_IDs == Article_IDs_N), "Article_IDs", ifelse(!(Study_Number == Study_Number_N), "Study_Number", ifelse(!(Subjects_Group == Subjects_Group_N), "Subjects_Group", NA_character_))))

## 2 篇文章待核对

Group3 <- bind_rows(Group3_bind,Group3_suppl)

#tabg3 <- data.frame(table(Group3_1$Article_IDs)) 
#tabg32 <- data.frame(table(Group3_2$Article_IDs_N))

#write.csv(tabg3,"tabg3.csv")
#write.csv(tabg32,"tabg32.csv")
```


### Combine the coding data and the proofreading data
```{r message=FALSE, warning=FALSE}

df_bind <- bind_rows(Group24567_bind,Group1_bind,Group3_bind)

```


## Check the Articles Journals
```{r}

df_indentification_Journal <- df_bind %>% 
  dplyr::mutate(IDs5=substr(Article_IDs_N,5,5)) %>% 
  dplyr::mutate(IDs5=recode(IDs5,"1"="心理学报","2"="心理科学","3"="中国临床心理学杂志",
                       "4"="心理发展与教育","5"="心理与行为研究")) %>% 
  dplyr::mutate(Journal_IDs5 = ifelse(Journal == IDs5, TRUE,FALSE)) %>%  
  dplyr::filter(Journal_IDs5 == "FALSE") %>% 
  dplyr::distinct(Article_IDs,.keep_all = TRUE)

## 117行数据待检查

##table(Chin_Subj_Coding_Data$Article_IDs)

## 20084071为摘要集，20081048缺少journal,20082370错误，20082379NA，20083033，20083067
```


## Check Articles' other coding information
```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}

#table(Chin_Subj_Coding_Data$Remark2)

#tryanalysis <- Chin_Subj_Coding_Data %>% 
 # dplyr::filter(Coder == "final") %>% 
  #dplyr::filter(is.na(Remark1)) %>% 
  #dplyr::filter(is.na(Remark2) | Remark2 != "被试重复使用")

## 这里如果合并了Proofreading之后发现coding basis的final是空的需要补全

#names(Chin_Subj_Coding_Data)

#temp_rownames <- data.frame(cdf= c(names(Chin_Subj_Coding_Data)))

#temp_un_reported01 <- c("Sample_Type","Age","Gender","SES",
                       # "Religious","Subjects_Area","Sampling_Method")

#class(Chin_Subj_Coding_Data$Study_Type)

#temp11 <- Chin_Subj_Coding_Data %>% 
 # filter(Coder == "final")
```


## Calculating report condition 
In our data, there are some data columns that need to calculate the report of the data,such as Gender, Age, SES, Educational attachment, Occupation, Ethnicity, Religious,Subjects_Recruitment_Area and  Sampling_Method,Subjects_Recruitment_Method. In this part, we will finish this analysis.


### Age report
```{r}
df_Age_Report <- Chin_Subj_Coding_Data %>%
  dplyr::filter(is.na(Remark1)) %>% 
  dplyr::filter(!grepl("重复", Remark2)) %>% 
  dplyr::select(Age) %>% 
  dplyr::count(Age) %>% 
  dplyr::mutate(Proportion = round(n / sum(n), 2) * 100,
                Site = "Age") %>% 
  dplyr::rename(Group = "Age")

df_Age_Report
##报告数据的每一列必须转化为画成一个图的数据
```  


### Gender report
```{r}
df_Gender_Report <- Chin_Subj_Coding_Data %>%
  dplyr::filter(is.na(Remark1)) %>% 
  dplyr::filter(!grepl("重复", Remark2)) %>% 
  dplyr::select(Gender) %>% 
  dplyr::count(Gender) %>% 
  dplyr::mutate(Proportion = round(n / sum(n), 2) * 100,
                Site = "Gender") %>% 
  dplyr::rename(Group = "Gender")

df_Gender_Report
```


### SES report
```{}

```


### Ethnicity report
```{r}
df_Ethnicity_Report <- Chin_Subj_Coding_Data %>%
  dplyr::filter(is.na(Remark1)) %>% 
  dplyr::filter(!grepl("重复", Remark2)) %>% 
  dplyr::select(Ethnicity) %>% 
  dplyr::count(Ethnicity) %>% 
  dplyr::mutate(Proportion = round(n / sum(n), 2) * 100,
                Site = "Ethnicity") %>% 
  dplyr::rename(Group = "Ethnicity")

df_Ethnicity_Report
```


### Religious report
```{r}
df_Religious_Report <- Chin_Subj_Coding_Data %>%
  dplyr::filter(is.na(Remark1)) %>% 
  dplyr::filter(!grepl("重复", Remark2)) %>% 
  dplyr::select(Religious) %>% 
  dplyr::count(Religious) %>% 
  dplyr::mutate(Proportion = round(n / sum(n), 2) * 100,
                Site = "Religious")%>% 
  dplyr::rename(Group = "Religious")

df_Religious_Report
```


### Subjects_Recruitment_Area report
```{r}

df_Subjects_Recruitment_Area_Report <- Chin_Subj_Coding_Data %>%
  dplyr::filter(is.na(Remark1)) %>% 
  dplyr::filter(!grepl("重复", Remark2)) %>% 
  dplyr::select(Subjects_Recruitment_Area) %>%
  dplyr::mutate(Subjects_Recruitment_Area = ifelse(grepl("[\u4e00-\u9fa5]",
                                                         Subjects_Recruitment_Area), 1, Subjects_Recruitment_Area)) %>%
                  dplyr::count(Subjects_Recruitment_Area) %>%
                  dplyr::mutate(Proportion = round(n / sum(n), 2) * 100,
                                Site = "Subjects_Recruitment_Area") %>% 
  dplyr::rename(Group = "Subjects_Recruitment_Area")

df_Subjects_Recruitment_Area_Report  
```


### Sampling_Method report
```{R}
df_Sampling_Method_Report <- Chin_Subj_Coding_Data %>%
  dplyr::filter(is.na(Remark1)) %>% 
  dplyr::filter(!grepl("重复", Remark2)) %>% 
  dplyr::select(Sampling_Method) %>% 
  dplyr::mutate(ifelse(Sampling_Method > 0 , "1", "0")) %>% 
  dplyr::count(Sampling_Method) %>% 
  dplyr::mutate(Proportion = round(n / sum(n), 2) * 100,
                Site = "Sampling_Method") %>% 
  dplyr::rename(Group = "Sampling_Method")

df_Sampling_Method_Report

```


### Subjects_Recruitment_Method report
```{r}

```


### Educational attachment report
```{r}
df_Educational_Attainment_Report <- Chin_Subj_Coding_Data %>%
  dplyr::filter(Sample_Type == "4") %>%
  dplyr::select(Educational_Attainment) %>% 
  dplyr::count(Educational_Attainment) %>% 
  dplyr::mutate(Proportion = round(n / sum(n), 2) * 100,
                Site = "Educational_Attainment")

df_Educational_Attainment_Report
```


### Occupation repot
```{r}
df_Occupation_Report <- Chin_Subj_Coding_Data %>%
  dplyr::filter(Sample_Type == "4") %>%
  dplyr::select(Occupation) %>% 
  dplyr::count(Occupation) %>% 
  dplyr::mutate(Proportion = round(n / sum(n), 2) * 100,
                Site = "Occupation")

df_Occupation_Report
```


### Combine all above data and plot
```{r}


df_report <- list(df_Age_Report,df_Gender_Report,df_Ethnicity_Report,
                              df_Religious_Report,df_Sampling_Method_Report,df_Subjects_Recruitment_Area_Report)

df_report <- dplyr::bind_rows(df_report)

df_report$Group <- replace(df_report$Group, df_report$Group == "0" , "unreported")

df_report$Group <- replace(df_report$Group, df_report$Group %in% c("1", "2","3") , "reported")

df_report %>% 
  ggplot(aes(Site,Proportion, fill = Group)) +
  geom_bar(stat = "identity") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab("Var")
```








```
