---
title: "Chin_Subj_Analysis_Stage2_V1"
author: "Lei Yue"
date: "2024-01-01"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Loading the data and Precossing the data
First, we load our first data sourse, namely, the five Chinese journals of coding data. Our coding scheme include three stage: pre-codding stage, coding stage and proofreading  coding stage. The coding data was producted in last two stages. We combine each coding data respectively becasuse these data was coded by different coding group.


### Loading the data of coding stage 
```{r message=FALSE, warning=FALSE}
rm(list = ls())

if (!require("pacman")) install.packages("pacman")

# use package "pacman" as loading R packages tools

pacman::p_load("tidyverse","rio","here")

file_list <- list.files(
  here::here("Stage_2_Code_Data"),
  pattern = ".xlsx",
  full.names = TRUE, recursive = TRUE)

df <- rio::import_list(file_list)


df <- lapply(df, function(df) {  
  df[] <- lapply(df, as.character)  
  return(df)  
})

rm(file_list)

```


### Check col names
I only corrected the inconsistencies in the case of letters and spelling errors in the column names. For any other inconsistencies in column names, I made the necessary modifications during the subsequent merging process.
```{r}
## Check the coding stage col names

Coding_Data_Names <- data.frame(Group1_Coding_Names = names(df[[1]]),
                       Group1_Coding_Suppl_Names = names(df[[2]]),
                       Group2_Coding_Names = names(df[[3]]),
                       Group3_Coding_Names = names(df[[4]]),
                       Group3_Coding_Suppl_Names = names(df[[5]]),
                       Group4_Coding_Names = names(df[[6]]),
                       Group5_Coding_Names = names(df[[7]]),
                       Group6_Coding_Names = names(df[[8]]),
                       Group7_Coding_Names = names(df[[9]])) 

check_row_equality1 <- function(row) {  
  all_equal <- all(row == row[1])  
  return(all_equal)  
}  
  
row_equalities1 <- apply(Coding_Data_Names, 1, check_row_equality1) 

### I found the names of 3,4,5, 19 cols are different and I modfication them.

colnames(df[[9]])[colnames(df[[9]]) == "First_author"] <- "First_Author"

colnames(df[[3]])[colnames(df[[3]]) == "Sample_Szie"] <- "Sample_Size"
colnames(df[[4]])[colnames(df[[4]]) == "Sample_Szie"] <- "Sample_Size"
colnames(df[[5]])[colnames(df[[5]]) == "Sample_Szie"] <- "Sample_Size"
colnames(df[[6]])[colnames(df[[6]]) == "Sample_Szie"] <- "Sample_Size"
colnames(df[[7]])[colnames(df[[7]]) == "Sample_Szie"] <- "Sample_Size"
colnames(df[[9]])[colnames(df[[9]]) == "Sample_Szie"] <- "Sample_Size"

rm(Coding_Data_Names,row_equalities1,check_row_equality1)

## Check the proofreading stage col names
Proofreading_Data_Names <- data.frame(Group1_Proofreading_Names = names(df[[10]]),
                                      Group2_Proofreading_Names = names(df[[11]]),
                                      Group3_Proofreading_Names = names(df[[12]]),
                                      Group4_Proofreading_Names = names(df[[13]]),
                                      Group5_Proofreading_Names = names(df[[14]]),
                                      Group6_Proofreading_Names = names(df[[15]]),
                                      Group7_Proofreading_Names = names(df[[16]]))

check_row_equality2 <- function(row) {  
  all_equal <- all(row == row[1])  
  return(all_equal)  
}  
  
row_equalities2 <- apply(Proofreading_Data_Names, 1, check_row_equality2) 

### I found the names of 8 cols are different and I modfication them.

colnames(df[[11]])[colnames(df[[11]]) == "target_population_N"] <- "Target_Population_N"

rm(Proofreading_Data_Names,row_equalities2,check_row_equality2)

```


### Combining the two stages' data (Group2,3,4,5,6, and 7)
```{r}
Group24567_1 <- dplyr::bind_rows(df[[3]],df[[6]],df[[7]],df[[8]],df[[9]]) %>% 
  dplyr::filter(Coder == "final") %>% 
  dplyr::select(-c(8,9,14:18,27,28,37,38))


Group24567_2 <- dplyr::bind_rows(df[[11]],df[[13]],df[[14]],df[[15]],df[[16]]) %>% 
  dplyr::filter(Coder == "final") %>%
  dplyr::rename_at(vars(1:4,7), ~paste0(., "_N"))

  
Group24567_bind <-  cbind(Group24567_1,Group24567_2) %>% 
  dplyr::select(1,30,2,31,8,32,11,33,3:7,9,10,12:29,34:48)


Group24567_bind_equal <- Group24567_bind %>%
  dplyr::select(3:8) %>% 
  dplyr::filter(!(Article_IDs == Article_IDs_N &
                    Study_Number == Study_Number_N &
                    Subjects_Group == Subjects_Group_N)) %>% 
  dplyr::mutate(Remark = ifelse(!(Article_IDs == Article_IDs_N), "Article_IDs", ifelse(!(Study_Number == Study_Number_N), "Study_Number", ifelse(!(Subjects_Group == Subjects_Group_N), "Subjects_Group", NA_character_))))

## The Articles_IDs, Study_Number, and Subject_Group of groups 2,4,5,6 and 7 are different in two coding stages (see Gourp24567_bind_equal) and now  we go back to the paper for modification.

Group24567_bind$Subjects_Group[125] <- Group24567_bind$Subjects_Group_N[125]

Group24567_bind$Subjects_Group[126] <- Group24567_bind$Subjects_Group_N[126]

Group24567_bind$Subjects_Group[127] <- Group24567_bind$Subjects_Group_N[127]
  
Group24567_bind$Subjects_Group[377] <- "传统识字教学组"
  
Group24567_bind$Subjects_Group[383] <- "健康对照组"

Group24567_bind$Subjects_Group[858] <- Group24567_bind$Subjects_Group_N[858]

Group24567_bind$Subjects_Group[859] <- Group24567_bind$Subjects_Group_N[859]

Group24567_bind$Subjects_Group[880] <- Group24567_bind$Subjects_Group_N[880]

Group24567_bind$Subjects_Group[881] <- Group24567_bind$Subjects_Group_N[881]

Group24567_bind$Subjects_Group[882] <- Group24567_bind$Subjects_Group_N[882]
  
Group24567_bind$Study_Number_N[975] <- 1
  
Group24567_bind$Study_Number_N[976] <- 2
  
Group24567_bind$Article_IDs[1057] <- 20181078
  
Group24567_bind$Subjects_Group_N[1076] <- "快乐经历"
  
Group24567_bind$Study_Number[1081] <- 0.1
  
Group24567_bind$Study_Number_N[1081] <- 0.1
  
Group24567_bind$Study_Number_N[1082] <- 0.2
  
Group24567_bind$Subjects_Group[1112] <- "控制组"
  
Group24567_bind$Study_Number_N[1176] <- 2

## run Group24567_bind_equal again and find this data.frame is not data available, thus we rm this data frame

rm(Group24567_bind_equal,Group24567_1,Group24567_2)

```


### Finding the distinct Ids in suppl documents
```{r }
Suppl_ID <- dplyr::bind_rows(df[[2]],df[[5]]) %>% 
  dplyr::filter(Coder == "final") %>%
  dplyr::distinct(Article_IDs)
```


### Loading the Group 1 data (include suppl)
```{r}
Group1_1 <- df[[1]] %>% 
  dplyr::filter(Coder == "final") %>% 
  dplyr::filter(!Article_IDs %in% Suppl_ID$Article_IDs) %>% 
  dplyr::select(-c(8,9,14:18,27,28,37,38))

Group1_suppl <- df[[2]] %>% 
  dplyr::filter(Coder == "final") %>% 
  dplyr::rename_at(vars(8,9,14:18,27,28,37,38), ~paste0(., "_N")) %>% 
  dplyr::mutate(Coder_N = NA, Article_IDs_N = NA, Study_Number_N = NA, 
                Subjects_Group_N = NA, Remark1_N = NA, Remark2_N = NA, 
                Remark3_N = NA, Coder2_N= NA) %>% 
  dplyr::mutate(Coder_N = Coder, Coder2_N = Coder,Article_IDs_N = Article_IDs,
                Study_Number_N = Study_Number, Subjects_Group_N = Subjects_Group, Remark1_N = Remark1,
                Remark2_N = Remark2, Remark3_N = Remark3)


Group1_2 <- df[[10]] %>% 
  dplyr::filter(Coder == "final") %>%
  dplyr::filter(!Article_IDs %in% Suppl_ID$Article_IDs) %>%
  dplyr::rename_at(vars(1:4,7), ~paste0(., "_N"))

Group1_bind <- cbind(Group1_1,Group1_2) %>%
  dplyr::select(1,30,2,31,8,32,11,33,3:7,9,10,12:29,34:48)

Group1_bind_equal <- Group1_bind %>%
  dplyr::select(3:8) %>% 
  dplyr::filter(!(Article_IDs == Article_IDs_N &
                    Study_Number == Study_Number_N &
                    Subjects_Group == Subjects_Group_N)) %>% 
  dplyr::mutate(Remark = ifelse(!(Article_IDs == Article_IDs_N), "Article_IDs", ifelse(!(Study_Number == Study_Number_N), "Study_Number", ifelse(!(Subjects_Group == Subjects_Group_N), "Subjects_Group", NA_character_))))

Group1_bind <- bind_rows(Group1_bind,Group1_suppl)

## The Articles_IDs, Study_Number, and Subject_Group are different in two coding stages (see Gourp1_bind_equal) and now  we go back to the paper for modification.

Group1_bind$Study_Number[170] <- Group1_bind$Study_Number_N[170]

Group1_bind$Study_Number[171] <- Group1_bind$Study_Number_N[171] 

Group1_bind$Study_Number[172] <- Group1_bind$Study_Number_N[172] 

Group1_bind$Study_Number[173] <- Group1_bind$Study_Number_N[173] 

## run Group1_bind_equal again and find this data.frame is not data available, thus we rm this data frame

rm(Group1_bind_equal,Group1_1,Group1_2,Group1_suppl)
``` 


### Loading the Group 3 data (include suppl)
```{r}
Group3_1 <- df[[4]] %>% 
  dplyr::filter(Coder == "final") %>% 
  dplyr::filter(!Article_IDs %in% Suppl_ID$Article_IDs) %>% 
  dplyr::select(-c(8,9,14:18,27,28,37,38))

# The coders in the First_Author and Journal columns because of the wrong order of column names, so the two columns of 1:41 data position is reversed, now swap the data back, in order to facilitate the subsequent data merge

Group3_1_Journal <- Group3_1[1:41,"Journal"]
Group3_1_First_Author <- Group3_1[1:41,"First_Author"]

Group3_1[1:41,"Journal"] <- Group3_1_First_Author
Group3_1[1:41,"First_Author"] <- Group3_1_Journal

Group3_1 <- Group3_1 %>% 
  dplyr::rename(First_Author = "Journal",Journal = "First_Author")

# continue sorting data
Group3_suppl <- df[[5]] %>% 
  dplyr::filter(Coder == "final") %>% 
  dplyr::rename_at(vars(8,9,14:18,27,28,37,38), ~paste0(., "_N")) %>% 
  dplyr::mutate(Coder_N = NA, Article_IDs_N = NA, Study_Number_N = NA, 
                Subjects_Group_N = NA, Remark1_N = NA, Remark2_N = NA, 
                Remark3_N = NA, Coder2_N= NA) %>% 
  dplyr::mutate(Coder_N = Coder, Coder2_N = Coder,Article_IDs_N = Article_IDs,
                Study_Number_N = Study_Number, Subjects_Group_N = Subjects_Group, Remark1_N = Remark1,
                Remark2_N = Remark2, Remark3_N = Remark3)


Group3_2 <- df[[12]] %>% 
  dplyr::filter(Coder == "final") %>%
  dplyr::filter(!Article_IDs %in% Suppl_ID$Article_IDs) %>%
  dplyr::rename_at(vars(1:4,7), ~paste0(., "_N"))

## two data frame have different rows, check and find that Articles_IDs 20213137 is uncode

Group3_1$Article_IDs[169] <- 20213137

Group3_1$Article_IDs[170] <- 20213137

Group3_1_20213137suppl <- data.frame(Coder = c("final","final"),
                                Article_IDs =c(20213137,20213137),
                                Article_Title =c("外显社会范畴加工与内隐社会范畴加工的年龄效应
","外显社会范畴加工与内隐社会范畴加工的年龄效应"),Journal = c("中国临床心理学杂志","中国临床心理学杂志"),
First_Author =c("王沛","王沛"),
Abstract1 =c(1,1),
Abstract2 =c(0,0),
Study_Number =c(2,2),
Remark1 =c(NA,NA),
Study_Type =c(1,1),
Subjects_Group =c("年轻被试","老年被试"),
Sample_Size =c(41,46),
Gender = c(1,1),
Male_Num =c(19,20),
Female_Num =c(22,26),
Age =c(1,1),
M_age =c(21,63),
SD_age=c(NA,NA),
Other_age =c("19-26","58-88"),
Ethnicity=c(0,0),
Ethnicity_info=c(NA,NA),
Religious=c(0,0),
Religious_info=c(NA,NA),
Subjects_Area =c(0,0),
Subjects_Area_info =c(NA,NA),
Subjects_Recruitment_Area =c(0,0),
Sampling_Method =c(0,0),
Remark2=c(NA,NA),
Remark3=c(NA,NA))

Group3_2_20213137suppl <- data.frame(Coder_N = c("final", "final","final","final"),
                                Article_IDs_N = c(20213137,20213137,20213137,20213137),
                                Study_Number_N = c(1,1,2,2),
                                Subjects_Group_N = c("年轻被试","老年被试","年轻被试","老年被试"),
                                Remark2_N = c(NA,NA,NA,NA),
                                Remark3_N = c(NA,NA,NA,NA),
                                Coder2_N = c("final","final","final","final"),
                                Target_Population_N =c(3,3,3,3),
                                Coding_Basis_N = c("本研究采用 Garner 选择性注意范式探究了认
知者年龄对内隐社会范畴加工和外显社会范畴加工的影响，以及内隐社会范畴加工与外显社会范畴加工之间的关系","本研究采用Garner选择性注意范式探究了认知者年龄对内隐社会范畴加工和外显社会范畴加工的影响，以及内隐社会范畴加工与外显社会范畴加工之间的关系","本研究采用Garner选择性注意范式探究了认知者年龄对内隐社会范畴加工和外显社会范畴加工的影响，以及内隐社会范畴加工与外显社会范畴加工之间的关系","本研究采用 Garner选择性注意范式探究了认知者年龄对内隐社会范畴加工和外显社会范畴加工的影响，以及内隐社会范畴加工与外显社会范畴加工之间的关系"),
                                Remark1_N = c(NA,NA,NA,NA),
                                Sample_Type_N = c(1,4,1,4),
                                Sample_Type_info_N =c ("其中年轻被试40人（男性18人，女性22人），均为大学生","老年被试35人（男性17人，女性 18 人），均来自某老年大学，年龄 58-88 岁，平均年龄64岁","其中年轻大学生被试 41 人（男性 19 人，女性 22 人），年龄 19-26岁，平均年龄21岁","老年被试46人（男性20人，女性26人），均来自某老年大学，年龄58-88岁，平均年龄63岁"),
                                Educational_Attainment_N =c(NA,0,NA,0),
                                Educational_Attainment_info_N =c(NA,NA,NA,NA),
                                Occupation_N = c(NA,0,NA,0),
                                SES_N =c(0,0,0,0),
                                SES_info_N =c(NA,NA,NA,NA),
                                Subjects_Recruitment_Method_N =c(1,1,1,1),
                                Subjects_Recruitment_Method_info_N =c(NA, NA,NA,NA))


Group3_1_20213137 <- Group3_1 %>% 
  dplyr::filter(Article_IDs == 20213137)

Group3_1 <- Group3_1 %>% 
  dplyr::filter(!(Article_IDs == 20213137))

Group3_1_20213137_bind <- rbind(Group3_1_20213137,Group3_1_20213137suppl)

Group3_1_20213137_bind <- cbind(Group3_1_20213137_bind,Group3_2_20213137suppl) %>% 
    dplyr::select(1,30,2,31,8,32,11,33,3:7,9,10,12:29,34:48)


Group3_bind <- cbind(Group3_1,Group3_2) %>%
  dplyr::select(1,30,2,31,8,32,11,33,3:7,9,10,12:29,34:48)


Group3_bind_equal <- Group3_bind %>%
  dplyr::select(3:8) %>% 
  dplyr::filter(!(Article_IDs == Article_IDs_N &
                    Study_Number == Study_Number_N &
                    Subjects_Group == Subjects_Group_N)) %>% 
  dplyr::mutate(Remark = ifelse(!(Article_IDs == Article_IDs_N), "Article_IDs", ifelse(!(Study_Number == Study_Number_N), "Study_Number", ifelse(!(Subjects_Group == Subjects_Group_N), "Subjects_Group", NA_character_))))


## The Articles_IDs, Study_Number, and Subject_Group are different in two coding stages (see Gourp1_bind_equal) and now  we go back to the paper for modification.

Group3_bind$Study_Number[27] <- 0

Group3_bind$Study_Number_N[131] <- 1

Group3_bind$Subjects_Group_N[130] <- "实验组"

Group3_bind$Subjects_Group_N[131] <- "控制组"

## Experiment 2 of Article_IDs 20184025 was not code, but experiment2 subjects was sames as experiment 1, therefore we  dont't recode it. 

Group3_1_20213137_bind[] <- lapply(Group3_1_20213137_bind,as.character)

Group3_suppl <- Group3_suppl %>% 
  dplyr::filter(!(Article_IDs == 20213137))

Group3_bind <- bind_rows(Group3_bind,Group3_suppl,Group3_1_20213137_bind)

rm(Group3_1,Group3_1_20213137,Group3_1_20213137_bind,Group3_1_20213137suppl,Group3_bind_equal,Group3_suppl,Group3_2,Group3_2_20213137suppl)

rm(Group3_1_Journal,Group3_1_First_Author)

```


### Combine the coding data and the proofreading data
```{r message=FALSE, warning=FALSE}

df_stage2_Journal_Code <- bind_rows(Group24567_bind,Group1_bind,Group3_bind)

### There are three articles that need to be replaced, and we will filter them out.
df_stage2_Journal_Code2 <- df_stage2_Journal_Code %>% 
  dplyr::filter(!Article_IDs %in% c(20084071,20182070,20185037))

```


## Check each code information and modification code information
### Coder(Coder2_N/Coder_N)

```{r message=FALSE, warning=FALSE}

any(is.na(df_stage2_Journal_Code2$Coder)) ### The code runs result is FALSE

any(is.na(df_stage2_Journal_Code2$Coder_N)) ### The code runs result is FALSE

any(is.na(df_stage2_Journal_Code2$Coder2_N)) ### The code runs result is TURE and further find NA rows
df_stage2_Journal_Code2$Article_IDs[is.na(df_stage2_Journal_Code2$Coder2_N)]

### The results of code run shows that 20211059, 20211061, 20213236, 20213239 is NA

df_stage2_Journal_Code2$Coder2_N[436] <- "final"
df_stage2_Journal_Code2$Coder2_N[437] <- "final"
df_stage2_Journal_Code2$Coder2_N[486] <- "final"
df_stage2_Journal_Code2$Coder2_N[487] <- "final"
```


### Article_IDs(Article_IDs_N)
```{r}
Article_IDs <-  df_stage2_Journal_Code2 %>% 
  dplyr::filter(is.na(Article_IDs))   ### The code runs results is 20083093 and 20181140

df_stage2_Journal_Code2$Article_IDs[62] <- 20083093
df_stage2_Journal_Code2$Article_IDs[73] <- 20181140


Article_IDs_N <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(is.na(Article_IDs_N))  ### The code runs results is no data

rm(Article_IDs,Article_IDs_N)
```


### Study_Number(Study_Number_N)
```{r}
Study_Number <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(is.na(Study_Number) | is.na(Study_Number_N))

### Article_IDs 20081127
df_stage2_Journal_Code2$Study_Number[28] <- 1
df_stage2_Journal_Code2$Study_Number_N[28] <- 1

### Article_IDs 20083093
df_stage2_Journal_Code2$Study_Number[62] <- 1
df_stage2_Journal_Code2$Study_Number_N[62] <- 1  ### 20083093 two coder codeed and completed "check", but they dont't complete "final"

### Article_IDs 20181140
df_stage2_Journal_Code2$Study_Number[73] <- 2  ### 20181140 same as 20083093

### Article_IDs 20181168
df_stage2_Journal_Code2$Study_Number_N[104] <- 0

### Article_IDs 20082054
df_stage2_Journal_Code2$Study_Number[246] <- 1
df_stage2_Journal_Code2$Study_Number_N[246] <- 1

### Article_IDs 20082069
df_stage2_Journal_Code2$Study_Number_N[254] <- 1

### Article_IDs 20082074
df_stage2_Journal_Code2$Study_Number[257:258] <- 1
df_stage2_Journal_Code2$Study_Number_N[257:258] <- 1

### Article_IDs 20082087
df_stage2_Journal_Code2$Study_Number_N[260] <- 1

### Article_IDs 20211046
df_stage2_Journal_Code2$Study_Number[432] <- 1
df_stage2_Journal_Code2$Study_Number_N[432] <- 1

### Article_IDs 20212097
df_stage2_Journal_Code2$Study_Number[928] <- 0
df_stage2_Journal_Code2$Study_Number[929] <- 0.1

### Article_IDs 20182192
df_stage2_Journal_Code2$Study_Number[1087] <- 1

### Article_IDs 20182193
df_stage2_Journal_Code2$Study_Number[1088] <- 1
df_stage2_Journal_Code2$Study_Number_N[1088] <- 1

### Article_IDs 20212172
df_stage2_Journal_Code2$Study_Number[1179] <- 1
df_stage2_Journal_Code2$Study_Number_N[1179] <- 1 

### Article_IDs 20083017
df_stage2_Journal_Code2$Study_Number_N[1298] <- 1

### Article_IDs 20183268
df_stage2_Journal_Code2$Study_Number[1393] <- 1
df_stage2_Journal_Code2$Study_Number_N[1393] <- 1 

### Article_IDs 20213023
df_stage2_Journal_Code2$Study_Number[1437] <- 1

### Article_IDs 20213039
df_stage2_Journal_Code2$Study_Number[1443] <- 1

### Article_IDs 20082013
df_stage2_Journal_Code2$Study_Number[1473] <- 1

### Artilce_IDs 20082029
df_stage2_Journal_Code2$Study_Number[1485] <- 1

rm(Study_Number)
```


### Subjects_Group
```{r}
Subjects_Group <- df_stage2_Journal_Code2 %>% 
  dplyr::filter((!is.na(Subjects_Group) & !is.na(Subjects_Group_N) & Subjects_Group != Subjects_Group_N) |
                  (is.na(Subjects_Group) & !is.na(Subjects_Group_N)) |
                  (!is.na(Subjects_Group) & is.na(Subjects_Group_N))) 


### Article_IDs 20083042
df_stage2_Journal_Code2$Subjects_Group[42] <- NA
df_stage2_Journal_Code2$Subjects_Group_N[42] <- NA

### Article_IDs 20181148
df_stage2_Journal_Code2$Subjects_Group[91] <- NA

### Article_IDs 20181162
df_stage2_Journal_Code2$Subjects_Group[98] <- NA

### Article_IDs 20181187
df_stage2_Journal_Code2$Subjects_Group_N[121] <- "积极怀旧组"
df_stage2_Journal_Code2$Subjects_Group_N[122] <- "主题怀旧组"

### Article_IDs 20182268
df_stage2_Journal_Code2$Subjects_Group_N[140:148] <- df_stage2_Journal_Code2$Subjects_Group[140:148]

### Article_IDs 20182019
df_stage2_Journal_Code2$Subjects_Group[339:341] <- df_stage2_Journal_Code2$Subjects_Group_N[339:341]

### Article_IDs 20182031
df_stage2_Journal_Code2$Subjects_Group[358:359] <- df_stage2_Journal_Code2$Subjects_Group_N[358:359]

### Article_IDs 20183071
df_stage2_Journal_Code2$Subjects_Group[369:370] <- df_stage2_Journal_Code2$Subjects_Group_N[369:370]

### Article_IDs 20182035
df_stage2_Journal_Code2$Subjects_Group_N[554] <- "海洛因戒断者组"

### Article_IDs 20082210
### Redundant Subjects Group
df_stage2_Journal_Code2$Subjects_Group[699:701] <- NA

### Article_IDs 20181023
df_stage2_Journal_Code2$Subjects_Group_N[788:791] <- df_stage2_Journal_Code2$Subjects_Group[788:791]

### Article_IDs 20182126
### Redundant Subjects Group
df_stage2_Journal_Code2$Subjects_Group[830:831] <- NA

### Article_IDs 20182131
df_stage2_Journal_Code2$Subjects_Group_N[832:833] <- df_stage2_Journal_Code2$Subjects_Group[832:833] 

### Article_IDs 20182174
df_stage2_Journal_Code2$Subjects_Group_N[1076] <- NA

### Article_IDs 20182192
df_stage2_Journal_Code2$Subjects_Group_N[1087] <- NA

### Article_IDs 20083017
df_stage2_Journal_Code2$Subjects_Group_N[1298:1299] <- df_stage2_Journal_Code2$Subjects_Group[1298:1299]

rm(Subjects_Group)

df_stage2_Journal_Code2 <- df_stage2_Journal_Code2 %>% 
  dplyr::mutate(Subjects_Group = if_else(Subjects_Group == 1, NA, Subjects_Group),
                Subjects_Group_N = if_else(Subjects_Group_N == 1, NA, Subjects_Group_N))
```


### Article_Title
```{r}
Article_Title <-  df_stage2_Journal_Code2 %>%
  dplyr::filter(is.na(Article_Title))

### Article_IDs 20083093
df_stage2_Journal_Code2$Article_Title[62] <-  "抑郁与自尊水平、自我效能感的关系研究"

### Article_IDs 20181140
df_stage2_Journal_Code2$Article_IDs[73] <- 20181140
df_stage2_Journal_Code2$Article_Title[73] <- "比例推理的过度使用及其认知机制：一项发展性的负启动研究"
## I found 20181140 had some coding info uncode

## Article_IDs 20085035
df_stage2_Journal_Code2$Article_Title[747] <- "《适应分量表》在蒙古族青少年群体中使用的信、效度检验"
 
### Article_IDs 20183171
df_stage2_Journal_Code2$Article_Title[867:868] <- "母亲消极完美主义与女儿内化问题：一个多重中介模型"
 
### Article_IDs 20183182
df_stage2_Journal_Code2$Article_Title[870:872] <- "父亲婚姻满意度与幼儿社会适应：父亲反应方式的中介作用"
 
### Article_IDs 20183188
df_stage2_Journal_Code2$Article_Title[873] <- "非营利机构员工相对剥夺感对情绪耗竭的影响：心理契约违背的中介作用"
 
### Article_IDs 20183052
df_stage2_Journal_Code2$Article_Title[1571] <- "学生同伴依恋与抑郁：自我认同感和宿舍人际关系的中介作用"

### Article_IDs 20183054
df_stage2_Journal_Code2$Article_Title[1572] <- "父母心理控制、自主支持与青少年外化问题行为：控制动机的中介作用"

### Article_IDs 20184022
df_stage2_Journal_Code2$Article_Title[1587:1592] <- "幼儿的自我投射能力对情景预见的影响：来自典型发展儿童和孤独症谱系障碍儿童的证据"

### Article_IDs 20211015
df_stage2_Journal_Code2$Article_Title[1671:1672] <- "如何激发员工绿色行为？绿色变革型领导与绿色人力资源管理实践的作用"

rm(Article_Title)
```


### First_Author and Journal
```{r}
First_Author_Journal <-  df_stage2_Journal_Code2 %>% 
  dplyr::filter(is.na(First_Author) | is.na(Journal)) %>% 
  dplyr::select(3,4,10,11)

### Article_IDs 20083093
df_stage2_Journal_Code2$First_Author[62] <- "戴琴"
df_stage2_Journal_Code2$Journal[62] <- "中国临床心理学杂志"

### Article_IDs 20181140
df_stage2_Journal_Code2$First_Author[73] <- "江荣焕"
df_stage2_Journal_Code2$Journal[73] <-  "心理学报"

### Article_IDs 20185166
df_stage2_Journal_Code2$First_Author[208] <- "张林" 

### Article_IDs 20215077
df_stage2_Journal_Code2$First_Author[241] <- "张昕"

### Article_IDs 20215078
df_stage2_Journal_Code2$First_Author[242] <- "张野"

### Article_IDs 20081048
df_stage2_Journal_Code2$First_Author[1273] <- "冯冬冬"
df_stage2_Journal_Code2$Journal[1273] <- "心理学报"

### Article_IDs 20082379
df_stage2_Journal_Code2$First_Author[1292] <- "安秋玲" 
df_stage2_Journal_Code2$Journal[1292] <- "心理科学"

### Article_IDS 20184027
df_stage2_Journal_Code2$First_Author[1669:1670] <- "童钰" 
df_stage2_Journal_Code2$Journal[1669:1670] <- "心理发展与教育"

### Article_IDs 20213153
df_stage2_Journal_Code2$First_Author[1678] <- "王鸿飞"
df_stage2_Journal_Code2$Journal[1678] <- "中国临床心理学杂志"

rm(First_Author_Journal)
```


### Remark
```{r}
Remark1 <- df_stage2_Journal_Code2 %>% 
  dplyr::select(3,14,39) %>% 
  dplyr::filter(if_any(c(Remark1, Remark1_N), ~!is.na(.) & nzchar(.)))


### Article_IDs 20214072
df_stage2_Journal_Code2$Remark1[976] <- "secondary"

### Article_IDs 20182193
df_stage2_Journal_Code2$Remark1_N[1088] <- "mining"

### Article_ID 20213088
df_stage2_Journal_Code2$Remark1_N[224] <- "qualitative"

### Article_IDs 20182192
df_stage2_Journal_Code2$Remark1_N[1087] <- "qualitative"

### Article_IDs 20082029
df_stage2_Journal_Code2$Remark1_N[1485] <- "qualitative"

### Article_IDs 20181168
#df_stage2_Journal_Code2$Remark1[104] <- "mining"
#df_stage2_Journal_Code2$Remark1_N[104] <- "mining"
#df_stage2_Journal_Code2$Remark1_N[105:106] <- NA

### Article_IDs 20082013
df_stage2_Journal_Code2$Remark1_N[1473] <- "secondary"

### Articel_IDs 20213305
df_stage2_Journal_Code2$Remark1[683] <- "inapplicable"
df_stage2_Journal_Code2$Remark1_N[683] <- "inapplicable"

### Article_IDs 20081055
df_stage2_Journal_Code2$Remark1[1278:1279] <- "inapplicable"
df_stage2_Journal_Code2$Remark1_N[1278:1279] <- "inapplicable"

### Article_IDs 20181039
df_stage2_Journal_Code2$Remark1[1025] <- "secondary"

### Article_IDs 20182257
df_stage2_Journal_Code2$Remark1[130] <- "secondary"
df_stage2_Journal_Code2$Remark1_N[130] <- "secondary"
df_stage2_Journal_Code2$Remark2[130] <- "与20182255被试重复"
df_stage2_Journal_Code2$Remark2_N[130] <- "与20182255被试重复"

### Article_IDs 20182271
df_stage2_Journal_Code2$Remark1[150] <- "secondary"

### Article_IDs 20182283
df_stage2_Journal_Code2$Remark1[155:156] <- "secondary"

### Article_IDs 20182028
df_stage2_Journal_Code2$Remark1[355] <- "non_human"
df_stage2_Journal_Code2$Remark1_N[355] <- "non_human"

### Article_IDs 20082165
df_stage2_Journal_Code2$Remark1[503] <- "inapplicable"
df_stage2_Journal_Code2$Remark1_N[503] <- "inapplicable"

### Article_IDs 20212013
df_stage2_Journal_Code2$Remark1[643] <- "inapplicable"
df_stage2_Journal_Code2$Remark1_N[643] <- "inapplicable"

### Article_IDs 20085023
df_stage2_Journal_Code2$Remark1[742] <- "secondary"

### Article_IDs 20213023
df_stage2_Journal_Code2$Remark1[1437] <- "mining"

### Article_IDs 20183360
df_stage2_Journal_Code2$Remark1[1574] <- "secondary"

### Article_IDs 20184019
df_stage2_Journal_Code2$Remark1[1586] <- "secondary" 

rm(Remark1)

Remark2 <- df_stage2_Journal_Code2 %>% 
  dplyr::select(3,32,34) %>%
  dplyr::filter(grepl("重复",Remark2)| grepl("重复",Remark2_N))

### Article_IDs 20081104
df_stage2_Journal_Code2$Remark2_N[21] <- "被试重复使用"

### Article_IDs 20081132
df_stage2_Journal_Code2$Remark2_N[30:31] <- "被试重复使用"

### Article_IDs 20083038
df_stage2_Journal_Code2$Remark2[38:39] <- "被试重复使用"
df_stage2_Journal_Code2$Remark2_N[38:39] <- "被试重复使用"

### Article_IDs 20083085
df_stage2_Journal_Code2$Remark2_N[60] <- "被试重复使用"

### Article_IDs 20213104
df_stage2_Journal_Code2$Remark2_N[231] <- "被试重复使用"
df_stage2_Journal_Code2$Remark3_N[231] <- "样本3重复使用样本2为重测"

### Article_IDs 20182030
df_stage2_Journal_Code2$Remark2_N[357] <- "被试重复使用"

### Article_IDs 20184042
df_stage2_Journal_Code2$Remark2_N[388] <- "被试重复使用"

### Article_IDs 20181022
df_stage2_Journal_Code2$Remark2[782:783] <- NA
df_stage2_Journal_Code2$Remark2[784:785] <- "被试重复使用"

### Article_IDs 20185003
df_stage2_Journal_Code2$Remark2_N[897] <- NA
df_stage2_Journal_Code2$Remark2[898] <- "被试重复使用"

rm(Remark2)

```


### Abstract1
```{r}
Abstract1 <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(is.na(Abstract1) & (is.na(Remark1) | Remark1 == "")) %>%
  dplyr::filter(is.na(Remark1_N)) %>% 
  dplyr::select(3,12,14)

### Article_IDs 20081070
df_stage2_Journal_Code2$Abstract1[6:7] <- 0

### Article_IDs 20081073
df_stage2_Journal_Code2$Abstract1[10] <- 0

### Article_IDs 20081127
df_stage2_Journal_Code2$Abstract1[28] <- "1b"

### Article_IDs 20081132
df_stage2_Journal_Code2$Abstract1[30:31] <- 123 

### Article_IDs 20081134
df_stage2_Journal_Code2$Abstract1[33] <- 1234

### Article_IDs 20083038
df_stage2_Journal_Code2$Abstract1[38:39] <- 14

### Article_IDs 20083039
df_stage2_Journal_Code2$Abstract1[41] <- 134

### Article_IDs 20083052
df_stage2_Journal_Code2$Abstract1[44] <- 0

### Article_IDs 20083067
df_stage2_Journal_Code2$Abstract1[51] <- 134

### Article_IDs 20181140
df_stage2_Journal_Code2$Abstract1[73] <- 123

### Article_IDs 20183334
df_stage2_Journal_Code2$Abstract1[183] <- 14

### Article_IDs 20182035 
df_stage2_Journal_Code2$Abstract1[555] <- 1

### Article_IDs 20085035
df_stage2_Journal_Code2$Abstract1[747] <-  "12348b"

### Article_IDs 20085044
df_stage2_Journal_Code2$Abstract1[752:754] <- "1234b"

### Article_IDs 20181017
df_stage2_Journal_Code2$Abstract1[773:776] <- 0

### Article_IDs 20181022
df_stage2_Journal_Code2$Abstract1[782:787] <- 8

### Article_IDs 20181023
df_stage2_Journal_Code2$Abstract1[788:793] <- 1238

### Article_IDs 20182075
df_stage2_Journal_Code2$Abstract1[794] <- 123

### Article_IDs 20182103
df_stage2_Journal_Code2$Abstract1[805:810] <- 123

### Article_IDs 20182125
df_stage2_Journal_Code2$Abstract1[825:829] <- 12345
 
rm(Abstract1)

```


### Abstract2
```{r message=FALSE, warning=FALSE}
Abstract2 <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(Sample_Type_N == c(1,5) & (is.na(Abstract2) | Abstract2 == "")) %>% 
  dplyr::select(3,40,13,14,39,41) %>% 
  dplyr::arrange(Sample_Type_N)

### Article_IDs 20081070
df_stage2_Journal_Code2$Abstract2[6:7] <- 0

### Article_IDs 20081132
df_stage2_Journal_Code2$Abstract2[30:31] <- 1

### Article_IDs 20181140
df_stage2_Journal_Code2$Abstract2[73] <- 1

### Article_IDs 20083204
df_stage2_Journal_Code2$Abstract2[284:286] <- 1

### Article_IDs 20181005
df_stage2_Journal_Code2$Abstract2[759:764] <- 0
  
### Article_IDs 20182103
df_stage2_Journal_Code2$Abstract2[805:810] <- 1

### Article_IDs 20082313
df_stage2_Journal_Code2$Abstract2[987:988] <- 0  

### Article_IDs 20082343
df_stage2_Journal_Code2$Abstract2[1000:1001] <- 0  

### Article_IDs 20082346
df_stage2_Journal_Code2$Abstract2[1003] <- 0 

### Article_IDs 20181028
df_stage2_Journal_Code2$Abstract2[1015:1018] <- 0

### Article_IDs 20181034
df_stage2_Journal_Code2$Abstract2[1021:1022] <- 0

### Article_IDs 20181037
df_stage2_Journal_Code2$Abstract2[1023:1024] <- 0

### Article_IDs 20181044
df_stage2_Journal_Code2$Abstract2[1027] <- 0

### Article_IDs 20181051
df_stage2_Journal_Code2$Abstract2[1028:1030] <- 0

### Article_IDs 20181052
df_stage2_Journal_Code2$Abstract2[1031:1032] <- 0

### Article_IDs 20181058
df_stage2_Journal_Code2$Abstract2[1033:1034] <- 0

### Article_IDs 20181061
df_stage2_Journal_Code2$Abstract2[1035:1037] <- 0

### Article_IDs 20181063
df_stage2_Journal_Code2$Abstract2[1038:1039] <- 0

### Article_IDs 20181065
df_stage2_Journal_Code2$Abstract2[1040:1043] <- 0

### Article_IDs 20181066
df_stage2_Journal_Code2$Abstract2[1044:1045] <- 0

### Article_IDs 20181073
df_stage2_Journal_Code2$Abstract2[1047:1050] <- 0

### Article_IDs 20181075
df_stage2_Journal_Code2$Abstract2[1051:1054] <- 0

### Article_IDs 20181078
df_stage2_Journal_Code2$Abstract2[1055] <- 0

### Article_IDs 20182164
df_stage2_Journal_Code2$Abstract2[1060:1063] <- 0

### Article_IDs 20182165
df_stage2_Journal_Code2$Abstract2[1064:1065] <- 0

### Article_IDs 20182168
df_stage2_Journal_Code2$Abstract2[1067:1075] <- 0

### Article_IDs 20182183
df_stage2_Journal_Code2$Abstract2[1082:1083] <- 0

### Article_IDs 20183231
df_stage2_Journal_Code2$Abstract2[1111] <- 1

### Article_IDs 20185058
df_stage2_Journal_Code2$Abstract2[1146:1147] <- 0

### Article_IDs 20185076
df_stage2_Journal_Code2$Abstract2[1157] <- 0

### Article_IDs 20212166
df_stage2_Journal_Code2$Abstract2[1174:1177] <- 0

### Article_IDs 20212175
df_stage2_Journal_Code2$Abstract2[1182:1183] <- 0

### Article_IDs 20212188
df_stage2_Journal_Code2$Abstract2[1187:1190] <- 0

### Article_IDs 20214085
df_stage2_Journal_Code2$Abstract2[1199:1200] <- 0

### Article_IDs 20215006
df_stage2_Journal_Code2$Abstract2[1203:1204] <- 0

### Article_IDs 20215007
df_stage2_Journal_Code2$Abstract2[1205:1206] <- 0

### Article_IDs 20215017
df_stage2_Journal_Code2$Abstract2[1210:1211] <- 0

### Article_IDs 20215023
df_stage2_Journal_Code2$Abstract2[1212:1214] <- 0

### Article_IDs 20215068
df_stage2_Journal_Code2$Abstract2[1232:1234] <- 0

### Article_IDs 20213155
df_stage2_Journal_Code2$Abstract2[1638:1639] <- 1

### Article_IDs 20213167
df_stage2_Journal_Code2$Abstract2[1643] <- 1


### Sample_Type is 5
### Article_IDs 20211064
df_stage2_Journal_Code2$Abstract2[447:452] <- 0

### Article_IDs 20213254
df_stage2_Journal_Code2$Abstract2[493:494] <- 1

### Article_IDs 20082188
df_stage2_Journal_Code2$Abstract2[515:516] <- 0

### Article_IDs 20213040
df_stage2_Journal_Code2$Abstract2[1444] <- 0

rm(Abstract2)
```


### Sample_Size
```{r}
Sample_Size <- df_stage2_Journal_Code2 %>% 
  dplyr::select(3,14,39,16,32,34) %>% 
  dplyr::filter(is.na(Sample_Size)) %>% 
  dplyr::filter(is.na(Remark1)) %>% 
  dplyr::filter(!grepl("重复",Remark2))

### Article_IDs 20083093
df_stage2_Journal_Code2$Sample_Size[62] <- 175

### Article_IDs 20181140
df_stage2_Journal_Code2$Sample_Size[73] <- 43

### Article_IDs 20182022
df_stage2_Journal_Code2$Remark2[354] <- "被试重复使用"
df_stage2_Journal_Code2$Remark2_N[354] <- "被试重复使用"

### Article_IDs 20182262
df_stage2_Journal_Code2$Sample_Size[724] <- 60

### Article_IDs 20082283
df_stage2_Journal_Code2$Sample_Size[732] <- 426

### Article_IDs 20085044
df_stage2_Journal_Code2$Sample_Size[753] <- 33
#Meanwhile, I found this article' subjects group was uncode.
#df_stage2_Journal_Code2$Subjects_Group[752:754] <- c("3岁组","4岁组","5岁组")
#df_stage2_Journal_Code2$Subjects_Group_N[752:754] <- c("3岁组","4岁组","5岁组")

### Article_IDs 20182101
df_stage2_Journal_Code2$Sample_Size[801] <- 29
df_stage2_Journal_Code2$Female_Num[801] <- 12

### Article_IDs 20182103
df_stage2_Journal_Code2$Sample_Size[807] <- 124
##### row808 isn't need
df_stage2_Journal_Code2$Sample_Size[812] <- 180

df_stage2_Journal_Code2$Sample_Size[811] <- 30
df_stage2_Journal_Code2$Female_Num[811] <- 17
df_stage2_Journal_Code2$Male_Num[811] <- 13
### Meanwhile, I found this article' Study3 should code "inapplicable" in Remark1( Remark1_N).
#df_stage2_Journal_Code2$Remark1[811] <- "inapplicable"
#df_stage2_Journal_Code2$Remark1_N[811] <- "inapplicable"

### Article_IDs 20081026
df_stage2_Journal_Code2$Sample_Size[1251] <- 284

### Article_IDs 20082009
df_stage2_Journal_Code2$Sample_Size[1471] <- 30
#meanwhile, I found names error of study number
df_stage2_Journal_Code2$Study_Number[1468:1471] <- c("1a","1b","2a","2b")
df_stage2_Journal_Code2$Study_Number_N[1468:1471] <- c("1a","1b","2a","2b")

rm(Sample_Size)
```


### Gender, Male_Num and Female_Num
```{r}
Gender <- df_stage2_Journal_Code2 %>% 
  dplyr::select(3,14,39,17,32,34) %>% 
  dplyr::filter(is.na(Gender)) %>% 
  dplyr::filter(is.na(Remark1)) %>% 
  dplyr::filter(!grepl("重复",Remark2))

### Article_IDs 20083093
df_stage2_Journal_Code2$Gender[62] <- 1
df_stage2_Journal_Code2$Male_Num[62] <- 55
df_stage2_Journal_Code2$Female_Num[62] <- 120

### Article_IDs 20181140
df_stage2_Journal_Code2$Gender[73] <- 1
df_stage2_Journal_Code2$Male_Num[73] <- 23
df_stage2_Journal_Code2$Female_Num[73] <- 20

rm(Gender)

Male_Female <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(Gender == 1 & (is.na(Male_Num) | is.na(Female_Num))) %>% 
  dplyr::select(3,16:19)


### Article_IDs 20184052
df_stage2_Journal_Code2$Female_Num[398] <- 1-0.571


### Article_IDs 20211034
df_stage2_Journal_Code2$Female_Num[423] <- 1-0.55


### Article_IDs 20211040
df_stage2_Journal_Code2$Male_Num[426] <- 210-117


### Article_IDs 20082283
df_stage2_Journal_Code2$Male_Num[732] <- 426
df_stage2_Journal_Code2$Female_Num[732] <- NA


### Article_IDs 20181007
df_stage2_Journal_Code2$Male_Num[765] <- 13
df_stage2_Journal_Code2$Female_Num[765] <- 12


### Article_IDs 20182103
df_stage2_Journal_Code2$Male_Num[809:810] <- NA
df_stage2_Journal_Code2$Male_Num[812] <- 180-86
df_stage2_Journal_Code2$Female_Num[812] <- 86

rm(Male_Female)
```


### Age, M_age, SD_age and Other_age
```{r}
Age <- df_stage2_Journal_Code2 %>% 
  dplyr::select(3,14,39,20,32,34) %>% 
  dplyr::filter(is.na(Age)) %>% 
  dplyr::filter(is.na(Remark1)) %>% 
  dplyr::filter(!grepl("重复",Remark2))
  
### Article_IDs 20083038
df_stage2_Journal_Code2$Age[37] <- 1

### Article_IDs 20083093
df_stage2_Journal_Code2$Age[62] <- 1
df_stage2_Journal_Code2$M_age[62] <- 26.02

### Article_IDs 20181140
df_stage2_Journal_Code2$Age[73] <- 1
df_stage2_Journal_Code2$M_age[73] <- 21.72
df_stage2_Journal_Code2$SD_age[73] <- 2.3

### Article_IDs 20182248
df_stage2_Journal_Code2$Age[126:127] <- 1

### Article_IDs 20185187
df_stage2_Journal_Code2$Age[215] <-  0

rm(Age)

Age_info <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(Age == 1) %>% 
  dplyr::filter(is.na(M_age) | is.na(SD_age)) %>% 
  dplyr::select(3,20:23,14,32,34,39)


### Article_IDs 20081134
df_stage2_Journal_Code2$M_age[33] <- 10.03

### Article_IDs 20181150
### I found 3 experiment in 20181150 and coder only code experiment 3.
df_stage2_Journal_Code2$Study_Number[93] <- 3
df_stage2_Journal_Code2$Study_Number_N[93] <- 3

### Article_IDs 20181162 
df_stage2_Journal_Code2$Other_age[100] <- "年龄集中在18-25岁"

### Article_IDs 20182267
df_stage2_Journal_Code2$SD_age[139] <- 1.64

### Articles_IDs 20182279
df_stage2_Journal_Code2$Other_age[153] <- "35-40为主(42.5%)"
df_stage2_Journal_Code2$Other_age[154] <- "25-30为主(45.9%)"

### Article_IDs 20183336
df_stage2_Journal_Code2$SD_age[184] <- 0.591

### Article_IDs 20183340
df_stage2_Journal_Code2$Other_age[186] <- "11岁60人，12岁140人，13岁189人，14岁146人，15岁101人，16岁62人"

### Article_IDs 20082069
df_stage2_Journal_Code2$Other_age[253] <- "10.3-13.5"
df_stage2_Journal_Code2$Other_age[254] <- "10.6-13.0"

### Article_IDs 20083204
df_stage2_Journal_Code2$Other_age[285:286] <- c("17-25","17-25")

### Article_IDs 20084031
df_stage2_Journal_Code2$M_age[313] <- 12.3

### Article_IDs 20182003
df_stage2_Journal_Code2$M_age[323] <- "男生8人（M=21.63），女生9人（M=21.89）"
df_stage2_Journal_Code2$SD_age[323] <- "男生8人（SD=1.32），女生9人（SD=1.17）"

### 20084045
df_stage2_Journal_Code2$Other_age[522:523] <- NA

### Article_IDs 20082281
df_stage2_Journal_Code2$Other_age[731] <- "19-23"

### Article_IDs 20082285
df_stage2_Journal_Code2$Other_age[733:734] <- "18-22"

### Article_IDs 20181020
### Redundant Group
df_stage2_Journal_Code2$M_age[779:779] <- 20.2
df_stage2_Journal_Code2$SD_age[779:779] <- 2.17

#### Article_IDs 20181023 
### Redundant Group

#### Article_IDs 20182133
### Redundant Group

### Article_IDs 20183192
### Redundant Group

### Article_IDs 20184162
df_stage2_Journal_Code2$Other_age[893] <- "参与作答的父母中父亲1047人，母亲1139人(其中继母或养母2人)，父母年龄在27.25～62.83岁之间，其中父亲平均年龄为41.44岁，母亲平均年龄为40.23岁"

### Article_IDs 20212091
df_stage2_Journal_Code2$M_age[927] <- 20.59
df_stage2_Journal_Code2$Other_age[927] <- "17-26"

### Article_IDs 20214070
df_stage2_Journal_Code2$M_age[975] <- 13.41
df_stage2_Journal_Code2$SD_age[975] <- 0.62

### Article_IDs 20214073
df_stage2_Journal_Code2$M_age[977] <- 13.69
df_stage2_Journal_Code2$SD_age[977] <- 1.42

### 20185038 
df_stage2_Journal_Code2$Other_age[1126] <- "年龄16–29岁439人，30–44岁153人，45–60岁27人，年龄资料缺失4人"

### Article_IDs 20181022
df_stage2_Journal_Code2$Other_age[1247] <- "13岁以下占28.9%，14到16岁占46.2%;17岁以上占24.9%"

### Article_IDs 20081026
df_stage2_Journal_Code2$M_age[1251] <- 20.20
df_stage2_Journal_Code2$SD_age[1251] <- 0.81
df_stage2_Journal_Code2$Other_age[1251] <- "18-24"

### Article_IDs 20082374
df_stage2_Journal_Code2$Age[1290] <- 1
df_stage2_Journal_Code2$Other_age[1290] <- "20-23"
df_stage2_Journal_Code2$Subjects_Recruitment_Area[1290] <- "福建"

### Article_IDs 20083017
df_stage2_Journal_Code2$Other_age[1298] <- "男女及各年级人数基本相等, 学生年龄为16-18岁"
df_stage2_Journal_Code2$Other_age[1299] <- " 高一学生64人,高二学生65人,高三学生53人,平均年龄分别为16.2、17.1和18.2岁"

### Article_IDs 20183018
df_stage2_Journal_Code2$Other_age[1300] <- "19-25"

### Article_IDs 20181091
df_stage2_Journal_Code2$Other_age[1311] <- "18-25"

### Article_IDs 20181133
df_stage2_Journal_Code2$Other_age[1352] <- "20-25"

### Article_IDs 20181139
df_stage2_Journal_Code2$Other_age[1359] <- "18-22"
df_stage2_Journal_Code2$Other_age[1360] <- "18-22"

### Article_IDs 20182207
df_stage2_Journal_Code2$SD_age[1364] <- "男性:6.56;女性:5.04"

### Article_IDs 20182228
df_stage2_Journal_Code2$M_age[1371] <-  "男性:10.01;女性:9.95"
df_stage2_Journal_Code2$SD_age[1371] <-  "男性:1.31;女性:1.38"

### Article_IDs 20182231
df_stage2_Journal_Code2$Other_age[1374] <- "年龄以25~30岁为主（38.6%）"

### Article_IDs 20183257
df_stage2_Journal_Code2$Other_age[1384] <- "21岁以下(2人)21~30岁(6人)31~40岁(13人)40岁以上(4人)"
df_stage2_Journal_Code2$Other_age[1385] <- "21岁以下(3人);21~30岁(9人);31~40岁(11人);40岁以上(2人)"

### Article_IDs 20213067
df_stage2_Journal_Code2$Other_age[1457] <- "年龄段：10~17岁10人，18~39岁355人，40~59岁159人，60~79岁21人"

### Article_IDs 20083173
df_stage2_Journal_Code2$Other_age[1514] <- "18-29岁:50人;30-39岁:18人;40岁以上:8人"

### Article_IDs 20181210
df_stage2_Journal_Code2$Other_age[1530] <- "按照年龄划分,25岁以下占18%,25~35岁占56.5,35~45岁占20.6%, 45岁以上占4.9%"
df_stage2_Journal_Code2$Other_age[1531] <- "按照年龄划分,35岁以下占40.9%,35~45岁占37.2%,45岁以上占21.9%"

### Article_IDs 20181213
df_stage2_Journal_Code2$Other_age[1535] <- "90.3%年龄介于 21~40 岁之间"
df_stage2_Journal_Code2$Other_age[1536] <- "21~40 岁占 95.7%"

### Article_IDs 20183042
df_stage2_Journal_Code2$Other_age[1568] <- "18-23"

### Article_IDs 20185084
df_stage2_Journal_Code2$Other_age[1658] <- "17-26"

### Article_IDs 20215085
df_stage2_Journal_Code2$Other_age[1659] <- "18-24"
df_stage2_Journal_Code2$Other_age[1660] <- "17-26"

### Article_IDs 20213137
df_stage2_Journal_Code2$Other_age[1682] <- "19-26"
df_stage2_Journal_Code2$Other_age[1683] <- "58-88"

rm(Age_info)
```


### Ethnicity and info
```{r}
Ethnicity <- df_stage2_Journal_Code2 %>% 
  dplyr::select(3,14,39,24,32,34) %>% 
  dplyr::filter(is.na(Ethnicity)) %>% 
  dplyr::filter(is.na(Remark1)) %>% 
  dplyr::filter(!grepl("重复",Remark2))

### Article_IDs 20083093
df_stage2_Journal_Code2$Ethnicity[62] <- 0

### Article_IDs 20181140
df_stage2_Journal_Code2$Ethnicity[73] <- 0

### Article_IDs 20185191
df_stage2_Journal_Code2$Ethnicity[218] <- 0

### Article_IDs 20181017
df_stage2_Journal_Code2$Ethnicity[775:776] <- 0

rm(Ethnicity)


Ethnicity_info <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(Ethnicity == 1 & is.na(Ethnicity)) %>% 
  dplyr::select(3,25,14,32,34,39)

rm(Ethnicity_info)
```


### Religious and info
```{r}
Religious <- df_stage2_Journal_Code2 %>% 
  dplyr::select(3,14,39,26,32,34) %>% 
  dplyr::filter(is.na(Religious)) %>% 
  dplyr::filter(is.na(Remark1)) %>% 
  dplyr::filter(!grepl("重复", Remark2))

### Article_IDs 20083093
df_stage2_Journal_Code2$Religious[62] <- 0

### Article_IDs 20181140
df_stage2_Journal_Code2$Religious[73] <- 0

### Article_IDs 20181081
df_stage2_Journal_Code2$Religious[1056] <- 0

### Article_IDs 20183229
df_stage2_Journal_Code2$Religious[1109] <- 0

### Article_IDs 20213029
df_stage2_Journal_Code2$Religious[1440] <- 0

rm(Religious)


Religious_info <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(Religious == 1 & is.na(Religious_info)) %>% 
  dplyr::select(3,27,14,32,34,39)

### In check process, 20182168' Religious_info need recode.
df_stage2_Journal_Code2$Religious_info[1067:1068] <- "4(无宗教信仰)"

rm(Religious_info)
```


### Subjects_Area and info
```{r}
Subjects_Area <- df_stage2_Journal_Code2 %>% 
  dplyr::select(3,14,39,28,32,34) %>% 
  dplyr::filter(is.na(Subjects_Area)) %>% 
  dplyr::filter(is.na(Remark1)) %>% 
  dplyr::filter(!grepl("重复", Remark2))

### Article_IDs 20083093
df_stage2_Journal_Code2$Subjects_Area[62] <- 0

### Article_IDs 20181140
df_stage2_Journal_Code2$Subjects_Area[73] <- 0

### Article_IDs 20082296
df_stage2_Journal_Code2$Subjects_Area[735:737] <- 0

### Article_IDs 20082298
df_stage2_Journal_Code2$Subjects_Area[738] <- 0

### Article_IDs 20085035
df_stage2_Journal_Code2$Subjects_Area[747] <- 0

### Article_IDs 20085044
df_stage2_Journal_Code2$Subjects_Area[752:754] <- 0

### Article_IDs 20183229
df_stage2_Journal_Code2$Subjects_Area[1109] <- 0

### Article_IDs 20213012
df_stage2_Journal_Code2$Subjects_Area[1434] <- 0

### Article_IDs 20213039
df_stage2_Journal_Code2$Subjects_Area[1443] <- 0

### Article_IDs 20211018
df_stage2_Journal_Code2$Subjects_Area[1675] <-  0

rm(Subjects_Area)

Subjects_Area_info <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(Subjects_Area >= 1 & is.na(Subjects_Area_info)) %>% 
  dplyr::select(3,28:29,14,39,32,34)


### Article_IDs 20215026
df_stage2_Journal_Code2$Subjects_Area_info[1216] <- "天津本地居住"

rm(Subjects_Area_info)
```


### Subjects_Recruitment_Area
```{r}
Subjects_Recruitment_Area <- df_stage2_Journal_Code2 %>% 
  dplyr::select(3,14,39,30,32,34) %>% 
  dplyr::filter(is.na(Subjects_Recruitment_Area)) %>% 
  dplyr::filter(is.na(Remark1)) %>% 
  dplyr::filter(!grepl("重复", Remark2))


### Article_IDs 20181140
df_stage2_Journal_Code2$Subjects_Recruitment_Area[73] <- "广东"

### Article_IDs 20182297
df_stage2_Journal_Code2$Subjects_Recruitment_Area[159] <- "东部;中部;西部"

### Article_IDs 20183326
df_stage2_Journal_Code2$Subjects_Recruitment_Area[172] <- "湖北"

### Article_IDs 20082064
df_stage2_Journal_Code2$Subjects_Recruitment_Area[250] <- "西北;东北;华北;华东;华南;华中;西南"

### Article_IDs 20181243
df_stage2_Journal_Code2$Subjects_Recruitment_Area[319] <- "福建;上海;宁夏"

### Article_IDs 20085035
df_stage2_Journal_Code2$Subjects_Recruitment_Area[747] <- "内蒙古"

### Article_IDs 20085044
df_stage2_Journal_Code2$Subjects_Recruitment_Area[752:754] <- "北京"

### Article_IDs 20181007
df_stage2_Journal_Code2$Subjects_Recruitment_Area[765:767] <- 0

### Article_IDs 20082339
df_stage2_Journal_Code2$Subjects_Recruitment_Area[995] <- 0

### Article_IDs 20081026
df_stage2_Journal_Code2$Subjects_Recruitment_Area[1251] <- "广东"

### Article_IDs 20183277
df_stage2_Journal_Code2$Subjects_Recruitment_Area[1394] <- 0

### Article_IDs 20183292
df_stage2_Journal_Code2$Subjects_Recruitment_Area[1398:1399] <- 0

### Article_IDs 20183308
df_stage2_Journal_Code2$Subjects_Recruitment_Area[1406] <- 0

### Article_IDs 20185083
df_stage2_Journal_Code2$Subjects_Recruitment_Area[1409:1410] <- 0

### Article_IDs 20185087
df_stage2_Journal_Code2$Subjects_Recruitment_Area[1411:1414] <- 0

### Article_IDs 20185096
df_stage2_Journal_Code2$Subjects_Recruitment_Area[1415] <- 0

### Article_IDs 20185110
df_stage2_Journal_Code2$Subjects_Recruitment_Area[1418] <- 0

### Article_IDs 20185114
df_stage2_Journal_Code2$Subjects_Recruitment_Area[1421] <- 0

### Article_IDs 20185121
df_stage2_Journal_Code2$Subjects_Recruitment_Area[1424] <- 0

### Article_IDs 20185128
df_stage2_Journal_Code2$Subjects_Recruitment_Area[1428] <- 0

### Article_IDs 20185130
df_stage2_Journal_Code2$Subjects_Recruitment_Area[1429] <- 0

### Article_IDs 20213037
df_stage2_Journal_Code2$Subjects_Recruitment_Area[1442] <- 0
### uncode experiment2????

### Article_IDs 20213047
df_stage2_Journal_Code2$Subjects_Recruitment_Area[1449:1450] <- 0

### Article_IDs 20213048
df_stage2_Journal_Code2$Subjects_Recruitment_Area[1451:1452] <- 0

### Article_IDs 20215076
df_stage2_Journal_Code2$Subjects_Recruitment_Area[1460] <- 0

rm(Subjects_Recruitment_Area)


```


### Sampling_Method
```{r}
Sampling_Method <- df_stage2_Journal_Code2 %>% 
  dplyr::select(3,14,39,31,32,34) %>% 
  dplyr::filter(is.na(Sampling_Method)) %>% 
  dplyr::filter(is.na(Remark1)) %>% 
  dplyr::filter(!grepl("重复", Remark2))


### Article_IDs 20083093
df_stage2_Journal_Code2$Sampling_Method[62] <- 0

### Article_IDs 20181140
df_stage2_Journal_Code2$Sampling_Method[73] <- 0

### Article_IDs 20082105
df_stage2_Journal_Code2$Sampling_Method[260:267] <- 1

### Article_IDs 20211067
df_stage2_Journal_Code2$Sampling_Method[453:454] <- 0

### Article_IDs 20082296
df_stage2_Journal_Code2$Sampling_Method[735:737] <- 2

### Article_IDs 20082298
df_stage2_Journal_Code2$Sampling_Method[738] <- 2

### Article_IDs 20182180
df_stage2_Journal_Code2$Sampling_Method[1078] <- 0

### Article_IDs 20182182
df_stage2_Journal_Code2$Sampling_Method[1079:1081] <- 0

### Article_IDs 2182183
df_stage2_Journal_Code2$Sampling_Method[1082:1083] <- 0

### Article_IDs 20182184
#I found this is "secondary"
df_stage2_Journal_Code2$Remark1[1084] <- "secondary"
df_stage2_Journal_Code2$Remark1_N[1084] <- "secondary"

### Article_IDs 20182188
df_stage2_Journal_Code2$Sampling_Method[1085] <- 0

### Article_IDs 20182191
#I found this is "qualitative"
df_stage2_Journal_Code2$Remark1[1086] <- "qualitative"
df_stage2_Journal_Code2$Remark1_N[1086] <- "qualitative"

### Article_IDs 20081026
df_stage2_Journal_Code2$Sampling_Method[1251] <- 1

rm(Sampling_Method)
```


### Target_Population_N and Coding_Basis 
```{r}
Target_Population_N <- df_stage2_Journal_Code2 %>% 
  dplyr::select(3,14,39,37,32,34) %>% 
  dplyr::filter(is.na(Target_Population_N)) %>% 
  dplyr::filter(is.na(Remark1)) %>% 
  dplyr::filter(!grepl("重复", Remark2))


### Article_IDs 20182267
df_stage2_Journal_Code2$Target_Population_N[138] <- 3

### Article_IDs 20213098
df_stage2_Journal_Code2$Target_Population_N[227] <- 1

### Article_IDs 20215077
df_stage2_Journal_Code2$Target_Population_N[241] <- 1
df_stage2_Journal_Code2$Coding_Basis_N[241] <- "负性生活事件与儿童反应性攻击性之间的关系：一个有多重中介变量的结构方程模型"

### Article_IDs 20082105
df_stage2_Journal_Code2$Target_Population_N[262:267] <- 3
df_stage2_Journal_Code2$Coding_Basis_N[262:267] <- "中国的心理治疗和咨询业近年来发展迅速中国的心理治疗文献的快速增长表明我国的心理治疗目前正处于一个快速发展时期"

### Article_IDs 20085022
df_stage2_Journal_Code2$Target_Population_N[741] <- 1
df_stage2_Journal_Code2$Coding_Basis_N[741] <- "本研究假定:思维风格会通过影响学习策略,而间接影响数学学业成就。也就是说,学习策略在思维风格与数学学业成就之间起到中介的作用。"

### Article_IDs 20212148
df_stage2_Journal_Code2$Target_Population_N[950] <- 3

### Article_IDs 20214067
df_stage2_Journal_Code2$Target_Population_N[972] <- 3

### Article_IDs 20081051
df_stage2_Journal_Code2$Target_Population_N[1274] <- 3
df_stage2_Journal_Code2$Coding_Basis_N[1274] <- "这表明当代西方文化中的理想模型———男性化模型并不适用于中国,理想的性别角色模型具有文化特异性。这一结果不仅增进和丰富了人们对文化对心理和行为的影响的认识,还对我国目前青少年良好个性品质的塑造和培养以及心理健康教育的实践具有重要指导作用。"

### Article_IDs 20183292
df_stage2_Journal_Code2$Target_Population_N[1398:1399] <- 3

### Article_IDs 20185096
df_stage2_Journal_Code2$Target_Population_N[1415] <- 3
df_stage2_Journal_Code2$Coding_Basis_N[1415] <- "（1）网站临场感对女性网络购买意愿具有显著的正向影响。（2）网站临场感可以通过风险感知和沉醉感的中介作用对女性网络购买意愿产生影响，且该中介作用包含了三条路径，即风险感知的中介作用、沉醉感的中介作用以及风险感知和沉醉感的链式中介作用。"

### Article_IDs 20185102
df_stage2_Journal_Code2$Target_Population_N[1416] <- 3

rm(Target_Population_N)

Coding_Basis <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(!is.na(Target_Population_N) & is.na(Coding_Basis_N)) %>% 
  dplyr::select(3,37:38,14,32,34,39)

rm(Coding_Basis)

```


### Sample_Type_N and Sample_Type_info_N
```{R}
Sample_Type_N <- df_stage2_Journal_Code2 %>% 
  dplyr::select(3,14,39,40,32,34) %>% 
  dplyr::filter(is.na(Sample_Type_N)) %>% 
  dplyr::filter(is.na(Remark1)) %>% 
  dplyr::filter(!grepl("重复", Remark2))


### Article_IDs 20081136
df_stage2_Journal_Code2$Sample_Type_N[35] <- 2

### Article_IDs 20082002
df_stage2_Journal_Code2$Sample_Type_N[36] <- 2

### Article_IDs 20085022
df_stage2_Journal_Code2$Sample_Type_N[741] <- 1

### Article_IDs 20182104
df_stage2_Journal_Code2$Sample_Type_N[813:814] <- 0

### Article_IDs 20081026
df_stage2_Journal_Code2$Sample_Type_N[1251] <- 0

### Article_IDs 20184025
df_stage2_Journal_Code2$Sample_Type_N[1596] <- 1

rm(Sample_Type_N)

Sample_Type_info_N <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(is.na(Sample_Type_info_N)) %>% 
  dplyr::filter(!is.na(Sample_Type_N)) %>% 
  dplyr::select(3,14,39,41,32,34)


### Article_IDs 20181176
df_stage2_Journal_Code2$Sample_Type_info_N[109] <- "选取34名河北师范大学在校大校生(男生16名,女生18名)作为被试"

### Article_IDs 20182018
df_stage2_Journal_Code2$Sample_Type_info_N[335] <- "132名学前末期儿童参与实验1"

### Article_IDs 20084068
df_stage2_Journal_Code2$Sample_Type_info_N[537] <- "从上海两所中等水平幼儿园的325名幼儿中以年龄班分层随机抽取180名3～6岁幼儿。"

### Article_IDs 20182050
df_stage2_Journal_Code2$Sample_Type_info_N[565] <- "再另外随机选取78名本科生完成Buss-Perry攻击性量表"

### Article_IDs 20182069
df_stage2_Journal_Code2$Sample_Type_info_N[582] <- "来自上海某小学的154名7岁儿童参与本研究"

### Article_IDs 20183142
df_stage2_Journal_Code2$Sample_Type_info_N[611] <- "研究对象为来自湖南省某综合医院心理科门诊的心理咨询就诊患者"

### Article_IDs 20212031
df_stage2_Journal_Code2$Sample_Type_info_N[649] <- "采用方便取样和滚雪球抽样的方式，通过网络宣传、社区招募、熟人介绍等方式面向社会公开征集被试.确认愿意参与研究的有效被试为106对。夫 妻的婚龄为15.13±11.20月（1~36月之间）"

### Sample_Type_N is 5, I need to reclassify the code once.

### Article_IDs 20085022
df_stage2_Journal_Code2$Sample_Type_info_N[741] <- "选取某大学二年级的理科生为被试"

### Article_IDs 20181022
df_stage2_Journal_Code2$Sample_Type_info_N[786] <- "汉族被试为四川省广安市两所公立中学的42名高中生"

### Article_IDs 20181065
df_stage2_Journal_Code2$Sample_Type_info_N[1042:1043] <- "大学生被试463人"
### I found study1' Sample_Type_info_N of this article is incorrect.
df_stage2_Journal_Code2$Sample_Type_info_N[1041] <- df_stage2_Journal_Code2$Sample_Type_info_N[1040]

### Article_IDs 20081026
df_stage2_Journal_Code2$Sample_Type_info_N[1251] <- "纸笔测验在中山大学完成，全部被试来自选修某选修课的学生"
### I found this article' Sample_Type_N is incorrect.
df_stage2_Journal_Code2$Sample_Type_N[1251] <- 1

### Article_IDs 20184025
df_stage2_Journal_Code2$Sample_Type_info_N[1596] <- "采用广告招募和公共课堂发问卷的方式从382名大学本科生中获取被试"

rm(Sample_Type_info_N)
```


### Subjects_Recruitment_Method_N and info
```{r}
Subjects_Recruitment_Method_N <- df_stage2_Journal_Code2 %>%
  dplyr::select(3,14,39,47,32,34) %>% 
  dplyr::filter(is.na(Subjects_Recruitment_Method_N)) %>% 
  dplyr::filter(is.na(Remark1)) %>% 
  dplyr::filter(!grepl("重复", Remark2))


### Article_IDs 20081134
df_stage2_Journal_Code2$Subjects_Recruitment_Method_N[33] <- 1

### Article_IDs 20182255
df_stage2_Journal_Code2$Subjects_Recruitment_Method_N[129] <- 1

### Article_IDs 20185165
df_stage2_Journal_Code2$Subjects_Recruitment_Method_N[206:207] <- 1

### Article_IDs 20185174
df_stage2_Journal_Code2$Subjects_Recruitment_Method_N[211] <- 1

### Article_IDs 20185191
df_stage2_Journal_Code2$Subjects_Recruitment_Method_N[218] <- 2

### Article_IDs 20213089
df_stage2_Journal_Code2$Subjects_Recruitment_Method_N[225] <- 1

### Article_IDs 20213091
df_stage2_Journal_Code2$Subjects_Recruitment_Method_N[226] <- 0

### Article_IDs 20213120
df_stage2_Journal_Code2$Subjects_Recruitment_Method_N[237] <- 2

### Article_IDs 20082067
df_stage2_Journal_Code2$Subjects_Recruitment_Method_N[252] <- 0

### Article_IDs 20085022
df_stage2_Journal_Code2$Subjects_Recruitment_Method_N[741] <- 1

### Article_IDs 20181005
df_stage2_Journal_Code2$Subjects_Recruitment_Method_N[763] <- 1

### Article_IDs 20185003
df_stage2_Journal_Code2$Subjects_Recruitment_Method_N[897] <- 1 

### Article_IDs 20214060
df_stage2_Journal_Code2$Subjects_Recruitment_Method_N[970] <- "1;2"

### Article_IDs 20181026
df_stage2_Journal_Code2$Subjects_Recruitment_Method_N[1251] <- 1

### Article_IDs 20183277
df_stage2_Journal_Code2$Subjects_Recruitment_Method_N[1394] <- 0

### Article_IDs 20183292
df_stage2_Journal_Code2$Subjects_Recruitment_Method_N[1398:1399] <- 0

### Article_IDs 20183295
df_stage2_Journal_Code2$Subjects_Recruitment_Method_N[1400] <- 1

### Article_IDs 20213024
df_stage2_Journal_Code2$Subjects_Recruitment_Method_N[1439] <- 1

### Article_IDs 20184025
### I found subjects of this study2 same as study1 ,namely "被试重复使用"
df_stage2_Journal_Code2$Remark2[1596] <- "被试重复使用"
df_stage2_Journal_Code2$Remark2_N[1596] <- "被试重复使用"

rm(Subjects_Recruitment_Method_N)

Subjects_Recruitment_Method_info_N <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(Subjects_Recruitment_Method_N == 2 | Subjects_Recruitment_Method_N == "1;2") %>% 
  dplyr::filter(is.na(Subjects_Recruitment_Method_info_N))%>% 
  dplyr::select(3,47:48,14,39,34,36)


### Article_IDs 20213104
df_stage2_Journal_Code2$Subjects_Recruitment_Method_info_N[230] <- "研究者社交网络招募被试，问卷星发放问卷"

### Article_IDs 20211040
df_stage2_Journal_Code2$Subjects_Recruitment_Method_info_N[424:428] <- "营销实验室"

rm(Subjects_Recruitment_Method_info_N)
```


### Educational_Attainment_N and info
```{r}
Educational_Attainment_N <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(Sample_Type_N >= 4 & is.na(Educational_Attainment_N)) %>% 
  dplyr::select(3,40:43,14,32,34,39)


### Article_IDs 20083052
df_stage2_Journal_Code2$Educational_Attainment_N[44] <- 1
df_stage2_Journal_Code2$Educational_Attainment_info_N[43]  <- "平均教育程度为14.1±1.7年" 

### Article_IDs 20083107
df_stage2_Journal_Code2$Educational_Attainment_N[67] <- 1
df_stage2_Journal_Code2$Educational_Attainment_info_N[67] <- "文化水平小学及以上"

### Article_IDs 20181143
df_stage2_Journal_Code2$Educational_Attainment_N[83:84] <- 0

### Article_IDs 20082105
df_stage2_Journal_Code2$Educational_Attainment_N[262:267] <- 0

### Article_IDs 20182017
df_stage2_Journal_Code2$Educational_Attainment_N[332] <- 0
df_stage2_Journal_Code2$Educational_Attainment_N[334] <- 0

### Article_IDs 20182085
df_stage2_Journal_Code2$Educational_Attainment_N[795] <- 0

### Article_IDs 20182148
df_stage2_Journal_Code2$Educational_Attainment_N[841] <- 0

### Article_IDs 20212122
### I found sample type of this study is not 5 but 1.
df_stage2_Journal_Code2$Sample_Type_N[942] <- 1
df_stage2_Journal_Code2$Sample_Type_info_N[942] <- "对559 名有过网络游戏经验的大学生进行调查"

### Article_IDs 20215035
### I found sample type of this study is not 5 but 2.
df_stage2_Journal_Code2$Sample_Type_N[1218] <- 2

### Article_IDs 20081037
df_stage2_Journal_Code2$Educational_Attainment_N[1266:1267] <- 1
df_stage2_Journal_Code2$Educational_Attainment_info_N[1266] <- "本研究的被试是某大学商学院参加“组织行为学”课程的 MBA 学生"
df_stage2_Journal_Code2$Educational_Attainment_info_N[1267] <- "本研究的参加者为商学院学习《组织行为学》课程的 MBA 学生"

### Article_IDs 20183264
df_stage2_Journal_Code2$Educational_Attainment_N[1388:1389] <- 1

rm(Educational_Attainment_N)
```


### Ocuupation_N
```{r}
Occupation_N <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(Sample_Type_N >= 4 & is.na(Occupation_N)) %>% 
  dplyr::select(3,40:41,44,14,32,34,39)


### Article_IDs 20083107
df_stage2_Journal_Code2$Occupation_N[67] <- 0

### Article_IDs 20185174
df_stage2_Journal_Code2$Occupation_N[211] <- 0

### Article_IDs 20182085
df_stage2_Journal_Code2$Occupation_N[795] <- 0

### Article_IDs 20182148
### I found Sample_Type_info_N of this study is incorrect
df_stage2_Journal_Code2$Sample_Type_info_N[841] <- "预实验2让被试对产品进行体验型和搜索型的评分，48名被试参与实验，有效被试46人，其中男性21人,女性25人"

###Article_IDs 20081037
df_stage2_Journal_Code2$Occupation_N[1266:1267] <- 0

### Article_IDs 20183257
df_stage2_Journal_Code2$Occupation_N[1385] <- 0

rm(Occupation_N)

```


### SES_N and info
```{r}
SES_N <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(Sample_Type_N >= 4 & is.na(SES_N)) %>% 
  dplyr::select(3,40:41,45:46,14,32,34,39)

### Article_IDs 20083093
df_stage2_Journal_Code2$SES_N[63:64] <- 0

### Article_IDs 20083107
df_stage2_Journal_Code2$SES_N[67] <- 2

### Article_IDs 20185174
df_stage2_Journal_Code2$SES_N[211] <- 2

### Article_IDs 20213120
df_stage2_Journal_Code2$SES_N[237] <- "1;2;3"

### Article_IDs 20215082
df_stage2_Journal_Code2$SES_N[243] <- "1;3"

### Article_IDs 20082105
df_stage2_Journal_Code2$SES_N[262:267] <- 1

### Article_IDs 20082107
df_stage2_Journal_Code2$SES_N[268:269] <- 2
df_stage2_Journal_Code2$SES_info_N[268] <- NA

rm(SES_N)

SES_info_N <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(SES_N == 5 | grepl("5",SES_N))

### Article_IDs 20214060
df_stage2_Journal_Code2$SES_info_N[970] <- "17.5%为贫困生,82.5%不是贫困生"

SES_info_N_2 <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(!is.na(SES_info_N))

df_stage2_Journal_Code2 <- df_stage2_Journal_Code2 %>% 
  dplyr::mutate(SES_info_N = if_else(SES_N == 5 | grepl("5",SES_N),SES_info_N,NA))

rm(SES_info_N,SES_info_N_2)
```


### Study_Type
```{r}
Study_Type <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(is.na(Study_Type)) %>% 
  dplyr::filter(is.na(Remark1) & !grepl("重复", Remark2_N)) %>% 
  dplyr::select(3,15,14,39,32,34)


### Article_IDs 20081127
df_stage2_Journal_Code2$Study_Type[28] <- 2
  
### Article_IDs 20181140
df_stage2_Journal_Code2$Study_Type[73] <- 1
  
### Article_IDs 20182268
df_stage2_Journal_Code2$Study_Type[143:148] <- 2
  
### Article_IDs 20183314
df_stage2_Journal_Code2$Study_Type[163:164] <- 1

### Article_IDs 20082054
df_stage2_Journal_Code2$Study_Type[246] <- 2
  
### Article_IDs 20082074
df_stage2_Journal_Code2$Study_Type[257:258] <- 1

### Article_IDs 20082087
df_stage2_Journal_Code2$Study_Type[260] <- df_stage2_Journal_Code2$Study_Type[259]

### Article_IDs 20084023
df_stage2_Journal_Code2$Study_Type[301] <- 2
  
### Article_IDs 20085040
df_stage2_Journal_Code2$Study_Type[749:751] <- 2
  
### Article_IDs 20085054
df_stage2_Journal_Code2$Study_Type[755:757] <- "测验"
  
### Article_IDs 20182125
df_stage2_Journal_Code2$Study_Type[827:829] <- 2
  
### Article_IDs 20182148
df_stage2_Journal_Code2$Study_Type[843] <- 1
  
### Article_IDs 20182188
df_stage2_Journal_Code2$Study_Type[1085] <- 2
  
### Article_IDs 20081026
df_stage2_Journal_Code2$Study_Type[1251] <- 2  
  
### Article_IDs 20213137
df_stage2_Journal_Code2$Study_Type[1682:1683] <-  1   

rm(Study_Type)
```


### Subjects_Group_NA
In the process of checking, I found that there were some Subjects_Group in the paper, but it was not recorded. The above code cannot check for both Subjects_Group and Subjects_Group_N columns as NA, so check the above again. Meanwhile,I found that our coding had some redundant group, so in this part, we tried to improve this problem as much as possible while checking that Subject_Group and Subject_Group_N were both NA.
```{r}
Subjects_Group2 <- df_stage2_Journal_Code2 %>% 
  dplyr::group_by(Article_IDs,Study_Number) %>% 
  dplyr::filter(n() >1 & (is.na(Subjects_Group) | is.na(Subjects_Group_N))) %>% 
  dplyr::ungroup() %>% 
  dplyr::select(3,7:8,14,32,34,39)

### Article_IDs 20083093
df_stage2_Journal_Code2$Subjects_Group[62] <- "抑郁情绪组"
df_stage2_Journal_Code2$Subjects_Group_N[62] <- "抑郁情绪组"

### Article_IDs 20181140
df_stage2_Journal_Code2$Subjects_Group[73] <- "大学生"
df_stage2_Journal_Code2$Subjects_Group_N[73] <- "大学生"

### Article_IDs 20082210
### Redundant Group
df_stage2_Journal_Code2 <- df_stage2_Journal_Code2 %>% 
  dplyr::slice(-c(700:701))

df_stage2_Journal_Code2$Sample_Size[699] <- 89

### Article_IDs 20082258
### Redundant Group
df_stage2_Journal_Code2 <- df_stage2_Journal_Code2 %>% 
  dplyr::slice(-c(715:717,719:721))

df_stage2_Journal_Code2$Sample_Size[714] <- 170
df_stage2_Journal_Code2$Sample_Size[715] <- 170

### Article_IDs 20085040
df_stage2_Journal_Code2$Subjects_Group[741:743] <- c("初一","初二","初三")
df_stage2_Journal_Code2$Subjects_Group_N[741:743] <- c("初一","初二","初三")

### Article_IDs 20085044
df_stage2_Journal_Code2$Subjects_Group[744:746] <- c("3岁组","4岁组","5岁组")
df_stage2_Journal_Code2$Subjects_Group_N[744:746] <- c("3岁组","4岁组","5岁组")

### Article_IDs 20181005
df_stage2_Journal_Code2$Subjects_Group[751:752] <- c("年轻组","老年组")
df_stage2_Journal_Code2$Subjects_Group_N[751:752] <- c("年轻组","老年组")
df_stage2_Journal_Code2$Subjects_Group[753:756] <- c("老年人情景特异性诱导","老年人控制性诱导","大学生情景特异性诱导","大学生控制性诱导")
df_stage2_Journal_Code2$Subjects_Group_N[753:756] <- c("老年人情景特异性诱导","老年人控制性诱导","大学生情景特异性诱导","大学生控制性诱导")

### Article_IDs 20181017
df_stage2_Journal_Code2$Subjects_Group[765:768] <- c("高汉语水平","低汉语水平","高汉语水平","低汉语水平")
df_stage2_Journal_Code2$Subjects_Group_N[765:768] <- c("高汉语水平","低汉语水平","高汉语水平","低汉语水平")

### Article_IDs 20182101
### Redundant Group
df_stage2_Journal_Code2 <- df_stage2_Journal_Code2 %>% 
  dplyr::slice(-c(790:792,794:796))

df_stage2_Journal_Code2$Sample_Size[789] <- 114
df_stage2_Journal_Code2$Sample_Size[790] <- 113

df_stage2_Journal_Code2$Male_Num [789] <- 55
df_stage2_Journal_Code2$Female_Num[789] <- 59
df_stage2_Journal_Code2$Male_Num[790] <- 56
df_stage2_Journal_Code2$Female_Num[790] <- 57

### Article_IDs 20182103
### Redundant Group
df_stage2_Journal_Code2 <- df_stage2_Journal_Code2 %>% 
  dplyr::slice(-794)

### Article_IDs 20182117
### Redundant Group
df_stage2_Journal_Code2 <- df_stage2_Journal_Code2 %>% 
  dplyr::slice(-c(803,801))

df_stage2_Journal_Code2$Sample_Size[800] <- 168
df_stage2_Journal_Code2$Male_Num[800] <- 37
df_stage2_Journal_Code2$Female_Num[800] <- 131
df_stage2_Journal_Code2$Age[800] <- 1
df_stage2_Journal_Code2$M_age[800] <- 20.59
df_stage2_Journal_Code2$SD_age[800] <- 1.46

df_stage2_Journal_Code2$Sample_Size[801] <- 72
df_stage2_Journal_Code2$Male_Num[801] <- 21
df_stage2_Journal_Code2$Female_Num[801] <- 51
df_stage2_Journal_Code2$Age[801] <- 1
df_stage2_Journal_Code2$M_age[801] <- 21.68
df_stage2_Journal_Code2$SD_age[801] <- 2.03

### Article_IDs 20182125
### Redundant Group
df_stage2_Journal_Code2 <- df_stage2_Journal_Code2 %>% 
  dplyr::slice(-809)

df_stage2_Journal_Code2$Sample_Size[808] <- 64
df_stage2_Journal_Code2$Female_Num[808] <- 64
df_stage2_Journal_Code2$Age[808] <- 1
df_stage2_Journal_Code2$M_age[808] <- 19.84
df_stage2_Journal_Code2$SD_age[808] <- 1.26

df_stage2_Journal_Code2 <- df_stage2_Journal_Code2 %>% 
  dplyr::slice(-c(810:811))

df_stage2_Journal_Code2$Sample_Size[809] <- 104
df_stage2_Journal_Code2$Female_Num[809] <- 104
df_stage2_Journal_Code2$Age[809] <- 1
df_stage2_Journal_Code2$M_age[809] <- 24.56
df_stage2_Journal_Code2$SD_age[809] <- 2.19
df_stage2_Journal_Code2$Subjects_Group[809] <- NA
df_stage2_Journal_Code2$Subjects_Group_N[809] <- NA

### Article_IDs 20182126
### Redundant Group
df_stage2_Journal_Code2 <- df_stage2_Journal_Code2 %>% 
  dplyr::slice(-811)

df_stage2_Journal_Code2$Sample_Size[810] <- 68
df_stage2_Journal_Code2$Gender[810] <- 1
df_stage2_Journal_Code2$Male_Num[810] <- 23
df_stage2_Journal_Code2$Female_Num[810] <- 45
df_stage2_Journal_Code2$Age[810] <- 1
df_stage2_Journal_Code2$M_age[810] <- 21.24
df_stage2_Journal_Code2$SD_age[810] <- 0.67

### Article_IDs 20215065
df_stage2_Journal_Code2$Subjects_Group[1208] <- "老年人"
df_stage2_Journal_Code2$Subjects_Group_N[1208] <- "老年人"
df_stage2_Journal_Code2$Age[1208] <- 1

### Article_IDs 20181091
df_stage2_Journal_Code2$Subjects_Group[1292] <- "场依存型"
df_stage2_Journal_Code2$Subjects_Group_N[1292] <- "场依存型"

### Article_IDs 20182239
df_stage2_Journal_Code2$Subjects_Group[1356:1357] <- c("9岁被试","13岁被试")
df_stage2_Journal_Code2$Subjects_Group_N[1356:1357] <- c("9岁被试","13岁被试")

### Article_IDs 20185126
df_stage2_Journal_Code2$Subjects_Group[1405] <- "中国样本"
df_stage2_Journal_Code2$Subjects_Group_N[1405] <- "中国样本"

### Article_IDs 20211015
df_stage2_Journal_Code2$Subjects_Group[1652:1653] <- c("领导者样本","员工样本")
df_stage2_Journal_Code2$Subjects_Group_N[1652:1653] <- c("领导者样本","员工样本")

rm(Subjects_Group2)

```


## Save Rdata
In order to reduce code repetition, The Rdata is saved.
```{r}
save(df,df_stage2_Journal_Code,df_stage2_Journal_Code2,
     Group1_bind,Group24567_bind,Group3_bind,
     file = "df_Pre_Stage2_Journal_Code.Rdata")
```


## Load the pre Rdata
```{r}
load("df_Pre_Stage2_Journal_Code.Rdata")
```


### All information detailed check again
```{r}
#str(df_stage2_Journal_Code2)

### fill all "  " character
df_stage2_Journal_Code2 <- df_stage2_Journal_Code2 %>% 
  dplyr::mutate_if(is.character, ~ifelse(. == "　",NA,.))


## Check Abstract2
Abstract2_detailed <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(Sample_Type_N == 1 & !(Abstract2 == 0|Abstract2 == 1))
rm(Abstract2_detailed)


## Check Sample_Size
Sample_Size_detailed <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(if_any(c("Male_Num","Female_Num"),~!is.na(.))) %>% 
  dplyr::filter(is.na(Sample_Size))
rm(Sample_Size_detailed)


## Check Gender
Gender_detalied <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(if_any(c("Male_Num","Female_Num"),~!is.na(.))) %>%
  dplyr::filter(Gender != 1)

### Article_IDs 20182268
df_stage2_Journal_Code2$Gender[146] <- 1


## Check Male and Female
Male_Female <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(Gender == 1 & (is.na(Male_Num) & is.na(Female_Num)))
### I find 2 rows was listed, but its indeed not have specific data
rm(Male_Female,Gender_detalied)


## Check Age
Age_detailed <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(if_any(c("M_age","SD_age","Other_age"),~!is.na(.))) %>%
  dplyr::filter(Age != 1)


## Check Age_info
Age_m_sd_other <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(Age == 1 & (is.na(M_age) & is.na(SD_age) & is.na(Other_age)))

### Article_IDs 20181133
df_stage2_Journal_Code2$Other_age[1330] <- "20-25"
rm(Age_m_sd_other,Age_detailed)


## Check Ethnicity
Ethnicity_detailed <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(!Ethnicity %in% c(0,1))

Ethnicity_detailed2 <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(Ethnicity != 1 & !is.na(Ethnicity_info))

df_stage2_Journal_Code2 <- df_stage2_Journal_Code2 %>% 
  dplyr::mutate(Ethnicity_info = if_else(Ethnicity == 0 , NA, Ethnicity_info))


## Check Ethnicity_info
Ethnicity_info_detailed <- df_stage2_Journal_Code2 %>%
  dplyr::filter(Ethnicity == 1 & is.na(Ethnicity_info))
rm(Ethnicity_detailed,Ethnicity_detailed2,Ethnicity_info_detailed)


## Check Religious
Religious_detailed <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(!Religious %in% c(0,1))


## Check Religious_info
Religious_info_detailed <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(Religious == 0 & !is.na(Religious_info))
rm(Religious_detailed,Religious_info_detailed)


## Check Subjects_Area
Subjects_Area_detailed <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(!Subjects_Area %in% c(0,1))


## Check Subjects_Area_info
Subjects_Area_info_detailed <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(Subjects_Area == 0 & !is.na(Subjects_Area_info))
### Article_IDs 20083038
df_stage2_Journal_Code2$Subjects_Area[37] <- 1
rm(Subjects_Area_detailed,Subjects_Area_info_detailed)


## Check Subjects_Recruitment_Area
Subjects_Recruitment_Area_detailed <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(!Subjects_Recruitment_Area %in% c(0,2)) %>% 
  dplyr::select(Article_IDs,Subjects_Recruitment_Area,Remark1,Remark2)
rm(Subjects_Recruitment_Area_detailed) 


## Check Sampling_Method
Sampling_Method_detailed <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(!Sampling_Method %in% c(0,1,2)) %>% 
  dplyr::select(Article_IDs,Sampling_Method,Remark1,Remark2)
###Article_IDs 20185128
df_stage2_Journal_Code2$Sampling_Method[1407] <- 0
rm(Sampling_Method_detailed)


## Target_Population
Target_Population_N_detailed <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(!Target_Population_N %in% c(0,1,2,3)) %>% 
  dplyr::select(Article_IDs,Target_Population_N,Remark1,Remark2)


## Coding_Basis
Coding_Basis_N_detailed <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(Target_Population_N %in% c(0,1,2,3) & is.na(Coding_Basis_N)) %>% 
  dplyr::select(Article_IDs,Target_Population_N,Coding_Basis_N,Remark1,Remark2)

### Article_IDs 20181140
df_stage2_Journal_Code2$Coding_Basis_N[68:79] <- "在解决问题的过程中,无论是儿童、青少年还是成人都需要抑制控制的参与,三者在抑制控制效率上没有差异"

### Article_IDs 20181186
df_stage2_Journal_Code2$Coding_Basis_N[118] <- df_stage2_Journal_Code2$Coding_Basis_N[120]

### Article_IDs 20181197
df_stage2_Journal_Code2$Coding_Basis_N[124] <- "(1)暴力环境接触对大学生网络攻击行为有着显著的正向影响,并间接地通过反刍思维对大学生网络攻击行为产生作用。"

### Article_IDs 20182261
df_stage2_Journal_Code2$Coding_Basis_N[132:135] <- "本研究的结论如下：（1）青少年的网络社交使用频率对网络成瘾倾向具有显著的影响；家庭社会经济地位调节着青少年网络社交使用频率与网络成瘾倾向直接的关系。具体而言，在高社会经济家庭中成长的个体,其网络成瘾倾向不受网络社交使用频率的影响，而在低社会经济家庭中成长的个体，其网络成瘾倾向受到网络社交使用频率的影响。" 

### Article_IDs 20083203
df_stage2_Journal_Code2$Coding_Basis_N[283] <- "编制中学生羞耻感量表"

### Article_IDs 20083210
df_stage2_Journal_Code2$Coding_Basis_N[288] <- "编制具有科学性和实用性的中学教师工作满意度量表"

### Article_IDs 20083227
df_stage2_Journal_Code2$Coding_Basis_N[290:291] <- "探讨心理干预对小学生学习困难的效果"

### Article_IDs 20084004
df_stage2_Journal_Code2$Coding_Basis_N[292:294] <- "本研究采用注意线索范式对小学生视觉选择性注意的发展及其影响因素进行了研究"

### Article_IDs 20084005
df_stage2_Journal_Code2$Coding_Basis_N[295] <- "结果发现：（1）分类记忆策略的发展既有突变过程也有渐变过程：分类记策略有生成缺陷表现为训练后的突然变化；分类忆策略则是一个可以自发形成的渐变过程.如果加以适当的训练也会发生突然的增长。（2）在材料熟悉度较低的情况下会使少量儿童产生分类记、忆策略使用缺陷现象。"

### Article_IDs 20084016
df_stage2_Journal_Code2$Coding_Basis_N[296] <- "（1）中学教师的创造力内隐观主要涵盖了创造性思维和创造性人格；教师一致认同高创造性学生有28个重要心理特征"

### Article_IDs 20084020
df_stage2_Journal_Code2$Coding_Basis_N[297:300] <- "目前,国内外并没有现成的工具直接测量儿童表征能力,为此我们拟编制一套儿童表征能力测验"

### Article_IDs 20084023
df_stage2_Journal_Code2$Coding_Basis_N[301] <- "本研究采用追踪研究方法,考察了儿童2岁、4岁、7岁、11岁时内隐问题行为和外显问题行为的稳定性和变化。"

### Article_IDs 20084025
df_stage2_Journal_Code2$Coding_Basis_N[302:305] <- "本研究从一个新的角度探讨了5～8岁儿童心理理论的发展,考察了为错误信念任务中的主人公贴上“聪明”或“笨”的标签是否能影响儿童错误信念任务的成绩"

### Article_IDs 20084026
df_stage2_Journal_Code2$Coding_Basis_N[306:309] <- "研究设计了无意义问题来考察5、6、8、10岁共128名儿童在回答问题时的反应倾向"

### Article_IDs 20084029
df_stage2_Journal_Code2$Coding_Basis_N[310] <- "（1）除坚毅进取性之外,小学儿童社会创造性倾向的各个维度及总分均与父亲的情感温暖、理解父亲的偏爱呈显著或极其显著的正相关,与父亲的惩罚、严厉呈显著的负相关"

### Article_IDs 20183097
df_stage2_Journal_Code2$Coding_Basis_N[378] <- "探讨体验式干预对减少学龄儿童意外伤害危险行为及意外伤害事件的效果"

### Article_IDs 20183098
df_stage2_Journal_Code2$Coding_Basis_N[379:381] <- "本研究为减少疾病的异质性，将首发精神分裂症患者分为阳性症状组（幻觉妄想）和阴性症状组（言语乏、自发运动减少及情感淡漠），对其可能的神经生物学基础进行研究"

### Article_IDs 20211059
df_stage2_Journal_Code2$Coding_Basis_N[436] <- "本研究从知觉和概念水平上为揭示物体颜色在联结记忆中的作用提供了证据。"

### Article_IDs 20211061
df_stage2_Journal_Code2$Coding_Basis_N[437] <- "本研究在中国社会文化背景下从外显和内隐两个层面验证了食物性别刻板印象的存在,系统考察了食物性别刻板印象对人们人物评价产生的影响,具有一定的理论价值与实践意义。"

### Article_IDs 20213236
df_stage2_Journal_Code2$Coding_Basis_N[486] <- "父母婚姻质量通过家庭亲密度与适应性的中介作用，以及家庭亲密度与适应性和亲子冲突的链式中介作用影响小学生内化问题"

### Article_IDs 20213239
df_stage2_Journal_Code2$Coding_Basis_N[487] <- "本研究发现护士出勤主义行为对健康生产力受损具有显著的正向预测作用，即护士带病参加工作行为频率越高，对其生产力的负面影响就越大，这一结论和前人的研究相似"

### Article_IDs 20084068
df_stage2_Journal_Code2$Coding_Basis_N[537] <- "3～6岁儿童数感发展的研究"
  
### Article_IDs 20182050  
df_stage2_Journal_Code2$Coding_Basis_N[565] <- "本研究主要探讨了不同领域厌恶情绪的时程加工特点，结果表明，不同领域的厌恶情感得到识别的先后顺序存在差异，病原体厌恶和道德厌恶率先得到识别，三种类型厌恶情绪在加工中期均得到识别，后期加工中个体对性厌恶情绪更为敏感，不同领域的厌恶情感对应了不同的加工机制。"

### Article_IDs 20182069
df_stage2_Journal_Code2$Coding_Basis_N[582] <- "本研究追踪考察139名儿童7岁、8岁和9岁时在计划和注意任务上的表现，并利用交叉滞后模型分析此期间计划能力与注意能力不同成分（持续性注意，抑制控制和选择性注意）在发展上的关系"

### Article_IDs 20212054
df_stage2_Journal_Code2$Coding_Basis_N[657] <- "人类生活的大部分时间都在编织各类大小不同、复杂抽象或简单具体不一的意义之网（Baumeister,1991）。换言之，每个人都在寻找或构建自身存在的意义。缺乏生命意义，个体会感到存在空虚，各种的心理与行为问题将随之产生"

### Article_IDs 20181017
df_stage2_Journal_Code2$Coding_Basis_N[767] <- "汉语熟练度不同的蒙汉双语者颜色范畴知觉效应存在差异,语言对知觉的作用在早期前注意阶段已有显现,Spair-Whorf假设在知觉早期加工过程中也成立"
  
### Article_IDs 20185030
df_stage2_Journal_Code2$Coding_Basis_N[895] <- "农民工是中国城镇化的产物，农民工群体的身份认同分化为本研究提供了典型的样本。众多学者的研究发现，新生代农民工群体产生了身份认同的分化，形成了“ 城市人” “ 农村人” “ 不清楚” 的不同认同类型"

### Article_IDs 20185033
df_stage2_Journal_Code2$Coding_Basis_N[896] <- "（1）亲社会动机对新颖性和有效性都有促进作用。（2）“自我-他人”与新颖性关系密切，对有效性影响不显著。（3）为自己创造比为他人创造更加具有创造性。（4）社会动机与“ 自我-他人” 对创造性的影响不存在交互作用。"

### Article_IDs 20212079
df_stage2_Journal_Code2$Coding_Basis_N[897] <- "本研究旨在探究父母学业参与和学生消极情绪的关系及作用机制"

### Article_IDs 20212082
df_stage2_Journal_Code2$Coding_Basis_N[898] <- "结果显示：(1)逻辑训练可以提高个体三段论推理的成绩；(2)训练前后非冲突任务的正确率均高于冲突任务，但训练后该差异趋势缩小；(3)训练对低理性思维方式个体在冲突任务正确率的提高效果更好。这表明逻辑训练可以有效地减弱推理中的信念偏差现象，且对低理性思维方式个体的效果尤其明显。"

### Article_IDs 20212083
df_stage2_Journal_Code2$Coding_Basis_N[899:900] <- "结果表明：词汇预测性影响儿童阅读的眼动行为和词汇加工，且作用大小和发生时程受阅读技能调节。"

### Article_IDs 20212085
df_stage2_Journal_Code2$Coding_Basis_N[901:902] <- "社交与工作导向情境对“热情优先效应”具有重要的增强与削弱作用。社交导向情境下，“热情优先效应”普遍存在；工作导向情境下，在热情与能力独立维度视角中，情境的削弱效应使得“热情优先效应”无法表现；而在热情与能力互依维度视角中，“热情优先效应”则强于情境对其的削弱效应。" 

### Article_IDs 20212091
df_stage2_Journal_Code2$Coding_Basis_N[906] <- "结果表明，红色及图形均可有效助推健康行为，与通常的黑色数字相比，二者相结合可使这一助推效果更为稳定。"

### Article_IDs 20212097
df_stage2_Journal_Code2$Coding_Basis_N[907:909] <- "无论处于何种加工方式，个体在人际互动中并非完全追求利益最大化或是积极互惠，而是会关注互动对象的信任水平。"

### Article_IDs 20212100
df_stage2_Journal_Code2$Coding_Basis_N[910] <- "总之，本研究结果表明采用基于认知诊断测评的个性化补救教学能够有效促进学生学习，为实践者应用认知诊断测评促进学生学习提供了实践依据"

### Article_IDs 20212105
df_stage2_Journal_Code2$Coding_Basis_N[912:914] <- "该结果表明实验操纵方式所引发的编码过程和记忆测试所需的检索过程性质上相匹配，而且延迟测试时，知觉非流畅可以促进学习，说明非流畅效应存在边界。"

### Article_IDs 20182191
df_stage2_Journal_Code2$Coding_Basis_N[1065] <- "通过对186名企业员工的调查分析发现，上司地位知觉对下属默契有显著的正向影响；反馈寻求行为在此过程中起部分中介作用；此外，下属观点采择能力调节了 反馈寻求行为与下属默契间的正向关系"

### Article_IDs 20183227
df_stage2_Journal_Code2$Coding_Basis_N[1087] <- "社交焦虑水平能够显著调节放逐后个体对积极面孔的注意脱离加工过程，对理解社交焦虑的起源与维持有重要启示"

### Article_IDs 20183229
df_stage2_Journal_Code2$Coding_Basis_N[1088] <- "长期海洛因戒断组在反应时上能够较好的解决冲突，但是长期吸食海洛因导致其认知控制功能损伤"

### Article_IDs 20185076
df_stage2_Journal_Code2$Coding_Basis_N[1136] <- "在本研究条件下，得到以下结论：（1）阅读水平和阅读任务均会影响英语阅读中的词频效应；（2）高水平组被试在英语阅读中的认知灵活性更强。"

### Article_IDs 20185077
df_stage2_Journal_Code2$Coding_Basis_N[1137] <- "本研究条件得出如下结论：（1）在以大学生为被试的研究中发现，次级任务影响被试内隐序列学习，且“数形”任务较“数声”任务产生更大的干扰作用；与单任务相比，双任务下的内隐学习量未发生显著消退。（2）在不同年级被试的研究中，除“数形组”小学生内隐学习消退以外，其他年级组均习得内隐规则且内隐学习量的任务效应与年级效应显著。"

### Article_IDs 20215008
df_stage2_Journal_Code2$Coding_Basis_N[1186] <- "对1137名一年级职高生实施问卷调查，探讨感知教师和父母自主支持、基本心理需要满足与内外化问题的关系。"

### Article_IDs 20215009
df_stage2_Journal_Code2$Coding_Basis_N[1187] <- "本研究旨在探讨累积生态风险与农村初中生攻击行为之间的关系，以及道德推脱的中介作用与共情的调节作用。"

### Article_IDs 20083033
df_stage2_Journal_Code2$Coding_Basis_N[1285] <- "探讨涉毒罪犯的改造意识。"

### Article_IDs 20182236
df_stage2_Journal_Code2$Coding_Basis_N[1354] <- "研究发现积极学业情绪在先前学业成就与学习策略、学习动机之间起完全中介作用；消极学业情绪（消极低唤醒）在先前学业成就与学习策略、学习动机之间起部分中介作用"

### Article_IDs 20185116
df_stage2_Journal_Code2$Coding_Basis_N[1442:1444] <- "本研究采用图-词干扰范式，通过检验口语句子产生中不同位置的名词的语义干扰效应,探讨大中小学生词汇选择的计划单元大小"

### Article_IDs 20183039
df_stage2_Journal_Code2$Coding_Basis_N[1641:1642] <- "状态权力感、特质权力感共同对补偿消费产生影响，大选择集不能有效修复低权力状态。"

### Article_IDs 20184027
df_stage2_Journal_Code2$Coding_Basis_N[1643:1649] <- "说明威胁性刺激觉察中的注意偏向在视觉搜索的早期阶段已经发生"

### Article_IDs 20213153
df_stage2_Journal_Code2$Coding_Basis_N[1656:1660] <- "编制青少年学业自豪与学业自大问卷，并检验其信效度"

rm(Target_Population_N_detailed,Coding_Basis_N_detailed)


## Sample_Type
Sample_Type_N_detailed <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(!Sample_Type_N %in% c(1:5)) %>% 
  dplyr::select(Article_IDs,Sample_Type_N,Sample_Type_info_N, Remark1,Remark2)

### Article_IDs 20182104
df_stage2_Journal_Code2$Sample_Type_N[798:799] <- 1
df_stage2_Journal_Code2 <- df_stage2_Journal_Code2 %>% 
  dplyr::mutate(Sample_Type_N = ifelse(grepl(";",Sample_Type_N),5,Sample_Type_N))  


## Sample_Type_info
Sample_Type_info_N_detailed <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(Sample_Type_N %in% c(1:5) & is.na(Sample_Type_info_N))
rm(Sample_Type_info_N_detailed,Sample_Type_N_detailed)


## Educational_Attainment
Educational_Attainment_N_detailed <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(Sample_Type_N %in% c(4,5) & is.na(Educational_Attainment_N)) %>% 
  dplyr::select(Article_IDs,Sample_Type_N,Sample_Type_info_N,Educational_Attainment_N,Remark1,Remark2)
### Article_IDs 20082248
df_stage2_Journal_Code2$Educational_Attainment_N[709:710] <- 0


## Educational_Attainment_info
Educational_Attainment_info_N_detailed <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(Educational_Attainment_N == 1 & is.na(Educational_Attainment_info_N)) %>%
  dplyr::select(Article_IDs,Sample_Type_N,Sample_Type_info_N,
                 Educational_Attainment_N,Educational_Attainment_info_N,Remark1,Remark2)

### Article_IDs 20081099
df_stage2_Journal_Code2$Educational_Attainment_info_N[17] <- "高中、中专及以下占8.68%,大专占25.00%, 本科占 52.08%, 硕士及以上占 12.15%"

### Article_IDs 20182258
df_stage2_Journal_Code2$Educational_Attainment_info_N[131] <- "学历大专以下28人，大专61人，本科 100 人，研究生及以上 12 人"

### Article_IDs 20183321
df_stage2_Journal_Code2$Educational_Attainment_info_N[169] <- "小学8人，初中22人，高中24人，大学21人，大学以上6人"

### Article_IDs 20185138
df_stage2_Journal_Code2$Educational_Attainment_info_N[197] <- "6.88%的父亲具有本科及以上学历，14.38%的父亲为高中学历，51.88%父亲为初中学历，26.88%的父亲学历低于初中"
df_stage2_Journal_Code2$Educational_Attainment_info_N[198] <- "5.00％的母亲具有本科及以上学历，5.63％的母亲为高中学历，43.75%的母亲为初中学历，45.63%的母亲学历低于初中"

### Article_IDs 20185191
df_stage2_Journal_Code2$Educational_Attainment_info_N[218] <- "本科5.36%，硕士30.35，博士64.29%"

### Article_IDs 20183137
df_stage2_Journal_Code2$Educational_Attainment_info_N[607] <- "平均受教育年限17.73"

### Article_IDs 20082283
df_stage2_Journal_Code2$Educational_Attainment_info_N[724] <- "大学文化程度"

### Article-IDs 20181005
df_stage2_Journal_Code2$Educational_Attainment_info_N[751:752] <- "老年被试为高中(中专)或以上学历, 与年轻被试的文化程度较为匹配"

### Article_IDs 20212149
df_stage2_Journal_Code2$Educational_Attainment_info_N[930] <- "在学历方面，高中或大专 96 人，占 37.209%；本科 156 人，占 60.465%，研究生或以上 7 人，占 2.713%"

rm(Educational_Attainment_N_detailed,Educational_Attainment_info_N_detailed)


## Occupation
Occupation_N_detailed <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(Sample_Type_N %in% c(4,5) & is.na(Occupation_N)) %>% 
  dplyr::select(Article_IDs,Sample_Type_N,Sample_Type_info_N,Occupation_N,Remark1,Remark2)
rm(Occupation_N_detailed)


## SES
SES_N_detailed <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(Sample_Type_N %in% c(4,5) & is.na(SES_N)) %>% 
  dplyr::select(Article_IDs,Sample_Type_N,Sample_Type_info_N,SES_N,Remark1,Remark2)


## SES_info
SES_info_N_detailed <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(SES_N == 5 & is.na(SES_info_N))
rm(SES_N_detailed,SES_info_N_detailed)
```


## Redundant Group
I found that some groups, especially the sixth group, had redundancy of subjects' group. Although some checks have been done above, in order to obtain more accurate and objective data, we conducted another check of the groups of subjects.

### Group 6
```{r}

### Article_IDs 20082280
df_stage2_Journal_Code2 <- df_stage2_Journal_Code2 %>% 
  dplyr::slice(-c(721:722))

df_stage2_Journal_Code2$Subjects_Group[720] <- NA
df_stage2_Journal_Code2$Subjects_Group_N[720] <- NA
df_stage2_Journal_Code2$Sample_Size[720] <- 12
df_stage2_Journal_Code2$Gender[720] <- 1
df_stage2_Journal_Code2$Male_Num[720] <- 5
df_stage2_Journal_Code2$Female_Num[720] <- 7


### Article_IDs 20085033
df_stage2_Journal_Code2 <- df_stage2_Journal_Code2 %>% 
  dplyr::slice(-c(735:736))

df_stage2_Journal_Code2$Subjects_Group[734] <- NA
df_stage2_Journal_Code2$Subjects_Group_N[734] <- NA
df_stage2_Journal_Code2$Male_Num[734] <- 30
df_stage2_Journal_Code2$Sample_Size[734] <- 30

### Article_IDs 20085054
df_stage2_Journal_Code2 <- df_stage2_Journal_Code2 %>% 
  dplyr::slice(-c(744:745))

df_stage2_Journal_Code2$Subjects_Group[743] <- NA
df_stage2_Journal_Code2$Subjects_Group_N[743] <- NA
df_stage2_Journal_Code2$Sample_Size[743] <- 314
df_stage2_Journal_Code2$Gender[743] <- 1
df_stage2_Journal_Code2$Male_Num[743] <- 161
df_stage2_Journal_Code2$Female_Num[743] <- 153

### Article_IDs 20181005
df_stage2_Journal_Code2$Remark3_N[747] <- "性别分组和年龄分组有冲突"

### Article_IDs 20181020
df_stage2_Journal_Code2 <- df_stage2_Journal_Code2 %>% 
  dplyr::slice(-c(764:765))

df_stage2_Journal_Code2$Subjects_Group[763] <- NA
df_stage2_Journal_Code2$Subjects_Group_N[763] <- NA
df_stage2_Journal_Code2$Sample_Size[763] <- 72
df_stage2_Journal_Code2$Gender[763] <- 1
df_stage2_Journal_Code2$Male_Num[763] <- 27
df_stage2_Journal_Code2$Female_Num[763] <- 45
df_stage2_Journal_Code2$M_age[763] <- 20.2
df_stage2_Journal_Code2$SD_age[763] <- 2.17
df_stage2_Journal_Code2$Other_age[763] <- "18-23"

df_stage2_Journal_Code2 <- df_stage2_Journal_Code2 %>% 
  dplyr::slice(-765)

df_stage2_Journal_Code2$Subjects_Group[764] <- NA
df_stage2_Journal_Code2$Subjects_Group_N[764] <- NA
df_stage2_Journal_Code2$Male_Num[764] <- 31
df_stage2_Journal_Code2$Female_Num[764] <- 42
df_stage2_Journal_Code2$M_age[764] <- 21.5
df_stage2_Journal_Code2$SD_age[764] <- 1.93
df_stage2_Journal_Code2$Other_age[764] <- "18-23"

### Article_IDs 20182103
df_stage2_Journal_Code2 <- df_stage2_Journal_Code2 %>% 
  dplyr::slice(-c(783:784))

df_stage2_Journal_Code2$Subjects_Group[782] <- NA
df_stage2_Journal_Code2$Subjects_Group_N[782] <- NA
df_stage2_Journal_Code2$Sample_Size[782] <- 291

### Article_IDs 20182120
df_stage2_Journal_Code2 <- df_stage2_Journal_Code2 %>% 
  dplyr::slice(-796)

df_stage2_Journal_Code2$Sample_Size[795] <- 90
df_stage2_Journal_Code2$Gender[795] <- 1
df_stage2_Journal_Code2$Male_Num[795] <- 30
df_stage2_Journal_Code2$Female_Num[795] <- 60
df_stage2_Journal_Code2$Age[795] <- 1
df_stage2_Journal_Code2$M_age[795] <- 22.5
df_stage2_Journal_Code2$SD_age[795] <- 0.28

### Article_IDs 20182133
df_stage2_Journal_Code2 <- df_stage2_Journal_Code2 %>% 
  dplyr::slice(-802)

df_stage2_Journal_Code2$Subjects_Group[801] <- NA
df_stage2_Journal_Code2$Subjects_Group_N[801] <- NA
df_stage2_Journal_Code2$Sample_Size[801] <- 21
df_stage2_Journal_Code2$Male_Num[801] <- 11
df_stage2_Journal_Code2$Female_Num[801] <- 9

### Article_IDs 20183150
df_stage2_Journal_Code2 <- df_stage2_Journal_Code2 %>% 
  dplyr::slice(-823)

df_stage2_Journal_Code2$Subjects_Group[822] <- NA
df_stage2_Journal_Code2$Subjects_Group_N[822] <- NA
df_stage2_Journal_Code2$Sample_Size[822] <- 643
df_stage2_Journal_Code2$Gender[822] <- 1
df_stage2_Journal_Code2$Male_Num[822] <- 296
df_stage2_Journal_Code2$Female_Num[822] <- 347
df_stage2_Journal_Code2$Age[822] <- 1
df_stage2_Journal_Code2$M_age[822] <- 11.98
df_stage2_Journal_Code2$SD_age[822] <- 1.74

### Article_IDs 20183192
df_stage2_Journal_Code2 <- df_stage2_Journal_Code2 %>% 
  dplyr::slice(-842)

df_stage2_Journal_Code2$Subjects_Group[841] <- NA
df_stage2_Journal_Code2$Subjects_Group_N[841] <- NA
df_stage2_Journal_Code2$Study_Type[841] <- 1
df_stage2_Journal_Code2$Sample_Size[841] <- 80
df_stage2_Journal_Code2$Gender[841] <- 1
df_stage2_Journal_Code2$Male_Num[841] <- 49
df_stage2_Journal_Code2$Female_Num[841] <- 31
df_stage2_Journal_Code2$Age[841] <- 1
df_stage2_Journal_Code2$M_age[841] <- 30.51
df_stage2_Journal_Code2$SD_age[841] <- 9.54
df_stage2_Journal_Code2$Other_age[841] <- NA
df_stage2_Journal_Code2$Educational_Attainment_info_N[841] <- "初中以下11人，高中及中专18人，大专以上51人"

### Article_IDs 20183198
df_stage2_Journal_Code2$Gender[843] <- 1
df_stage2_Journal_Code2$Male_Num[843] <- 27
df_stage2_Journal_Code2$Female_Num[843] <- 18
df_stage2_Journal_Code2$Age[843] <- 1
df_stage2_Journal_Code2$M_age[843] <- 53.63
df_stage2_Journal_Code2$SD_age[843] <- 9.34
df_stage2_Journal_Code2$Gender[844] <- 1
df_stage2_Journal_Code2$Male_Num[844] <- 29
df_stage2_Journal_Code2$Female_Num[844] <- 21
df_stage2_Journal_Code2$Age[844] <- 1
df_stage2_Journal_Code2$M_age[844] <- 57.30
df_stage2_Journal_Code2$SD_age[844] <- 9.63   

### Article_IDs 20184162
df_stage2_Journal_Code2$M_age[857] <- "父亲:41.44;母亲:40.23"

### Article_IDs 20185017
df_stage2_Journal_Code2 <- df_stage2_Journal_Code2 %>% 
  dplyr::slice(-c(871:872))

df_stage2_Journal_Code2$Subjects_Group[870] <- NA
df_stage2_Journal_Code2$Subjects_Group_N[870] <- NA
df_stage2_Journal_Code2$Sample_Size[870] <- 31
df_stage2_Journal_Code2$Female_Num[870] <- 31
df_stage2_Journal_Code2$M_age[870] <- 22.1

### Article_IDs 20212083
df_stage2_Journal_Code2 <- df_stage2_Journal_Code2 %>% 
  dplyr::slice(-883)

df_stage2_Journal_Code2$Sample_Size[882] <- 44
df_stage2_Journal_Code2$Subjects_Group[882] <- NA
df_stage2_Journal_Code2$Subjects_Group_N[882] <- NA
```


### Other Groups
```{r}
### Article_IDs 20182248
df_stage2_Journal_Code2$M_age[125:127] <- c("3.54","4.53","5.50")
df_stage2_Journal_Code2$SD_age[125:127] <- c("0.28","0.27","0.26")

### Article_IDs 20181225
df_stage2_Journal_Code2$Male_Num[1502] <- 0.712
df_stage2_Journal_Code2$Female_Num[1502] <- 1-0.712
df_stage2_Journal_Code2$Male_Num[1503] <- 0.456
df_stage2_Journal_Code2$Female_Num[1503] <- 1-0.456
df_stage2_Journal_Code2$Age[1502:1503] <- 1
df_stage2_Journal_Code2$Other_age[1502] <- "30 岁及以上的占 65.1%"
df_stage2_Journal_Code2$Other_age[1503] <- "30 岁以下的人占56.4%"

### Article_IDs 20183001
df_stage2_Journal_Code2$Educational_Attainment_info_N[1513:1515] <- c("受教育水平(年):M=13.78,SD=1.72","受教育水平(年）:M=13.67,SD=2.90","受教育水平(年）:M=13.10,SD=1.63")

### Article_IDs 20211013
df_stage2_Journal_Code2$Remark3[1588] <- "分组时性别与年龄冲突，总数为68人，其中男生37人"

### Article_IDs 20211025
df_stage2_Journal_Code2 <- df_stage2_Journal_Code2 %>% 
  dplyr::slice(-1593)

df_stage2_Journal_Code2$Subjects_Group[1592] <- NA
df_stage2_Journal_Code2$Subjects_Group_N[1592] <- NA
df_stage2_Journal_Code2$Sample_Size[1592] <- 480

### Article_IDs 20182022
df_stage2_Journal_Code2$Sample_Size[352:353] <- c(102,488)
df_stage2_Journal_Code2$Age[352:353] <- 1
df_stage2_Journal_Code2$Male_Num[352:353] <- c(0.353,0.336)
df_stage2_Journal_Code2$Female_Num[352:353] <- c(1-0.353,1-0.336)

### Article_IDs 20184112
df_stage2_Journal_Code2$M_age[618:619] <- 11
df_stage2_Journal_Code2$Other_age[618:619] <- NA

### Article_IDs 20082341
df_stage2_Journal_Code2$Gender[957:959] <- 1
df_stage2_Journal_Code2$Male_Num[957:959] <- c(40,36,47)
df_stage2_Journal_Code2$Female_Num[957:959] <- c(43,40,33)

### Article_IDs 20182183
df_stage2_Journal_Code2$M_age[1043] <- NA
df_stage2_Journal_Code2$SD_age[1043] <- NA

### Article_IDs 20083017
df_stage2_Journal_Code2$Gender[1259] <- 1
df_stage2_Journal_Code2$Male_Num[1259] <- 374/2
df_stage2_Journal_Code2$Female_Num[1259] <- 374/2

### Article_IDs 20183257
df_stage2_Journal_Code2$Female_Num[1345:1346] <- 0
### Article 20183264
df_stage2_Journal_Code2$Female_Num[1348:1350] <- 0
```








```
