---
title: "Notebook_BTS_Data_Preprocess"
author: "Lei Yue"
date: "2025-02-06"
output: html_document
---

**Special Note:**BTS\_, This indicates data sourced from large-scale international collaborations.

# install and library packages
```{r}
rm(list = ls())

if (!require("pacman")) install.packages("pacman")

# use package "pacman" as loading R packages tools

pacman::p_load("tidyverse","here","rio")
```


# Load the data of BTS

Here, we first converted some data that is not in .xlsx format.
```{r}
library(haven)

## read data
## BTS_Van_Bavel_et_al_2022
BTS_Van_Bavel_et_al_2022 <- haven::read_sav("BTS_Van_Bavel_et_al_2022.sav") %>% 
  dplyr::mutate(Gender = ifelse(Gender == 1, "Male", "Female"))

## BTS_Manokara_et_al_2022
BTS_Manokara_et_al_2022 <- haven::read_sav("BTS_Manokara_et_al_2022.sav") %>% 
  dplyr::mutate(Gender = ifelse(Gender == 1, "Male", "Female"))

## save data
write.csv(BTS_Van_Bavel_et_al_2022, file = "BTS_Van_Bavel_et_al_2022.csv",row.names = FALSE)
write.csv(BTS_Manokara_et_al_2022, file = "BTS_Manokara_et_al_2022.csv",row.names = FALSE)

## Here, I remove some data sets to reduce data set clutter.
rm(BTS_Manokara_et_al_2022,BTS_Van_Bavel_et_al_2022)
```

Next, I loaded all BTS data and processed BTS data.

```{r message=FALSE, warning=FALSE, include=FALSE}
file_list <- list.files(here("D://chin-subj//2_Data_Extraction//2_1 CHN_Journal_Code//2_2_6_Data_Analysis"), ## If you need to learn or repeat the code document, please replace it with your local file address
                        pattern = ".csv",
                        full.names = TRUE,
                        recursive = TRUE)

BTS_data_list <- list()  
 
for (file in file_list) {  
    
  BTS_file <- readr::read_csv(file)  
  BTS_data_list[[tools::file_path_sans_ext(basename(file))]] <- BTS_file  

}  

BTS_data_list <- BTS_data_list[grepl("BTS_",names(BTS_data_list),ignore.case = TRUE)]

BTS0 <- BTS_data_list
BTS <- BTS0

rm(BTS_file)

## Here, I remove some data sets to reduce data set clutter.
rm(file,file_list,BTS_data_list)
```

# Process BTS data

Uniform country codes facilitate subsequent data processing and analysis, especially for batch processing and analysis of data. Thus, I created a unified table of country codes.

```{r}
if(!require("countrycode")) install.packages("countrycode")

Countrycodelist <- codelist

Countrycodelist_iso2_iso3 <- Countrycodelist %>% 
  dplyr::select(country.name.en,iso2c,iso3c) %>% 
  dplyr::rename(Countryfullname = 1,ISO2 = 2, ISO3 = 3)

Countrycodelist_iso2_iso3$ISO2[Countrycodelist_iso2_iso3$Countryfullname == "Kosovo"] <- "XK"
Countrycodelist_iso2_iso3$ISO3[Countrycodelist_iso2_iso3$Countryfullname == "Kosovo"] <- "XKX"

## Here, I remove some data sets to reduce data set clutter.
rm(Countrycodelist)
```

The third hypothesis requires countries to be divided into WEIRD and non-WEIRD, so I created a data.frame of WEIRD countries to facilitate subsequent analysis and visualization.

```{r}
WEIRD <- codelist %>% 
  dplyr::select(3,6,iso2c,iso3c,region,region23) %>% 
  dplyr::mutate(WEIRD = ifelse(continent == "Europe" | region == "North America","WEIRD",NA),
                WEIRD = ifelse(continent %in% c("Africa","Asia") | region == "Latin America & Caribbean" | region == "East Asia & Pacific", "Non_WEIRD",WEIRD)) %>% 
  dplyr::mutate(WEIRD = ifelse(country.name.en %in% c("Israel","Australia","New Zealand"), "WEIRD",WEIRD),
                WEIRD = ifelse(is.na(WEIRD),"Non_WEIRD",WEIRD))
```


As the data for the large-scale international collaboration project is constantly updated, recording the names and order of data frames in the list here will facilitate the subsequent improvement of the code.
```{r}
names(BTS)

#  [1] "BTS_Anllo_et_al_2023"                                                              
#  [2] "BTS_Arechar_et_al_2023"                                                            
#  [3] "BTS_Awad_et_al_2018"                                                               
#  [4] "BTS_Azevedo_et_al_2022_mainland"                                                   
#  [5] "BTS_Azevedo_et_al_2022_taiwan"                                                     
#  [6] "BTS_Bago_et_al_2022"                                                               
#  [7] "BTS_Bertolo_et_al_2023"                                                            
#  [8] "BTS_Bosson_et_al_2021"                                                             
#  [9] "BTS_Buchanan_et_al_2023"                                                           
# [10] "BTS_Dorison_et_al_2020"                                                            
# [11] "BTS_Eriksson_et_al_2021"                                                           
# [12] "BTS_Everett_et_al_2021"                                                            
# [13] "BTS_Fernandez_Velasco_et_al_2023"                                                  
# [14] "BTS_Greenberg_et_al_2022"                                                          
# [15] "BTS_Hoogeveen_et_al_2022"                                                          
# [16] "BTS_Hu_et_al_2019"                                                                 
# [17] "BTS_Jones_et_al_2021"                                                              
# [18] "BTS_Kelsey_et_al_2024"                                                             
# [19] "BTS_Kirkland_et_al_2022"                                                           
# [20] "BTS_Klein_et_al_2018_Slate1"                                                       
# [21] "BTS_Klein_et_al_2018_Slate2"                                                       
# [22] "BTS_Kowal_et_al_2022"                                                              
# [23] "BTS_Manokara_et_al_2022"                                                           
# [24] "BTS_Pizzol_et_al_2023"                                                             
# [25] "BTS_Psychological_Science_Accelerator_Self_Determination_Theory_Collaboration_2022"
# [26] "BTS_Ruggeri_et_al_2020"                                                            
# [27] "BTS_Ruggeri_et_al_2022"                                                            
# [28] "BTS_Sorokowski_et_al_2023"                                                         
# [29] "BTS_Tybur_et_al_2016"                                                              
# [30] "BTS_Van_Bavel_et_al_2022"                                                          
# [31] "BTS_Vlasceanu_et_al_2023"                                                          
# [32] "BTS_Wang_et_al_2021" 

## save each data.frame colnames
colname_list <- list()

# 遍历列表中的每个数据框
for (name in names(BTS)) {
  
  df <- BTS[[name]]
  col_names <- colnames(df)
  
  temp_df <- data.frame(
    data_source = name,
    column_name = col_names
  )
  colname_list[[name]] <- temp_df
}

# 将结果列表合并为一个数据框
BTS_colnames <- do.call(rbind, colname_list)
rm(colname_list,temp_df,col_names,name,df)
```



In this part, I tried to batch country code.

```{r}
# str(BTS)

## Handle some more specific encodings
names(BTS[[20]])[names(BTS[[20]]) == "Country_now"] <- "Country"  ## BTS_Klein 2018 Slate1

names(BTS[[21]])[names(BTS[[21]]) == "Country_now"] <- "Country"  ## BTS_Klein 2018 Slate2

names(BTS[[22]])[names(BTS[[22]]) == "Country_now"] <- "Country"  ## BTS_Kowal 2018 Slate1

names(BTS[[32]])[names(BTS[[32]]) == "Country_now"] <- "Country"  ## BTS_Wang 2021

BTS[[9]]$Country <- trimws(sub(".*-(\\s*)", "", BTS[[9]]$Country))    ## BTS_Buchanan 2023
BTS[[32]]$Country <- trimws(sub(".*-(\\s*)", "", BTS[[32]]$Country))  ## BTS_Wang 2021




BTS <- BTS[-c(6,14,18,19,29)] ## remove data.frame with the country code as num (Bago et al 2022、Greenberg et al 2022、Kirkland et al 2022、Tybur et al 2016)
## remove data.frame with incorrect country name (Kelsey et al 2024)



## Batch processing of country codes for different data sources
BTS <- lapply(BTS,function(df){
  
  df <- df %>% 
    mutate(#Country = toupper(Country),
           Country = case_when(Country %in% c("TW","HK","MO") ~ "CN",
                               Country %in% c("TWN","HKG","MAC") ~ "CHN",
                               Country %in% c("Taiwan","Macao","Hong Kong, China","Hong Kong") ~ "China",
                               Country %in% c("Bosnia and Herzegovina","Bosnia and. Herz.") ~ "Bosnia & Herzegovina",
                               Country %in% c("England","Northern Ireland","Wales") ~ "United Kingdom",
                               Country %in% c("SlovakRepublic") ~ "Slovakia",
                               Country %in% c("Czech Republic") ~ "Czechia",
                               Country %in% c("Macedonia") ~ "North Macedonia",
                               Country %in% c("The Netherlands") ~ "Netherlands",
                               #Country %in% c("US","USA") ~ "United States",
                               TRUE ~ Country
                               ),
           Country = toupper(Country),
           Country = ifelse(nchar(Country) > 3, str_to_title(Country),Country),
           Countrycode = ifelse(nchar(Country) > 3, "Countryfullname", 
                                ifelse(nchar(Country) == 3, "ISO3", "ISO2")))
  
  return(df)
  
})



## Check the country code of the BTS data
BTS_countrycode_check <- lapply(BTS, function(df){
  
  df <- df %>% 
    dplyr::group_by(Countrycode) %>% 
    dplyr::summarise(n=n()) %>% 
    dplyr::ungroup()
  
  return(df)
})

BTS_countrycode_check <- do.call(rbind, BTS_countrycode_check)



## process abnormal Countrycode
## BTS_Anllo_et_al_2023
BTS[[1]] <- BTS[[1]] %>% 
  dplyr::mutate(Country = ifelse(Country == "USA", "United States",Country),
                Countrycode = ifelse(Country == "United States", "Countryfullname",Countrycode))


## BTS_Arechar_et_al_2023
BTS[[2]] <- BTS[[2]] %>% 
  dplyr::mutate(Country = ifelse(Country == "UK", "GB",Country))


## BTS_Bertolo_et_al_2023
BTS[[6]] <- BTS[[6]] %>% 
  dplyr::mutate(Country = case_when(Country == "Antigua And Barbuda" ~  "Antigua & Barbuda",
                                    Country == "Artsakh"  ~  "Azerbaijan", #*
                                    Country %in% c("Côte D'ivoire","Ivory Coast") ~  "Côte d’Ivoire",
                                    Country == "Democratic People's Republic Of Korea" ~ "North Korea",
                                    Country == "Democratic Republic Of The Congo" ~ "Congo - Kinshasa",
                                    Country == "East Timor" ~  "Timor-Leste",
                                    Country == "Kingdom Of The Netherlands"  ~  "Netherlands",
                                    Country == "Micronesia"  ~ "Micronesia (Federated States of)",
                                    Country == "Myanmar"  ~  "Myanmar (Burma)",
                                    # Country == "Northern Cyprus" #*
                                    Country == "Palestine"  ~ "Palestinian Territories",
                                    Country == "Sahrawi Arab Democratic Republic" ~ "Western Sahara", #*
                                    Country == "Saint Kitts And Nevis" ~ "St. Kitts & Nevis",
                                    Country == "Saint Lucia" ~ "St. Lucia",
                                    Country == "Saint Vincent And The Grenadines" ~  "St. Vincent & Grenadines",
                                    # Country == "Somaliland" ~ "", #*
                                    # Country == "South Ossetia" ~ "", #*
                                    Country == "Swaziland" ~ "Eswatini",
                                    Country == "São Tomé And Príncipe" ~ "São Tomé & Príncipe",
                                    Country == "The Bahamas" ~ "Bahamas",
                                    Country == "The Gambia" ~ "Gambia",
                                    # Country == "Transnistria" ~ "", #*
                                    Country == "Trinidad And Tobago" ~ "Trinidad & Tobago",
                                    TRUE ~ Country))


## BTS_Bosson_et_al_2021
BTS[[7]] <- BTS[[7]] %>% 
  dplyr::mutate(Country = ifelse(Country == "USA", "United States",Country),
                Country = ifelse(Country == "CHN", "China",Country),
                Country = ifelse(Country == "UEA", "United Kingdom",Country),
                Countrycode = ifelse(Country == "United States" | Country == "China" | Country == "United Kingdom", "Countryfullname",Countrycode))



## BTS_Buchanan_et_al_2023
BTS[[8]] <- BTS[[8]] %>% 
  dplyr::mutate(Country = ifelse(Country == "Ken, Na", "KEN",Country),
                Countrycode = ifelse(Country == "KEN", "ISO3",Countrycode))


## BTS_Dorison_et_al_2020
BTS[[9]] <- BTS[[9]] %>% 
  dplyr::mutate(Country = ifelse(Country == "Many", NA,Country),
                Countrycode = ifelse(Countrycode == "CountryfullnameN", NA,Countrycode)) 


## BTS_Eriksson_et_al_2021
BTS[[10]] <- BTS[[10]] %>% 
  dplyr::mutate(Country = case_when(Country == "Ivory Coast" ~  "Côte d’Ivoire",
                                    Country == "Trinidad And Tobago" ~ "Trinidad & Tobago",
                                    Country == "UAE" ~ "United Kingdom",
                                    TRUE ~ Country))


## Everett_et_al_2021
BTS[[11]] <- BTS[[11]] %>% 
  dplyr::mutate(Country = ifelse(Country == "Kingdom Of Saudi Arabia","Saudi Arabia",Country))


## BTS_Hoogeveen_et_al_2022
BTS[[13]] <- BTS[[13]] %>% 
  dplyr::mutate(Country = case_when(Country %in% c("Isr1","Isr2") ~ "ISR",
                                    Country %in% c("Ita1","Ita2") ~ "ITA",
                                    Country %in% c("Sgp1","Sgp2") ~ "SGP",
                                    Country %in% c("Usa1","Usa2") ~ "USA",
                                    TRUE ~ Country),
                Countrycode = ifelse(Countrycode == "Countryfullname", "ISO3",Countrycode))



## BTS_Jones_et_al_2021
# BTS[[15]] <- BTS[[15]] %>% 
#   dplyr::mutate(Countrycode = ifelse(Country == "--",NA,Countrycode),
#                 Country = ifelse(Country = "--",NA,Country))


## BTS_Klein_et_al_2018 Slate1
BTS[[16]] <- BTS[[16]] %>% 
  dplyr::mutate(Country = ifelse(Country == "UK", "United Kingdom",Country),
                Country = ifelse(Country == "USA", "United States",Country),
                Countrycode = ifelse(Country == "United Kingdom" | Country == "United States", "Countryfullname",Countrycode))


## BTS_Klein_et_al_2018 Slate2
BTS[[17]] <- BTS[[17]] %>% 
  dplyr::mutate(Country = ifelse(Country == "UK", "United Kingdom",Country),
                Country = ifelse(Country == "USA", "United States",Country),
                Countrycode = ifelse(Country == "United Kingdom" | Country == "United States", "Countryfullname",Countrycode))


## BTS_Kowal_et_al_2022
BTS[[18]] <- BTS[[18]] %>% 
  dplyr::mutate(Country = ifelse(Country == "UK", "United Kingdom",Country),
                Country = ifelse(Country == "USA", "United States",Country),
                Countrycode = ifelse(Country == "United Kingdom" | Country == "United States", "Countryfullname",Countrycode))



## BTS_Pizzol_et_al_2023
BTS[[20]] <- BTS[[20]] %>% 
  dplyr::mutate(Country = case_when(Country == "Korea, Rep." ~  "South Korea",
                                    Country == "Russian Federation" ~ "Russia",
                                    Country == "Slovak Republic" ~ "Slovakia",
                                    Country == "Taiwan, China" ~ "China",
                                    Country == "Venezuela, Rb" ~ "Venezuela",
                                    TRUE ~ Country))


## BTS_Psychological_Science_Accelerator_Self_Determination_Theory_Collaboration_2022
BTS[[21]] <- BTS[[21]] %>% 
  dplyr::mutate(Country = ifelse(Country == "Iran", "IRN",Country),
                Countrycode = ifelse(Country == "IRN", "ISO3",Countrycode))


## BTS_Ruggeri_et_al_2020
BTS[[22]] <- BTS[[22]] %>% 
  dplyr::mutate(Country = ifelse(Country == "UK", "United Kingdom",Country),
                Country = ifelse(Country == "USA", "United States",Country),
                Country = ifelse(Country == "Mainland China", "China",Country),
                Countrycode = ifelse(Country == "United Kingdom" | Country == "United States", "Countryfullname",Countrycode))



## BTS_Sorokowski_et_al_2023
BTS[[24]] <- BTS[[24]] %>% 
  dplyr::mutate(Country = ifelse(Country == "The Netherlands", "Netherlands",Country))


## BTS_Vlasceanu_et_al_2023
BTS[[26]] <- BTS[[26]] %>% 
  dplyr::mutate(Country = ifelse(Country == "UK", "United Kingdom",Country),
                Country = ifelse(Country == "USA", "United States",Country),
                Countrycode = ifelse(Country == "United Kingdom" | Country == "United States", "Countryfullname",Countrycode),
                Country = case_when(Country == "Newzealand" ~ "New Zealand",
                                    Country == "Northmacedonia" ~ "North Macedonia",
                                    Country == "Saudiarabia" ~ "Saudi Arabia",
                                    Country == "Southafrica" ~ "South Africa",
                                    Country == "Southkorea" ~ "South Korea",
                                    Country == "Srilanka" ~ "Sri Lanka",
                                    Country == "Unitedarabemirates" ~ "United Arab Emirates",
                                    TRUE ~ Country))


## BTS_Wang_et_al_2021
BTS[[27]] <- BTS[[27]] %>% 
  dplyr::mutate(Country = ifelse(Country == "China", "CHN",Country),
                Countrycode = ifelse(Country == "CHN", "ISO3",Countrycode))

  
## Combine the BTS_data and Countrycodelist_iso2_iso3
Countrycode_merge <- function(df, Countrycode) {  
  
  Countrycode_lengths <- nchar(as.character(df$Country))  
  Countrycode_lengths <- Countrycode_lengths[!is.na(Countrycode_lengths)]  
 
  if (all(Countrycode_lengths == 2)) {  
    
    merge_key <- "ISO2"  
  } else if (any(Countrycode_lengths > 3)) {  
   
    merge_key <- "Countryfullname"  
  } else {  
   
    merge_key <- "ISO3"  
  }  
    
  merged_df <- merge(df, Countrycode, by.x = "Country", by.y = merge_key, all.x = TRUE)  
    
  return(merged_df)  
}  
  
BTS <- lapply(BTS, Countrycode_merge, Countrycode = Countrycodelist_iso2_iso3)  

## Change the column name so that each BTS data has "ISO3"
BTS <- lapply(BTS,function(df){
  
  if(!"ISO3" %in% names(df)){
    
    df <- df %>% 
      dplyr::mutate(ISO3 = Country)
  }
  
  return(df)
  
})

## Change the column name so that each BTS data has "ISO2"
BTS <- lapply(BTS,function(df){
  
  if(!"ISO2" %in% names(df)){
    
    df <- df %>% 
      dplyr::mutate(ISO2 = Country)
  }
  
  return(df)
  
})


## Change the column name so that each BTS data has "countryfullname"
BTS <- lapply(BTS,function(df){
  
  if(!"Countryfullname" %in% names(df)){
    
    df <- df %>% 
      dplyr::mutate(Countryfullname = Country)
  }
  
  return(df)
  
})


## Because the country code of the countrycode package is the full name, but some of the actual data set is recorded by abbreviation (for example: United States is USA), so this part is not converted properly, and is now found and processed separately.
## BTS_Bertolo_et_al_2023
BTS[[6]] <- BTS[[6]] %>% 
  dplyr::mutate(Article_Id = "Bertolo_et_al_2023")


BTS_na <- lapply(BTS, function(df){
  
  df <- df %>% 
    dplyr::filter(is.na(ISO3)) %>% 
    dplyr::select(Article_Id, Country, ISO3)
  
  return(df)
})

BTS_na <- do.call(rbind,BTS_na)

BTS_na_table <- BTS_na %>% 
  dplyr::group_by(Article_Id,Country) %>% 
  dplyr::summarise(n=n())
```


process gender data of BTS
```{r}
## Batch processing of gender for different data sources
BTS <- lapply(BTS,function(df){
  
  df <- df %>% 
    dplyr::mutate(Gender = case_when(Gender %in% c("f","F") ~ "Female",
                              Gender %in% c("m","M") ~ "Male",
                              TRUE ~ Gender),
           Gender = str_to_title(Gender))
  
  return(df)
  
})


## Check the gender of the BTS data
BTS_gender_check <- lapply(BTS, function(df){
  
  df <- df %>% 
    dplyr::group_by(Gender) %>% 
    dplyr::summarise(n=n()) %>% 
    dplyr::ungroup()
  
  return(df)
})

BTS_gender_check <- do.call(rbind, BTS_gender_check)

# BTS_gender_check %>% 
#   dplyr::filter(Gender %in% c("Female","Male")) %>% 
#   dplyr::summarise(n=sum(n))

# write.csv(BTS_gender_check,"BTS_gender_check.csv")
```


process age data of BTS
```{r}
# bts1 <- BTS[[32]]
# 
# table(bts1$Education)

```


```{r include=FALSE}
## Here, I remove some data sets to reduce data set clutter.
rm(BTS_na_table,BTS_na,Countrycode_merge,BTS_countrycode_check)
gc()
```


# Save Rdata
```{r}
save(BTS0, BTS, file = "BTS.Rdata")
```

