---
title: "Notebook_Coding_Consistency"
author: "Lei Yue"
date: "2024-12-08"
output: html_document
---

## Load packages
```{r}
rm(list = ls())

if(!require("pacman"))install.packages("pacman")

p_load("here","tidyverse","rio","readxl")

```


## Load data
```{r warning=FALSE}
# getwd()

file_list <- list.files(
  here("C:/Users/yuelei/Desktop/Stage_2_Code_Data"),
  pattern = ".xlsx",
  full.names = TRUE, recursive = TRUE)

df <- rio::import_list(file_list) 

df <- df[grepl("CE",names(df),ignore.case = TRUE)]

df <- lapply(df, function(df) {  
  df[] <- lapply(df, as.character)  
  return(df)  
})

# df1 <- df[[1]]
# 
# table(df1$Coder)
```


## check colnames
```{r}
# names(df)

## check the coding stage colnames
Coding_datalist_names <- data.frame(Chin_Subj_Coding_Group1_8_9_CE = names(df[[1]]),
                                   Chin_Subj_Coding_Group1_8_9_CE_suppl3 = names(df[[2]]),
                                   Chin_Subj_Coding_Group2_CE = names(df[[3]]),
                                   Chin_Subj_Coding_Group3_CE = names(df[[4]]),
                                   Chin_Subj_Coding_Group3_CE_suppl6 = names(df[[5]]),
                                   Chin_Subj_Coding_Group4_CE = names(df[[6]]),
                                   Chin_Subj_Coding_Group5_CE = names(df[[7]]),
                                   Chin_Subj_Coding_Group6_CE = names(df[[8]]),
                                   Chin_Subj_Coding_Group7_CE = names(df[[9]]))

Check_row_equality1 <- function(row) {  
  all_equal <- all(row == row[1])  
  return(all_equal)  
}  
  
Row_equalities1 <- apply(Coding_datalist_names, 1, Check_row_equality1) 
### I found the names of 3,4,5, 19 cols are different and I modfi them
colnames(df[[9]])[colnames(df[[9]]) == "First_author"] <- "First_Author"

colnames(df[[3]])[colnames(df[[3]]) == "Sample_Szie"] <- "Sample_Size"
colnames(df[[4]])[colnames(df[[4]]) == "Sample_Szie"] <- "Sample_Size"
colnames(df[[5]])[colnames(df[[5]]) == "Sample_Szie"] <- "Sample_Size"
colnames(df[[6]])[colnames(df[[6]]) == "Sample_Szie"] <- "Sample_Size"
colnames(df[[7]])[colnames(df[[7]]) == "Sample_Szie"] <- "Sample_Size"
colnames(df[[9]])[colnames(df[[9]]) == "Sample_Szie"] <- "Sample_Size"

## Adjust the column names of the eighth data frame in the list to be consistent with the column names of other data frame (Chin_Subj_Coding_Group6_CE)
df[[8]] <- df[[8]][,c(1:2,5,3,4,6:40)]

## Adjust the column names for Chin_Subj_Coding_Group3_CE and Chin_Subj_Coding_Group3_CE_suppl6 to be consistent with the other data frame, but note that there are problems with the `Journal` and `First_Author`columns of these two data frame are recorded backwards
# df4 <- df[[4]]
# df5 <- df[[5]]
df[[4]] <- df[[4]][,c(1:3,5,4,6:40)]
df[[5]] <- df[[5]][,c(1:3,5,4,6:40)]

## check the proofreading stage colnames
Proofreading_datalist_names <- data.frame(Chin_Subj_Proofreading_Group1_CE = names(df[[10]]),
                                          Chin_Subj_Proofreading_Group2_CE = names(df[[11]]),
                                          Chin_Subj_Proofreading_Group3_CE = names(df[[12]]),
                                          Chin_Subj_Proofreading_Group4_CE = names(df[[13]]),
                                          Chin_Subj_Proofreading_Group5_CE = names(df[[14]]),
                                          Chin_Subj_Proofreading_Group6_CE = names(df[[15]]),
                                          Chin_Subj_Proofreading_Group7_CE = names(df[[16]]))

Check_row_equality2 <- function(row) {  
  all_equal <- all(row == row[1])  
  return(all_equal)  
}  
  
Row_equalities2 <- apply(Proofreading_datalist_names, 1, Check_row_equality2) 

### I found the names of 8 cols are different and I modfi them.

colnames(df[[11]])[colnames(df[[11]]) == "target_population_N"] <- "Target_Population_N"

# rm(Proofreading_Data_Names,row_equalities2,check_row_equality2)
```


## merge data
firstly, I will merge group 2,4,5,6,7
```{r}
Group24567_1 <- dplyr::bind_rows(df[[3]],df[[6]],df[[7]],df[[8]],df[[9]]) %>% 
  # dplyr::filter(Coder != "final") %>% 
  dplyr::select(-c(8,9,14:18,27,28,37,38))

Group24567_2 <- dplyr::bind_rows(df[[11]],df[[13]],df[[14]],df[[15]],df[[16]]) %>% 
  # dplyr::filter(Coder != "final") %>%
  dplyr::rename_at(vars(1:4,7), ~paste0(., "_N"))

Group24567_bind <-  cbind(Group24567_1,Group24567_2) %>% 
  dplyr::select(1,30,2,31,8,32,11,33,3:7,9,10,12:29,34:48)

# table(Group24567_1$Coder)
```


Secondly, I will find distinctinve Suppl IDs
```{r}
Suppl_ID <- dplyr::bind_rows(df[[2]],df[[5]]) %>% 
  dplyr::filter(Coder == "final") %>%
  dplyr::distinct(Article_IDs)
```


Thirdly, I will megrge group 1.
```{r}
Group1_1 <- df[[1]] %>% 
  # dplyr::filter(Coder != "final") %>% 
  dplyr::slice(-c(693:696,725:728)) %>%  ## filter Article_IDs 20185094 and 20185116
  dplyr::select(-c(8,9,14:18,27,28,37,38)) %>% 
  dplyr::mutate(Subjects_Group = ifelse(Subjects_Group == "3+M8:M28",3,Subjects_Group))

Group1_suppl <- df[[2]] %>% 
  # dplyr::filter(Coder != "final") %>% 
  dplyr::rename_at(vars(8,9,14:18,27,28,37,38), ~paste0(., "_N")) %>% 
  dplyr::mutate(Coder_N = NA, Article_IDs_N = NA, Study_Number_N = NA, 
                Subjects_Group_N = NA, Remark1_N = NA, Remark2_N = NA, 
                Remark3_N = NA, Coder2_N= NA) %>% 
  dplyr::mutate(Coder_N = Coder, Coder2_N = Coder,Article_IDs_N = Article_IDs,
                Study_Number_N = Study_Number, Subjects_Group_N = Subjects_Group, Remark1_N = Remark1,
                Remark2_N = Remark2, Remark3_N = Remark3)

Group1_2 <- df[[10]] %>% 
  # dplyr::filter(Coder != "final") %>%
  dplyr::slice(-c(693:700,729:740)) %>%  ## filter Article_IDs 20185094 and 20185116
  dplyr::rename_at(vars(1:4,7), ~paste0(., "_N"))

Group1_bind <- cbind(Group1_1,Group1_2) %>%
  dplyr::select(1,30,2,31,8,32,11,33,3:7,9,10,12:29,34:48)

Group1_bind <- bind_rows(Group1_bind,Group1_suppl)
```


Fouth, I will merge group6.
```{r}
Group3_1 <- df[[4]] %>% 
  dplyr::slice(-c(405:420,541:544,673:680,701:708,721:732)) %>% ## Filter Article_IDs 20183039, 20184027, 20211015, 20211018, 20183137, and 20213153
  dplyr::select(-c(8,9,14:18,27,28,37,38))

# continue sorting data
Group3_suppl <- df[[5]] %>% 
  dplyr::rename_at(vars(8,9,14:18,27,28,37,38), ~paste0(., "_N")) %>% 
  dplyr::mutate(Coder_N = NA, Article_IDs_N = NA, Study_Number_N = NA, 
                Subjects_Group_N = NA, Remark1_N = NA, Remark2_N = NA, 
                Remark3_N = NA, Coder2_N= NA) %>% 
  dplyr::mutate(Coder_N = Coder, Coder2_N = Coder,Article_IDs_N = Article_IDs,
                Study_Number_N = Study_Number, Subjects_Group_N = Subjects_Group, Remark1_N = Remark1,
                Remark2_N = Remark2, Remark3_N = Remark3)

Group3_2 <- df[[12]] %>% 
  dplyr::slice(-c(405:412,533:548,677:700,721:736,749:768)) %>% ## ## Filter Article_IDs 20183039, 20184027, 20211015, 20211018, 20183137, and 20213153
  dplyr::rename_at(vars(1:4,7), ~paste0(., "_N"))

Group3_bind <- cbind(Group3_1,Group3_2) %>%
  dplyr::select(1,30,2,31,8,32,11,33,3:7,9,10,12:29,34:48) %>% 
  rbind(Group3_suppl)
```


### Combine the coding data and the proofreading data
```{r message=FALSE, warning=FALSE}
Coding_consistency_preprocess_data <- bind_rows(Group24567_bind,Group1_bind,Group3_bind)

num_groups <- nrow(Coding_consistency_preprocess_data) / 4

Coding_consistency_preprocess_data$Sequence_IDs <- sprintf("%04d_%d", rep(1:num_groups, each=4), rep(1:4, times=num_groups))

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data %>% 
  dplyr::select(49,1:48) %>% 
  dplyr::filter(Coder != "final")

# names(Coding_consistency_preprocess_data1)

# writexl::write_xlsx(Coding_consistency_preprocess_data1,"Coding_consistency_preprocess_data1.xlsx")
```


## Article_IDs N
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(Article_IDs_N = ifelse(Article_IDs_N == "　",NA,Article_IDs_N),
                Article_IDs_N = ifelse(Coder == "check" & is.na(Article_IDs_N),"Chin_Subj",Article_IDs_N))

# table(Coding_consistency_preprocess_data1$Article_IDs_N)

rm(results)


results <- data.frame(Article_Title= character(),
                      Article_IDs_N_coder1 = as.character(),
                      Article_IDs_N_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder2_code <- Coding_consistency_preprocess_data1$Article_IDs_N[i+1]
  stored_score <- Coding_consistency_preprocess_data1$Article_IDs_N[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code) || grepl(coder2_code, coder1_code)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     Article_IDs_N_coder1 = coder1_code,
                                     Article_IDs_N_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")

## 20085033
Coding_consistency_preprocess_data1$Article_IDs_N[c(2241,2244)] <- 1

## 20085054
Coding_consistency_preprocess_data1$Article_IDs_N[c(2274,2277)] <- 3
```

## Study Number N
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(Study_Number_N = ifelse(Study_Number_N == "　",NA,Study_Number_N),
                Study_Number_N = ifelse(Coder == "check" & is.na(Study_Number_N),"Chin_Subj",Study_Number_N))

# table(Coding_consistency_preprocess_data1$Study_Number_N)

rm(results)

results <- data.frame(Article_IDs_N = character(),
                      Study_Number_N_coder1 = as.character(),
                      Study_Number_N_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$Study_Number_N[i]
  coder2_code <- Coding_consistency_preprocess_data1$Study_Number_N[i+1]
  stored_score <- Coding_consistency_preprocess_data1$Study_Number_N[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code) || grepl(coder2_code, coder1_code)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     Study_Number_N_coder1 = coder1_code,
                                     Study_Number_N_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")


## revise check
## 20083038
Coding_consistency_preprocess_data1$Study_Number_N[117] <- 1
 
## 20083039
Coding_consistency_preprocess_data1$Study_Number_N[123] <- 1

## 20181168
Coding_consistency_preprocess_data1$Study_Number_N[312] <- 1

## 20211046
Coding_consistency_preprocess_data1$Study_Number_N[1296] <- 3

## 20212097
Coding_consistency_preprocess_data1$Study_Number_N[2790] <- 1
Coding_consistency_preprocess_data1$Study_Number_N[2793] <- 1

## 20182182
Coding_consistency_preprocess_data1$Study_Number_N[3243] <- 3

## 20182193
Coding_consistency_preprocess_data1$Study_Number_N[3270] <- 3

## 20185037
Coding_consistency_preprocess_data1$Study_Number_N[3378] <- 3

## 20212172
Coding_consistency_preprocess_data1$Study_Number_N[3546] <- 3

## 20083017
Coding_consistency_preprocess_data1$Study_Number_N[3903] <- 1

## 20082044
Coding_consistency_preprocess_data1$Study_Number_N[4485] <- 1
Coding_consistency_preprocess_data1$Study_Number_N[4488] <- 1  
```


## Subjects Group N
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(Subjects_Group_N = ifelse(Subjects_Group_N == "　",NA,Subjects_Group_N),
                Subjects_Group_N = ifelse(Coder == "check" & is.na(Subjects_Group_N),"Chin_Subj",Subjects_Group_N))

# table(Coding_consistency_preprocess_data1$Subjects_Group_N)

rm(results)


results <- data.frame(Article_IDs_N = character(),
                      Subjects_Group_N_coder1 = as.character(),
                      Subjects_Group_N_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$Subjects_Group_N[i]
  coder2_code <- Coding_consistency_preprocess_data1$Subjects_Group_N[i+1]
  stored_score <- Coding_consistency_preprocess_data1$Subjects_Group_N[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    Coding_consistency_preprocess_data1$Subjects_Group_N[i+2] <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code) || grepl(coder2_code, coder1_code)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     Subjects_Group_N_coder1 = coder1_code,
                                     Subjects_Group_N_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")

## 20083067
Coding_consistency_preprocess_data1$Subjects_Group_N[153] <- 3

## 20083093
Coding_consistency_preprocess_data1$Subjects_Group_N[189] <- 1

## 20181187
Coding_consistency_preprocess_data1$Subjects_Group_N[c(363,366)] <- 3

## 20182268
Coding_consistency_preprocess_data1$Subjects_Group_N[c(420,423,426,429,432,435,438,441,444)] <- 3

## 20082210
Coding_consistency_preprocess_data1$Subjects_Group_N[c(2103,2106,2109)] <- 3

## 20082258
Coding_consistency_preprocess_data1$Subjects_Group_N[c(2154,2157,2160,2163,2166,2169,2172,2175)] <- 3

## 20181005
Coding_consistency_preprocess_data1$Subjects_Group_N[c(2283,2286)] <- 1
Coding_consistency_preprocess_data1$Subjects_Group_N[c(2289,2292,2295,2298)] <- 3

## 20181017
Coding_consistency_preprocess_data1$Subjects_Group_N[c(2325,2328,2331,2334)] <- 3

## 20181023
Coding_consistency_preprocess_data1$Subjects_Group_N[c(2370,2373,2376,2379)] <- 1

## 20182101
Coding_consistency_preprocess_data1$Subjects_Group_N[c(2397,2400,2403,2406,2409,2412,2415,2418)] <- 3

## 20182103
Coding_consistency_preprocess_data1$Subjects_Group_N[2430] <- 3

## 20182117
Coding_consistency_preprocess_data1$Subjects_Group_N[c(2451,2454,2457,2460)] <- 3

## 20182125
Coding_consistency_preprocess_data1$Subjects_Group_N[c(2481,2484)] <- 3

## 20182126
Coding_consistency_preprocess_data1$Subjects_Group_N[c(2496,2499)] <- 3

## 20182131
Coding_consistency_preprocess_data1$Subjects_Group_N[c(2502,2505)] <- 3

## 20183150
Coding_consistency_preprocess_data1$Subjects_Group_N[c(2574,2577)] <- 3

## 20183192
Coding_consistency_preprocess_data1$Subjects_Group_N[c(2634,2637)] <- 1

## 20183198
Coding_consistency_preprocess_data1$Subjects_Group_N[c(2640,2643,2646)] <- 3

## 20181091
Coding_consistency_preprocess_data1$Subjects_Group_N[3948] <- 3

## 20182239
Coding_consistency_preprocess_data1$Subjects_Group_N[4143] <- 3
```


## Article Title
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(Article_Title  = ifelse(Article_Title == "　",NA,Article_Title),
                Article_Title  = ifelse(Coder == "check" & is.na(Article_Title),"Chin_Subj",Article_Title))

# table(Coding_consistency_preprocess_data1$Article_Title)

rm(results)


results <- data.frame(Article_Title= character(),
                      Article_Title_coder1 = as.character(),
                      Article_Title_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$Article_Title[i]
  coder2_code <- Coding_consistency_preprocess_data1$Article_Title[i+1]
  stored_score <- Coding_consistency_preprocess_data1$Article_Title[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code) || grepl(coder2_code, coder1_code)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     Article_Title_coder1 = coder1_code,
                                     Article_Title_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")


## revise check

## 20081070
Coding_consistency_preprocess_data1$Article_Title[21] <- 1

## 20182289
Coding_consistency_preprocess_data1$Article_Title[474] <- 1

## 20082105
Coding_consistency_preprocess_data1$Article_Title[798] <- 3

## 20082296
Coding_consistency_preprocess_data1$Article_Title[2211] <- 3
Coding_consistency_preprocess_data1$Article_Title[2214] <- 3
Coding_consistency_preprocess_data1$Article_Title[2217] <- 3

## 20085035
Coding_consistency_preprocess_data1$Article_Title[2247] <- 3

## 20181002
Coding_consistency_preprocess_data1$Article_Title[2280] <- 3

## 20181008
Coding_consistency_preprocess_data1$Article_Title[2310] <- 3

## 20181011
Coding_consistency_preprocess_data1$Article_Title[2313] <- 3

## 20181017
Coding_consistency_preprocess_data1$Article_Title[2325] <- 3
Coding_consistency_preprocess_data1$Article_Title[2328] <- 3
Coding_consistency_preprocess_data1$Article_Title[2331] <- 3
Coding_consistency_preprocess_data1$Article_Title[2334] <- 3

## 20181020
Coding_consistency_preprocess_data1$Article_Title[2337] <- 3
Coding_consistency_preprocess_data1$Article_Title[2346] <- 3
Coding_consistency_preprocess_data1$Article_Title[2349] <- 3

## 20181022
Coding_consistency_preprocess_data1$Article_Title[c(2352,2355,2358,2361,2364,2367)] <- 3

## 20181023
Coding_consistency_preprocess_data1$Article_Title[c(2370,2373,2376,2379,2382,2385)] <- 3

## 20182104
Coding_consistency_preprocess_data1$Article_Title[c(2445,2448)] <- 3

## 20182125
Coding_consistency_preprocess_data1$Article_Title[c(2481,2484,2487,2490,2493)] <- 3

## 20183052
Coding_consistency_preprocess_data1$Article_Title[4722] <- 3

## 20183054
Coding_consistency_preprocess_data1$Article_Title[4725] <- 3

## 20184022
Coding_consistency_preprocess_data1$Article_Title[c(4770,4773,4776,4779,4782,4785)] <- 3

## 20184127
Coding_consistency_preprocess_data1$Article_Title[1893] <- 3

## 20182103
Coding_consistency_preprocess_data1$Article_Title[c(2421,2424,2427,2430,2433,2436)] <- 3

## 20182075
Coding_consistency_preprocess_data1$Article_Title[2388] <- 3

## 20182085
Coding_consistency_preprocess_data1$Article_Title[2391] <- 3
```


## First Author
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(First_Author  = ifelse(First_Author == "　",NA,First_Author),
                First_Author  = ifelse(Coder == "check" & is.na(First_Author),"Chin_Subj",First_Author))

# table(Coding_consistency_preprocess_data1$First_Author)

rm(results)


results <- data.frame(Article_Title= character(),
                      First_Author_coder1 = as.character(),
                      First_Author_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$First_Author[i]
  coder2_code <- Coding_consistency_preprocess_data1$First_Author[i+1]
  stored_score <- Coding_consistency_preprocess_data1$First_Author[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code) || grepl(coder2_code, coder1_code)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     First_Author_coder1 = coder1_code,
                                     First_Author_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")


###          no found
```


## Journal
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(Journal = ifelse(Journal == "　",NA,Journal),
                Journal = ifelse(Coder == "check" & is.na(Journal),"Chin_Subj",Journal))

# table(Coding_consistency_preprocess_data1$Journal)

rm(results)


results <- data.frame(Article_Title= character(),
                      Journal_coder1 = as.character(),
                      Journal_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$Journal[i]
  coder2_code <- Coding_consistency_preprocess_data1$Journal[i+1]
  stored_score <- Coding_consistency_preprocess_data1$Journal[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code) || grepl(coder2_code, coder1_code)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     Journal_coder1 = coder1_code,
                                     Journal_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")

## 20182248
Coding_consistency_preprocess_data1$Journal[c(375,378,381)] <- 1

## 20181002
Coding_consistency_preprocess_data1$Journal[2280] <- 1

## 20181005
Coding_consistency_preprocess_data1$Journal[c(2283,2286,2289,2292,2295,2298)] <- 1

## 20181007
Coding_consistency_preprocess_data1$Journal[c(2301,2304,2307)] <- 1

## 20181008
Coding_consistency_preprocess_data1$Journal[2310] <- 1

## 20181011
Coding_consistency_preprocess_data1$Journal[2313] <- 1

## 20181015
Coding_consistency_preprocess_data1$Journal[c(2316,2319)] <- 1

## 20181017
Coding_consistency_preprocess_data1$Journal[c(2325,2328,2331,2334)] <- 1

## 20181020
Coding_consistency_preprocess_data1$Journal[c(2337,2346,2349)] <- 1

## 20181022
Coding_consistency_preprocess_data1$Journal[c(2352,2355,2358,2361,2364,2367)] <- 1

## 20183145
Coding_consistency_preprocess_data1$Journal[2568] <- 1

## 20183256
Coding_consistency_preprocess_data1$Journal[3363] <- 3

## 20081043
Coding_consistency_preprocess_data1$Journal[c(3813,3816,3819,3822)] <- 3

## 20081055
Coding_consistency_preprocess_data1$Journal[c(3843,3846)] <- 3

## 20213137
Coding_consistency_preprocess_data1$Journal[c(5040,5043,5046,5049)] <- 1

## 20213153
Coding_consistency_preprocess_data1$Journal[c(5052,5055,5058,5061,5064)] <- 1
```


## Abstract1
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(Abstract1 = ifelse(Abstract1 == "　",NA,Abstract1),
                Abstract1 = ifelse(Coder == "check" & is.na(Abstract1),"Chin_Subj",Abstract1))

# table(Coding_consistency_preprocess_data1$Journal)

rm(results)


results <- data.frame(Article_Title= character(),
                      Abstract1_coder1 = as.character(),
                      Abstract1_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$Abstract1[i]
  coder2_code <- Coding_consistency_preprocess_data1$Abstract1[i+1]
  stored_score <- Coding_consistency_preprocess_data1$Abstract1[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code) || grepl(coder2_code, coder1_code)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     Abstract1_coder1 = coder1_code,
                                     Abstract1_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")

## 20082002
Coding_consistency_preprocess_data1$Abstract1[108] <- 1

## 20083054
Coding_consistency_preprocess_data1$Abstract1[135] <- 1

## 20181178
Coding_consistency_preprocess_data1$Abstract1[c(333,336)] <- 2

## 20182267
Coding_consistency_preprocess_data1$Abstract1[c(414,417)] <- 2

## 20085023
Coding_consistency_preprocess_data1$Abstract1[2232] <- 1

## 20181017
Coding_consistency_preprocess_data1$Abstract1[c(2325,2328,2331,2334)] <- 1

## 20181022
Coding_consistency_preprocess_data1$Abstract1[c(2352,2355,2358,2361,2364,2367)] <- 1

# 20181023
Coding_consistency_preprocess_data1$Abstract1[c(2382,2385)] <- 3

## 20185111
Coding_consistency_preprocess_data1$Abstract1[4269] <- 1

## 20083114
Coding_consistency_preprocess_data1$Abstract1[4506] <- 2

## 20083128
Coding_consistency_preprocess_data1$Abstract1[c(4518,4521)] <- 1

## 20181212
Coding_consistency_preprocess_data1$Abstract1[4611] <- 2

## 20181187
Coding_consistency_preprocess_data1$Abstract1[c(363,366,369)] <- 2

## 20182103
Coding_consistency_preprocess_data1$Abstract1[c(2421,2424,2427,2430,2433,2436)] <- 1

### 20182193
Coding_consistency_preprocess_data1$Abstract1[3270] <- 3

## 20181081
Coding_consistency_preprocess_data1$Abstract1[3174] <- 2

## 20185037
Coding_consistency_preprocess_data1$Abstract1[3378] <- 3

## 20212172
Coding_consistency_preprocess_data1$Abstract1[3546] <- 3

## 20183165
Coding_consistency_preprocess_data1$Abstract1[2592] <- 1

## 20183200
Coding_consistency_preprocess_data1$Abstract1[c(2649,2652,2655,2658)] <- 1
```


## Abstract2
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(Abstract2 = ifelse(Abstract2 == "　",NA,Abstract2),
                Abstract2 = ifelse(Coder == "check" & is.na(Abstract2),"Chin_Subj",Abstract2))

# table(Coding_consistency_preprocess_data1$Abstract2)

rm(results)


results <- data.frame(Article_Title= character(),
                      Abstract2_coder1 = as.character(),
                      Abstract2_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$Abstract2[i]
  coder2_code <- Coding_consistency_preprocess_data1$Abstract2[i+1]
  stored_score <- Coding_consistency_preprocess_data1$Abstract2[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    Coding_consistency_preprocess_data1$Abstract2[i+2] <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code) || grepl(coder2_code, coder1_code)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     Abstract2_coder1 = coder1_code,
                                     Abstract2_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")

## 20181081
Coding_consistency_preprocess_data1$Abstract2[3174] <- 1

## 20182103
Coding_consistency_preprocess_data1$Abstract2[c(2421,2424,2427,2430,2433,2436)] <- 1

## 20182183
Coding_consistency_preprocess_data1$Abstract2[c(3252,3255)] <- 1

## 20183200
Coding_consistency_preprocess_data1$Abstract2[c(2649,2652)] <- 1

## 20183226
Coding_consistency_preprocess_data1$Abstract2[c(3318,3321,3324,3327)] <- 1

## 20183227
Coding_consistency_preprocess_data1$Abstract2[3330] <- 1

## 20215007
Coding_consistency_preprocess_data1$Abstract2[c(3624,3627)] <- 1

## 20215042
Coding_consistency_preprocess_data1$Abstract2[3666] <- 1

## 20185111
Coding_consistency_preprocess_data1$Abstract2[4269] <- 1

## 20183324
Coding_consistency_preprocess_data1$Abstract2[513] <- 1 
```


## Remark1 N
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(Remark1_N = ifelse(Remark1_N == "　",NA,Remark1_N),
                Remark1_N = ifelse(Coder == "check" & is.na(Remark1_N),"Chin_Subj",Remark1_N))

# table(Coding_consistency_preprocess_data1$Remark1_N)

rm(results)


results <- data.frame(Article_Title= character(),
                      Remark1_N_coder1 = as.character(),
                      Remark1_N_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$Remark1_N[i]
  coder2_code <- Coding_consistency_preprocess_data1$Remark1_N[i+1]
  stored_score <- Coding_consistency_preprocess_data1$Remark1_N[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    Coding_consistency_preprocess_data1$Remark1_N[i+2] <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code) || grepl(coder2_code, coder1_code)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     Remark1_N_coder1 = coder1_code,
                                     Remark1_N_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")


## NO FOUND
```


## Remark2 N
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(Remark2_N = ifelse(Remark2_N == "　",NA,Remark2_N),
                Remark2_N = ifelse(Coder == "check" & is.na(Remark1_N),"Chin_Subj",Remark2_N))

# table(Coding_consistency_preprocess_data1$Remark2_N)

rm(results)


results <- data.frame(Article_Title= character(),
                      Remark2_N_coder1 = as.character(),
                      Remark2_N_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$Remark2_N[i]
  coder2_code <- Coding_consistency_preprocess_data1$Remark2_N[i+1]
  stored_score <- Coding_consistency_preprocess_data1$Remark2_N[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    Coding_consistency_preprocess_data1$Remark2_N[i+2] <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code) || grepl(coder2_code, coder1_code)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     Remark2_N_coder1 = coder1_code,
                                     Remark2_N_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")

## NO FOUND
```


## Study Type
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(Study_Type = ifelse(Study_Type == "　",NA,Study_Type),
                Study_Type = ifelse(Coder == "check" & is.na(Study_Type),"Chin_Subj",Study_Type))

# table(Coding_consistency_preprocess_data1$Remark1_N)

rm(results)


results <- data.frame(Article_Title= character(),
                      Study_Type_coder1 = as.character(),
                      Study_Type_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$Study_Type[i]
  coder2_code <- Coding_consistency_preprocess_data1$Study_Type[i+1]
  stored_score <- Coding_consistency_preprocess_data1$Study_Type[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    Coding_consistency_preprocess_data1$Study_Type[i+2] <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code) || grepl(coder2_code, coder1_code)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     Study_Type_coder1 = coder1_code,
                                     Study_Type_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")

## 20081026
Coding_consistency_preprocess_data1$Study_Type[3762] <- 1

## 20185007
Coding_consistency_preprocess_data1$Study_Type[c(2706,2709,2712,2715)] <- 1

## 20085040
Coding_consistency_preprocess_data1$Study_Type[c(2253,2256,2259)] <- 1

## 20085054
Coding_consistency_preprocess_data1$Study_Type[c(2271,2274,2277)] <- 1

## 20181152
Coding_consistency_preprocess_data1$Study_Type[c(285,291)] <- 1

## 20182261
Coding_consistency_preprocess_data1$Study_Type[405] <- 1

## 20182268
Coding_consistency_preprocess_data1$Study_Type[c(423,426)] <- 1

## 20182275
Coding_consistency_preprocess_data1$Study_Type[453] <- 1

## 20182283
Coding_consistency_preprocess_data1$Study_Type[c(465,468)] <- 1

## 20182297
Coding_consistency_preprocess_data1$Study_Type[477] <- 1

## 20183314
Coding_consistency_preprocess_data1$Study_Type[c(489,492)] <- 1

## 20183321
Coding_consistency_preprocess_data1$Study_Type[c(498,501,504,507)] <- 1

## 20185007
Coding_consistency_preprocess_data1$Study_Type[c(2706,2709,2712,2715)] <- 1

## 20185030
Coding_consistency_preprocess_data1$Study_Type[2754] <- 1

## 20082365
Coding_consistency_preprocess_data1$Study_Type[3033] <- 2
```


## Sample Size
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(Sample_Size = ifelse(Sample_Size == "　",NA,Sample_Size),
                Sample_Size = ifelse(Coder == "check" & is.na(Sample_Size),"Chin_Subj",Sample_Size))

# table(Coding_consistency_preprocess_data1$Sample_Size)

rm(results)


results <- data.frame(Article_Title= character(),
                      Sample_Size_coder1 = as.character(),
                      Sample_Size_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$Sample_Size[i]
  coder2_code <- Coding_consistency_preprocess_data1$Sample_Size[i+1]
  stored_score <- Coding_consistency_preprocess_data1$Sample_Size[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    Coding_consistency_preprocess_data1$Sample_Size[i+2] <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code) || grepl(coder2_code, coder1_code)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     Sample_Size_coder1 = coder1_code,
                                     Sample_Size_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")

## 20083058
Coding_consistency_preprocess_data1$Sample_Size[141] <- 1

## 20181152
Coding_consistency_preprocess_data1$Sample_Size[c(288,291)] <- 1

## 20183312
Coding_consistency_preprocess_data1$Sample_Size[486] <- 1

## 20183321
Coding_consistency_preprocess_data1$Sample_Size[c(498,501,504,507)] <- 1

## 20082061
Coding_consistency_preprocess_data1$Sample_Size[744] <- 1

## 20082262
Coding_consistency_preprocess_data1$Sample_Size[2178] <- 1

## 20082283
Coding_consistency_preprocess_data1$Sample_Size[2202] <- 1

## 20085044
Coding_consistency_preprocess_data1$Sample_Size[2265] <- 1

## 20181023
Coding_consistency_preprocess_data1$Sample_Size[c(2370,2373)] <- 1

## 20182101
Coding_consistency_preprocess_data1$Sample_Size[2409] <- 1

## 20182103
Coding_consistency_preprocess_data1$Sample_Size[c(2427,2430,2433,2436,2439,2442)] <- 1

## 20183178
Coding_consistency_preprocess_data1$Sample_Size[2613] <- 1

## 20183192
Coding_consistency_preprocess_data1$Sample_Size[c(2634,2637)] <- 1

## 20081026
Coding_consistency_preprocess_data1$Sample_Size[c(3762)] <- 1

## 20215075
Coding_consistency_preprocess_data1$Sample_Size[4386] <- 1

## 20082023
Coding_consistency_preprocess_data1$Sample_Size[4446] <- 1

## 20083114
Coding_consistency_preprocess_data1$Sample_Size[4506] <- 1
```


## Gender
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(Gender = ifelse(Gender == "　",NA,Gender),
                Gender = ifelse(Coder == "check" & is.na(Gender),"Chin_Subj",Gender))

# table(Coding_consistency_preprocess_data1$Gender)

rm(results)


results <- data.frame(Article_Title= character(),
                      Gender_coder1 = as.character(),
                      Gender_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$Gender[i]
  coder2_code <- Coding_consistency_preprocess_data1$Gender[i+1]
  stored_score <- Coding_consistency_preprocess_data1$Gender[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    Coding_consistency_preprocess_data1$Gender[i+2] <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code) || grepl(coder2_code, coder1_code)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     Gender_coder1 = coder1_code,
                                     Gender_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")


## 20182248
Coding_consistency_preprocess_data1$Gender[c(375,378,381)] <- 1

## 20182268
Coding_consistency_preprocess_data1$Gender[438] <- 1

## 20183192
Coding_consistency_preprocess_data1$Gender[c(2634,2637)] <- 1

## 20183198
Coding_consistency_preprocess_data1$Gender[c(2640,2643,2646)] <- 1
```


## Female Num
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(Female_Num = ifelse(Female_Num == "　",NA,Female_Num),
                Female_Num = ifelse(Coder == "check" & is.na(Female_Num),"Chin_Subj",Female_Num))

# table(Coding_consistency_preprocess_data1$Female_Num)

rm(results)


results <- data.frame(Article_Title= character(),
                      Female_Num_coder1 = as.character(),
                      Female_Num_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$Female_Num[i]
  coder2_code <- Coding_consistency_preprocess_data1$Female_Num[i+1]
  stored_score <- Coding_consistency_preprocess_data1$Female_Num[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    Coding_consistency_preprocess_data1$Female_Num[i+2] <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code) || grepl(coder2_code, coder1_code)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     Female_Num_coder1 = coder1_code,
                                     Female_Num_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")

## 20081099
Coding_consistency_preprocess_data1$Female_Num[51] <- 3

## 20181166
Coding_consistency_preprocess_data1$Female_Num[309] <- 1

## 20182248
Coding_consistency_preprocess_data1$Female_Num[c(375,378,381)] <- 1

## 20182267
Coding_consistency_preprocess_data1$Female_Num[414] <- 1

## 20182289
Coding_consistency_preprocess_data1$Female_Num[474] <- 1

## 20183321
Coding_consistency_preprocess_data1$Female_Num[c(504,507)] <- 1

## 20183333
Coding_consistency_preprocess_data1$Female_Num[543] <- 1

## 20082105
Coding_consistency_preprocess_data1$Female_Num[c(786,789,792,795,798,801)] <- 1

## 20182035
Coding_consistency_preprocess_data1$Female_Num[c(1665,1668)] <- 1

## 20183107
Coding_consistency_preprocess_data1$Female_Num[1776] <- 1

## 20214015
Coding_consistency_preprocess_data1$Female_Num[2070] <- 1

## 20082279
Coding_consistency_preprocess_data1$Female_Num[2187] <- 1

## 20181007
Coding_consistency_preprocess_data1$Female_Num[2301] <- 1

## 20182101
Coding_consistency_preprocess_data1$Female_Num[2409] <- 1

## 20182103
Coding_consistency_preprocess_data1$Female_Num[c(2430,2433,2436,2439,2442)] <- 1

## 20185003
Coding_consistency_preprocess_data1$Female_Num[c(2697,2700)] <- 1

## 20183226
Coding_consistency_preprocess_data1$Female_Num[3321] <- 1

## 20083007
Coding_consistency_preprocess_data1$Female_Num[3894] <- 1

## 20181104
Coding_consistency_preprocess_data1$Female_Num[3987] <- 1

## 20082030
Coding_consistency_preprocess_data1$Female_Num[4467] <- 1

## 20083112
Coding_consistency_preprocess_data1$Female_Num[4500] <- 1

## 20083114
Coding_consistency_preprocess_data1$Female_Num[4506] <- 1

## 20181212
Coding_consistency_preprocess_data1$Female_Num[c(4608,4611)] <- 1
```


## Male Num
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(Male_Num = ifelse(Male_Num == "　",NA,Male_Num),
                Male_Num = ifelse(Coder == "check" & is.na(Male_Num),"Chin_Subj",Male_Num))

# table(Coding_consistency_preprocess_data1$Male_Num)

rm(results)


results <- data.frame(Article_Title= character(),
                      Male_Num_coder1 = as.character(),
                      Male_Num_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$Male_Num[i]
  coder2_code <- Coding_consistency_preprocess_data1$Male_Num[i+1]
  stored_score <- Coding_consistency_preprocess_data1$Male_Num[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    Coding_consistency_preprocess_data1$Male_Num[i+2] <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code) || grepl(coder2_code, coder1_code)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     Male_Num_coder1 = coder1_code,
                                     Male_Num_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")


## 20081099
Coding_consistency_preprocess_data1$Male_Num[51] <- 3

## 20081102
Coding_consistency_preprocess_data1$Male_Num[54] <-  1

## 20181166
Coding_consistency_preprocess_data1$Male_Num[309] <- 1

## 20181178
Coding_consistency_preprocess_data1$Male_Num[c(333,336)] <- 1

## 20182248
Coding_consistency_preprocess_data1$Male_Num[c(375,378,381)] <- 1

## 20182257
Coding_consistency_preprocess_data1$Male_Num[390] <- 1

## 20182267
Coding_consistency_preprocess_data1$Male_Num[417] <- 1

## 20183321
Coding_consistency_preprocess_data1$Male_Num[c(498,501)] <- 1

## 20082105
Coding_consistency_preprocess_data1$Male_Num[c(786,789,792,795,798,801)] <- 1

## 20211040
Coding_consistency_preprocess_data1$Male_Num[1278] <- 1

## 20214015
Coding_consistency_preprocess_data1$Male_Num[2070] <- 1

## 20082279
Coding_consistency_preprocess_data1$Male_Num[2187] <- 1

## 20082283
Coding_consistency_preprocess_data1$Male_Num[2202] <- 1

## 20181007
Coding_consistency_preprocess_data1$Male_Num[2301] <- 1

## 20181023
Coding_consistency_preprocess_data1$Male_Num[c(2370,2373)] <- 1

## 20182103
Coding_consistency_preprocess_data1$Male_Num[c(2439,2442)] <- 1

## 20182137
Coding_consistency_preprocess_data1$Male_Num[c(2514,2517)] <- 1

## 20185003
Coding_consistency_preprocess_data1$Male_Num[c(2697,2700)] <- 1

## 20083007
Coding_consistency_preprocess_data1$Male_Num[3894] <- 1

## 20082030
Coding_consistency_preprocess_data1$Male_Num[4467] <- 1

## 20083112
Coding_consistency_preprocess_data1$Male_Num[4500] <- 1

## 20083114
Coding_consistency_preprocess_data1$Male_Num[4506] <- 1

## 20181212
Coding_consistency_preprocess_data1$Male_Num[c(4608,4611)] <- 1
```


## Age
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(Age = ifelse(Age == "　",NA,Age),
                Age = ifelse(Coder == "check" & is.na(Age),"Chin_Subj",Age))

# table(Coding_consistency_preprocess_data1$Age)

rm(results)


results <- data.frame(Article_Title= character(),
                      Age_coder1 = as.character(),
                      Age_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$Age[i]
  coder2_code <- Coding_consistency_preprocess_data1$Age[i+1]
  stored_score <- Coding_consistency_preprocess_data1$Age[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    Coding_consistency_preprocess_data1$Age[i+2] <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code) || grepl(coder2_code, coder1_code)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     Age_coder1 = coder1_code,
                                     Age_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")

## 20181152
Coding_consistency_preprocess_data1$Age[c(288,291)] <- 1

## 20213091
Coding_consistency_preprocess_data1$Age[678] <- 1

## 20181023
Coding_consistency_preprocess_data1$Age[c(2370,2373,2376,2379,2382,2385)] <- 1

## 20182118
Coding_consistency_preprocess_data1$Age[c(2463,2466,2469,2472)] <- 1

## 20182153
Coding_consistency_preprocess_data1$Age[2559] <- 1

## 20183154
Coding_consistency_preprocess_data1$Age[2580] <- 1

## 20183171
Coding_consistency_preprocess_data1$Age[2607] <- 1

## 20183198
Coding_consistency_preprocess_data1$Age[c(2640,2643,2646)] <- 1

## 20213153
Coding_consistency_preprocess_data1$Age[c(5052,5055)] <- 1

```


## M_age
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(M_age = ifelse(M_age == "　",NA,M_age),
                M_age = ifelse(Coder == "check" & is.na(M_age),"Chin_Subj",M_age))

# table(Coding_consistency_preprocess_data1$M_age)

rm(results)


results <- data.frame(Article_Title= character(),
                      M_age_coder1 = as.character(),
                      M_age_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$M_age[i]
  coder2_code <- Coding_consistency_preprocess_data1$M_age[i+1]
  stored_score <- Coding_consistency_preprocess_data1$M_age[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    Coding_consistency_preprocess_data1$M_age[i+2] <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code) || grepl(coder2_code, coder1_code)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     M_age_coder1 = coder1_code,
                                     M_age_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")

## 20081061
Coding_consistency_preprocess_data1$M_age[3] <- 1

## 20081124
Coding_consistency_preprocess_data1$M_age[c(69,72,75,78)] <- 1

## 20184045
Coding_consistency_preprocess_data1$M_age[1170] <- 3

## 20213254
Coding_consistency_preprocess_data1$M_age[1479] <- 3

## 20213296
Coding_consistency_preprocess_data1$M_age[2043] <- 3

## 20215102
Coding_consistency_preprocess_data1$M_age[2097] <- 3

### 20085044
Coding_consistency_preprocess_data1$M_age[c(2262,2265,2268)] <- 1

## 20181007
Coding_consistency_preprocess_data1$M_age[c(2301,2304,2307)] <- 1

## 20181022
Coding_consistency_preprocess_data1$M_age[c(2352,2358)] <- 1

## 20183182
Coding_consistency_preprocess_data1$M_age[2616] <- 1

## 20185001
Coding_consistency_preprocess_data1$M_age[c(2688,2691,2694)] <- 3

## 20212091
Coding_consistency_preprocess_data1$M_age[2787] <- 1

## 20214070
Coding_consistency_preprocess_data1$M_age[2931] <- 3

## 20214073
Coding_consistency_preprocess_data1$M_age[2937] <- 3

## 20182184
Coding_consistency_preprocess_data1$M_age[3258] <- 1

## 20083114
Coding_consistency_preprocess_data1$M_age[4506] <- 1

## 20083052
Coding_consistency_preprocess_data1$M_age[132] <- 1
```


## SD_age
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(SD_age = ifelse(SD_age == "　",NA,SD_age),
                SD_age = ifelse(Coder == "check" & is.na(SD_age),"Chin_Subj",SD_age))

# table(Coding_consistency_preprocess_data1$SD_age)

rm(results)


results <- data.frame(Article_Title= character(),
                      SD_age_coder1 = as.character(),
                      SD_age_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$SD_age[i]
  coder2_code <- Coding_consistency_preprocess_data1$SD_age[i+1]
  stored_score <- Coding_consistency_preprocess_data1$SD_age[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    Coding_consistency_preprocess_data1$SD_age[i+2] <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code) || grepl(coder2_code, coder1_code)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     SD_age_coder1 = coder1_code,
                                     SD_age_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")

## 20081061
Coding_consistency_preprocess_data1$SD_age[3] <- 1

## 20081124
Coding_consistency_preprocess_data1$SD_age[c(69,72,75,78)] <- 1

## 20083052
Coding_consistency_preprocess_data1$SD_age[132] <- 1

## 20083058
Coding_consistency_preprocess_data1$SD_age[141] <- 1

## 20181143
Coding_consistency_preprocess_data1$SD_age[252] <- 1

## 20182267
Coding_consistency_preprocess_data1$SD_age[c(414,417)] <- 1

## 20182268
Coding_consistency_preprocess_data1$SD_age[444] <- 1

## 20183336
Coding_consistency_preprocess_data1$SD_age[552] <- 3

## 20213296
Coding_consistency_preprocess_data1$SD_age[2043] <- 1

## 20085044
Coding_consistency_preprocess_data1$SD_age[c(2262,2265,2268)] <- 1

## 20181002
Coding_consistency_preprocess_data1$SD_age[2280] <- 1

## 20181007
Coding_consistency_preprocess_data1$SD_age[c(2301,2304,2307)] <- 1

## 20183182
Coding_consistency_preprocess_data1$SD_age[2616] <- 1

## 20185001
Coding_consistency_preprocess_data1$SD_age[c(2688,2691,2694)] <- 3

## 20214070
Coding_consistency_preprocess_data1$SD_age[2931] <- 3

## 20214073
Coding_consistency_preprocess_data1$SD_age[2937] <- 3

## 20181207
Coding_consistency_preprocess_data1$SD_age[4578] <- 1

```


## Other age
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(Other_age = ifelse(SD_age == "　",NA,Other_age),
                Other_age = ifelse(Other_age == "check" & is.na(Other_age),"Chin_Subj",Other_age))

# table(Coding_consistency_preprocess_data1$Other_age)

rm(results)


results <- data.frame(Article_Title= character(),
                      Other_age_coder1 = as.character(),
                      Other_age_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$Other_age[i]
  coder2_code <- Coding_consistency_preprocess_data1$Other_age[i+1]
  stored_score <- Coding_consistency_preprocess_data1$Other_age[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    Coding_consistency_preprocess_data1$Other_age[i+2] <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code) || grepl(coder2_code, coder1_code)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     Other_age_coder1 = coder1_code,
                                     Other_age_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")

## 20081088
Coding_consistency_preprocess_data1$Other_age[36] <- 1

## 20081104
Coding_consistency_preprocess_data1$Other_age[57] <- 1

## 20182263
Coding_consistency_preprocess_data1$Other_age[408] <- 1

## 20184130
Coding_consistency_preprocess_data1$Other_age[1899] <- 1

## 20184137
Coding_consistency_preprocess_data1$Other_age[1902] <- 1

## 20212034
Coding_consistency_preprocess_data1$Other_age[c(1956,1959,1962)] <- 1

## 20182035
Coding_consistency_preprocess_data1$Other_age[1665] <- 1

## 20085029
Coding_consistency_preprocess_data1$Other_age[2235] <- 3

## 20181008
Coding_consistency_preprocess_data1$Other_age[2310] <- 3

## 20183171
Coding_consistency_preprocess_data1$Other_age[2607] <- 3

## 20183182
Coding_consistency_preprocess_data1$Other_age[c(2619,2622)] <- 3

## 20184149
Coding_consistency_preprocess_data1$Other_age[2664] <- 3

## 20182183
Coding_consistency_preprocess_data1$Other_age[3252] <- 1

## 20081026
Coding_consistency_preprocess_data1$Other_age[c(3762,3765)] <- 1
```


## Ethnicity
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(Ethnicity = ifelse(Ethnicity == "　",NA,Ethnicity),
                Ethnicity = ifelse(Ethnicity == "check" & is.na(Ethnicity),"Chin_Subj",Ethnicity))

# table(Coding_consistency_preprocess_data1$Ethnicity)

rm(results)


results <- data.frame(Article_Title= character(),
                      Ethnicity_coder1 = as.character(),
                      Ethnicity_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$Ethnicity[i]
  coder2_code <- Coding_consistency_preprocess_data1$Ethnicity[i+1]
  stored_score <- Coding_consistency_preprocess_data1$Ethnicity[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    Coding_consistency_preprocess_data1$Ethnicity[i+2] <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code) || grepl(coder2_code, coder1_code)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     Ethnicity_coder1 = coder1_code,
                                     Ethnicity_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")


## 20083079
Coding_consistency_preprocess_data1$Ethnicity[171] <- 1

## 20181152
Coding_consistency_preprocess_data1$Ethnicity[c(288,291)] <- 1

## 20182248
Coding_consistency_preprocess_data1$Ethnicity[c(375,378,381)] <- 1

## 20181017
Coding_consistency_preprocess_data1$Ethnicity[c(2331,2334)] <- 1

## 20083173
Coding_consistency_preprocess_data1$Ethnicity[4551] <- 1
```


## Ethnicity_info
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(Ethnicity_info = ifelse(Ethnicity_info == "　",NA,Ethnicity_info),
                Ethnicity_info = ifelse(Ethnicity_info == "check" & is.na(Ethnicity_info),"Chin_Subj",Ethnicity_info))

# table(Coding_consistency_preprocess_data1$Ethnicity_info)

rm(results)


results <- data.frame(Article_Title= character(),
                      Ethnicity_info_coder1 = as.character(),
                      Ethnicity_info_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$Ethnicity_info[i]
  coder2_code <- Coding_consistency_preprocess_data1$Ethnicity_info[i+1]
  stored_score <- Coding_consistency_preprocess_data1$Ethnicity_info[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    Coding_consistency_preprocess_data1$Ethnicity_info[i+2] <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code) || grepl(coder2_code, coder1_code)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     Ethnicity_info_coder1 = coder1_code,
                                     Ethnicity_info_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")

## 20181146
Coding_consistency_preprocess_data1$Ethnicity_info[267] <- 1

## 20181022
Coding_consistency_preprocess_data1$Ethnicity_info[2364] <- 1

## 20181023
Coding_consistency_preprocess_data1$Ethnicity_info[c(2370,2373,2376,2379)] <- 1
```


## Religious
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(Religious = ifelse(Religious == "　",NA,Religious),
                Religious = ifelse(Religious == "check" & is.na(Religious),"Chin_Subj",Religious))

# table(Coding_consistency_preprocess_data1$Religious)

rm(results)


results <- data.frame(Article_Title= character(),
                      Religious_coder1 = as.character(),
                      Religious_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$Religious[i]
  coder2_code <- Coding_consistency_preprocess_data1$Religious[i+1]
  stored_score <- Coding_consistency_preprocess_data1$Religious[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    Coding_consistency_preprocess_data1$Religious[i+2] <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code) || grepl(coder2_code, coder1_code)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     Religious_coder1 = coder1_code,
                                     Religious_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")

## 20181152
Coding_consistency_preprocess_data1$Religious[c(288,291)] <- 1
```


## Religious_info
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(Religious_info = ifelse(Religious_info == "　",NA,Religious_info),
                Religious_info = ifelse(Religious_info == "check" & is.na(Religious_info),"Chin_Subj",Religious_info))

# table(Coding_consistency_preprocess_data1$Religious_info)

rm(results)


results <- data.frame(Article_Title= character(),
                      Religious_info_coder1 = as.character(),
                      Religious_info_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$Religious_info[i]
  coder2_code <- Coding_consistency_preprocess_data1$Religious_info[i+1]
  stored_score <- Coding_consistency_preprocess_data1$Religious_info[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    Coding_consistency_preprocess_data1$Religious_info[i+2] <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code) || grepl(coder2_code, coder1_code)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     Religious_info_coder1 = coder1_code,
                                     Religious_info_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")

## no found
```


## Subjects_Area
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(Subjects_Area = ifelse(Subjects_Area == "　",NA,Subjects_Area),
                Subjects_Area = ifelse(Subjects_Area == "check" & is.na(Subjects_Area),"Chin_Subj",Subjects_Area))

# table(Coding_consistency_preprocess_data1$Subjects_Area)

rm(results)


results <- data.frame(Article_Title= character(),
                      Subjects_Area_coder1 = as.character(),
                      Subjects_Area_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$Subjects_Area[i]
  coder2_code <- Coding_consistency_preprocess_data1$Subjects_Area[i+1]
  stored_score <- Coding_consistency_preprocess_data1$Subjects_Area[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    Coding_consistency_preprocess_data1$Subjects_Area[i+2] <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code) || grepl(coder2_code, coder1_code)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     Subjects_Area_coder1 = coder1_code,
                                     Subjects_Area_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")

## 20181152
Coding_consistency_preprocess_data1$Subjects_Area[c(288,291)] <- 1

## 20082296
Coding_consistency_preprocess_data1$Subjects_Area[c(2211,2214,2217)] <- 1

## 20082298
Coding_consistency_preprocess_data1$Subjects_Area[2220] <- 1

## 20085035
Coding_consistency_preprocess_data1$Subjects_Area[2247] <- 1

## 20085044
Coding_consistency_preprocess_data1$Subjects_Area[c(2262,2265,2268)] <- 1

## 20185124
Coding_consistency_preprocess_data1$Subjects_Area[4284] <- 3
```


## Subjects_Area_info
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(Subjects_Area_info = ifelse(Subjects_Area_info == "　",NA,Subjects_Area_info),
                Subjects_Area_info = ifelse(Subjects_Area_info == "check" & is.na(Subjects_Area_info),"Chin_Subj",Subjects_Area_info))

# table(Coding_consistency_preprocess_data1$Subjects_Area_info)

rm(results)


results <- data.frame(Article_Title= character(),
                      Subjects_Area_info_coder1 = as.character(),
                      Subjects_Area_info_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$Subjects_Area_info[i]
  coder2_code <- Coding_consistency_preprocess_data1$Subjects_Area_info[i+1]
  stored_score <- Coding_consistency_preprocess_data1$Subjects_Area_info[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    Coding_consistency_preprocess_data1$Subjects_Area_info[i+2] <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code) || grepl(coder2_code, coder1_code)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     Subjects_Area_info_coder1 = coder1_code,
                                     Subjects_Area_info_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")

## 20213190
Coding_consistency_preprocess_data1$Subjects_Area_info[4953] <- 1

```


## Subjects_Recruitment_Area
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(Subjects_Recruitment_Area = ifelse(Subjects_Recruitment_Area == "　",NA,Subjects_Recruitment_Area),
                Subjects_Recruitment_Area = ifelse(Subjects_Recruitment_Area == "check" & is.na(Subjects_Recruitment_Area),"Chin_Subj",Subjects_Recruitment_Area))

# table(Coding_consistency_preprocess_data1$Subjects_Recruitment_Area)

rm(results)


results <- data.frame(Article_Title= character(),
                      Subjects_Recruitment_Area_info_coder1 = as.character(),
                      Subjects_Recruitment_Area_info_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$Subjects_Recruitment_Area[i]
  coder2_code <- Coding_consistency_preprocess_data1$Subjects_Recruitment_Area[i+1]
  stored_score <- Coding_consistency_preprocess_data1$Subjects_Recruitment_Area[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    Coding_consistency_preprocess_data1$Subjects_Recruitment_Area[i+2] <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code) || grepl(coder2_code, coder1_code)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     Subjects_Recruitment_Area_info_coder1 = coder1_code,
                                     Subjects_Recruitment_Area_info_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")

## 20083076
Coding_consistency_preprocess_data1$Subjects_Recruitment_Area[165] <- 1

## 20181152
Coding_consistency_preprocess_data1$Subjects_Recruitment_Area[c(288,291)] <- 1

## 20182265
Coding_consistency_preprocess_data1$Subjects_Recruitment_Area[411] <- 2

## 20182205
Coding_consistency_preprocess_data1$Subjects_Recruitment_Area[4095] <- 3

## 20182204
Coding_consistency_preprocess_data1$Subjects_Recruitment_Area[4092] <- 3

## 20081029
Coding_consistency_preprocess_data1$Subjects_Recruitment_Area[3786] <- 3

## 20081007
Coding_consistency_preprocess_data1$Subjects_Recruitment_Area[3735] <- 3

## 20183229
Coding_consistency_preprocess_data1$Subjects_Recruitment_Area[3336] <- 1

## 20183221
Coding_consistency_preprocess_data1$Subjects_Recruitment_Area[3312] <- 3

## 20183198
Coding_consistency_preprocess_data1$Subjects_Recruitment_Area[c(2640,2643,2646)] <- 1

## 20183192
Coding_consistency_preprocess_data1$Subjects_Recruitment_Area[c(2634,2637)] <- 1

## 20181023
Coding_consistency_preprocess_data1$Subjects_Recruitment_Area[c(2370,2373,2376,2379,2382,2385)] <- 3

## 20085044
Coding_consistency_preprocess_data1$Subjects_Recruitment_Area[c(2262,2265,2268)] <- 1

## 20085035
Coding_consistency_preprocess_data1$Subjects_Recruitment_Area[2247] <- 3

## 20082251
Coding_consistency_preprocess_data1$Subjects_Recruitment_Area[c(2145,2148,2151)] <- 1

## 20082248
Coding_consistency_preprocess_data1$Subjects_Recruitment_Area[c(2139,2142)] <- 1

## 20082240
Coding_consistency_preprocess_data1$Subjects_Recruitment_Area[2136] <- 1

## 20082237
Coding_consistency_preprocess_data1$Subjects_Recruitment_Area[2133] <- 1

## 20082236
Coding_consistency_preprocess_data1$Subjects_Recruitment_Area[2130] <- 1

## 20082229
Coding_consistency_preprocess_data1$Subjects_Recruitment_Area[2121] <- 1

## 20082227
Coding_consistency_preprocess_data1$Subjects_Recruitment_Area[c(2112,2115,2118)] <- 1

## 20214010
Coding_consistency_preprocess_data1$Subjects_Recruitment_Area[2064] <- 3

## 20212056
Coding_consistency_preprocess_data1$Subjects_Recruitment_Area[1980] <- 3

## 20183326
Coding_consistency_preprocess_data1$Subjects_Recruitment_Area[c(516,519)] <- 3

## 20182298
Coding_consistency_preprocess_data1$Subjects_Recruitment_Area[480] <- 3

## 20182297
Coding_consistency_preprocess_data1$Subjects_Recruitment_Area[477] <- 3

## 20182289
Coding_consistency_preprocess_data1$Subjects_Recruitment_Area[474] <- 3

## 20182287
Coding_consistency_preprocess_data1$Subjects_Recruitment_Area[471] <- 3

## 20185141
Coding_consistency_preprocess_data1$Subjects_Recruitment_Area[597] <- 1
```


## Sampling_Method 
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(Sampling_Method = ifelse(Sampling_Method == "　",NA,Sampling_Method),
                Sampling_Method = ifelse(Sampling_Method == "check" & is.na(Sampling_Method),"Chin_Subj",Sampling_Method))

# table(Coding_consistency_preprocess_data1$Sampling_Method)

rm(results)


results <- data.frame(Article_Title= character(),
                      Sampling_Method_coder1 = as.character(),
                      Sampling_Method_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$Sampling_Method[i]
  coder2_code <- Coding_consistency_preprocess_data1$Sampling_Method[i+1]
  stored_score <- Coding_consistency_preprocess_data1$Sampling_Method[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    Coding_consistency_preprocess_data1$Sampling_Method[i+2] <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code) || grepl(coder2_code, coder1_code)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     Sampling_Method_coder1 = coder1_code,
                                     Sampling_Method_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")

## 20181152
Coding_consistency_preprocess_data1$Sampling_Method[c(288,291)] <- 1

## 20181176
Coding_consistency_preprocess_data1$Sampling_Method[324] <- 1

## 20181187
Coding_consistency_preprocess_data1$Sampling_Method[369] <- 1

## 20182248
Coding_consistency_preprocess_data1$Sampling_Method[c(375,378,381)] <- 1

## 20182268
Coding_consistency_preprocess_data1$Sampling_Method[444] <- 3

## 20182297
Coding_consistency_preprocess_data1$Sampling_Method[477] <- 1

## 20183321
Coding_consistency_preprocess_data1$Sampling_Method[c(498,501,504,507)] <- 1

## 20185166
Coding_consistency_preprocess_data1$Sampling_Method[624] <- 1

## 20082112
Coding_consistency_preprocess_data1$Sampling_Method[816] <- 1

## 20082296
Coding_consistency_preprocess_data1$Sampling_Method[c(2211,2214,2217)] <- 1

## 20082298
Coding_consistency_preprocess_data1$Sampling_Method[2220] <- 1

## 20182138
Coding_consistency_preprocess_data1$Sampling_Method[c(2520,2523)] <- 1

## 20183149
Coding_consistency_preprocess_data1$Sampling_Method[2571] <- 1

## 20183167
Coding_consistency_preprocess_data1$Sampling_Method[c(2598,2601)] <- 1

## 20183188
Coding_consistency_preprocess_data1$Sampling_Method[2625] <- 1

## 20185007
Coding_consistency_preprocess_data1$Sampling_Method[c(2706,2709,2712,2715)] <- 1

## 20214053
Coding_consistency_preprocess_data1$Sampling_Method[2901] <- 1

## 20182180
Coding_consistency_preprocess_data1$Sampling_Method[3240] <- 1

## 20183229
Coding_consistency_preprocess_data1$Sampling_Method[3333] <- 1
Coding_consistency_preprocess_data1$Sampling_Method[3336] <- 3

## 20081026
Coding_consistency_preprocess_data1$Sampling_Method[3762] <- 1

## 20181083
Coding_consistency_preprocess_data1$Sampling_Method[3939] <- 1
```


## Target_Population_N
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(Target_Population_N = ifelse(Target_Population_N == "　",NA,Target_Population_N),
                Target_Population_N = ifelse(Target_Population_N == "check" & is.na(Target_Population_N),"Chin_Subj",Target_Population_N))

# table(Coding_consistency_preprocess_data1$Target_Population_N)

rm(results)


results <- data.frame(Article_Title= character(),
                      Target_Population_N_coder1 = as.character(),
                      Target_Population_N_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$Target_Population_N[i]
  coder2_code <- Coding_consistency_preprocess_data1$Target_Population_N[i+1]
  stored_score <- Coding_consistency_preprocess_data1$Target_Population_N[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    Coding_consistency_preprocess_data1$Target_Population_N[i+2] <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code) || grepl(coder2_code, coder1_code)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     Target_Population_N_coder1 = coder1_code,
                                     Target_Population_N_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")

## 20182267
Coding_consistency_preprocess_data1$Target_Population_N[414] <- 1

## 20213098
Coding_consistency_preprocess_data1$Target_Population_N[681] <- 1

## 20215077
Coding_consistency_preprocess_data1$Target_Population_N[723] <- 1

## 20182051
Coding_consistency_preprocess_data1$Target_Population_N[1704] <- 1

## 20082236
Coding_consistency_preprocess_data1$Target_Population_N[2130] <- 1

## 20185026
Coding_consistency_preprocess_data1$Target_Population_N[2751] <- 1

## 20212148
Coding_consistency_preprocess_data1$Target_Population_N[2856] <- 1

## 20182236
Coding_consistency_preprocess_data1$Target_Population_N[4134] <- 1

## 20183292
Coding_consistency_preprocess_data1$Target_Population_N[c(4203,4206)] <- 1

## 20185096
Coding_consistency_preprocess_data1$Target_Population_N[4254] <- 1

## 20185102
Coding_consistency_preprocess_data1$Target_Population_N[4257] <- 1

## 20083110
Coding_consistency_preprocess_data1$Target_Population_N[4497] <- 1

```


## Sample_Type_N
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(Sample_Type_N = ifelse(Sample_Type_N == "　",NA,Sample_Type_N),
                Sample_Type_N = ifelse(Sample_Type_N == "check" & is.na(Sample_Type_N ),"Chin_Subj",Sample_Type_N))

# table(Coding_consistency_preprocess_data1$Sample_Type_N)

rm(results)


results <- data.frame(Article_Title= character(),
                      Sample_Type_N_coder1 = as.character(),
                      Sample_Type_N_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$Sample_Type_N[i]
  coder2_code <- Coding_consistency_preprocess_data1$Sample_Type_N[i+1]
  stored_score <- Coding_consistency_preprocess_data1$Sample_Type_N[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    Coding_consistency_preprocess_data1$Sample_Type_N[i+2] <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code) || grepl(coder2_code, coder1_code)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     Sample_Type_N_coder1 = coder1_code,
                                     Sample_Type_N_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")

## 20182268
Coding_consistency_preprocess_data1$Sample_Type_N[444] <- 1

## 20183326
Coding_consistency_preprocess_data1$Sample_Type_N[c(528,531,534)] <- 1

## 20183344
Coding_consistency_preprocess_data1$Sample_Type_N[c(561,564)] <- 1

## 20084057
Coding_consistency_preprocess_data1$Sample_Type_N[1596] <- 1

## 20182247
Coding_consistency_preprocess_data1$Sample_Type_N[4158] <- 1

## 20083109
Coding_consistency_preprocess_data1$Sample_Type_N[4494] <- 1

## 20083110
Coding_consistency_preprocess_data1$Sample_Type_N[4497] <- 1

## 20083170
Coding_consistency_preprocess_data1$Sample_Type_N[4548] <- 1

## 20181208
Coding_consistency_preprocess_data1$Sample_Type_N[c(4581,4584,4587,4590)] <- 1

## 20181212
Coding_consistency_preprocess_data1$Sample_Type_N[c(4608,4611)] <- 1

## 20181213
Coding_consistency_preprocess_data1$Sample_Type_N[c(4614,4617)] <- 1

## 20181223
Coding_consistency_preprocess_data1$Sample_Type_N[c(4626,4629)] <- 1

## 20181231
Coding_consistency_preprocess_data1$Sample_Type_N[4641] <- 1

## 20181236
Coding_consistency_preprocess_data1$Sample_Type_N[c(4647,4650)] <- 1

## 20183001
Coding_consistency_preprocess_data1$Sample_Type_N[c(4665,4668,4671)] <- 1

## 20183013
Coding_consistency_preprocess_data1$Sample_Type_N[4683] <- 1

```


## Sample_Type_info_N
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(Sample_Type_info_N = ifelse(Sample_Type_info_N == "　",NA,Sample_Type_info_N),
                Sample_Type_info_N = ifelse(Sample_Type_info_N == "check" & is.na(Sample_Type_info_N ),"Chin_Subj",Sample_Type_info_N))

# table(Coding_consistency_preprocess_data1$Sample_Type_info_N)

rm(results)


results <- data.frame(Article_Title= character(),
                      Sample_Type_info_N_coder1 = as.character(),
                      Sample_Type_info_N_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$Sample_Type_info_N[i]
  coder2_code <- Coding_consistency_preprocess_data1$Sample_Type_info_N[i+1]
  stored_score <- Coding_consistency_preprocess_data1$Sample_Type_info_N[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    Coding_consistency_preprocess_data1$Sample_Type_info_N[i+2] <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code,fixed = TRUE)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     Sample_Type_info_N_coder1 = coder1_code,
                                     Sample_Type_info_N_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")

## 20182267
Coding_consistency_preprocess_data1$Sample_Type_info_N[c(414)] <- 3

## 20183312
Coding_consistency_preprocess_data1$Sample_Type_info_N[486] <- 3

## 20183344
Coding_consistency_preprocess_data1$Sample_Type_info_N[564] <- 3

## 20213079
Coding_consistency_preprocess_data1$Sample_Type_info_N[666] <- 3

## 20213104
Coding_consistency_preprocess_data1$Sample_Type_info_N[687] <- 1
Coding_consistency_preprocess_data1$Sample_Type_info_N[690] <- 3

## 20082107
Coding_consistency_preprocess_data1$Sample_Type_info_N[804] <- 3
Coding_consistency_preprocess_data1$Sample_Type_info_N[807] <- 1

## 20082112
Coding_consistency_preprocess_data1$Sample_Type_info_N[813] <- 3
Coding_consistency_preprocess_data1$Sample_Type_info_N[816] <- 1

## 20211045
Coding_consistency_preprocess_data1$Sample_Type_info_N[c(1287,1290)] <- 3

## 20211046
Coding_consistency_preprocess_data1$Sample_Type_info_N[c(1293,1296)] <- 3

## 20211047
Coding_consistency_preprocess_data1$Sample_Type_info_N[1299] <- 3

## 20211052
Coding_consistency_preprocess_data1$Sample_Type_info_N[1302] <- 3

## 20211059
Coding_consistency_preprocess_data1$Sample_Type_info_N[c(1305,1308)] <- 3

## 20211061
Coding_consistency_preprocess_data1$Sample_Type_info_N[c(1311,1317)] <- 2
Coding_consistency_preprocess_data1$Sample_Type_info_N[c(1314,1320)] <- 3

## 20211064
Coding_consistency_preprocess_data1$Sample_Type_info_N[c(1341,1344,1347,1350,1353,1356)] <- 3

## 20211071
Coding_consistency_preprocess_data1$Sample_Type_info_N[c(1365,1368)] <- 3

## 20213223
Coding_consistency_preprocess_data1$Sample_Type_info_N[c(1431,1437)] <- 3
Coding_consistency_preprocess_data1$Sample_Type_info_N[c(1434,1440)] <- 2

## 20183326
Coding_consistency_preprocess_data1$Sample_Type_info_N[c(528)] <- 3
```


## Educational_Attainment_N
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(Educational_Attainment_N = ifelse(Educational_Attainment_N == "　",NA,Educational_Attainment_N),
                Educational_Attainment_N = ifelse(Educational_Attainment_N == "check" & is.na(Educational_Attainment_N ),"Chin_Subj",Educational_Attainment_N))

# table(Coding_consistency_preprocess_data1$Educational_Attainment_N)

rm(results)


results <- data.frame(Article_Title= character(),
                      Educational_Attainment_N_coder1 = as.character(),
                      Educational_Attainment_N_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$Educational_Attainment_N[i]
  coder2_code <- Coding_consistency_preprocess_data1$Educational_Attainment_N[i+1]
  stored_score <- Coding_consistency_preprocess_data1$Educational_Attainment_N[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    Coding_consistency_preprocess_data1$Educational_Attainment_N[i+2] <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code) || grepl(coder2_code, coder1_code)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     Educational_Attainment_N_coder1 = coder1_code,
                                     Educational_Attainment_N_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")


## 20183229
Coding_consistency_preprocess_data1$Educational_Attainment_N[3333] <- 1

## 20181209
Coding_consistency_preprocess_data1$Educational_Attainment_N[c(4593,4596)] <- 1

## 20181212
Coding_consistency_preprocess_data1$Educational_Attainment_N[c(4608,4611)] <- 1

## 20183001
Coding_consistency_preprocess_data1$Educational_Attainment_N[c(4668,4671)] <- 1

## 20183023
Coding_consistency_preprocess_data1$Educational_Attainment_N[c(4692,4695)] <- 1
```


## Educational_Attainment_info_N
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(Educational_Attainment_info_N = ifelse(Educational_Attainment_info_N == "　",NA,Educational_Attainment_info_N),
                Educational_Attainment_info_N = ifelse(Educational_Attainment_info_N == "check" & is.na(Educational_Attainment_info_N),"Chin_Subj",Educational_Attainment_info_N))

# table(Coding_consistency_preprocess_data1$Educational_Attainment_info_N)

rm(results)


results <- data.frame(Article_Title= character(),
                      Educational_Attainment_info_N_coder1 = as.character(),
                      Educational_Attainment_info_N_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$Educational_Attainment_info_N[i]
  coder2_code <- Coding_consistency_preprocess_data1$Educational_Attainment_info_N[i+1]
  stored_score <- Coding_consistency_preprocess_data1$Educational_Attainment_info_N[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    Coding_consistency_preprocess_data1$Educational_Attainment_info_N[i+2] <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code,fixed = TRUE)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     Educational_Attainment_info_N_coder1 = coder1_code,
                                     Educational_Attainment_info_N_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")

## 20183137
Coding_consistency_preprocess_data1$Educational_Attainment_info_N[1827] <- 1

## 20183229
Coding_consistency_preprocess_data1$Educational_Attainment_info_N[3333] <- 1
```


## Occupation_N
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(Occupation_N = ifelse(Occupation_N == "　",NA,Occupation_N),
                Occupation_N = ifelse(Occupation_N == "check" & is.na(Occupation_N ),"Chin_Subj",Occupation_N))

# table(Coding_consistency_preprocess_data1$Occupation_N)

rm(results)


results <- data.frame(Article_Title= character(),
                      Occupation_N_coder1 = as.character(),
                      Occupation_N_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$Occupation_N[i]
  coder2_code <- Coding_consistency_preprocess_data1$Occupation_N[i+1]
  stored_score <- Coding_consistency_preprocess_data1$Occupation_N[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    Coding_consistency_preprocess_data1$Occupation_N[i+2] <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code) || grepl(coder2_code, coder1_code)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     Occupation_N_coder1 = coder1_code,
                                     Occupation_N_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")

## 20083107
Coding_consistency_preprocess_data1$Occupation_N[201] <- 1

## 20213067
Coding_consistency_preprocess_data1$Occupation_N[4380] <- 1

## 20083128
Coding_consistency_preprocess_data1$Occupation_N[c(4518,4521)] <- 1

## 20181213
Coding_consistency_preprocess_data1$Occupation_N[c(4614,4617)] <- 1

## 20181225
Coding_consistency_preprocess_data1$Occupation_N[c(4632,4635)] <- 1

## 20181228
Coding_consistency_preprocess_data1$Occupation_N[4638] <- 1

## 20181235
Coding_consistency_preprocess_data1$Occupation_N[4644] <- 1
```


## SES_N
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(SES_N = ifelse(SES_N == "　",NA,SES_N),
                SES_N = ifelse(SES_N == "check" & is.na(SES_N),"Chin_Subj",SES_N))

# table(Coding_consistency_preprocess_data1$SES_N)

rm(results)


results <- data.frame(Article_Title= character(),
                      SES_N_coder1 = as.character(),
                      SES_N_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$SES_N[i]
  coder2_code <- Coding_consistency_preprocess_data1$SES_N[i+1]
  stored_score <- Coding_consistency_preprocess_data1$SES_N[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    Coding_consistency_preprocess_data1$SES_N[i+2] <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code) || grepl(coder2_code, coder1_code)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     SES_N_coder1 = coder1_code,
                                     SES_N_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")


## 20181140
Coding_consistency_preprocess_data1$SES_N[204] <- 3

## 20185167
Coding_consistency_preprocess_data1$SES_N[627] <- 3

## 20183158
Coding_consistency_preprocess_data1$SES_N[2586] <- 1

## 20185126
Coding_consistency_preprocess_data1$SES_N[c(4287,4290)] <- 1

## 20185128
Coding_consistency_preprocess_data1$SES_N[4293] <- 1

## 20215073
Coding_consistency_preprocess_data1$SES_N[4383] <- 1

## 20215076
Coding_consistency_preprocess_data1$SES_N[4389] <- 1

## 20083110
Coding_consistency_preprocess_data1$SES_N[4497] <- 1

## 20083116
Coding_consistency_preprocess_data1$SES_N[c(4509,4512)] <- 1

## 20083128
Coding_consistency_preprocess_data1$SES_N[c(4518,4521)] <- 1

## 20181202
Coding_consistency_preprocess_data1$SES_N[c(4563,4569)] <- 1

## 20181206
Coding_consistency_preprocess_data1$SES_N[4575] <- 1

## 20181209
Coding_consistency_preprocess_data1$SES_N[c(4593,4596)] <- 1

## 20181212
Coding_consistency_preprocess_data1$SES_N[c(4608,4611)] <- 1

## 20181231
Coding_consistency_preprocess_data1$SES_N[4641] <- 1

## 20183001
Coding_consistency_preprocess_data1$SES_N[c(4668,4671)] <- 1

## 20183023
Coding_consistency_preprocess_data1$SES_N[c(4692,4695)] <- 1

## 20181136
Coding_consistency_preprocess_data1$SES_N[c(4080,4083)] <- 2
```


## SES_info_N
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(SES_info_N = ifelse(SES_info_N  == "　",NA,SES_info_N),
                SES_info_N = ifelse(SES_info_N == "check" & is.na(SES_info_N),"Chin_Subj",SES_info_N))

# table(Coding_consistency_preprocess_data1$SES_info_N)

rm(results)


results <- data.frame(Article_Title= character(),
                      SES_info_N_coder1 = as.character(),
                      SES_info_N_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$SES_info_N[i]
  coder2_code <- Coding_consistency_preprocess_data1$SES_info_N[i+1]
  stored_score <- Coding_consistency_preprocess_data1$SES_info_N[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    Coding_consistency_preprocess_data1$SES_info_N[i+2] <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code) || grepl(coder2_code, coder1_code)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     SES_info_N_coder1 = coder1_code,
                                     SES_info_N_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")

## 20182180
Coding_consistency_preprocess_data1$SES_info_N[3240] <- 1

## 20212151
Coding_consistency_preprocess_data1$SES_info_N[3501] <- 1

## 20215042
Coding_consistency_preprocess_data1$SES_info_N[c(3666,3669,3672)] <- 1

## 20183236
Coding_consistency_preprocess_data1$SES_info_N[c(3342)] <- 1
```


## Subjects_Recruitment_Method_N
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(Subjects_Recruitment_Method_N = ifelse(Subjects_Recruitment_Method_N  == "　",NA,Subjects_Recruitment_Method_N),
                SES_info_N = ifelse(Subjects_Recruitment_Method_N == "check" & is.na(Subjects_Recruitment_Method_N),"Chin_Subj",Subjects_Recruitment_Method_N))

# table(Coding_consistency_preprocess_data1$Subjects_Recruitment_Method_N)

rm(results)


results <- data.frame(Article_Title= character(),
                      Subjects_Recruitment_Method_N_coder1 = as.character(),
                      Subjects_Recruitment_Method_N_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$Subjects_Recruitment_Method_N[i]
  coder2_code <- Coding_consistency_preprocess_data1$Subjects_Recruitment_Method_N[i+1]
  stored_score <- Coding_consistency_preprocess_data1$Subjects_Recruitment_Method_N[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    Coding_consistency_preprocess_data1$Subjects_Recruitment_Method_N[i+2] <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code) || grepl(coder2_code, coder1_code)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     Subjects_Recruitment_Method_N_coder1 = coder1_code,
                                     Subjects_Recruitment_Method_N_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")


## 20182255
Coding_consistency_preprocess_data1$Subjects_Recruitment_Method_N[387] <- 1

## 20185191
Coding_consistency_preprocess_data1$Subjects_Recruitment_Method_N[654] <- 1

## 20213104
Coding_consistency_preprocess_data1$Subjects_Recruitment_Method_N[687] <- 2

## 20213120
Coding_consistency_preprocess_data1$Subjects_Recruitment_Method_N[711] <- 1

## 20183138
Coding_consistency_preprocess_data1$Subjects_Recruitment_Method_N[1830] <- 1

## 20214066
Coding_consistency_preprocess_data1$Subjects_Recruitment_Method_N[2919] <- 1

## 20214068
Coding_consistency_preprocess_data1$Subjects_Recruitment_Method_N[c(2925,2928)] <- 1

## 20214070
Coding_consistency_preprocess_data1$Subjects_Recruitment_Method_N[2931] <- 1

## 20182231
Coding_consistency_preprocess_data1$Subjects_Recruitment_Method_N[4131] <- 1

## 20182239
Coding_consistency_preprocess_data1$Subjects_Recruitment_Method_N[c(4140,4143)] <- 1

## 20183264
Coding_consistency_preprocess_data1$Subjects_Recruitment_Method_N[c(4170,4173,4176)] <- 1

## 20183285
Coding_consistency_preprocess_data1$Subjects_Recruitment_Method_N[4197] <- 1

## 20183296
Coding_consistency_preprocess_data1$Subjects_Recruitment_Method_N[4292] <- 1

## 20185082
Coding_consistency_preprocess_data1$Subjects_Recruitment_Method_N[4233] <- 1

## 20185083
Coding_consistency_preprocess_data1$Subjects_Recruitment_Method_N[4236] <- 1

## 20185087
Coding_consistency_preprocess_data1$Subjects_Recruitment_Method_N[c(4242,4245,4248,4251)] <- 1

## 20185114
Coding_consistency_preprocess_data1$Subjects_Recruitment_Method_N[4272] <- 1

## 20185124
Coding_consistency_preprocess_data1$Subjects_Recruitment_Method_N[4284] <- 1

## 20213024
Coding_consistency_preprocess_data1$Subjects_Recruitment_Method_N[4326] <- 1

## 20213055
Coding_consistency_preprocess_data1$Subjects_Recruitment_Method_N[4371] <- 1

## 20213056
Coding_consistency_preprocess_data1$Subjects_Recruitment_Method_N[4374] <- 1

## 20083110
Coding_consistency_preprocess_data1$Subjects_Recruitment_Method_N[4497] <- 1

## 20083128
Coding_consistency_preprocess_data1$Subjects_Recruitment_Method_N[c(4518,4521)] <- 1

## 20181208
Coding_consistency_preprocess_data1$Subjects_Recruitment_Method_N[c(4581,4584)] <- 1

## 20181213
Coding_consistency_preprocess_data1$Subjects_Recruitment_Method_N[c(4614,4617)] <- 1

## 20184035
Coding_consistency_preprocess_data1$Subjects_Recruitment_Method_N[4818] <- 3

## 20211015
Coding_consistency_preprocess_data1$Subjects_Recruitment_Method_N[5031] <- 1
```



## Subjects_Recruitment_Method_info_N
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(Subjects_Recruitment_Method_info_N = ifelse(Subjects_Recruitment_Method_info_N  == "　",NA,Subjects_Recruitment_Method_info_N),
                SES_info_N = ifelse(Subjects_Recruitment_Method_info_N == "check" & is.na(Subjects_Recruitment_Method_info_N),"Chin_Subj",Subjects_Recruitment_Method_info_N))

# table(Coding_consistency_preprocess_data1$Subjects_Recruitment_Method_info_N)

rm(results)


results <- data.frame(Article_Title= character(),
                      Subjects_Recruitment_Method_info_N_coder1 = as.character(),
                      Subjects_Recruitment_Method_info_N_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$Subjects_Recruitment_Method_info_N[i]
  coder2_code <- Coding_consistency_preprocess_data1$Subjects_Recruitment_Method_info_N[i+1]
  stored_score <- Coding_consistency_preprocess_data1$Subjects_Recruitment_Method_info_N[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    Coding_consistency_preprocess_data1$Subjects_Recruitment_Method_info_N[i+2] <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code) || grepl(coder2_code, coder1_code)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     Subjects_Recruitment_Method_info_N_coder1 = coder1_code,
                                     Subjects_Recruitment_Method_info_N_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")

## 20213104
Coding_consistency_preprocess_data1$Subjects_Recruitment_Method_info_N[687] <- 2

## 20082069
Coding_consistency_preprocess_data1$Subjects_Recruitment_Method_info_N[c(759,762)] <- 1

## 20082118
Coding_consistency_preprocess_data1$Subjects_Recruitment_Method_info_N[822] <- 1

## 20184050
Coding_consistency_preprocess_data1$Subjects_Recruitment_Method_info_N[1188] <- 1

## 20082004
Coding_consistency_preprocess_data1$Subjects_Recruitment_Method_info_N[4407] <- 1

## 20181212
Coding_consistency_preprocess_data1$Subjects_Recruitment_Method_info_N[4611] <- 1

## 20211015
Coding_consistency_preprocess_data1$Subjects_Recruitment_Method_info_N[5031] <- 1

## 20082046
Coding_consistency_preprocess_data1$Subjects_Recruitment_Method_info_N[732] <- 3

```


# Check Again
```{r}
# names(Coding_consistency_preprocess_data1)


Check_data <- Coding_consistency_preprocess_data1 %>% 
  dplyr::filter(Coder_N == "check") %>% 
  dplyr::select(-c(Coder,Coder2_N,Article_IDs,Study_Number,Subjects_Group,
                   Remark1,Remark2,Remark3,Remark3_N,Coding_Basis_N))


## calculate the categroires of check value
check_list <- list()

for (i in names(Check_data)){
  
  
  check_table <- data.frame(table(Check_data[[i]])) %>% 
    dplyr::mutate(col_names = names(Check_data[i]))
  
  check_list[[i]] <- check_table
  
}

check_table <- do.call(rbind, check_list)

check_table <- check_table %>% 
  dplyr::filter(col_names != "Sequence_IDs")  ## no found outliers
```


In fact, I found some check still is NA, so I will reprocess them
## Article_IDs_N
```{r}
Check_NA <- Check_data %>% 
  dplyr::select(Sequence_IDs,Article_IDs_N) %>% 
  dplyr::filter(is.na(Article_IDs_N))

## no found
```


## Study_Number_N
```{r}
rm(Check_NA)

Check_NA <- Check_data %>% 
  dplyr::select(Sequence_IDs,Study_Number_N) %>% 
  dplyr::filter(is.na(Study_Number_N))

## no found
```

## Subjects_Group_N
```{r}
rm(Check_NA)

Check_NA <- Check_data %>% 
  dplyr::select(Sequence_IDs,Subjects_Group_N) %>% 
  dplyr::filter(is.na(Subjects_Group_N))

## no found
```


## Article_Title
```{r}
rm(Check_NA)

Check_NA <- Check_data %>% 
  dplyr::select(Sequence_IDs,Article_Title) %>% 
  dplyr::filter(is.na(Article_Title))

## no found
```


## First_Author
```{r}
rm(Check_NA)

Check_NA <- Check_data %>% 
  dplyr::select(Sequence_IDs,First_Author) %>% 
  dplyr::filter(is.na(First_Author))

## no found
```


## Journal
```{r}
rm(Check_NA)

Check_NA <- Check_data %>% 
  dplyr::select(Sequence_IDs,Journal) %>% 
  dplyr::filter(is.na(Journal))

## no found
```


## Abstract1
```{r}
rm(Check_NA)

Check_NA <- Check_data %>% 
  dplyr::select(Sequence_IDs,Abstract1) %>% 
  dplyr::filter(is.na(Abstract1))

## no found
```


## Abstract2
```{r}
rm(Check_NA)

Check_NA <- Check_data %>% 
  dplyr::select(Sequence_IDs,Abstract2) %>% 
  dplyr::filter(is.na(Abstract2))

## no found
```


## Study_Type
```{r}
rm(Check_NA)

Check_NA <- Check_data %>% 
  dplyr::select(Sequence_IDs,Study_Type) %>% 
  dplyr::filter(is.na(Study_Type))

## no found
```


## Sample_Size
```{r}
rm(Check_NA)

Check_NA <- Check_data %>% 
  dplyr::select(Sequence_IDs,Sample_Size) %>% 
  dplyr::filter(is.na(Sample_Size))

## no found
```


## Gender
```{r}
rm(Check_NA)

Check_NA <- Check_data %>% 
  dplyr::select(Sequence_IDs,Gender) %>% 
  dplyr::filter(is.na(Gender))

## no found
```


## Female_Num
```{r}
rm(Check_NA)

Check_NA <- Check_data %>% 
  dplyr::select(Sequence_IDs,Female_Num) %>% 
  dplyr::filter(is.na(Female_Num))

## no found
```


## Male_Num
```{r}
rm(Check_NA)

Check_NA <- Check_data %>% 
  dplyr::select(Sequence_IDs,Male_Num) %>% 
  dplyr::filter(is.na(Male_Num))

## no found
```


## Age
```{r}
rm(Check_NA)

Check_NA <- Check_data %>% 
  dplyr::select(Sequence_IDs,Age) %>% 
  dplyr::filter(is.na(Age))

## no found
```


## M_age
```{r}
rm(Check_NA)

Check_NA <- Check_data %>% 
  dplyr::select(Sequence_IDs,M_age) %>% 
  dplyr::filter(is.na(M_age))

## no found
```


## SD_age
```{r}
rm(Check_NA)

Check_NA <- Check_data %>% 
  dplyr::select(Sequence_IDs,SD_age) %>% 
  dplyr::filter(is.na(SD_age))

## no found
```


## Other_age
```{r}
rm(Check_NA)

Check_NA <- Check_data %>% 
  dplyr::select(Sequence_IDs,Other_age) %>% 
  dplyr::filter(is.na(Other_age))

## 1110_3 
Coding_consistency_preprocess_data1$Other_age[3330] <- 1
```


## Ethnicity
```{r}
rm(Check_NA)

Check_NA <- Check_data %>% 
  dplyr::select(Sequence_IDs,Ethnicity) %>% 
  dplyr::filter(is.na(Ethnicity))

## no found
```


## Ethnicity_info
```{r}
rm(Check_NA)

Check_NA <- Check_data %>% 
  dplyr::select(Sequence_IDs,Ethnicity_info) %>% 
  dplyr::filter(is.na(Ethnicity_info))

## no found
```

## Religious
```{r}
rm(Check_NA)

Check_NA <- Check_data %>% 
  dplyr::select(Sequence_IDs,Religious) %>% 
  dplyr::filter(is.na(Religious))

## 1087_3
Coding_consistency_preprocess_data1$Religious[3261] <- 3
```


## Religious_info
```{r}
rm(Check_NA)

Check_NA <- Check_data %>% 
  dplyr::select(Sequence_IDs,Religious_info) %>% 
  dplyr::filter(is.na(Religious_info))

## 1071_3 ~ 1088_3
start_index <- 3213
end_index <- 3264

indices <- seq(start_index, end_index, by = 3)

Coding_consistency_preprocess_data1$Religious_info[indices] <- 1

## 1091_3 ~ 1110_3
start_index <- 3273
end_index <- 3330
indices <- seq(start_index, end_index, by = 3)

Coding_consistency_preprocess_data1$Religious_info[indices] <- 1

After_NA <- Coding_consistency_preprocess_data1 %>% 
  dplyr::filter(Coder_N == "check" & is.na(Religious_info))
```


## Subjects_Area
```{r}
rm(Check_NA)

Check_NA <- Check_data %>% 
  dplyr::select(Sequence_IDs,Subjects_Area) %>% 
  dplyr::filter(is.na(Subjects_Area))

## no found
```


## Subjects_Area_info
```{r}
rm(Check_NA)

Check_NA <- Check_data %>% 
  dplyr::select(Sequence_IDs,Subjects_Area_info) %>% 
  dplyr::filter(is.na(Subjects_Area_info))

## 1219_3
Coding_consistency_preprocess_data1$Subjects_Area_info[3657] <- 1
```


## Subjects_Recruitment_Area
```{r}
rm(Check_NA)

Check_NA <- Check_data %>% 
  dplyr::select(Sequence_IDs,Subjects_Recruitment_Area) %>% 
  dplyr::filter(is.na(Subjects_Recruitment_Area))

## no found
```


## Sampling_Method
```{r}
rm(Check_NA)

Check_NA <- Check_data %>% 
  dplyr::select(Sequence_IDs,Sampling_Method) %>% 
  dplyr::filter(is.na(Sampling_Method))

## 1081_3 ~ 1088_3
start_index <- 3243
end_index <- 3264
indices <- seq(start_index, end_index, by = 3)

Coding_consistency_preprocess_data1$Sampling_Method[indices] <- 1
# Coding_consistency_preprocess_data1$Sampling_Method[3241:3264]

After_NA <- Coding_consistency_preprocess_data1 %>% 
  dplyr::filter(Coder_N == "check" & is.na(Sampling_Method))
```


## Remark1_N
```{r}
rm(Check_NA)

Check_NA <- Check_data %>% 
  dplyr::select(Sequence_IDs,Remark1_N) %>% 
  dplyr::filter(is.na(Remark1_N))

## no found
```


## Remark2_N
```{r}
rm(Check_NA)

Check_NA <- Check_data %>% 
  dplyr::select(Sequence_IDs,Remark2_N) %>% 
  dplyr::filter(is.na(Remark2_N))

## 0448_3
Coding_consistency_preprocess_data1$Remark2_N[1344] <- 1

## 0474_3
Coding_consistency_preprocess_data1$Remark2_N[1422] <- 1
```


## Target_Population_N
```{r}
rm(Check_NA)

Check_NA <- Check_data %>% 
  dplyr::select(Sequence_IDs,Target_Population_N) %>% 
  dplyr::filter(is.na(Target_Population_N))

## 1084_3 ~ 1085_3
Coding_consistency_preprocess_data1$Target_Population_N[c(3252,3255)] <- 1
```


## Sample_Type_N
```{r}
rm(Check_NA)

Check_NA <- Check_data %>% 
  dplyr::select(Sequence_IDs,Sample_Type_N) %>% 
  dplyr::filter(is.na(Sample_Type_N))

## 1081_3 ~ 1083_3
Coding_consistency_preprocess_data1$Sample_Type_N[c(3243,3246,3249)] <- 1
```


## Sample_Type_info_N
```{r}
rm(Check_NA)

Check_NA <- Check_data %>% 
  dplyr::select(Sequence_IDs,Sample_Type_info_N) %>% 
  dplyr::filter(is.na(Sample_Type_info_N))

## 0414_3 ~ 0428_3

Coding_consistency_preprocess_data1$Sample_Type_info_N[c(1242,1245,1248,1251,1254,1257,1260,1263)] <- 3
Coding_consistency_preprocess_data1$Sample_Type_info_N[c(1266,1269)] <- 2
Coding_consistency_preprocess_data1$Sample_Type_info_N[c(1272,1275,1278,1281,1284)] <- 1

## 0441_3 ~ 0446_3
Coding_consistency_preprocess_data1$Sample_Type_info_N[c(1323,1326,1329,1332,1335,1338)] <- 3

## 0453_3 ~ 0454_3
Coding_consistency_preprocess_data1$Sample_Type_info_N[c(1359,1362)] <- 2

## 0457_3 ~ 0476_3
# Coding_consistency_preprocess_data1$Sample_Type_info_N[1369:1428]
start_index <- 1371
end_index <- 1428
indices <- seq(start_index, end_index, by = 3)

Coding_consistency_preprocess_data1$Sample_Type_info_N[indices] <- 3

## 0481_3 ~ 0497_3
# Coding_consistency_preprocess_data1$Sample_Type_info_N[1441:1491]
start_index <- 1443
end_index <- 1491
indices <- seq(start_index, end_index, by = 3)

Coding_consistency_preprocess_data1$Sample_Type_info_N[indices] <- 3

## 1098_3 ~ 1137_3 ## It does not contain 1126_3, but after looking at the data again, it check is 3, so the consecutive assignment does not affect the result.
# Coding_consistency_preprocess_data1$Sample_Type_info_N[3292:3411]

start_index <- 3294
end_index <- 3411
indices <- seq(start_index, end_index, by = 3)

Coding_consistency_preprocess_data1$Sample_Type_info_N[indices] <- 3

## 1179_3 ~ 1180_3
Coding_consistency_preprocess_data1$Sample_Type_info_N[c(3537,3540)] <- 3

After_NA <- Coding_consistency_preprocess_data1 %>% 
  dplyr::filter(Coder_N == "check" & is.na(Sample_Type_info_N))
```


## Educational_Attainment_N
```{r}
rm(Check_NA)

Check_NA <- Check_data %>% 
  dplyr::select(Sequence_IDs,Educational_Attainment_N) %>% 
  dplyr::filter(is.na(Educational_Attainment_N))

## 0491_3
Coding_consistency_preprocess_data1$Educational_Attainment_N[1473] <- 1
```


## Educational_Attainment_info_N
```{r}
rm(Check_NA)

Check_NA <- Check_data %>% 
  dplyr::select(Sequence_IDs,Educational_Attainment_info_N) %>% 
  dplyr::filter(is.na(Educational_Attainment_info_N))

## 0422_3 ~ 0423_3
Coding_consistency_preprocess_data1$Educational_Attainment_info_N[c(1266,1269)] <- 3

## 0447_3 ~ 0452_3
Coding_consistency_preprocess_data1$Educational_Attainment_info_N[c(1341,1344,1347,1353,1356)] <- 3
Coding_consistency_preprocess_data1$Educational_Attainment_info_N[1350] <- 1

## 0470_3  0477_3  0479_3  0487_3  
Coding_consistency_preprocess_data1$Educational_Attainment_info_N[c(1410,1431,1437,1461)] <- 3

## 0491_3 ~ 0494_3
# Coding_consistency_preprocess_data1$Educational_Attainment_info_N[1471:1482]
Coding_consistency_preprocess_data1$Educational_Attainment_info_N[1476] <- 1
Coding_consistency_preprocess_data1$Educational_Attainment_info_N[c(1473,1479,1482)] <- 3

## 1104_3
Coding_consistency_preprocess_data1$Educational_Attainment_info_N[3312] <- 1

## 1114_3
Coding_consistency_preprocess_data1$Educational_Attainment_info_N[3342] <- 3

## 1168_3 1169_3
Coding_consistency_preprocess_data1$Educational_Attainment_info_N[c(3504,3507)] <- 1
```


## Occupation_N
```{r}
rm(Check_NA)

Check_NA <- Check_data %>% 
  dplyr::select(Sequence_IDs,Occupation_N) %>% 
  dplyr::filter(is.na(Occupation_N))

## no found
```


## SES_N
```{r}
rm(Check_NA)

Check_NA <- Check_data %>% 
  dplyr::select(Sequence_IDs,SES_N) %>% 
  dplyr::filter(is.na(SES_N))

## no found
```


## SES_info_N
```{r}
rm(Check_NA)

Check_NA <- Check_data %>% 
  dplyr::select(Sequence_IDs,SES_info_N) %>% 
  dplyr::filter(is.na(SES_info_N))

## no found
```


## Subjects_Recruitment_Method_N
```{r}
rm(Check_NA)

Check_NA <- Check_data %>% 
  dplyr::select(Sequence_IDs,Subjects_Recruitment_Method_N) %>% 
  dplyr::filter(is.na(Subjects_Recruitment_Method_N))

## 1117_3
Coding_consistency_preprocess_data1$Subjects_Recruitment_Method_N[3351] <- 1
```


## Subjects_Recruitment_Method_info_N
```{r}
rm(Check_NA)

Check_NA <- Check_data %>% 
  dplyr::select(Sequence_IDs,Subjects_Recruitment_Method_info_N) %>% 
  dplyr::filter(is.na(Subjects_Recruitment_Method_info_N))

## no found
```


## find NA again
```{r}
rm(Check_NA)

NA_table <- Coding_consistency_preprocess_data1 %>% 
  dplyr::filter(Coder_N == "check")

NA_table2 <- data.frame(sapply(NA_table, function(x) sum(is.na(x))))


## no found
```


## Save Rdata
```{r}
Chin_Subj_check_data <- Coding_consistency_preprocess_data1 %>% 
  dplyr::filter(Coder_N == "check") %>% 
  dplyr::select(-c(Coder,Coder2_N,Remark1,Remark2,Remark3,Remark3_N,
                   Study_Number,Subjects_Group,Article_IDs,Coding_Basis_N))

# names(check)
# 
save(Chin_Subj_check_data,
      file = "Chin_Subj_check_data.Rdata")
# load("Chin_Subj_check_data.Rdata")
```

