---
title: "Notebook_Coding_Consistency"
author: "Lei Yue"
date: "2024-12-08"
output: html_document
---

## Load packages
```{r}
rm(list = ls())

if(!require("pacman"))install.packages("pacman")

p_load("here","tidyverse","rio","readxl")

```


## Load data
```{r warning=FALSE}
# getwd()

file_list <- list.files(
  here("C:/Users/yuelei/Desktop/Stage_2_Code_Data"),
  pattern = ".xlsx",
  full.names = TRUE, recursive = TRUE)

df <- rio::import_list(file_list) 

df <- df[grepl("CE",names(df),ignore.case = TRUE)]

df <- lapply(df, function(df) {  
  df[] <- lapply(df, as.character)  
  return(df)  
})

# df1 <- df[[1]]
# 
# table(df1$Coder)
```


## check colnames
```{r}
# names(df)

## check the coding stage colnames
Coding_datalist_names <- data.frame(Chin_Subj_Coding_Group1_8_9_CE = names(df[[1]]),
                                   Chin_Subj_Coding_Group1_8_9_CE_suppl3 = names(df[[2]]),
                                   Chin_Subj_Coding_Group2_CE = names(df[[3]]),
                                   Chin_Subj_Coding_Group3_CE = names(df[[4]]),
                                   Chin_Subj_Coding_Group3_CE_suppl6 = names(df[[5]]),
                                   Chin_Subj_Coding_Group4_CE = names(df[[6]]),
                                   Chin_Subj_Coding_Group5_CE = names(df[[7]]),
                                   Chin_Subj_Coding_Group6_CE = names(df[[8]]),
                                   Chin_Subj_Coding_Group7_CE = names(df[[9]]))

Check_row_equality1 <- function(row) {  
  all_equal <- all(row == row[1])  
  return(all_equal)  
}  
  
Row_equalities1 <- apply(Coding_datalist_names, 1, Check_row_equality1) 
### I found the names of 3,4,5, 19 cols are different and I modfi them
colnames(df[[9]])[colnames(df[[9]]) == "First_author"] <- "First_Author"

colnames(df[[3]])[colnames(df[[3]]) == "Sample_Szie"] <- "Sample_Size"
colnames(df[[4]])[colnames(df[[4]]) == "Sample_Szie"] <- "Sample_Size"
colnames(df[[5]])[colnames(df[[5]]) == "Sample_Szie"] <- "Sample_Size"
colnames(df[[6]])[colnames(df[[6]]) == "Sample_Szie"] <- "Sample_Size"
colnames(df[[7]])[colnames(df[[7]]) == "Sample_Szie"] <- "Sample_Size"
colnames(df[[9]])[colnames(df[[9]]) == "Sample_Szie"] <- "Sample_Size"

## Adjust the column names of the eighth data frame in the list to be consistent with the column names of other data frame (Chin_Subj_Coding_Group6_CE)
df[[8]] <- df[[8]][,c(1:2,5,3,4,6:40)]

## Adjust the column names for Chin_Subj_Coding_Group3_CE and Chin_Subj_Coding_Group3_CE_suppl6 to be consistent with the other data frame, but note that there are problems with the `Journal` and `First_Author`columns of these two data frame are recorded backwards
# df4 <- df[[4]]
# df5 <- df[[5]]
df[[4]] <- df[[4]][,c(1:3,5,4,6:40)]
df[[5]] <- df[[5]][,c(1:3,5,4,6:40)]

## check the proofreading stage colnames
Proofreading_datalist_names <- data.frame(Chin_Subj_Proofreading_Group1_CE = names(df[[10]]),
                                          Chin_Subj_Proofreading_Group2_CE = names(df[[11]]),
                                          Chin_Subj_Proofreading_Group3_CE = names(df[[12]]),
                                          Chin_Subj_Proofreading_Group4_CE = names(df[[13]]),
                                          Chin_Subj_Proofreading_Group5_CE = names(df[[14]]),
                                          Chin_Subj_Proofreading_Group6_CE = names(df[[15]]),
                                          Chin_Subj_Proofreading_Group7_CE = names(df[[16]]))

Check_row_equality2 <- function(row) {  
  all_equal <- all(row == row[1])  
  return(all_equal)  
}  
  
Row_equalities2 <- apply(Proofreading_datalist_names, 1, Check_row_equality2) 

### I found the names of 8 cols are different and I modfi them.

colnames(df[[11]])[colnames(df[[11]]) == "target_population_N"] <- "Target_Population_N"

# rm(Proofreading_Data_Names,row_equalities2,check_row_equality2)
```


## merge data
firstly, I will merge group 2,4,5,6,7
```{r}
Group24567_1 <- dplyr::bind_rows(df[[3]],df[[6]],df[[7]],df[[8]],df[[9]]) %>% 
  # dplyr::filter(Coder != "final") %>% 
  dplyr::select(-c(8,9,14:18,27,28,37,38))

Group24567_2 <- dplyr::bind_rows(df[[11]],df[[13]],df[[14]],df[[15]],df[[16]]) %>% 
  # dplyr::filter(Coder != "final") %>%
  dplyr::rename_at(vars(1:4,7), ~paste0(., "_N"))

Group24567_bind <-  cbind(Group24567_1,Group24567_2) %>% 
  dplyr::select(1,30,2,31,8,32,11,33,3:7,9,10,12:29,34:48)

# table(Group24567_1$Coder)
```


Secondly, I will find distinctinve Suppl IDs
```{r}
Suppl_ID <- dplyr::bind_rows(df[[2]],df[[5]]) %>% 
  dplyr::filter(Coder == "final") %>%
  dplyr::distinct(Article_IDs)
```


Thirdly, I will megrge group 1.
```{r}
Group1_1 <- df[[1]] %>% 
  # dplyr::filter(Coder != "final") %>% 
  dplyr::slice(-c(693:696,725:728)) %>%  ## filter Article_IDs 20185094 and 20185116
  dplyr::select(-c(8,9,14:18,27,28,37,38)) %>% 
  dplyr::mutate(Subjects_Group = ifelse(Subjects_Group == "3+M8:M28",3,Subjects_Group))

Group1_suppl <- df[[2]] %>% 
  # dplyr::filter(Coder != "final") %>% 
  dplyr::rename_at(vars(8,9,14:18,27,28,37,38), ~paste0(., "_N")) %>% 
  dplyr::mutate(Coder_N = NA, Article_IDs_N = NA, Study_Number_N = NA, 
                Subjects_Group_N = NA, Remark1_N = NA, Remark2_N = NA, 
                Remark3_N = NA, Coder2_N= NA) %>% 
  dplyr::mutate(Coder_N = Coder, Coder2_N = Coder,Article_IDs_N = Article_IDs,
                Study_Number_N = Study_Number, Subjects_Group_N = Subjects_Group, Remark1_N = Remark1,
                Remark2_N = Remark2, Remark3_N = Remark3)

Group1_2 <- df[[10]] %>% 
  # dplyr::filter(Coder != "final") %>%
  dplyr::slice(-c(693:700,729:740)) %>%  ## filter Article_IDs 20185094 and 20185116
  dplyr::rename_at(vars(1:4,7), ~paste0(., "_N"))

Group1_bind <- cbind(Group1_1,Group1_2) %>%
  dplyr::select(1,30,2,31,8,32,11,33,3:7,9,10,12:29,34:48)

Group1_bind <- bind_rows(Group1_bind,Group1_suppl)
```


Fouth, I will merge group6.
```{r}
Group3_1 <- df[[4]] %>% 
  dplyr::slice(-c(405:420,541:544,673:680,701:708,721:732)) %>% ## Filter Article_IDs 20183039, 20184027, 20211015, 20211018, 20183137, and 20213153
  dplyr::select(-c(8,9,14:18,27,28,37,38))

# continue sorting data
Group3_suppl <- df[[5]] %>% 
  dplyr::rename_at(vars(8,9,14:18,27,28,37,38), ~paste0(., "_N")) %>% 
  dplyr::mutate(Coder_N = NA, Article_IDs_N = NA, Study_Number_N = NA, 
                Subjects_Group_N = NA, Remark1_N = NA, Remark2_N = NA, 
                Remark3_N = NA, Coder2_N= NA) %>% 
  dplyr::mutate(Coder_N = Coder, Coder2_N = Coder,Article_IDs_N = Article_IDs,
                Study_Number_N = Study_Number, Subjects_Group_N = Subjects_Group, Remark1_N = Remark1,
                Remark2_N = Remark2, Remark3_N = Remark3)

Group3_2 <- df[[12]] %>% 
  dplyr::slice(-c(405:412,533:548,677:700,721:736,749:768)) %>% ## ## Filter Article_IDs 20183039, 20184027, 20211015, 20211018, 20183137, and 20213153
  dplyr::rename_at(vars(1:4,7), ~paste0(., "_N"))

Group3_bind <- cbind(Group3_1,Group3_2) %>%
  dplyr::select(1,30,2,31,8,32,11,33,3:7,9,10,12:29,34:48) %>% 
  rbind(Group3_suppl)
```


### Combine the coding data and the proofreading data
```{r message=FALSE, warning=FALSE}
Coding_consistency_preprocess_data <- bind_rows(Group24567_bind,Group1_bind,Group3_bind)

num_groups <- nrow(Coding_consistency_preprocess_data) / 4

Coding_consistency_preprocess_data$Sequence_IDs <- sprintf("%04d_%d", rep(1:num_groups, each=4), rep(1:4, times=num_groups))

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data %>% 
  dplyr::select(49,1:48) %>% 
  dplyr::filter(Coder != "final")

# writexl::write_xlsx(Coding_consistency_preprocess_data1,"Coding_consistency_preprocess_data1.xlsx")
```


## Article_IDs
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(Article_IDs_N = ifelse(Article_IDs_N == "　",NA,Article_IDs_N),
                Article_IDs_N = ifelse(Coder == "check" & is.na(Article_IDs_N),"Chin_Subj",Article_IDs_N))

# table(Coding_consistency_preprocess_data1$Article_IDs_N)

rm(results)


results <- data.frame(Article_Title= character(),
                      Article_IDs_N_coder1 = as.character(),
                      Article_IDs_N_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder2_code <- Coding_consistency_preprocess_data1$Article_IDs_N[i+1]
  stored_score <- Coding_consistency_preprocess_data1$Article_IDs_N[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code) || grepl(coder2_code, coder1_code)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     Article_IDs_N_coder1 = coder1_code,
                                     Article_IDs_N_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")

## 20085033
Coding_consistency_preprocess_data1$Article_IDs_N[c(2241,2244)] <- 1

## 20085054
Coding_consistency_preprocess_data1$Article_IDs_N[c(2274,2277)] <- 3
```

## Study Number N
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(Study_Number_N = ifelse(Study_Number_N == "　",NA,Study_Number_N),
                Study_Number_N = ifelse(Coder == "check" & is.na(Study_Number_N),"Chin_Subj",Study_Number_N))

# table(Coding_consistency_preprocess_data1$Study_Number_N)

rm(results)

results <- data.frame(Article_IDs_N = character(),
                      Study_Number_N_coder1 = as.character(),
                      Study_Number_N_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$Study_Number_N[i]
  coder2_code <- Coding_consistency_preprocess_data1$Study_Number_N[i+1]
  stored_score <- Coding_consistency_preprocess_data1$Study_Number_N[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code) || grepl(coder2_code, coder1_code)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     Study_Number_N_coder1 = coder1_code,
                                     Study_Number_N_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")


## revise check
## 20083038
Coding_consistency_preprocess_data1$Study_Number_N[117] <- 1
 
## 20083039
Coding_consistency_preprocess_data1$Study_Number_N[123] <- 1

## 20181168
Coding_consistency_preprocess_data1$Study_Number_N[312] <- 1

## 20211046
Coding_consistency_preprocess_data1$Study_Number_N[1296] <- 3

## 20212097
Coding_consistency_preprocess_data1$Study_Number_N[2790] <- 1
Coding_consistency_preprocess_data1$Study_Number_N[2793] <- 1

## 20182182
Coding_consistency_preprocess_data1$Study_Number_N[3243] <- 3

## 20182193
Coding_consistency_preprocess_data1$Study_Number_N[3270] <- 3

## 20185037
Coding_consistency_preprocess_data1$Study_Number_N[3378] <- 3

## 20212172
Coding_consistency_preprocess_data1$Study_Number_N[3546] <- 3

## 20083017
Coding_consistency_preprocess_data1$Study_Number_N[3903] <- 1

## 20082044
Coding_consistency_preprocess_data1$Study_Number_N[4485] <- 1
Coding_consistency_preprocess_data1$Study_Number_N[4488] <- 1  
```


## Subjects Group N
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(Subjects_Group_N = ifelse(Subjects_Group_N == "　",NA,Subjects_Group_N),
                Subjects_Group_N = ifelse(Coder == "check" & is.na(Subjects_Group_N),"Chin_Subj",Subjects_Group_N))

# table(Coding_consistency_preprocess_data1$Subjects_Group_N)

rm(results)


results <- data.frame(Article_IDs_N = character(),
                      Subjects_Group_N_coder1 = as.character(),
                      Subjects_Group_N_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$Subjects_Group_N[i]
  coder2_code <- Coding_consistency_preprocess_data1$Subjects_Group_N[i+1]
  stored_score <- Coding_consistency_preprocess_data1$Subjects_Group_N[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code) || grepl(coder2_code, coder1_code)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     Subjects_Group_N_coder1 = coder1_code,
                                     Subjects_Group_N_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")


## revise check
```


## Article Title
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(Article_Title  = ifelse(Article_Title == "　",NA,Article_Title),
                Article_Title  = ifelse(Coder == "check" & is.na(Article_Title),"Chin_Subj",Article_Title))

# table(Coding_consistency_preprocess_data1$Article_Title)

rm(results)


results <- data.frame(Article_Title= character(),
                      Article_Title_coder1 = as.character(),
                      Article_Title_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$Article_Title[i]
  coder2_code <- Coding_consistency_preprocess_data1$Article_Title[i+1]
  stored_score <- Coding_consistency_preprocess_data1$Article_Title[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code) || grepl(coder2_code, coder1_code)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     Article_Title_coder1 = coder1_code,
                                     Article_Title_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")


## revise check

## 20081070
Coding_consistency_preprocess_data1$Article_Title[21] <- 1

## 20182289
Coding_consistency_preprocess_data1$Article_Title[474] <- 1

## 20082105
Coding_consistency_preprocess_data1$Article_Title[798] <- 3

## 20082296
Coding_consistency_preprocess_data1$Article_Title[2211] <- 3
Coding_consistency_preprocess_data1$Article_Title[2214] <- 3
Coding_consistency_preprocess_data1$Article_Title[2217] <- 3

## 20085035
Coding_consistency_preprocess_data1$Article_Title[2247] <- 3

## 20181002
Coding_consistency_preprocess_data1$Article_Title[2280] <- 3

## 20181008
Coding_consistency_preprocess_data1$Article_Title[2310] <- 3

## 20181011
Coding_consistency_preprocess_data1$Article_Title[2313] <- 3

## 20181017
Coding_consistency_preprocess_data1$Article_Title[2325] <- 3
Coding_consistency_preprocess_data1$Article_Title[2328] <- 3
Coding_consistency_preprocess_data1$Article_Title[2331] <- 3
Coding_consistency_preprocess_data1$Article_Title[2334] <- 3

## 20181020
Coding_consistency_preprocess_data1$Article_Title[2337] <- 3
Coding_consistency_preprocess_data1$Article_Title[2346] <- 3
Coding_consistency_preprocess_data1$Article_Title[2349] <- 3

## 20181022
Coding_consistency_preprocess_data1$Article_Title[c(2352,2355,2358,2361,2364,2367)] <- 3

## 20181023
Coding_consistency_preprocess_data1$Article_Title[c(2370,2373,2376,2379,2382,2385)] <- 3

## 20182104
Coding_consistency_preprocess_data1$Article_Title[c(2445,2448)] <- 3

## 20182125
Coding_consistency_preprocess_data1$Article_Title[c(2481,2484,2487,2490,2493)] <- 3

## 20183052
Coding_consistency_preprocess_data1$Article_Title[4722] <- 3

## 20183054
Coding_consistency_preprocess_data1$Article_Title[4725] <- 3

## 20184022
Coding_consistency_preprocess_data1$Article_Title[c(4770,4773,4776,4779,4782,4785)] <- 3

## 20184127
Coding_consistency_preprocess_data1$Article_Title[1893] <- 3

## 20182103
Coding_consistency_preprocess_data1$Article_Title[c(2421,2424,2427,2430,2433,2436)] <- 3

## 20182075
Coding_consistency_preprocess_data1$Article_Title[2388] <- 3

## 20182085
Coding_consistency_preprocess_data1$Article_Title[2391] <- 3
```


## First Author
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(First_Author  = ifelse(First_Author == "　",NA,First_Author),
                First_Author  = ifelse(Coder == "check" & is.na(First_Author),"Chin_Subj",First_Author))

# table(Coding_consistency_preprocess_data1$First_Author)

rm(results)


results <- data.frame(Article_Title= character(),
                      First_Author_coder1 = as.character(),
                      First_Author_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$First_Author[i]
  coder2_code <- Coding_consistency_preprocess_data1$First_Author[i+1]
  stored_score <- Coding_consistency_preprocess_data1$First_Author[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code) || grepl(coder2_code, coder1_code)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     First_Author_coder1 = coder1_code,
                                     First_Author_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")


###          no found
```


## Journal
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(Journal = ifelse(Journal == "　",NA,Journal),
                Journal = ifelse(Coder == "check" & is.na(Journal),"Chin_Subj",Journal))

# table(Coding_consistency_preprocess_data1$Journal)

rm(results)


results <- data.frame(Article_Title= character(),
                      Journal_coder1 = as.character(),
                      Journal_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$Journal[i]
  coder2_code <- Coding_consistency_preprocess_data1$Journal[i+1]
  stored_score <- Coding_consistency_preprocess_data1$Journal[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code) || grepl(coder2_code, coder1_code)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     Journal_coder1 = coder1_code,
                                     Journal_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")

## 20182248
Coding_consistency_preprocess_data1$Journal[c(375,378,381)] <- 1

## 20181002
Coding_consistency_preprocess_data1$Journal[2280] <- 1

## 20181005
Coding_consistency_preprocess_data1$Journal[c(2283,2286,2289,2292,2295,2298)] <- 1

## 20181007
Coding_consistency_preprocess_data1$Journal[c(2301,2304,2307)] <- 1

## 20181008
Coding_consistency_preprocess_data1$Journal[2310] <- 1

## 20181011
Coding_consistency_preprocess_data1$Journal[2313] <- 1

## 20181015
Coding_consistency_preprocess_data1$Journal[c(2316,2319)] <- 1

## 20181017
Coding_consistency_preprocess_data1$Journal[c(2325,2328,2331,2334)] <- 1

## 20181020
Coding_consistency_preprocess_data1$Journal[c(2337,2346,2349)] <- 1

## 20181022
Coding_consistency_preprocess_data1$Journal[c(2352,2355,2358,2361,2364,2367)] <- 1

## 20183145
Coding_consistency_preprocess_data1$Journal[2568] <- 1

## 20183256
Coding_consistency_preprocess_data1$Journal[3363] <- 3

## 20081043
Coding_consistency_preprocess_data1$Journal[c(3813,3816,3819,3822)] <- 3

## 20081055
Coding_consistency_preprocess_data1$Journal[c(3843,3846)] <- 3

## 20213137
Coding_consistency_preprocess_data1$Journal[c(5040,5043,5046,5049)] <- 1

## 20213153
Coding_consistency_preprocess_data1$Journal[c(5052,5055,5058,5061,5064)] <- 1
```


## Abstract1
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(Abstract1 = ifelse(Abstract1 == "　",NA,Abstract1),
                Abstract1 = ifelse(Coder == "check" & is.na(Abstract1),"Chin_Subj",Abstract1))

# table(Coding_consistency_preprocess_data1$Journal)

rm(results)


results <- data.frame(Article_Title= character(),
                      Abstract1_coder1 = as.character(),
                      Abstract1_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$Abstract1[i]
  coder2_code <- Coding_consistency_preprocess_data1$Abstract1[i+1]
  stored_score <- Coding_consistency_preprocess_data1$Abstract1[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code) || grepl(coder2_code, coder1_code)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     Abstract1_coder1 = coder1_code,
                                     Abstract1_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")

## 20082002
Coding_consistency_preprocess_data1$Abstract1[108] <- 1

## 20083054
Coding_consistency_preprocess_data1$Abstract1[135] <- 1

## 20181178
Coding_consistency_preprocess_data1$Abstract1[c(333,336)] <- 2

## 20182267
Coding_consistency_preprocess_data1$Abstract1[c(414,417)] <- 2

## 20085023
Coding_consistency_preprocess_data1$Abstract1[2232] <- 1

## 20181017
Coding_consistency_preprocess_data1$Abstract1[c(2325,2328,2331,2334)] <- 1

## 20181022
Coding_consistency_preprocess_data1$Abstract1[c(2352,2355,2358,2361,2364,2367)] <- 1

# 20181023
Coding_consistency_preprocess_data1$Abstract1[c(2382,2385)] <- 3

## 20185111
Coding_consistency_preprocess_data1$Abstract1[4269] <- 1

## 20083114
Coding_consistency_preprocess_data1$Abstract1[4506] <- 2

## 20083128
Coding_consistency_preprocess_data1$Abstract1[c(4518,4521)] <- 1

## 20181212
Coding_consistency_preprocess_data1$Abstract1[4611] <- 2

## 20181187
Coding_consistency_preprocess_data1$Abstract1[c(363,366,369)] <- 2

## 20182103
Coding_consistency_preprocess_data1$Abstract1[c(2421,2424,2427,2430,2433,2436)] <- 1

### 20182193
Coding_consistency_preprocess_data1$Abstract1[3270] <- 3

## 20181081
Coding_consistency_preprocess_data1$Abstract1[3174] <- 2

## 20185037
Coding_consistency_preprocess_data1$Abstract1[3378] <- 3

## 20212172
Coding_consistency_preprocess_data1$Abstract1[3546] <- 3

## 20183165
Coding_consistency_preprocess_data1$Abstract1[2592] <- 1

## 20183200
Coding_consistency_preprocess_data1$Abstract1[c(2649,2652,2655,2658)] <- 1
```


## Abstract2
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(Abstract2 = ifelse(Abstract2 == "　",NA,Abstract2),
                Abstract2 = ifelse(Coder == "check" & is.na(Abstract2),"Chin_Subj",Abstract2))

# table(Coding_consistency_preprocess_data1$Abstract2)

rm(results)


results <- data.frame(Article_Title= character(),
                      Abstract2_coder1 = as.character(),
                      Abstract2_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$Abstract2[i]
  coder2_code <- Coding_consistency_preprocess_data1$Abstract2[i+1]
  stored_score <- Coding_consistency_preprocess_data1$Abstract2[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    Coding_consistency_preprocess_data1$Abstract2[i+2] <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code) || grepl(coder2_code, coder1_code)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     Abstract2_coder1 = coder1_code,
                                     Abstract2_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")

## 20181081
Coding_consistency_preprocess_data1$Abstract2[3174] <- 1

## 20182103
Coding_consistency_preprocess_data1$Abstract2[c(2421,2424,2427,2430,2433,2436)] <- 1

## 20182183
Coding_consistency_preprocess_data1$Abstract2[c(3252,3255)] <- 1

## 20183200
Coding_consistency_preprocess_data1$Abstract2[c(2649,2652)] <- 1

## 20183226
Coding_consistency_preprocess_data1$Abstract2[c(3318,3321,3324,3327)] <- 1

## 20183227
Coding_consistency_preprocess_data1$Abstract2[3330] <- 1

## 20215007
Coding_consistency_preprocess_data1$Abstract2[c(3624,3627)] <- 1

## 20215042
Coding_consistency_preprocess_data1$Abstract2[3666] <- 1

## 20185111
Coding_consistency_preprocess_data1$Abstract2[4269] <- 1

## 20183324
Coding_consistency_preprocess_data1$Abstract2[513] <- 1 
```


## Remark1 N
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(Remark1_N = ifelse(Remark1_N == "　",NA,Remark1_N),
                Remark1_N = ifelse(Coder == "check" & is.na(Remark1_N),"Chin_Subj",Remark1_N))

# table(Coding_consistency_preprocess_data1$Remark1_N)

rm(results)


results <- data.frame(Article_Title= character(),
                      Remark1_N_coder1 = as.character(),
                      Remark1_N_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$Remark1_N[i]
  coder2_code <- Coding_consistency_preprocess_data1$Remark1_N[i+1]
  stored_score <- Coding_consistency_preprocess_data1$Remark1_N[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    Coding_consistency_preprocess_data1$Remark1_N[i+2] <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code) || grepl(coder2_code, coder1_code)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     Remark1_N_coder1 = coder1_code,
                                     Remark1_N_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")


## NO FOUND
```


## Remark2 N
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(Remark2_N = ifelse(Remark2_N == "　",NA,Remark2_N),
                Remark2_N = ifelse(Coder == "check" & is.na(Remark1_N),"Chin_Subj",Remark2_N))

# table(Coding_consistency_preprocess_data1$Remark2_N)

rm(results)


results <- data.frame(Article_Title= character(),
                      Remark2_N_coder1 = as.character(),
                      Remark2_N_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$Remark2_N[i]
  coder2_code <- Coding_consistency_preprocess_data1$Remark2_N[i+1]
  stored_score <- Coding_consistency_preprocess_data1$Remark2_N[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    Coding_consistency_preprocess_data1$Remark2_N[i+2] <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code) || grepl(coder2_code, coder1_code)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     Remark2_N_coder1 = coder1_code,
                                     Remark2_N_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")

## NO FOUND
```


## Study Type
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(Study_Type = ifelse(Study_Type == "　",NA,Study_Type),
                Study_Type = ifelse(Coder == "check" & is.na(Study_Type),"Chin_Subj",Study_Type))

# table(Coding_consistency_preprocess_data1$Remark1_N)

rm(results)


results <- data.frame(Article_Title= character(),
                      Study_Type_coder1 = as.character(),
                      Study_Type_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$Study_Type[i]
  coder2_code <- Coding_consistency_preprocess_data1$Study_Type[i+1]
  stored_score <- Coding_consistency_preprocess_data1$Study_Type[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    Coding_consistency_preprocess_data1$Study_Type[i+2] <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code) || grepl(coder2_code, coder1_code)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     Study_Type_coder1 = coder1_code,
                                     Study_Type_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")

## 20081026
Coding_consistency_preprocess_data1$Study_Type[3762] <- 1

## 20185007
Coding_consistency_preprocess_data1$Study_Type[c(2706,2709,2712,2715)] <- 1

## 20085040
Coding_consistency_preprocess_data1$Study_Type[c(2253,2256,2259)] <- 1

## 20085054
Coding_consistency_preprocess_data1$Study_Type[c(2271,2274,2277)] <- 1

## 20181152
Coding_consistency_preprocess_data1$Study_Type[c(285,291)] <- 1

## 20182261
Coding_consistency_preprocess_data1$Study_Type[405] <- 1

## 20182268
Coding_consistency_preprocess_data1$Study_Type[c(423,426)] <- 1

## 20182275
Coding_consistency_preprocess_data1$Study_Type[453] <- 1

## 20182283
Coding_consistency_preprocess_data1$Study_Type[c(465,468)] <- 1

## 20182297
Coding_consistency_preprocess_data1$Study_Type[477] <- 1

## 20183314
Coding_consistency_preprocess_data1$Study_Type[c(489,492)] <- 1

## 20183321
Coding_consistency_preprocess_data1$Study_Type[c(498,501,504,507)] <- 1

## 20185007
Coding_consistency_preprocess_data1$Study_Type[c(2706,2709,2712,2715)] <- 1

## 20185030
Coding_consistency_preprocess_data1$Study_Type[2754] <- 1

## 20082365
Coding_consistency_preprocess_data1$Study_Type[3033] <- 2
```


## Sample Size
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(Sample_Size = ifelse(Sample_Size == "　",NA,Sample_Size),
                Sample_Size = ifelse(Coder == "check" & is.na(Sample_Size),"Chin_Subj",Sample_Size))

# table(Coding_consistency_preprocess_data1$Sample_Size)

rm(results)


results <- data.frame(Article_Title= character(),
                      Sample_Size_coder1 = as.character(),
                      Sample_Size_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$Sample_Size[i]
  coder2_code <- Coding_consistency_preprocess_data1$Sample_Size[i+1]
  stored_score <- Coding_consistency_preprocess_data1$Sample_Size[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    Coding_consistency_preprocess_data1$Sample_Size[i+2] <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code) || grepl(coder2_code, coder1_code)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     Sample_Size_coder1 = coder1_code,
                                     Sample_Size_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")

# 
# results %>% 
#   distinct(Article_IDs_N)
```


## Gender
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(Gender = ifelse(Gender == "　",NA,Gender),
                Gender = ifelse(Coder == "check" & is.na(Gender),"Chin_Subj",Gender))

# table(Coding_consistency_preprocess_data1$Gender)

rm(results)


results <- data.frame(Article_Title= character(),
                      Gender_coder1 = as.character(),
                      Gender_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$Gender[i]
  coder2_code <- Coding_consistency_preprocess_data1$Gender[i+1]
  stored_score <- Coding_consistency_preprocess_data1$Gender[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    Coding_consistency_preprocess_data1$Gender[i+2] <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code) || grepl(coder2_code, coder1_code)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     Gender_coder1 = coder1_code,
                                     Gender_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")


## 20182248
Coding_consistency_preprocess_data1$Gender[c(375,378,381)] <- 1

## 20182268
Coding_consistency_preprocess_data1$Gender[438] <- 1

## 20183192
Coding_consistency_preprocess_data1$Gender[c(2634,2637)] <- 1

## 20183198
Coding_consistency_preprocess_data1$Gender[c(2640,2643,2646)] <- 1
```


## Female Num
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(Female_Num = ifelse(Female_Num == "　",NA,Female_Num),
                Female_Num = ifelse(Coder == "check" & is.na(Female_Num),"Chin_Subj",Female_Num))

# table(Coding_consistency_preprocess_data1$Female_Num)

rm(results)


results <- data.frame(Article_Title= character(),
                      Female_Num_coder1 = as.character(),
                      Female_Num_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$Female_Num[i]
  coder2_code <- Coding_consistency_preprocess_data1$Female_Num[i+1]
  stored_score <- Coding_consistency_preprocess_data1$Female_Num[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    Coding_consistency_preprocess_data1$Female_Num[i+2] <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code) || grepl(coder2_code, coder1_code)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     Female_Num_coder1 = coder1_code,
                                     Female_Num_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")

## 20081099
Coding_consistency_preprocess_data1$Female_Num[51] <- 3

## 20181166
Coding_consistency_preprocess_data1$Female_Num[309] <- 1

## 20182248
Coding_consistency_preprocess_data1$Female_Num[c(375,378,381)] <- 1

## 20182267
Coding_consistency_preprocess_data1$Female_Num[414] <- 1

## 20182289
Coding_consistency_preprocess_data1$Female_Num[474] <- 1

## 20183321
Coding_consistency_preprocess_data1$Female_Num[c(504,507)] <- 1

## 20183333
Coding_consistency_preprocess_data1$Female_Num[543] <- 1

## 20082105
Coding_consistency_preprocess_data1$Female_Num[c(786,789,792,795,798,801)] <- 1

## 20182035
Coding_consistency_preprocess_data1$Female_Num[c(1665,1668)] <- 1

## 20183107
Coding_consistency_preprocess_data1$Female_Num[1776] <- 1

## 20214015
Coding_consistency_preprocess_data1$Female_Num[2070] <- 1

## 20082279
Coding_consistency_preprocess_data1$Female_Num[2187] <- 1

## 20181007
Coding_consistency_preprocess_data1$Female_Num[2301] <- 1

## 20182101
Coding_consistency_preprocess_data1$Female_Num[2409] <- 1

## 20182103
Coding_consistency_preprocess_data1$Female_Num[c(2430,2433,2436,2439,2442)] <- 1

## 20185003
Coding_consistency_preprocess_data1$Female_Num[c(2697,2700)] <- 1

## 20183226
Coding_consistency_preprocess_data1$Female_Num[3321] <- 1

## 20083007
Coding_consistency_preprocess_data1$Female_Num[3894] <- 1

## 20181104
Coding_consistency_preprocess_data1$Female_Num[3987] <- 1

## 20082030
Coding_consistency_preprocess_data1$Female_Num[4467] <- 1

## 20083112
Coding_consistency_preprocess_data1$Female_Num[4500] <- 1

## 20083114
Coding_consistency_preprocess_data1$Female_Num[4506] <- 1

## 20181212
Coding_consistency_preprocess_data1$Female_Num[c(4608,4611)] <- 1
```


## Male Num
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(Male_Num = ifelse(Male_Num == "　",NA,Male_Num),
                Male_Num = ifelse(Coder == "check" & is.na(Male_Num),"Chin_Subj",Male_Num))

# table(Coding_consistency_preprocess_data1$Male_Num)

rm(results)


results <- data.frame(Article_Title= character(),
                      Male_Num_coder1 = as.character(),
                      Male_Num_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$Male_Num[i]
  coder2_code <- Coding_consistency_preprocess_data1$Male_Num[i+1]
  stored_score <- Coding_consistency_preprocess_data1$Male_Num[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    Coding_consistency_preprocess_data1$Male_Num[i+2] <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code) || grepl(coder2_code, coder1_code)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     Male_Num_coder1 = coder1_code,
                                     Male_Num_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")


## 20081099
Coding_consistency_preprocess_data1$Male_Num[51] <- 3

## 20081102
Coding_consistency_preprocess_data1$Male_Num[54] <-  1

## 20181166
Coding_consistency_preprocess_data1$Male_Num[309] <- 1

## 20181178
Coding_consistency_preprocess_data1$Male_Num[c(333,336)] <- 1

## 20182248
Coding_consistency_preprocess_data1$Male_Num[c(375,378,381)] <- 1

## 20182257
Coding_consistency_preprocess_data1$Male_Num[390] <- 1

## 20182267
Coding_consistency_preprocess_data1$Male_Num[417] <- 1

## 20183321
Coding_consistency_preprocess_data1$Male_Num[c(498,501)] <- 1

## 20082105
Coding_consistency_preprocess_data1$Male_Num[c(786,789,792,795,798,801)] <- 1

## 20211040
Coding_consistency_preprocess_data1$Male_Num[1278] <- 1

## 20214015
Coding_consistency_preprocess_data1$Male_Num[2070] <- 1

## 20082279
Coding_consistency_preprocess_data1$Male_Num[2187] <- 1

## 20082283
Coding_consistency_preprocess_data1$Male_Num[2202] <- 1

## 20181007
Coding_consistency_preprocess_data1$Male_Num[2301] <- 1

## 20181023
Coding_consistency_preprocess_data1$Male_Num[c(2370,2373)] <- 1

## 20182103
Coding_consistency_preprocess_data1$Male_Num[c(2439,2442)] <- 1

## 20182137
Coding_consistency_preprocess_data1$Male_Num[c(2514,2517)] <- 1

## 20185003
Coding_consistency_preprocess_data1$Male_Num[c(2697,2700)] <- 1

## 20083007
Coding_consistency_preprocess_data1$Male_Num[3894] <- 1

## 20082030
Coding_consistency_preprocess_data1$Male_Num[4467] <- 1

## 20083112
Coding_consistency_preprocess_data1$Male_Num[4500] <- 1

## 20083114
Coding_consistency_preprocess_data1$Male_Num[4506] <- 1

## 20181212
Coding_consistency_preprocess_data1$Male_Num[c(4608,4611)] <- 1
```


## Age
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(Age = ifelse(Age == "　",NA,Age),
                Age = ifelse(Coder == "check" & is.na(Age),"Chin_Subj",Age))

# table(Coding_consistency_preprocess_data1$Age)

rm(results)


results <- data.frame(Article_Title= character(),
                      Age_coder1 = as.character(),
                      Age_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$Age[i]
  coder2_code <- Coding_consistency_preprocess_data1$Age[i+1]
  stored_score <- Coding_consistency_preprocess_data1$Age[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    Coding_consistency_preprocess_data1$Age[i+2] <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code) || grepl(coder2_code, coder1_code)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     Age_coder1 = coder1_code,
                                     Age_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")

## 20181152
Coding_consistency_preprocess_data1$Age[c(288,291)] <- 1

## 20213091
Coding_consistency_preprocess_data1$Age[678] <- 1

## 20181023
Coding_consistency_preprocess_data1$Age[c(2370,2373,2376,2379,2382,2385)] <- 1

## 20182118
Coding_consistency_preprocess_data1$Age[c(2463,2466,2469,2472)] <- 1

## 20182153
Coding_consistency_preprocess_data1$Age[2559] <- 1

## 20183154
Coding_consistency_preprocess_data1$Age[2580] <- 1

## 20183171
Coding_consistency_preprocess_data1$Age[2607] <- 1

## 20183198
Coding_consistency_preprocess_data1$Age[c(2640,2643,2646)] <- 1

## 20213153
Coding_consistency_preprocess_data1$Age[c(5052,5055)] <- 1

```


## M_age
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(M_age = ifelse(M_age == "　",NA,M_age),
                M_age = ifelse(Coder == "check" & is.na(M_age),"Chin_Subj",M_age))

# table(Coding_consistency_preprocess_data1$M_age)

rm(results)


results <- data.frame(Article_Title= character(),
                      M_age_coder1 = as.character(),
                      M_age_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$M_age[i]
  coder2_code <- Coding_consistency_preprocess_data1$M_age[i+1]
  stored_score <- Coding_consistency_preprocess_data1$M_age[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    Coding_consistency_preprocess_data1$M_age[i+2] <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code) || grepl(coder2_code, coder1_code)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     M_age_coder1 = coder1_code,
                                     M_age_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")

## 20081061
Coding_consistency_preprocess_data1$M_age[3] <- 1

## 20081124
Coding_consistency_preprocess_data1$M_age[c(69,72,75,78)] <- 1

## 20184045
Coding_consistency_preprocess_data1$M_age[1170] <- 3

## 20213254
Coding_consistency_preprocess_data1$M_age[1479] <- 3

## 20213296
Coding_consistency_preprocess_data1$M_age[2043] <- 3

## 20215102
Coding_consistency_preprocess_data1$M_age[2097] <- 3

### 20085044
Coding_consistency_preprocess_data1$M_age[c(2262,2265,2268)] <- 1

## 20181007
Coding_consistency_preprocess_data1$M_age[c(2301,2304,2307)] <- 1

## 20181022
Coding_consistency_preprocess_data1$M_age[c(2352,2358)] <- 1

## 20183182
Coding_consistency_preprocess_data1$M_age[2616] <- 1

## 20185001
Coding_consistency_preprocess_data1$M_age[c(2688,2691,2694)] <- 3

## 20212091
Coding_consistency_preprocess_data1$M_age[2787] <- 1

## 20214070
Coding_consistency_preprocess_data1$M_age[2931] <- 3

## 20214073
Coding_consistency_preprocess_data1$M_age[2937] <- 3

## 20182184
Coding_consistency_preprocess_data1$M_age[3258] <- 1

## 20083114
Coding_consistency_preprocess_data1$M_age[4506] <- 1

## 20083052
Coding_consistency_preprocess_data1$M_age[132] <- 1
```


## SD_age
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(SD_age = ifelse(SD_age == "　",NA,SD_age),
                SD_age = ifelse(Coder == "check" & is.na(SD_age),"Chin_Subj",SD_age))

# table(Coding_consistency_preprocess_data1$SD_age)

rm(results)


results <- data.frame(Article_Title= character(),
                      SD_age_coder1 = as.character(),
                      SD_age_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$SD_age[i]
  coder2_code <- Coding_consistency_preprocess_data1$SD_age[i+1]
  stored_score <- Coding_consistency_preprocess_data1$SD_age[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    Coding_consistency_preprocess_data1$SD_age[i+2] <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code) || grepl(coder2_code, coder1_code)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     SD_age_coder1 = coder1_code,
                                     SD_age_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")
```


## Other age
```{r}
## first, I process NA value or NULL value

Coding_consistency_preprocess_data1 <- Coding_consistency_preprocess_data1 %>% 
  dplyr::mutate(Other_age = ifelse(SD_age == "　",NA,Other_age),
                Other_age = ifelse(Other_age == "check" & is.na(Other_age),"Chin_Subj",Other_age))

# table(Coding_consistency_preprocess_data1$Other_age)

rm(results)


results <- data.frame(Article_Title= character(),
                      Other_age_coder1 = as.character(),
                      Other_age_coder2 = as.character(),
                      calculated_score = numeric(), 
                      stored_score = character(), 
                      stringsAsFactors = FALSE)


for (i in seq(1, nrow(Coding_consistency_preprocess_data1), by = 3))  {
  
  Article_IDs_N <- Coding_consistency_preprocess_data1$Article_IDs_N[i]
  coder1_code <- Coding_consistency_preprocess_data1$Other_age[i]
  coder2_code <- Coding_consistency_preprocess_data1$Other_age[i+1]
  stored_score <- Coding_consistency_preprocess_data1$Other_age[i+2]
  
   if (is.na(coder1_code) & is.na(coder2_code)) {
    calculated_score <- 3
    Coding_consistency_preprocess_data1$Other_age[i+2] <- 3
    
   } else if (is.na(coder1_code) || is.na(coder2_code)){
     calculated_score <- 1
     
   } else if (coder1_code == coder2_code) {
      calculated_score <- 3
      
    } else if (grepl(coder1_code, coder2_code) || grepl(coder2_code, coder1_code)) {
    calculated_score <- 2
    
    } else {
    calculated_score <- 1
    }

results <- rbind(results, data.frame(Article_IDs_N = Article_IDs_N,
                                     Other_age_coder1 = coder1_code,
                                     Other_age_coder2 = coder2_code,
                                     calculated_score = calculated_score, 
                                     stored_score = as.character(stored_score)))
}


results <- results %>% 
  dplyr::mutate(Equal = ifelse(calculated_score == stored_score,"TRUE","FALSE")) %>%
  dplyr::filter(Equal == "FALSE" | calculated_score == 2 | calculated_score == "2" | stored_score == 2 | stored_score == "2")
```

