---
title: "Notebook_Coding_Consistency"
author: "Lei Yue"
date: "2024-12-08"
output: html_document
---

## Load packages
```{r}
rm(list = ls())

if(!require("pacman"))install.packages("pacman")

p_load("here","tidyverse","rio","readxl","irr")

```


## Load data
```{r warning=FALSE}
if (!require("pacman")) install.packages("pacman")

# use package "pacman" as loading R packages tools

pacman::p_load("tidyverse","rio","here")

getwd()

file_list <- list.files(
  here("C:/Users/ynian/Desktop/Stage_2_Code_Data"),
  pattern = ".xlsx",
  full.names = TRUE, recursive = TRUE)

df <- rio::import_list(file_list) 

 
df <-   df[grepl("Group",names(df),ignore.case = TRUE)]


df <- lapply(df, function(df) {  
  df[] <- lapply(df, as.character)  
  return(df)  
})

rm(file_list)
```


## Check col names
I only corrected the inconsistencies in the case of letters and spelling errors in the column names. For any other inconsistencies in column names, I made the necessary modifications during the subsequent merging process.
```{r}
## Check the coding stage col names


Coding_Data_Names <- data.frame(Group1_Coding_Names = names(df[[1]]),
                       Group1_Coding_Suppl_Names = names(df[[2]]),
                       Group2_Coding_Names = names(df[[3]]),
                       Group3_Coding_Names = names(df[[4]]),
                       Group3_Coding_Suppl_Names = names(df[[5]]),
                       Group4_Coding_Names = names(df[[6]]),
                       Group5_Coding_Names = names(df[[7]]),
                       Group6_Coding_Names = names(df[[8]]),
                       Group7_Coding_Names = names(df[[9]])) 

check_row_equality1 <- function(row) {  
  all_equal <- all(row == row[1])  
  return(all_equal)  
}  
  
row_equalities1 <- apply(Coding_Data_Names, 1, check_row_equality1) 

### I found the names of 3,4,5, 19 cols are different and I modfication them.

colnames(df[[9]])[colnames(df[[9]]) == "First_author"] <- "First_Author"

colnames(df[[3]])[colnames(df[[3]]) == "Sample_Szie"] <- "Sample_Size"
colnames(df[[4]])[colnames(df[[4]]) == "Sample_Szie"] <- "Sample_Size"
colnames(df[[5]])[colnames(df[[5]]) == "Sample_Szie"] <- "Sample_Size"
colnames(df[[6]])[colnames(df[[6]]) == "Sample_Szie"] <- "Sample_Size"
colnames(df[[7]])[colnames(df[[7]]) == "Sample_Szie"] <- "Sample_Size"
colnames(df[[9]])[colnames(df[[9]]) == "Sample_Szie"] <- "Sample_Size"

rm(Coding_Data_Names,row_equalities1,check_row_equality1)

## Check the proofreading stage col names
Proofreading_Data_Names <- data.frame(Group1_Proofreading_Names = names(df[[10]]),
                                      Group2_Proofreading_Names = names(df[[11]]),
                                      Group3_Proofreading_Names = names(df[[12]]),
                                      Group4_Proofreading_Names = names(df[[13]]),
                                      Group5_Proofreading_Names = names(df[[14]]),
                                      Group6_Proofreading_Names = names(df[[15]]),
                                      Group7_Proofreading_Names = names(df[[16]]))

check_row_equality2 <- function(row) {  
  all_equal <- all(row == row[1])  
  return(all_equal)  
}  
  
row_equalities2 <- apply(Proofreading_Data_Names, 1, check_row_equality2) 

### I found the names of 8 cols are different and I modfication them.

colnames(df[[11]])[colnames(df[[11]]) == "target_population_N"] <- "Target_Population_N"

rm(Proofreading_Data_Names,row_equalities2,check_row_equality2)

```


## Combining the two stages' data (Group2,4,5,6, and 7)
```{r}
Group24567_1 <- dplyr::bind_rows(df[[3]],df[[6]],df[[7]],df[[8]],df[[9]])


Group24567_2 <- dplyr::bind_rows(df[[11]],df[[13]],df[[14]],df[[15]],df[[16]]) %>% 
  dplyr::rename_at(vars(1:4,7), ~paste0(., "_N"))

  
Group24567_bind <-  cbind(Group24567_1,Group24567_2) %>% 
  dplyr::select(1,30,2,31,8,32,11,33,3:7,9,10,12:29,34:48) %>% 
  dplyr::filter(Coder != "check" & Coder != "Check")

```


## Finding the distinct Ids in suppl documents
```{r }
Suppl_ID <- dplyr::bind_rows(df[[2]],df[[5]]) %>% 
  dplyr::filter(Coder == "final") %>%
  dplyr::distinct(Article_IDs)
```


## Loading the Group 1 data (include suppl)
```{r}
Group1_1 <- df[[1]] %>% 
  dplyr::filter(Coder != "check" & Coder != "Check") %>% 
  dplyr::filter(!Article_IDs %in% Suppl_ID$Article_IDs) %>% 
  dplyr::select(-c(8,9,14:18,27,28,37,38))


Group1_suppl <- df[[2]] %>% 
  dplyr::filter(Coder != "check" & Coder != "Check") %>% 
  dplyr::rename_at(vars(8,9,14:18,27,28,37,38), ~paste0(., "_N")) %>% 
  dplyr::mutate(Coder_N = NA, Article_IDs_N = NA, Study_Number_N = NA, 
                Subjects_Group_N = NA, Remark1_N = NA, Remark2_N = NA, 
                Remark3_N = NA, Coder2_N= NA) %>% 
  dplyr::mutate(Coder_N = Coder, Coder2_N = Coder,Article_IDs_N = Article_IDs,
                Study_Number_N = Study_Number, Subjects_Group_N = Subjects_Group, Remark1_N = Remark1,
                Remark2_N = Remark2, Remark3_N = Remark3)


Group1_2 <- df[[10]] %>% 
  dplyr::filter(Coder != "check" & Coder != "Check") %>% 
  dplyr::filter(!Article_IDs %in% Suppl_ID$Article_IDs) %>%
  dplyr::rename_at(vars(1:4,7), ~paste0(., "_N"))


Group1_bind <- cbind(Group1_1,Group1_2) %>%
  dplyr::select(1,30,2,31,8,32,11,33,3:7,9,10,12:29,34:48)


Group1_bind <- bind_rows(Group1_bind,Group1_suppl)
``` 


## Loading the Group 3 data (include suppl)
```{r}
Group3_1 <- df[[4]] %>% 
  dplyr::filter(!Article_IDs %in% Suppl_ID$Article_IDs) %>% 
  dplyr::select(-c(8,9,14:18,27,28,37,38))

# The coders in the First_Author and Journal columns because of the wrong order of column names, so the two columns of 1:41 data position is reversed, now swap the data back, in order to facilitate the subsequent data merge
target_rows <- rep(seq(1, 161, by = 4), each = 2) + 0:1

Group3_1_Journal <- Group3_1[target_rows,"Journal"]
Group3_1_First_Author <- Group3_1[target_rows,"First_Author"]

Group3_1[target_rows,"Journal"] <- Group3_1_First_Author
Group3_1[target_rows,"First_Author"] <- Group3_1_Journal

Group3_1 <- Group3_1 %>% 
  dplyr::rename(First_Author = "Journal",Journal = "First_Author") %>% 
  dplyr::filter(Coder != "check" & Coder != "Check") %>% 
  dplyr::filter(Article_IDs != 20211037)

# continue sorting data
Group3_suppl <- df[[5]] %>% 
  dplyr::filter(Coder != "check" & Coder != "Check") %>% 
  dplyr::rename_at(vars(8,9,14:18,27,28,37,38), ~paste0(., "_N")) %>% 
  dplyr::mutate(Coder_N = NA, Article_IDs_N = NA, Study_Number_N = NA, 
                Subjects_Group_N = NA, Remark1_N = NA, Remark2_N = NA, 
                Remark3_N = NA, Coder2_N= NA) %>% 
  dplyr::mutate(Coder_N = Coder, Coder2_N = Coder,Article_IDs_N = Article_IDs,
                Study_Number_N = Study_Number, Subjects_Group_N = Subjects_Group, Remark1_N = Remark1,
                Remark2_N = Remark2, Remark3_N = Remark3)


Group3_2 <- df[[12]] %>% 
  dplyr::filter(Coder != "check" & Coder != "Check") %>% 
  dplyr::filter(!Article_IDs %in% Suppl_ID$Article_IDs) %>%
  dplyr::rename_at(vars(1:4,7), ~paste0(., "_N"))


Group3_bind <- cbind(Group3_1,Group3_2) %>%
  dplyr::select(1,30,2,31,8,32,11,33,3:7,9,10,12:29,34:48)

Group3_bind <- bind_rows(Group3_bind,Group3_suppl)
```


## load the replaced article data
```{r}
Relaced_articles <- readxl::read_xlsx("Chin_Subj_articles_replaced_CE.xlsx") %>% 
  dplyr::select(-rows) %>% 
  dplyr::filter(Coder != "check")

Relaced_articles <- Relaced_articles %>% 
  dplyr::mutate(Coder_N = Coder, Coder2_N = Coder,
                Article_IDs_N = Article_IDs, Study_Number_N = Study_Number,
                Subjects_Group_N = Subjects_Group, Remark1_N = Remark1,
                Remark2_N = Remark2, Remark3_N = Remark3,
                Subjects_Area = NA, Subjects_Area_info = NA) %>% 
  dplyr::mutate(across(everything(), as.character))
```


## Combine all data
```{r message=FALSE, warning=FALSE}
Chin_Subj_CE <- bind_rows(Group24567_bind,Group1_bind,Group3_bind,Relaced_articles)
```


## divide two data.frame for the subsequent analysis
```{r}
Coder1 <- Chin_Subj_CE[seq(1, nrow(Chin_Subj_CE), by = 3), ]

Coder2 <- Chin_Subj_CE[seq(1,nrow(Chin_Subj_CE), by = 3), ]
```
