---
title: "Notebook_Data_Analysis_CHN_Sample_Stage2_RR_V2"
author: "Lei Yue"
date: "2024-04-20"
output: html_document
---


In "Notebook_Data_Analysis_CHN_Sample_Stage2_RR_V1.Rmd"， I prereprocess the journal code data. In this Rmd(V2), we enter the informal process data.


First, load library.
# Install and Load packages
```{r message=FALSE, warning=FALSE}
rm(list = ls())

if (!require("pacman")) install.packages("pacman")

# use package "pacman" as loading R packages tools

pacman::p_load("tidyverse","here","rio")
pacman::p_load("geojsonsf","sf","RColorBrewer","ggspatial","patchwork","ggrepel","maps")
pacman::p_load("truncnorm","BayesFactor", "gtools", "bruceR")
```


And then, I loaded the data. The data includes data from the first Stage 1 of the pre-registration report (primarily Census data and CFPS2018 data), Chinese journal coding data, and data from Big Team Science (BTS).
# Load data
## Load the data of stage 1 and Chinese journals coding data
```{r}
load("df_Pre_Stage2_Journal_Code.Rdata")

load("df_chinese_subj_rr_stage1.Rdata")

## Here, I remove some data sets to reduce data set clutter.
rm(df,df_PSA001,df_stage2_Journal_Code,Group1_bind,Group24567_bind,Group3_bind,df_regionCode)
```


## Load the data of BTS
Here, we first converted some data that is not in .xlsx format.
```{r}
library(haven)

## read data
## BTS_Van_Bavel_et_al_2022
BTS_Van_Bavel_et_al_2022 <- haven::read_sav("BTS_Van_Bavel_et_al_2022.sav") %>% 
  dplyr::mutate(Gender = ifelse(Gender == 1, "Male", "Female"))

## BTS_Manokara_et_al_2022
BTS_Manokara_et_al_2022 <- haven::read_sav("BTS_Manokara_et_al_2022.sav") %>% 
  dplyr::mutate(Gender = ifelse(Gender == 1, "Male", "Female"))

## save data
write.csv(BTS_Van_Bavel_et_al_2022, file = "BTS_Van_Bavel_et_al_2022.csv",row.names = FALSE)
write.csv(BTS_Manokara_et_al_2022, file = "BTS_Manokara_et_al_2022.csv",row.names = FALSE)


## Here, I remove some data sets to reduce data set clutter.
rm(BTS_Manokara_et_al_2022,BTS_Van_Bavel_et_al_2022)
```


Next, I loaded all BTS data and processed BTS data.
```{r message=FALSE, warning=FALSE, include=FALSE}
file_list <- list.files(here("D://chin-subj//2_Data_Extraction//2_1 CHN_Journal_Code//2_2_6_Data_Analysis"), ## If you need to learn or repeat the code document, please replace it with your local file address
                        pattern = ".csv",
                        full.names = TRUE,
                        recursive = TRUE)

BTS_data_list <- list()  
 
for (file in file_list) {  
    
  BTS_file <- readr::read_csv(file)  
  BTS_data_list[[tools::file_path_sans_ext(basename(file))]] <- BTS_file  

}  

BTS_data_list <- BTS_data_list[grepl("BTS_",names(BTS_data_list),ignore.case = TRUE)]

BTS_data <- BTS_data_list
rm(BTS_file)


## Here, I remove some data sets to reduce data set clutter.
rm(file,file_list,BTS_data_list)
```


### Process Country code of BTS
Uniform country codes facilitate subsequent data processing and analysis, especially for batch processing and analysis of data. Thus, I created a unified table of country codes.
```{r}
if(!require("countrycode")) install.packages("countrycode")

Countrycodelist <- codelist

Countrycodelist_iso2_iso3 <- Countrycodelist %>% 
  dplyr::select(country.name.en,iso2c,iso3c) %>% 
  dplyr::rename(Countryfullname = 1,ISO2 = 2, ISO3 = 3)

Countrycodelist_iso2_iso3$ISO2[Countrycodelist_iso2_iso3$Countryfullname == "Kosovo"] <- "XK"
Countrycodelist_iso2_iso3$ISO3[Countrycodelist_iso2_iso3$Countryfullname == "Kosovo"] <- "XKX"


## Here, I remove some data sets to reduce data set clutter.
rm(Countrycodelist)
```


The third hypothesis requires countries to be divided into WEIRD and non-WEIRD, so I created a data.frame of WEIRD  countries to facilitate subsequent analysis and visualization
```{r}
WEIRD_code <- codelist %>% 
  dplyr::select(3,6,iso2c,iso3c,region,region23) %>% 
  dplyr::mutate(WEIRD = ifelse(continent == "Europe" | region == "North America","WEIRD",NA),
                WEIRD = ifelse(continent %in% c("Africa","Asia") | region == "Latin America & Caribbean" | region == "East Asia & Pacific", "Non_WEIRD",WEIRD)) %>% 
  dplyr::mutate(WEIRD = ifelse(country.name.en %in% c("Israel","Australia","New Zealand"), "WEIRD",WEIRD),
                WEIRD = ifelse(is.na(WEIRD),"Non_WEIRD",WEIRD))

#table(WEIRD_code$region)
```


In this part, I tried to batch country code.
```{r}
## Handle some more specific encodings
BTS_data[[5]]$Country <- trimws(sub(".*-(\\s*)", "", BTS_data[[5]]$Country)) 
BTS_data[[14]]$Country <- trimws(sub(".*-(\\s*)", "", BTS_data[[14]]$Country)) 
names(BTS_data[[11]])[names(BTS_data[[11]]) == "Country_now"] <- "Country"


## Batch processing of country codes for different data sources
BTS_data <- lapply(BTS_data,function(df){
  
  df <- df %>% 
    mutate(#Country = toupper(Country),
           Country = case_when(Country %in% c("TW","HK","MO") ~ "CN",
                               Country %in% c("TWN","HKG","MAC") ~ "CHN",
                               Country %in% c("Taiwan","Macao","Hong Kong, China","Hong Kong") ~ "China",
                               Country %in% c("Bosnia and Herzegovina","Bosnia and. Herz.") ~ "Bosnia & Herzegovina",
                               Country %in% c("England","Northern Ireland","Wales") ~ "United Kingdom",
                               Country %in% c("SlovakRepublic") ~ "Slovakia",
                               Country %in% c("Czech Republic") ~ "Czechia",
                               Country %in% c("Macedonia") ~ "North Macedonia",
                               Country %in% c("The Netherlands") ~ "Netherlands",
                               #Country %in% c("US","USA") ~ "United States",
                               TRUE ~ Country
                               ),
           Country = toupper(Country),
           Country = ifelse(nchar(Country) > 3, str_to_title(Country),Country),
           Countrycode = ifelse(nchar(Country) > 3, "Countryfullname", 
                                ifelse(nchar(Country) == 3, "ISO3", "ISO2")))
  
  return(df)
  
})


## Check the country code of the BTS data
BTS_countrycode_check <- lapply(BTS_data, function(df){
  
  df <- df %>% 
    dplyr::group_by(Countrycode) %>% 
    dplyr::summarise(n=n()) %>% 
    dplyr::ungroup()
  
  return(df)
})

BTS_countrycode_check <- do.call(rbind, BTS_countrycode_check)

## process abnormal Countrycode
BTS_data[[4]] <- BTS_data[[4]] %>% 
  dplyr::mutate(Countrycode = ifelse(Country == "USA", "Countryfullname",Countrycode)) ## I found UEA, a non-country code

BTS_data[[5]] <- BTS_data[[5]] %>% 
  dplyr::mutate(Countrycode = ifelse(Country == "Ken, Na", "ISO3",Countrycode),
                Country = ifelse(Country == "Ken, Na", "KEN",Country))

BTS_data[[6]] <- BTS_data[[6]] %>% 
  dplyr::mutate(Countrycode = ifelse(Country == "Many", NA,Countrycode),
                Country = ifelse(Country == "Many", NA, Country))
  


## Combine the BTS_data and Countrycodelist_iso2_iso3
Countrycode_merge <- function(df, Countrycode) {  
  
  Countrycode_lengths <- nchar(as.character(df$Country))  
  Countrycode_lengths <- Countrycode_lengths[!is.na(Countrycode_lengths)]  
 
  if (all(Countrycode_lengths == 2)) {  
    
    merge_key <- "ISO2"  
  } else if (any(Countrycode_lengths > 3)) {  
   
    merge_key <- "Countryfullname"  
  } else {  
   
    merge_key <- "ISO3"  
  }  
    
  merged_df <- merge(df, Countrycode, by.x = "Country", by.y = merge_key, all.x = TRUE)  
    
  return(merged_df)  
}  
  
BTS_data <- lapply(BTS_data, Countrycode_merge, Countrycode = Countrycodelist_iso2_iso3)  


## Change the column name so that each BTS data has "ISO3"
BTS_data <- lapply(BTS_data,function(df){
  
  if(!"ISO3" %in% names(df)){
    
    df <- df %>% 
      dplyr::mutate(ISO3 = Country)
  }
  
  return(df)
  
})


## Change the column name so that each BTS data has "ISO2"
BTS_data <- lapply(BTS_data,function(df){
  
  if(!"ISO2" %in% names(df)){
    
    df <- df %>% 
      dplyr::mutate(ISO2 = Country)
  }
  
  return(df)
  
})


## Because the country code of the countrycode package is the full name, but some of the actual data set is recorded by abbreviation (for example: United States is USA), so this part is not converted properly, and is now found and processed separately.
BTS_data_na <- lapply(BTS_data, function(df){
  
  df <- df %>% 
    dplyr::filter(is.na(ISO3)) %>% 
    dplyr::select(Article_Id, Country, ISO3)
  
  return(df)
})

BTS_data_na <- do.call(rbind,BTS_data_na)

BTS_data_na_table <- data.frame(table(BTS_data_na$Country)) 


## Handle UK and UA separately
BTS_data <- lapply(BTS_data,function(df){
  
  df <- df %>% 
    dplyr::mutate(ISO2 = ifelse(Country == "UK" |Country == "UEA","GB",ISO2),
                  ISO2 = ifelse(Country == "US" | Country == "USA", "US",ISO2),
                  ISO3 = ifelse(Country == "UK"|Country == "UEA","GBR",ISO3),
                  ISO3 = ifelse(Country == "US" | Country == "USA", "USA",ISO3))
  
  return(df)
  
})

```


```{r include=FALSE}
## Here, I remove some data sets to reduce data set clutter.
rm(BTS_data_na_table,BTS_data_na,Countrycode_merge,BTS_countrycode_check)

gc()
```


Here, I used self-defined function in Stage1 to calculate Bayesian multinomial test
# Define a Func to calculate Bayesian multinomial test
## Algorithm in R
```
lbeta.xa <- sum(lgamma(alphas + counts)) - lgamma(sum(alphas + counts))
lbeta.a  <- sum(lgamma(alphas)) - lgamma(sum(alphas))

LogBF10 <- (lbeta.xa-lbeta.a) + (0 - sum(counts * log(thetas))) 
```


Here, `alphas` defined the prior Dirichlet distribution, e.g., noninformative prior is a vector of $1$ s, `counts` are the observed frequencies.

To use the algorithm in R, we defined a function here:
```{r}
BayesMultiNomial <- function(dataset, factor, observed, expected, default_prior = TRUE, prior = NA){
  # datase - the input dataframe
  # factor - column name of the factor,
  # observed - column name of the column contains counts information for the observed,
  # expected - column name of the column contains counts information for the expected,
  # default_prior - whether use the default, defused prior
  # prior - priors defined by users
  
  fact_level <- dataset %>% dplyr::select(all_of(factor)) %>% dplyr::pull()
  observed_data <- dataset %>% dplyr::select(all_of(observed)) %>% dplyr::pull()
  names(observed_data) <- fact_level
  expected_data <- dataset %>% dplyr::select(all_of(expected)) %>% dplyr::pull()
  n_levels <- length(observed_data)
  
  
  if (default_prior & all(is.na(prior))) {
    prior <- rep(1, n_levels)
  } else{
    if (is.character(prior)){
      prior <- dataset %>% dplyr::select(all_of(prior)) %>% dplyr::pull()
    } else if (is.array(prior)){
      prior <-  prior
    } else if (is.numeric(prior)){
      prior <-  prior
    } else{
      print("prior much a column of the input data or a vector")
    }
  }
  
  alphas <- prior
  counts <- observed_data
  thetas <- expected_data
  
  if(sum(thetas) != 1) {
    thetas <- thetas/sum(thetas)
    }
  
  expected <- setNames(sum(counts)*thetas, names(counts))
  
  lbeta.xa <- sum(lgamma(alphas + counts)) - lgamma(sum(alphas + counts))
  lbeta.a  <- sum(lgamma(alphas)) - lgamma(sum(alphas))

  if (any(rowSums(cbind(thetas, counts)) == 0)) {
    LogBF10 <- (lbeta.xa-lbeta.a)
  } else {
    LogBF10 <- (lbeta.xa-lbeta.a) + (0 - sum(counts * log(thetas))) 
  }

  BF <- data.frame(LogBF10 = LogBF10,
                   BF10    = exp(LogBF10),
                   BF01    = 1/exp(LogBF10))

  return(list(BF       = BF,
              expected = expected))
  
}
```


At this point, I have finished loading the package and data. Next, I analyzed the data and visualized it according to the logic of the written protocal.

I began by analyzing the basic case of the two data sets (BTS and Chinese journals).
# Overview of participants
## The basic situation of Chinese journals coding data
```{r}
### In order to facilitate the subsequent exclusion of foreign samples, the Subjects_Recruitment_Area information 29 of 20211064 was changed to Chinese character 29
df_stage2_Journal_Code2$Subjects_Recruitment_Area[447] <- "被试填答IP覆盖了二十九个省、自治区、直辖市"


df_Articles <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(is.na(Remark1) & !grepl("重复",Remark2)) %>% 
  dplyr::filter(!grepl("2",Subjects_Recruitment_Area))

df_Articles_num <- df_Articles %>% 
  dplyr::distinct(Article_IDs) ## A total 962 articles

df_Study_num <- df_Articles %>% 
  dplyr::distinct(Article_IDs,Study_Number) ## A total 1216 studies


## Here, I remove some data sets to reduce data set clutter.
rm(df_Articles,df_Articles_num,df_Study_num)
```


## The basic situation about BTS data
```{r}
BTS_Overview <- lapply(BTS_data,function(df){
  
  df <- df %>% 
    dplyr::select(Article_Id,ISO3,ISO2)
  
  return(df)
})

BTS_Overview <- do.call(rbind,BTS_Overview)

BTS_Overview2 <- BTS_Overview %>% 
  dplyr::filter(!is.na(ISO2)) %>%   ## ISO2 is used to subsequent visualize the spatial distribution in and filter out the data with countries as NA.
  dplyr::group_by(ISO2) %>% 
  dplyr::summarise(n = n()) %>% 
  dplyr::mutate(Proportion = round(n/sum(n)*100,2),
                FloorPro = floor(Proportion),
                index = Proportion - FloorPro,
                Site = "BTS")

sum(BTS_Overview2$Proportion)


BTS_Overview2_idx <- BTS_Overview2 %>% 
  group_by(Site) %>% 
  summarise(sum = sum(FloorPro)) %>% 
  ungroup()

```


## try percent 100
```{r}
# bts_overviewfill <- data.frame(matrix(ncol = ncol(BTS_Overview2),nrow = 0))
# colnames(bts_overviewfill) <- colnames(BTS_Overview2)
# 
# for (i in 1:nrow(BTS_Overview2_idx)) {
#   
#   df55 <- BTS_Overview2 %>% 
#     dplyr::filter(Site == BTS_Overview2_idx$Site[i]) %>% 
#     dplyr::arrange(desc(index))
#   
#   if(BTS_Overview2_idx$sum[i] < 100) {
#     
#     for(j in seq(100 - BTS_Overview2_idx$sum[i])){
#       
#       df55$FloorPro[j] <- df55$FloorPro[j] + 1
#     }
#       bts_overviewfill <- rbind(bts_overviewfill,df55)
#   }
# 
#    return(bts_overviewfill)
# 
# }
# 
# sum(bts_overviewfill$FloorPro)
```


## The reported situation of Chinese Journals
```{r}
df_CHN_report <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(is.na(Remark1) & !grepl("重复",Remark2)) %>%
  dplyr::filter(!grepl("2",Subjects_Recruitment_Area)) %>% 
  dplyr::mutate(Subjects_Recruitment_Area = ifelse(Subjects_Recruitment_Area == 0, 0, 1),
                Sampling_Method = ifelse(Sampling_Method == 0, 0 ,1),
                SES_N = ifelse(SES_N == 0, 0, 1),
                Subjects_Recruitment_Method_N = ifelse(Subjects_Recruitment_Method_N == 0, 0, 1)) %>%
  dplyr::group_by(Article_IDs,Study_Number) %>% 
  dplyr::summarise(Age = max(Age) > 0,
                   Gender = max(Gender) > 0,
                   Religious = max(Religious) > 0,
                   Ethnicity = max(Ethnicity) > 0,
                   Sampling_Method = max(Sampling_Method) > 0,
                   Recruitment_Area = max(Subjects_Recruitment_Area) > 0,
                   Recruitment_Method = max(Subjects_Recruitment_Method_N) > 0,
                   SES = max(SES_N) > 0,
                   .groups = "drop") %>% 
  dplyr::select(3:last_col())

report_list <- list()

for (i in names(df_CHN_report)){
  
  
  report_table <- data.frame(table(df_CHN_report[[i]])) %>% 
    dplyr::mutate(col_names = names(df_CHN_report[i]),
                  proportion = round(Freq / sum(Freq),2))
  
  report_list[[i]] <- report_table
  
}

df_CHN_report <- do.call(rbind, report_list) %>% 
  dplyr::mutate(Var1 = ifelse(Var1 == "TRUE", "Reported","Unreported")) 



### Calculate reported status of Educational_Attainment and Occupation
Educational_Occupation <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(is.na(Remark1) & !grepl("重复",Remark2)) %>%
  dplyr::filter(!grepl("2",Subjects_Recruitment_Area)) %>%
  dplyr::filter(Sample_Type_N %in% c(4,5)) %>% 
  dplyr::group_by(Article_IDs,Study_Number) %>% 
  dplyr::summarise(Educational_Attainment_N = max(Educational_Attainment_N) > 0,
                Occupation_N = max(Occupation_N) > 0,.groups = "drop")   ### 294 studies

# table(Educational_Occupation$Educational_Attainment_N) ## FALSE 162 TRUE 132
# table(Educational_Occupation$Occupation_N)  ## FALSE 193 TRUE 101


Educational_Occupation_table <- data.frame(Var1 = c("Unreported","Reported","Unreported","Reported"),
                                           Freq = c(162,132,193,101),
                                           col_names= c("Educational_Attainment","Educational_Attainment","Occupation","Occupation"),
                                           proportion = c(0.55,0.45,0.66,0.34))

df_CHN_report <- rbind(df_CHN_report,Educational_Occupation_table) %>% 
  dplyr::mutate(col_names = factor(col_names, 
                                   labels = c("Gender","Age","Recruitment Method","Recruitment Area","Educational Attainment",
                                              "Occupation","Sampling Method","SES","Ethnicity","Religious"
                                             ),
                                   levels = c("Gender","Age","Recruitment_Method","Recruitment_Area","Educational_Attainment",
                                              "Occupation","Sampling_Method","SES","Ethnicity","Religious")))
```


### Visualize subjects information reported  situations in Chinese journals 
```{r}
Fig_Journal_report <- ggplot(df_CHN_report,aes(col_names,proportion,fill=Var1))+
  geom_col()+
  labs(x="",y="%")+
  theme_classic()+
  theme(panel.border =element_rect(fill=NA,color="black"),
        legend.position = "bottom",
        legend.box.spacing = unit(2,"pt"),
        legend.text = element_text(size = 20, family = "serif"),
        legend.title = element_blank(),
        axis.title = element_text(size = 20,family = "serif"),
        axis.text = element_text(size = 20,family = "serif"))+
  scale_x_discrete(guide = guide_axis(angle = 45))+
  scale_fill_manual(values = c("#00BFC4","#B2B2B2"))

Fig_Journal_report

ggsave("Fig_Journal_report.pdf", Fig_Journal_report, device = "pdf", width=16, height = 9)


## Here, I remove some data sets to reduce data set clutter.
rm(report_list,report_table,i,Educational_Occupation,Educational_Occupation_table)
```


### Specific reports on some demographic categories
```{r}
df_age_report_detail <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(is.na(Remark1) & !grepl("重复",Remark2)) %>%
  dplyr::filter(!grepl("2",Subjects_Recruitment_Area)) %>% 
  dplyr::select(Article_IDs,Study_Number,Subjects_Group,Age,M_age,SD_age,Other_age) %>%
  dplyr::filter(Age == 1)

### Age report studies num
df_age_report_detail_study_num <- df_age_report_detail %>%
    dplyr::distinct(Article_IDs,Study_Number) ## 989 studies
  

### Age fuzzy report studies num
df_fuzzy_age_report <- df_age_report_detail %>% 
  dplyr::filter(is.na(M_age)) 

## 20082227,20083017,20183340,20183097,20214027 Other age include Mage
##这里后面还需要重新处理一下部分Otherage包含Mage的情况

df_fuzzy_age_report_study_num <- df_fuzzy_age_report %>% 
  dplyr::distinct(Article_IDs,Study_Number) ## 130-5=125


## Here, I remove some data sets to reduce data set clutter.
rm(df_age_report_detail,df_age_report_detail_study_num,
   df_fuzzy_age_report,df_fuzzy_age_report_study_num)
```


In this section, I began by testing and analyzing three main hypotheses.
# Test three hypotheses
## Test the 1st hypothesis
### Gender
Process gender data from Chinese journals.
```{r warning=FALSE}
## Minor revision
df_stage2_Journal_Code2$Male_Num[1258] <- 0
df_stage2_Journal_Code2$Female_Num[1634] <- 0.5950


## Process the gender data of CHN Journal
df_stage2_Journal_Code_Gender <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(is.na(Remark1) & !grepl("重复",Remark2)) %>% 
  dplyr::filter(Subjects_Recruitment_Area !=2) %>% 
  dplyr::mutate(Male_Num = as.numeric(Male_Num),
                Female_Num = as.numeric(Female_Num)) %>% 
  dplyr::select(Article_IDs,Study_Number,Subjects_Group_N,Sample_Size,Gender,Male_Num,Female_Num,Remark1,Remark2,Remark3)


## Part of the gender data is the proportion recorded, and part is the number of people, so I deal with it separately.

df_stage2_Journal_Code_Gender_decimal <- df_stage2_Journal_Code_Gender %>% 
  dplyr::filter(Gender == 1) %>% 
  dplyr::filter(Male_Num < 1 & Female_Num < 1) %>% 
  dplyr::select(Article_IDs,Sample_Size,Study_Number,Subjects_Group_N,Gender,Male_Num,Female_Num) %>% 
  # dplyr::mutate(Male_Num = round(Male_Num,2),
  #               Female_Num = round(Female_Num,2)) %>% 
  dplyr::rename(Male_Proportion = Male_Num,
               Female_Proportion =  Female_Num)

df_stage2_Journal_Code_Gender_integer <- df_stage2_Journal_Code_Gender %>%
  dplyr::filter(Gender == 1) %>% 
  dplyr::filter(Male_Num > 1 | Female_Num > 1) %>% 
  dplyr::select(Article_IDs,Study_Number,Subjects_Group_N,Sample_Size,Gender,Male_Num,Female_Num)


## Multiple groups of data are removed during processing, so re-create the data.frame and then merge them.

df_stage2_Journal_Code_Gender_integer_add <- data.frame(
  Article_IDs = c("20185082","20213045","20213048","20213048","20215075"),
  Study_Number = c(1,1,1,2,1),
  Subjects_Group_N = c(NA,NA,NA,NA,"父亲"),
  Sample_Size = c(33,81,68,59,310),
  Gender = 1,
  Male_Num = c(26,49,31,28,310),
  Female_Num = c(7,32,37,31,0))

df_stage2_Journal_Code_Gender_integer2 <- df_stage2_Journal_Code_Gender_integer %>% 
  rbind(df_stage2_Journal_Code_Gender_integer_add)


## Process decimal
df_stage2_Journal_Code_Gender_decimal2 <- df_stage2_Journal_Code_Gender_decimal %>% 
  dplyr::mutate(Sample_Size = as.numeric(Sample_Size),
                Male_Num = floor(Sample_Size*Male_Proportion),
                Female_Num = Sample_Size - Male_Num) %>% 
  dplyr::select(1:5,8:9)


## merge all chinese journal gender data
df_CHN_Journal_Gender <- rbind(df_stage2_Journal_Code_Gender_decimal2,
                               df_stage2_Journal_Code_Gender_integer2)


## calculate total gender proportion
df_CHN_Journal_Gender_Total <- df_CHN_Journal_Gender %>%
  dplyr::summarise(Male_Num = sum(Male_Num),
                   Female_Num = sum(Female_Num,na.rm = TRUE),
                   Male_Proportion = round(Male_Num/(Male_Num + Female_Num),2)*100,
                   Female_Proportion = round(Female_Num/(Male_Num + Female_Num),2)*100,
                   Data_Source = "Chinese papers") 


df_CHN_Journal_Gender_Total2 <- data.frame(Gender = c("Male","Female"),
                                          n = c(233377,272477),
                                          Proportion = c(46,54),
                                          Data_Source = "Chinese papers")

```


Process gender data from BTS.
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
BTS_gender_list <- list()

for(i in seq_along(BTS_data)) {
  
  BTS_data_name <- names(BTS_data)[i] 
  
 if ("Gender" %in% names(BTS_data[[i]])) {  
   
  BTS_gender <- BTS_data[[i]] %>% 
    dplyr::mutate(Gender = str_to_title(Gender)) %>% 
    dplyr::filter(Gender == "Female" | Gender == "Male") %>% 
    dplyr::mutate(#Proportion = round(count/sum(count),2),
                  Data_Source =  BTS_data_name)
  
  BTS_gender_list[[BTS_data_name]] <- BTS_gender
  
} else {  
 
    cat(sprintf("Skipping '%s' because it does not contain a 'Gender' column.\n", BTS_data_name))  
  } 

}

```


Combine gender data from Chinese Journal and BTS
```{r}
## Extracting China data
BTS_CHN_gender <- lapply(BTS_gender_list, function(df){
  
  df %>% 
    dplyr::filter(grepl("CHN", ISO3, ignore.case = TRUE)) %>% 
    dplyr::select(ISO3,Data_Source,Gender) 

})

BTS_CHN_gender <- do.call(rbind, BTS_CHN_gender) %>% 
  dplyr::group_by(Gender) %>% 
  dplyr::summarise(n = n()) %>% 
  dplyr::mutate(Proportion = round(n/sum(n),2)*100) %>% 
  dplyr::ungroup() %>%
  dplyr::mutate(Data_Source = "BTS Chinese")
  
  

## Combine CHN journal data and set factor

Journal_BTS_CHN_gender <- BTS_CHN_gender %>% 
  bind_rows(df_CHN_Journal_Gender_Total2) %>% 
  dplyr::mutate(Gender =  stringr::str_to_title(Gender))

Journal_BTS_CHN_gender_factor <- Journal_BTS_CHN_gender %>% 
  dplyr::filter(Gender == "Female") %>% 
  dplyr::arrange(Proportion) %>% 
  dplyr::pull(Data_Source)

Journal_BTS_CHN_gender <- Journal_BTS_CHN_gender %>% 
  dplyr::mutate(Data_Source = factor(Data_Source,
                                     levels = Journal_BTS_CHN_gender_factor))
```


Visualize gender data for Chinese journals and BTS
```{r}
H1_Fig_gender <- ggplot(data = Journal_BTS_CHN_gender,aes(Data_Source,Proportion,fill = Gender))+
  geom_col()+
  geom_hline(yintercept = 50, linetype = "dashed", color = "#666666")+
  labs(y="Proportion")+
  theme_classic()+
  theme(panel.border =element_rect(fill=NA,color="black"),
        legend.position = "bottom",
        legend.box.spacing = unit(2,"pt"),
        legend.text = element_text(size = 20, family = "serif"),
        legend.title = element_blank(),
        axis.title = element_text(size = 20,family = "serif"),
        axis.text = element_text(size = 20,family = "serif"))#,
      #  axis.text.x = element_text(angle = 90, hjust = 1))

# ggsave("Fig_Journal_BTS_CHN_gender.pdf", Fig_Journal_BTS_CHN_gender, device = "pdf", width=18, height = 9)

H1_Fig_gender 

# BTS1 <- Journal_BTS_CHN_gender$data
```


Here I tested whether the gender proportion distribution from Chinese five journal data are similar to that of the BTS data. I used Bayesian multinomial test (Bayesian goodness-of-fit test) to examine whether the observed (BTS data) fit the expected (Chinese five journal data). 


$H_0$: $\theta = c$, where $c$ is defined by Chinese five journal data;
$H_1$: $\theta$ is free to vary.


```{r}
Journal_BTS_CHN_gender_bayes <- Journal_BTS_CHN_gender %>% 
  dplyr::select(1,3:4) %>% 
  tidyr::pivot_wider(names_from = Data_Source, values_from = Proportion)

BF_H1_gender <- BayesMultiNomial(dataset = Journal_BTS_CHN_gender_bayes,
                                             factor = "Gender",
                                             observed = "BTS Chinese",
                                             expected = "Chinese papers") 

```


I found moderate evidence for the $H_1$ that the gender proportion from Chinese five journal data is different from that of BTS data, with $Log(BF_{10})$ = `r BF_H1_gender$BF$LogBF10`.


At the end of gender data processing for hypothesis 1, I removed some data sets to reduce data set clutter.
```{r}
rm(BTS_CHN_gender,BTS_gender,
   df_CHN_Journal_Gender_Total,df_CHN_Journal_Gender_Total2,
   df_stage2_Journal_Code_Gender,df_stage2_Journal_Code_Gender_decimal,
   df_stage2_Journal_Code_Gender_decimal2,df_stage2_Journal_Code_Gender_integer,
   df_stage2_Journal_Code_Gender_integer_add,df_stage2_Journal_Code_Gender_integer2,
   Journal_BTS_CHN_gender_bayes)
```


### Age
Reprocess age data from Chinese journals.
```{r warning=FALSE}
## I found some outliers for M_age, so I processed this part of the data first.
df_stage2_Journal_Code2$Sample_Type_N[1082] <- 2
df_stage2_Journal_Code2$Sample_Type_N[183] <- 2
df_stage2_Journal_Code2$Sample_Type_N[1190:1191] <- 2
df_stage2_Journal_Code2$M_age[1500] <- 31.6
df_stage2_Journal_Code2$M_age[407] <- "男性69.14;女性67.16"
df_stage2_Journal_Code2$M_age[1039] <- NA
df_stage2_Journal_Code2$M_age[1041] <- NA
df_stage2_Journal_Code2$SD_age[1039] <- NA
df_stage2_Journal_Code2$SD_age[1041] <- NA
df_stage2_Journal_Code2$M_age[1052] <- NA
df_stage2_Journal_Code2$SD_age[1052] <- NA
df_stage2_Journal_Code2$Sample_Type_N[300] <- 3
df_stage2_Journal_Code2$Age[351:352] <- 0 ## 20182022 Original article age report error, 0 here

## little error
df_stage2_Journal_Code2$Male_Num[1420] <- "幼儿：154；父亲：310"


## In the following process, we found 3 rows include Mage = 0 and SDage = 0.
## 20182182
df_stage2_Journal_Code2$M_age[1040] <- NA
df_stage2_Journal_Code2$M_age[1042] <- NA
df_stage2_Journal_Code2$M_age[1053] <- NA

df_stage2_Journal_Code2$SD_age[1040] <- NA
df_stage2_Journal_Code2$SD_age[1042] <- NA
df_stage2_Journal_Code2$SD_age[1053] <- NA

## Filter M_age have multiple group data
df_stage2_Journal_Code_Age_str <- df_stage2_Journal_Code2 %>% 
  dplyr::slice(492,370,856,879,1406,726,725,724,1413,
               1288,489,322,1331,1324,407,362,374,495,
               1419) %>% 
  dplyr::select(Article_IDs,Study_Number,Subjects_Group,Sample_Type_N,Age,M_age,SD_age,Other_age,Remark1,Remark2,Remark3)



## Rebuild for M_age' multiple group of data
df_stage2_Journal_Code_Mage_multiple_group <- data.frame(
  Article_IDs = c(20213254,20213254,20183078,20183078,20183078,20184162,20184162,20212079,
                  20212079,20213045,20213045,20213045,20082296,20082296,20082296,20082296,
                  20082296,20082296,20213054,20213054,20181109,20181109,20213244,20213244,
                  20182003,20182003,20182228,20182228,20182207,20182207,20184083,20184083,
                  20183060,20183060,20183087,20183087,20215094,20215094,20215094,20215075,20215075),
  Study_Number = 1,
  Subjects_Group = c("样本1大学生","样本1高中生","儿童","父亲","母亲","父亲","母亲","高一",
                     "高二","精分患者","健康同胞","健康对照","小班男","小班女","中班男","中班女",
                     "大班男","大班女","男生","女生","男生","女生","男生","女生",
                     "男生","女生","男生","女生","男生","女生","男生","女生",
                     "男生","女生","男生","女生","四年级","五年级", "六年级","幼儿","父亲"),
  Sample_Type_N = c(1,2,2,4,4,4,4,2,2,4,4,
                    4,3,3,3,3,3,3,3,3,2,
                    2,1,1,1,1,2,2,4,4,4,
                    4,1,1,1,1,2,2,2,3,4),
  Sample_Size = c(404,341,760,760,760,1047,1139,821,
                  748,27,27,27,NA,NA,NA,NA,
                  NA,NA,169,135,102,116,199,346,
                  8,9,213,192,62,68,258,258,
                  201,201,109,109,166,265,174,310,154),
  Age = 1,
  M_age = c(21.12,16.44,9.74,39.15,36.99,41.44,40.23,15.36,16.35,25.44,
            25.56,27.44,3.77,3.85,4.73,4.83,5.68,5.77,4.69,4.79,
            14.23,14.08,18.71,18.84,21.63,21.89,10.01,9.95,27.90,
            26.75,69.14,67.16,20.94,21.51,21.10,21.80,10.10,11.07,
            12.03,5.02,36.11),
  SD_age = c(1.45,0.73,1.46,3.73,2.95,NA,NA,0.52,0.52,5.92,6.44,7.24,
             0.3,0.23,0.25,0.29,0.32,0.32,0.58,0.56,0.69,0.58,1.78,1.66,
             1.32,1.17,1.31,1.38,6.56,5.04,7.40,6.44,2.33,2.31,2.37,1.69,
             0.31,0.34,0.30,0.93,4.91),
  Other_age = NA,
  Remark1 = NA,
  Remark2 = NA,
  Remark3 = NA)


## Process Other_age information separately
df_stage2_Journal_Code_Mage_multiple_group$Other_age[1] <- "17-25"
df_stage2_Journal_Code_Mage_multiple_group$Other_age[2] <- "15-19"



## I found that there are some M_age that have multiple groups, but no Chinese character identification, so it is not recognized in the above filter, so it is dealt with separately here

df_stage2_Journal_Code_Mage_semicolon <- data.frame(
  Article_IDs = c(20084068,20084068,20084068,20084068,20084068,20084068,20082182,20082182,
                  20082182,20082182,20185082,20185082,20183133,20183133,20182052,20182052,
                  20182052,20182052,20212031,20212031,20184130,20184130,20215102,20215102),
  Study_Number = c(1,1,1,1,1,1,1,1,2,2,1,1,
                   1,1,1,1,2,2,1,1,1,1,1,1),
  Subjects_Group = c("中班男","中班女","小班男","小班女","大班男","大班女",
                     "6、7岁","10、11岁","6、7岁","10、11岁","男生","女生",
                     "男生","女生","男生","女生","男生","女生","男生","女生",
                     "父亲","母亲","父亲","母亲"),
  Sample_Type_N =c(3,3,3,3,3,3,2,2,2,2,3,3,
                   1,1,5,5,5,5,5,5,4,4,4,4),
  Sample_Size = c(30,30,29,30,30,31,
                  35,30,25,24,26,7,
                  30,30,15,11,9,17,106,106,
                  280,280,572,5721),
  Age = 1,
  M_age = c(4.73,4.83,3.77,3.85,5.68,5.77,7.06,11.18,7.24,11.42,5.73,3.28,
            20.4,20.3,20.77,20.69,20.91,20.67,29.62,28.00,36.61,34.24,41.37,38.88) ,
  SD_age = c(0.25,0.29,0.3,0.23,0.32,0.32,0.38,0.35,0.39,0.34,0.74,0.56,
             1.2,1.1,1.8,2.09,2.65,1.31,3.37,2.26,4.06,3.38,4.74,3.87),
  Other_age = NA,
  Remark1 = NA,
  Remark2 = NA,
  Remark3 = NA)


## Process Other_age information separately
df_stage2_Journal_Code_Mage_semicolon$Other_age[21:22] <- c("27-53","26-50")


#The above cases where there are multiple age groups will be recognized as NA in the code run, so they need to be removed.These removed data are the data contained in the data.frame above.
df_stage2_Journal_Code_Age <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(Subjects_Recruitment_Area != 2) %>% 
  dplyr::mutate(M_age = as.numeric(M_age), SD_age = as.numeric(SD_age)) %>% 
  dplyr::mutate(M_age = round(M_age,2), SD_age = round(SD_age,2)) %>% 
  dplyr::select(Article_IDs,Study_Number,Subjects_Group,Sample_Type_N,Sample_Size,Age,M_age,SD_age,Other_age,Remark1,Remark2,Remark3) %>% 
  dplyr::slice(-c(492,370,856,879,1406,724:726,
                  1413,1288,489,322,1331,1324,407,
                  362,374,495,1419,536:538,509,
                  510,1368,600,567,568,648,630,696))

## Merge data
df_stage2_Journal_Code_Age2 <- rbind(df_stage2_Journal_Code_Age,df_stage2_Journal_Code_Mage_multiple_group) %>% 
  rbind(df_stage2_Journal_Code_Mage_semicolon)

rm(df_stage2_Journal_Code_Mage_multiple_group,df_stage2_Journal_Code_Mage_semicolon,df_stage2_Journal_Code_Age_str)

#Special Note 1: In the process of M_age data, I found some data that may be outlier, so I grouped them based on "Sample_Type_N" and indeed found some abnormal data. In order to ensure that subsequent analysis is affected as little as possible, we will check it based on "df_stage2_Journal_Code2" and put the relevant code at the beginning of this section. This way, subsequent analysis will not be affected by these outlier. I hope the order here will not cause any inconvenience for you.

Summrise_MAge <- df_stage2_Journal_Code_Age2 %>%
  dplyr::filter(!is.na(M_age)) %>% 
  dplyr::group_by(Sample_Type_N) %>% 
  dplyr::summarise(Min_Mage = min(M_age),
                   Max_Mage  = max(M_age),
                   Mean_Mage  = mean(M_age))
rm(Summrise_MAge)

df_stage2_Journal_Code2_SampleType1 <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(Sample_Type_N == 1) ## M_age no outlier was found after sorting
rm(df_stage2_Journal_Code2_SampleType1)

df_stage2_Journal_Code2_SampleType2 <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(Sample_Type_N == 2) ## M_age no outlier was found after sorting
rm(df_stage2_Journal_Code2_SampleType2)

df_stage2_Journal_Code2_SampleType3 <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(Sample_Type_N == 3) ## 1 outlier was found after sorting
rm(df_stage2_Journal_Code2_SampleType3)

df_stage2_Journal_Code2_SampleType4 <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(Sample_Type_N == 4) ## outlier was found after sorting
rm(df_stage2_Journal_Code2_SampleType4)

df_stage2_Journal_Code2_SampleType5 <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(Sample_Type_N == 5) ## I may need to re-process Sample_Type 5
rm(df_stage2_Journal_Code2_SampleType5)

```


Since raw data is not available for papers in Chinese journals, I simulated the raw data using the method used in the Stges 1 of registration report. It is then combined with BTS and compared with census data.

First, I created a function that groups ages into five-year intervals for the purpose of creating a Population pyramid chart.
```{r}
Sim_Sens_mult_five <- function(Mean0, diff_age, SD0, sample_N=Sample_Size){

  
  ageData_five <-  c(pnorm(4, mean = Mean0, sd = SD0) * sample_N,
                 (pnorm(9, mean = Mean0, sd = SD0) - pnorm(4, mean = Mean0, sd = SD0)) *sample_N,
                 (pnorm(14, mean = Mean0, sd = SD0) - pnorm(9, mean = Mean0, sd = SD0)) *sample_N,
                 (pnorm(19, mean = Mean0, sd = SD0) - pnorm(14, mean = Mean0, sd = SD0)) *sample_N,
                 (pnorm(24, mean = Mean0, sd = SD0) - pnorm(19, mean = Mean0, sd = SD0)) *sample_N,
                 (pnorm(29, mean = Mean0, sd = SD0) - pnorm(24, mean = Mean0, sd = SD0)) *sample_N,
                 (pnorm(34, mean = Mean0, sd = SD0) - pnorm(29, mean = Mean0, sd = SD0)) *sample_N,
                 (pnorm(39, mean = Mean0, sd = SD0) - pnorm(34, mean = Mean0, sd = SD0)) *sample_N,
                 (pnorm(44, mean = Mean0, sd = SD0) - pnorm(39, mean = Mean0, sd = SD0)) *sample_N,
                 (pnorm(49, mean = Mean0, sd = SD0) - pnorm(44, mean = Mean0, sd = SD0)) *sample_N,
                 (pnorm(54, mean = Mean0, sd = SD0) - pnorm(49, mean = Mean0, sd = SD0)) *sample_N,
                 (pnorm(59, mean = Mean0, sd = SD0) - pnorm(54, mean = Mean0, sd = SD0)) *sample_N,
                 (pnorm(64, mean = Mean0, sd = SD0) - pnorm(59, mean = Mean0, sd = SD0)) *sample_N,
                 (pnorm(69, mean = Mean0, sd = SD0) - pnorm(64, mean = Mean0, sd = SD0)) *sample_N,
                 (pnorm(74, mean = Mean0, sd = SD0) - pnorm(69, mean = Mean0, sd = SD0)) *sample_N,
                 (pnorm(79, mean = Mean0, sd = SD0) - pnorm(74, mean = Mean0, sd = SD0)) *sample_N,
                 (pnorm(84, mean = Mean0, sd = SD0) - pnorm(79, mean = Mean0, sd = SD0)) *sample_N,
                 (pnorm(89, mean = Mean0, sd = SD0) - pnorm(84, mean = Mean0, sd = SD0)) *sample_N,
                 (pnorm(94, mean = Mean0, sd = SD0) - pnorm(89, mean = Mean0, sd = SD0)) *sample_N,
                 (1 - pnorm(94, mean = Mean0, sd = SD0)) * sample_N)
  
  
    # create a dataframe with ageData_five
  Sim_agefive_df <- setNames(data.frame(matrix(ncol = 2, nrow = 20)), c("ageBins", "sim1"))
  Sim_agefive_df$ageBins <- c("0~4","5~9","10~14","15~19","20~24",
                              "25~29","30~34","35~39","40~44","45~49",
                              "50~54","55~59","60~64","65~69","70~74",
                              "75~79","80~84","85~89", "90~94",">=95")
  Sim_agefive_df$sim1[1:20] <- ageData_five
  

  return(Sim_agefive_df)
}


## Filter non-NA data makes it easier for subsequent simulations.
Sim_Journal_age <- df_stage2_Journal_Code_Age2 %>% 
  dplyr::filter(Age != 0) %>% 
  dplyr::filter(!is.na(M_age) & !is.na(SD_age)) %>% 
  dplyr::filter(!is.na(Sample_Size)) %>% 
  dplyr::mutate(Sample_Size =  as.numeric(Sample_Size))


## Use simulation function to process data.
Sim_Journal_age_five1 <- lapply(1:nrow(Sim_Journal_age),function(i){
  
  Sim_Sens_mult_five(Mean0 = Sim_Journal_age$M_age[i],
                diff_age = 0,
                SD0 = Sim_Journal_age$SD_age[i],
                sample_N = Sim_Journal_age$Sample_Size[i])
  
  })


Sim_Journal_age_five2 <- do.call(rbind,Sim_Journal_age_five1)


Sim_Journal_age_five3 <- Sim_Journal_age_five2 %>% 
  dplyr::group_by(ageBins) %>% 
  dplyr::summarise(sim1 = round(sum(sim1,na.rm = TRUE))) %>% 
  dplyr::ungroup() %>% 
  dplyr::mutate(ageBins =factor(ageBins,
                                levels = c("0~4","5~9","10~14","15~19","20~24",
                                           "25~29","30~34","35~39","40~44","45~49",
                                           "50~54","55~59","60~64","65~69","70~74",
                                           "75~79","80~84","85~89", "90~94",">=95")))


## Calculate the sample difference between the coded data and the simulated data
sum(Sim_Journal_age$Sample_Size)-sum(Sim_Journal_age_five3$sim1,na.rm = TRUE) 
```


I then continued to use the same steps to divide age into psychological developmental stages.
```{r}
Sim_Sens_mult_PsyStages <- function(Mean1, diff_age, SD1, sample_N=Sample_Size){
  
  
  ageData_PsyStages <-  c(pnorm(17, mean = Mean1, sd = SD1) * sample_N,
                          (pnorm(26, mean = Mean1, sd = SD1) - pnorm(17, mean = Mean1, sd = SD1)) *sample_N,
                          (pnorm(41, mean = Mean1, sd = SD1) - pnorm(26, mean = Mean1, sd = SD1)) *sample_N,
                          (pnorm(60, mean = Mean1, sd = SD1) - pnorm(41, mean = Mean1, sd = SD1)) *sample_N,
                          (1 - pnorm(60, mean = Mean1, sd = SD1)) * sample_N)
  
    
  # create a dataframe with ageData_PsyStages
  Sim_agePsyStages_df <- setNames(data.frame(matrix(ncol = 2, nrow = 5)), c("ageBins", "sim1"))
  Sim_agePsyStages_df$ageBins <- c("<=17", "18~25", "26~40", "41~60", ">=61")
  Sim_agePsyStages_df$sim1[1:5] <- ageData_PsyStages
  

  return(Sim_agePsyStages_df)
}


## Use simulation function to process data. 
Sim_Journal_age_PsyStages1 <- lapply(1:nrow(Sim_Journal_age),function(i){
  
  Sim_Sens_mult_PsyStages(Mean1 = Sim_Journal_age$M_age[i],
                diff_age = 0,
                SD1 = Sim_Journal_age$SD_age[i],
                sample_N = Sim_Journal_age$Sample_Size[i])
  
  })


Sim_Journal_age_PsyStages2 <- do.call(rbind,Sim_Journal_age_PsyStages1)


Sim_Journal_age_PsyStages3 <- Sim_Journal_age_PsyStages2 %>% 
  dplyr::group_by(ageBins) %>% 
  dplyr::summarise(sim1 = round(sum(sim1,na.rm = TRUE))) %>% 
  dplyr::ungroup() %>% 
  dplyr::mutate(ageBins =factor(ageBins,
                                levels = c("<=17","18~25", "26~40", "41~60", ">=61")))


## Calculate the sample difference between the coded data and the simulated data
sum(Sim_Journal_age$Sample_Size)-sum(Sim_Journal_age_PsyStages3$sim1,na.rm = TRUE)
```


Meanwhile, I created func to process age data simulation in 10-year-old segment.
```{r}
Sim_Sens_mult_interval10 <- function(Mean2, diff_age2, SD2, sample_N2=Sample_Size){

  
  # 0~10, 11~20, 21~30, 31~40, 41~50, 51~60, 61~
  ageData_interval10 <-  c(pnorm(10, mean = Mean2, sd = SD2) * sample_N2,
                           (pnorm(21, mean = Mean2, sd = SD2) - pnorm(10, mean = Mean2, sd = SD2)) *sample_N2,
                           (pnorm(31, mean = Mean2, sd = SD2) - pnorm(21, mean = Mean2, sd = SD2)) *sample_N2,
                           (pnorm(41, mean = Mean2, sd = SD2) - pnorm(31, mean = Mean2, sd = SD2)) *sample_N2,
                           (pnorm(51, mean = Mean2, sd = SD2) - pnorm(41, mean = Mean2, sd = SD2)) *sample_N2,
                           (pnorm(61, mean = Mean2, sd = SD2) - pnorm(51, mean = Mean2, sd = SD2)) *sample_N2,
                           (1 - pnorm(61, mean = Mean2, sd = SD2)) * sample_N2  
)
  
  
    # create a dataframe with ageData1 and ageData2:
  Sim_ageinterval10_df <- setNames(data.frame(matrix(ncol = 2, nrow = 7)), c("ageBins", "sim1"))
  Sim_ageinterval10_df$ageBins <- c("<=10", "11~20", "21~30", "31~40", "41~50", "51~60", ">=61")
  Sim_ageinterval10_df$sim1[1:7] <- ageData_interval10
  
  
  return(Sim_ageinterval10_df)
}


Sim_Journal_age_interval101 <- lapply(1:nrow(Sim_Journal_age),function(i){
  
  Sim_Sens_mult_interval10(Mean2 = Sim_Journal_age$M_age[i],
                diff_age2 = 0,
                SD2 = Sim_Journal_age$SD_age[i],
                sample_N2 = Sim_Journal_age$Sample_Size[i])
  
  })


Sim_Journal_age_interval102 <- do.call(rbind,Sim_Journal_age_interval101)


## Use simulation function to process data. 
Sim_Journal_age_interval103 <- Sim_Journal_age_interval102 %>% 
  dplyr::group_by(ageBins) %>% 
  dplyr::summarise(sim1 = round(sum(sim1,na.rm = TRUE))) %>% 
  dplyr::ungroup() %>% 
  dplyr::mutate(ageBins =factor(ageBins,
                                levels = c("<=10", "11~20", "21~30", 
                                           "31~40", "41~50", "51~60", ">=61")))
  


## Calculate the sample difference between the coded data and the simulated data
sum(Sim_Journal_age$Sample_Size)-sum(Sim_Journal_age_interval103$sim1,na.rm = TRUE)
```


And I calculated the proportion of age data for different segments to facilitate visualization and Bayesian calculation.
```{r}
## 5-old-year
Sim_Journal_age_five3_prop <- Sim_Journal_age_five3 %>% 
  dplyr::mutate(Proportion = round((sim1/sum(sim1))*100,2),
                Data_Source = "Chinese papers")

# sum(Sim_Journal_age_five3_prop$Proportion)


## PsyStages
Sim_Journal_age_PsyStages3_prop <- Sim_Journal_age_PsyStages3 %>% 
    dplyr::mutate(Proportion = round((sim1/sum(sim1))*100,2),
                Data_Source = "Chinese papers")

# sum(Sim_Journal_age_PsyStages3_prop$Proportion)


## 10-old_year
Sim_Journal_age_interval103_prop <- Sim_Journal_age_interval103 %>% 
    dplyr::mutate(Proportion = round((sim1/sum(sim1))*100,2),
                Data_Source = "Chinese papers")

# sum(Sim_Journal_age_interval103_prop$Proportion)
```


Process age data from BTS.
```{r}
BTS_age_list <- list()

for(i in seq_along(BTS_data)){
  
  BTS_data_name <- names(BTS_data)[i]
  
  if("Age" %in% names(BTS_data[[i]])){
    
    BTS_age <- BTS_data[[i]] %>% 
      dplyr::filter(!is.na(Age) & !is.na(ISO3)) %>% 
      dplyr::select(Article_Id,Age,ISO3) %>% 
      #dplyr::group_by(ISO3) %>% 
      dplyr::mutate(ageBins = cut(Age,
                                breaks = c(-Inf,4.5,9.5,14.5,19.5,24.5,
                                           29.5,34.5,39.5,44.5,49.5,
                                           54.5,59.5,64.5,69.5,74.5,
                                           79.5,84.5,89.5,94.5,Inf),
                                labels = c("0~4","5~9","10~14","15~19","20~24",
                                 "25~29","30~34","35~39","40~44","45~49",
                                 "50~54","55~59","60~64","65~69","70~74",
                                 "75~79","80~84","85~89", "90~94",">=95" ),
                                levels = c("0~4","5~9","10~14","15~19","20~24",
                                 "25~29","30~34","35~39","40~44","45~49",
                                 "50~54","55~59","60~64","65~69","70~74",
                                 "75~79","80~84","85~89", "90~94",">=95" ))) #%>% 
    #dplyr::count(ageBins) %>% 
    #dplyr::mutate(Proportion = round((n/sum(n))*100,2),
     #             BTS_data_source = BTS_data_name)
  

 
  
BTS_age_list[[BTS_data_name]] <- BTS_age
  
} else {  
 
    cat(sprintf("Skipping '%s' because it does not contain a 'Age' column.\n", BTS_data_name))  
  } 
}


## merge data.frame in list
BTS_age <-  bind_rows(BTS_age_list)
```


Filter CHN age data from BTS, Combine BTS CHN data and Chinese journals data.
```{r}
BTS_CHN_age <- BTS_age %>% 
  dplyr::filter(ISO3 == "CHN") %>% 
  dplyr::count(ageBins) %>% 
  dplyr::mutate(Proportion = round((n/sum(n))*100,2),
                Data_Source = "BTS Chinese")

## add 3 rows of ageBins without data
BTS_CHN_age_3rows <- data.frame(ageBins = c("0~4","5~9","10~14"),
                                n = 0,
                                Proportion = 0,
                                Data_Source = "BTS Chinese")

## combine 2 dataframe
Journal_BTS_CHN_age <- Sim_Journal_age_five3_prop %>% 
  dplyr::rename(n = 2) %>% 
  dplyr::bind_rows(BTS_CHN_age,BTS_CHN_age_3rows)


## set ageBins as factor to plot
Journal_BTS_CHN_age <- Journal_BTS_CHN_age %>% 
  dplyr::mutate(ageBins = factor(ageBins,
                                 levels = c("0~4","5~9","10~14","15~19","20~24",
                                 "25~29","30~34","35~39","40~44","45~49",
                                 "50~54","55~59","60~64","65~69","70~74",
                                 "75~79","80~84","85~89", "90~94",">=95" )))

```


Visualize age data from Chinese journals and census7.
```{r}
H1_Fig_age <- ggplot(data= Journal_BTS_CHN_age, aes(x=ageBins, y=ifelse(Data_Source=="BTS Chinese", -Proportion, Proportion),fill = Data_Source)) +
  geom_col(alpha=0.8, width = 1) +
  coord_flip() +
  labs(y="Proportion", x = "Age bins", color=NULL)+
  scale_fill_manual(values = c("BTS Chinese" = "#619CFF", "Chinese papers" = "#7CAE00")) +
  theme_classic()+
  theme(panel.border =element_rect(fill=NA,color="black"),
        legend.position ="bottom",
        legend.box.spacing = unit(2,"pt"),
        legend.text = element_text(size = 16, family = "serif"),
        legend.title = element_blank(),
        axis.title = element_text(size = 16,family = "serif"),
        axis.text = element_text(size = 16,family = "serif"))


H1_Fig_age


H1_Fig_gender_age <- H1_Fig_gender + H1_Fig_age +
  plot_annotation(tag_levels = 'A')


ggsave("H1_Fig_gender_age.pdf", H1_Fig_gender_age, device = "pdf", width=18, height = 9)


H1_Fig_gender_age
```


Process age for Bayesian multinomial test. First of all, I processed BTS CHN age in psychological development stages.
```{r}
BTS_age_list_PsyStages <- list()

for(i in seq_along(BTS_data)){
  
  BTS_data_name <- names(BTS_data)[i]
  
  if("Age" %in% names(BTS_data[[i]])){
    
    BTS_age <- BTS_data[[i]] %>% 
      dplyr::filter(!is.na(Age) & !is.na(ISO3)) %>% 
      dplyr::select(Article_Id,Age,ISO3) %>% 
      #dplyr::group_by(ISO3) %>% 
      dplyr::mutate(ageBins = cut(Age,
                                breaks = c(0, 17.5, 25.5, 40.5, 60.5, Inf),
                                labels = c("<=17","18~25","26~40", "41~60", ">=61"),
                                levels = c("<=17","18~25","26~40", "41~60", ">=61")))
  
BTS_age_list_PsyStages[[BTS_data_name]] <- BTS_age
  
} else {  
 
    cat(sprintf("Skipping '%s' because it does not contain a 'Age' column.\n", BTS_data_name))  
  } 
}


## merge data.frame in list
BTS_age_PsyStages <-  do.call(rbind,BTS_age_list_PsyStages)
```


Secondly, I processed BTS CHN age in 10-year-old segment.
```{r}
BTS_age_list_interval10 <- list()

for(i in seq_along(BTS_data)){
  
  BTS_data_name <- names(BTS_data)[i]
  
  if("Age" %in% names(BTS_data[[i]])){
    
    BTS_age <- BTS_data[[i]] %>% 
      dplyr::filter(!is.na(Age) & !is.na(ISO3)) %>% 
      dplyr::select(Article_Id,Age,ISO3) %>% 
      #dplyr::group_by(ISO3) %>% 
      dplyr::mutate(ageBins = cut(Age,
                                breaks = c(0, 10.5, 20.5, 30.5, 40.5, 50.5, 60.5, Inf),
                                labels = c("<=10","11~20","21~30", "31~40", "41~50", "51~60", ">=61"),
                                levels = c("<=10","11~20","21~30", "31~40", "41~50", "51~60", ">=61")))
  
BTS_age_list_interval10[[BTS_data_name]] <- BTS_age
  
} else {  
 
    cat(sprintf("Skipping '%s' because it does not contain a 'Age' column.\n", BTS_data_name))  
  } 
}


## merge data.frame in list
BTS_age_interval10 <-  do.call(rbind,BTS_age_list_interval10)
```


And then, I filtered BTS CHN data.
```{r}
## psychological development stages in BTS
BTS_CHN_age_PsyStages <- BTS_age_PsyStages %>% 
  dplyr::filter(ISO3 == "CHN") %>% 
  dplyr::select(1,4) %>% 
  dplyr::count(ageBins) %>% 
  dplyr::mutate(Proportion = round((n/sum(n))*100,2),
                Data_Source = "BTS CHN age")


## 10-year-old segment in BTS
BTS_CHN_age_interval10 <- BTS_age_interval10 %>% 
  dplyr::filter(ISO3 == "CHN") %>% 
  dplyr::select(1,4) %>% 
  dplyr::count(ageBins) %>% 
  dplyr::mutate(Proportion = round((n/sum(n))*100,2),
                Data_Source = "BTS CHN age") 

```


Next, I Combined two CHN data to Bayesian multinomial test in two different classifications (PsyStages and 10-year-old). One is PsyStages.
```{r}
Journal_BTS_CHN_PsyStages_bayes <- Sim_Journal_age_PsyStages3_prop %>% 
  dplyr::rename(n = 2) %>% 
  bind_rows(BTS_CHN_age_PsyStages) %>% 
  dplyr::select(-2) %>% 
  tidyr::pivot_wider(names_from = Data_Source, values_from = Proportion)

  
BF_H1_PsyStages_Journal_BTS <- BayesMultiNomial(dataset = Journal_BTS_CHN_PsyStages_bayes,
                                          factor = "ageBins",
                                          observed = "BTS CHN age",
                                          expected = "Chinese papers")
```


The other is interval10.
```{r}
BTS_CHN_age_interval10_addrow <- BTS_CHN_age_interval10 %>% 
  dplyr::add_row(ageBins = "<=10", n = 0, Proportion = 0, Data_Source = "BTS CHN age")


Journal_BTS_CHN_interval10_bayes <- Sim_Journal_age_interval103_prop %>% 
  dplyr::rename(n = 2) %>% 
  bind_rows(BTS_CHN_age_interval10_addrow) %>%
  dplyr::select(-2) %>% 
  tidyr::pivot_wider(names_from = Data_Source, values_from = Proportion)


BF_H1_interval10_Journal_BTS <- BayesMultiNomial(dataset = Journal_BTS_CHN_interval10_bayes,
                                          factor = "ageBins",
                                          observed = "BTS CHN age",
                                          expected = "Chinese papers")
```


When we divide the age into 10 years,we found strong evidence for the $H_1$ that the age distribution from BTS data is different from that of Chinese journal data, with $Log(BF_{10})$ = `r BF_H1_interval10_Journal_BTS$BF$LogBF10`.

When we divide age into stages of psychological development, we found strong evidence for the $H_1$ that the age distribution from BTS data is different from that of Chinese journal data, with $Log(BF_{10})$ = `r BF_H1_PsyStages_Journal_BTS$BF$LogBF10`.



## Test the 2st hypothesis
### Gender
First of all, I processed gender data of the Census 7th data and the CFPS2018 data.
```{r}
## Process the gender data of census 7
df_census7_Gender <- df_census7 %>%
  dplyr::select(c(6,7)) %>%        
  dplyr::slice(c(6)) %>%
  dplyr::rename(male=1, 
                female=2) %>%
  dplyr::mutate(Data_Source = "Census 7") %>%
  tidyr::pivot_longer(c(male, female), 
                      names_to = "Gender",
                      values_to = "Proportion") %>%
  dplyr::mutate(Proportion = round(as.numeric(Proportion), 0))

## Process the gender data of CFPS2018
df_CFPS2018_Gender <- df_CFPS2018 %>%
  dplyr::rename(Gender = QA002) %>%
  dplyr::count(Gender) %>%
  dplyr::filter(!is.na(Gender)) %>%
  dplyr::mutate(Proportion = round(n / sum(n), 2) * 100,
                Data_Source = "CFPS 2018",
                Gender= ifelse(Gender == 1, "male", "female")) %>%
  dplyr::select(Data_Source, Gender, Proportion)
```


Secondly, I extracted Chinese gender of the BTS data and combined Chinese subjects from two data sources.
```{r}
## extract BTS CHN gender data
H2_BTS_CHN_gender <- lapply(BTS_gender_list, function(df){
  
  df %>% 
    dplyr::filter(grepl("CHN", ISO3, ignore.case = TRUE)) %>% 
    dplyr::select(ISO3,Data_Source,Gender) 

})

H2_BTS_CHN_gender <- do.call(rbind, H2_BTS_CHN_gender)

## merge BTS and Chinese papers and calculate gender num and proportion
H2_Journal_Gender <- df_CHN_Journal_Gender %>% 
  dplyr::select(6:7) %>% 
  dplyr::mutate(Data_Source = "Chinese papers")


H2_BTS_CHN_gender2 <- H2_BTS_CHN_gender %>% 
  dplyr::group_by(Gender) %>% 
  dplyr::summarise(n = n()) %>% 
  dplyr::mutate(Data_Source = "BTS Chinese") %>% 
  tidyr::pivot_wider(names_from = Gender,values_from = n) %>% 
  dplyr::rename(Male_Num = 3,Female_Num = 2)


H2_BTS_Journal_gender <- rbind(H2_Journal_Gender,H2_BTS_CHN_gender2) %>% 
  dplyr::summarise(Male_Num = sum(Male_Num),
                   Female_Num = sum(Female_Num,na.rm = TRUE),
                   Male_Proportion = round(Male_Num/(Male_Num + Female_Num),2)*100,
                   Female_Proportion = round(Female_Num/(Male_Num + Female_Num),2)*100) 

H2_BTS_Journal_gender2 <- data.frame(Gender = c("Male","Female"),
                                     n = c(247188,286648),
                                     Proportion = c(46,54),
                                     Data_Source = "Chinese Subjects pool")
```


And then, I combined all Chinese gender data and visualized them.
```{r}
### merge three source data
H2_gender <- bind_rows(df_census7_Gender,df_CFPS2018_Gender,H2_BTS_Journal_gender2) %>% 
  dplyr::mutate(Gender = str_to_title(Gender))


## visualization
H2_Fig_gender <- ggplot(H2_gender,aes(Data_Source,Proportion,fill= Gender))+
  geom_col()+
  geom_hline(yintercept = 50, linetype = "dashed", color = "#666666")+
  labs(y="Proportion")+
  theme_classic()+
  theme(panel.border =element_rect(fill=NA,color="black"),
        legend.position = "bottom",
        legend.box.spacing = unit(2,"pt"),
        legend.text = element_text(size = 20, family = "serif"),
        legend.title = element_blank(),
        axis.title = element_text(size = 20,family = "serif"),
        axis.text = element_text(size = 20,family = "serif"))


H2_Fig_gender

# ggsave("H2_fig_gender.pdf", H2_fig_gender, device = "pdf", width=18, height = 9)
```


### Age
Similarly, for age data, I first processed the Census data and the CFPS2018 data.
```{r}
## Process age data for the census 6
df_census6_Age <- df_census6 %>% 
  dplyr::filter(row_number() %% 6 == 0) %>%
  dplyr::select(1,2,5) %>% 
  dplyr::rename(ageBins = 1, Proportion = 3) %>% 
  dplyr::mutate(Proportion = as.numeric(Proportion)) %>% 
  dplyr::mutate(ageBins = str_remove(ageBins, "岁")) %>%
  dplyr::mutate(ageBins = str_replace_all(ageBins, "-", "~")) %>%
  dplyr::slice(-21) 

df_census6_Age$ageBins[20] <- ">=95"

df_census6_Age <- df_census6_Age %>% 
  dplyr::group_by(ageBins) %>% 
  dplyr::summarise(Proportion = sum(Proportion)) %>% 
  dplyr::mutate(Data_Source = "Census 6") %>% 
  dplyr::ungroup() %>% 
  dplyr::arrange(ageBins) %>% 
  dplyr::mutate(ageBins = factor(ageBins, 
                                 levels =c("0~4","5~9","10~14","15~19","20~24",
                                 "25~29","30~34","35~39","40~44","45~49",
                                 "50~54","55~59","60~64","65~69","70~74",
                                 "75~79","80~84","85~89", "90~94",">=95" )))
  


## Process age data for the census 7 
df_census7_Age <- df_census7 %>%
  dplyr::rename(ageBins = 1,Proportion = 5) %>% 
  dplyr::filter(str_detect(ageBins,"岁")) %>%
  dplyr::select(1,2,5) %>% 
  dplyr::mutate(Proportion = as.numeric(Proportion)) %>% 
  dplyr::mutate(ageBins = str_remove(ageBins, "岁")) %>%
  dplyr::mutate(ageBins = str_replace_all(ageBins, "-", "~")) %>% 
  dplyr::slice(-21)

df_census7_Age$ageBins[20] <- ">=95" 
df_census7_Age$Proportion[20] <- 0.06+0.01


df_census7_Age <- df_census7_Age %>% 
  dplyr::group_by(ageBins) %>% 
  dplyr::summarise(Proportion = sum(Proportion)) %>% 
  dplyr::mutate(Data_Source = "Census 7") %>% 
  dplyr::ungroup() %>% 
  dplyr::mutate(ageBins = factor(ageBins, 
                                 levels =c("0~4","5~9","10~14","15~19","20~24",
                                 "25~29","30~34","35~39","40~44","45~49",
                                 "50~54","55~59","60~64","65~69","70~74",
                                 "75~79","80~84","85~89", "90~94",">=95" )))
```


Then, I combined Chinese age data of BTS and Chinese journals.
```{r}
Journal_BTS_CHN_age2 <- Journal_BTS_CHN_age %>% 
  dplyr::select(1:2) %>% 
  dplyr::group_by(ageBins) %>% 
  dplyr::summarise(n = sum(n)) %>% 
  dplyr::mutate(Proportion = round((n/sum(n)*100),2))


# sum(Journal_BTS_CHN_age2$Proportion)
```


Finally, I visualized all Chinese age data and combined figure of gender and age. 
```{r}
H2_Fig_age <- ggplot(data= df_census7_Age, 
       aes(x=ageBins, y = Proportion, fill="Census 7")) +
  geom_col(alpha=0.5, width = 1) +
  geom_line(data = Journal_BTS_CHN_age2, aes(x=ageBins, 
                y = Proportion,group = 1,color = "Chinese Subjects pool"),size =1)+
  scale_fill_manual(values=c("Census 7"="#00BFC4")) +  
  scale_color_manual(values=c("Chinese Subjects pool" = "red")) +
  scale_y_continuous(limits = c(0,35))+
  coord_flip() +
  labs(y="Proportion", x = "Age bins")+
  theme_classic()+
  theme(panel.border =element_rect(fill=NA,color="black"),
        legend.position = "bottom",
        legend.box.spacing = unit(2,"pt"),
        legend.text = element_text(size = 16, family = "serif"),
        legend.title = element_blank(),
        axis.title = element_text(size = 16,family = "serif"),
        axis.text = element_text(size = 16,family = "serif"))


H2_Fig_age


H2_Fig_gender_age <- H2_Fig_gender + H2_Fig_age +
  plot_annotation(tag_levels = 'A')


ggsave("H2_Fig_gender_age.pdf", H2_Fig_gender_age, device = "pdf", width=18, height = 9)


H2_Fig_gender_age
```


### Region
As stated in RR stage1, I tried to analysis region data. As a first step, I processed Subjects_Recruitment_Area data from Chinese journals.
```{r}
df_CHN_Journal_Area <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(is.na(Remark1) & !grepl("重复",Remark2)) %>% 
  dplyr::select(Article_IDs,Study_Number_N,Subjects_Group_N,Subjects_Recruitment_Area)

df_CHN_Journal_Area_02 <- df_CHN_Journal_Area %>% 
  dplyr::filter(Subjects_Recruitment_Area == 0 | Subjects_Recruitment_Area == 2)

df_CHN_Journal_Area_1 <- df_CHN_Journal_Area %>% 
  dplyr::filter(Subjects_Recruitment_Area != 0 & Subjects_Recruitment_Area != 2)

df_CHN_Journal_Area_1$Subjects_Recruitment_Area <- gsub("[；、,:]", ";", df_CHN_Journal_Area_1$Subjects_Recruitment_Area)

df_CHN_Journal_Area_Separate <- df_CHN_Journal_Area_1 %>% 
  tidyr::separate_rows(Subjects_Recruitment_Area,sep = ";") %>% 
  dplyr::mutate(Subjects_Recruitment_Area = gsub("自治区|回族自治区|维吾尔自治区|壮族自治区","",Subjects_Recruitment_Area))


Province <- c("新疆","西藏","甘肃","青海","内蒙古",
              "宁夏","四川","重庆","陕西","贵州","云南",
              "北京","山西","河北","河南","湖北","湖南",
              "广西","广东","香港","澳门","台湾","海南",
              "黑龙江","吉林","辽宁","天津","山东","江苏",
              "安徽","上海","浙江","江西","福建")

df_CHN_Journal_Area_Province <- df_CHN_Journal_Area_Separate %>% 
  dplyr::filter(Subjects_Recruitment_Area %in% Province)

df_CHN_Journal_Area_Province_add <- data.frame(
 Article_IDs = 20182261,
 Study_Number_N = 1,
 Subjects_Group_N = "小学生",
 Subjects_Recruitment_Area = c("河南","甘肃"))

df_CHN_Journal_Area_Province <- rbind(df_CHN_Journal_Area_Province,df_CHN_Journal_Area_Province_add)

df_CHN_Journal_Province_count <- df_CHN_Journal_Area_Province %>% 
  dplyr::count(Subjects_Recruitment_Area) %>% 
  dplyr::mutate(Proportion = round((n/sum(n))*100,2),
                Count_Bins = cut(Proportion,
                                 breaks = c(-Inf,1,5,10,Inf),
                labels = c("<1","1~5","5~10",">=10")))
```


The second step, I processed of provincial distribution of population for census7.
```{r message=FALSE, warning=FALSE, include=FALSE}
df_census7_province <- readxl::read_xls("A0101.xls") %>% 
  dplyr::select(1,5) %>% 
  dplyr::rename(province = 1, population = 2) %>% 
  dplyr::filter(!is.na(province)) %>% 
  dplyr::slice(-c(1:2)) %>% 
  dplyr::mutate(population = as.numeric(population))

df_census7_3 <- data.frame(province = c("台湾","香港","澳门"),
                           population =c(23561236,7474200,683218))
df_census7_province <- rbind(df_census7_province,df_census7_3) %>% 
  dplyr::mutate(proportion = round((population / sum(population))*100,2)) %>% 
  dplyr::mutate(proportion_bins = cut(proportion,
                                      breaks = c(-Inf,1,5,10,Inf),
                                      labels = c("<1","1~5","5~10",">=10")))

df_census7_province$province <- gsub(" ", "", df_census7_province$province)  
```


The third step, I processed of provincial distribution of population for CFPS2018.
```{r}
## process CFPS2018 province data
df_CFPS2018_province <- data.frame(table(df_CFPS2018$PROVCD18)) %>% 
  dplyr::rename(province = 1,population=2) %>% 
  dplyr::mutate(province = c("北京","天津","河北","山西","内蒙古","辽宁","吉林",
                             "黑龙江","上海","江苏","浙江","安徽","福建","江西",
                             "山东","河南","湖北","湖南","广东","广西","海南",
                             "重庆","四川","贵州","云南","西藏","陕西","甘肃",
                             "青海","宁夏","新疆")) %>% 
  dplyr::mutate(proportion = round((population/sum(population))*100,2),
                Data_Source = "CFPS 2018",
                proportion_bins = cut(proportion,
                                      breaks = c(-Inf,1,5,10,Inf),
                                      labels = c("<1","1~5","5~10",">=10")))
```


Finally, I visualized geographic distribution and calculated Bayesian multinomial test for region.
```{r}
API_pre <-  "http://xzqh.mca.gov.cn/data/"
## 读取全国数据
China <-  st_read(dsn = paste0(API_pre, "quanguo.json"), stringsAsFactors=FALSE) 
## 使用 4326 地理坐标系
st_crs(China) <-  4326

# 读取国界线数据
China_line <-  st_read(dsn = paste0(API_pre, "quanguo_Line.geojson"), stringsAsFactors=FALSE) 
st_crs(China_line) <-  4326
## 选择区划代码为国界线的区域
gjx <- China_line[China_line$QUHUADAIMA == "guojiexian",]

# 读取省份经纬度
province <- readxl::read_xlsx("province.xlsx")
colour <- readxl::read_xlsx("colour.xlsx") %>% 
  dplyr::mutate(QUHUADAIMA = as.character(QUHUADAIMA),
                colour_CHN_Journal = 0,
                colour_census7 = 0,
                colour_cfps2018 = 0)

colour$QUHUADAIMA[which(colour$province =="重庆")] <- "500000"

colour$colour_census7[colour$province %in% df_census7_province$province [df_census7_province$proportion_bins == "<1"]] <- 1
colour$colour_census7[colour$province %in% df_census7_province$province [df_census7_province$proportion_bins == "1~5"]] <- 2
colour$colour_census7[colour$province %in% df_census7_province$province [df_census7_province$proportion_bins == "5~10"]] <- 3
colour$colour_census7[colour$province %in% df_census7_province$province [df_census7_province$proportion_bins == ">=10"]] <- 4



colour$colour_CHN_Journal[which(colour$province =="台湾"| colour$province =="澳门")] <- "0"

colour$colour_CHN_Journal[colour$province %in% df_CHN_Journal_Province_count $Subjects_Recruitment_Area[df_CHN_Journal_Province_count$Count_Bins == "<1"]] <- 1
colour$colour_CHN_Journal[colour$province %in% df_CHN_Journal_Province_count $Subjects_Recruitment_Area[df_CHN_Journal_Province_count$Count_Bins == "1~5"]] <- 2
colour$colour_CHN_Journal[colour$province %in% df_CHN_Journal_Province_count $Subjects_Recruitment_Area[df_CHN_Journal_Province_count$Count_Bins == "5~10"]] <- 3
colour$colour_CHN_Journal[colour$province %in% df_CHN_Journal_Province_count $Subjects_Recruitment_Area[df_CHN_Journal_Province_count$Count_Bins == ">=10"]] <- 4


colour$colour_cfps2018[colour$province %in% df_CFPS2018_province$province [df_census7_province$proportion_bins == "<1"]] <- 1
colour$colour_cfps2018[colour$province %in% df_CFPS2018_province$province [df_CFPS2018_province$proportion_bins == "1~5"]] <- 2
colour$colour_cfps2018[colour$province %in% df_CFPS2018_province$province [df_CFPS2018_province$proportion_bins == "5~10"]] <- 3
colour$colour_cfps2018[colour$province %in% df_CFPS2018_province$province [df_CFPS2018_province$proportion_bins == ">=10"]] <- 4



colour <- colour %>%
  dplyr::mutate(colour_CHN_Journal = factor(colour_CHN_Journal, 
                                          levels = c("0","1", "2", "3", "4")),
                colour_census7 = factor(colour_census7,
                                         levels = c("0","1", "2", "3", "4")),
                colour_cfps2018 = factor(colour_cfps2018,
                                         levels = c("0","1", "2", "3", "4")))

China <- dplyr::left_join(China,colour,by= "QUHUADAIMA")
China$colour_CHN_Journal[which(China$province =="台湾")] <- "0"


## Chinese journal papers
Journal_Area <- ggplot() +
  geom_sf(data = China,aes(fill = factor(colour_CHN_Journal))) +
  scale_fill_manual(values = c("#FFFFFF", "#C6DBEF","#6BAED6", "#2171B5", "#08306B"),
                    breaks = c("0","1","2", "3", "4"),
                    labels = c("0", "<1%","<5%", "<10%",">=10%"),drop = FALSE) +
  geom_sf(data = gjx) +
  labs(title = "Journal subjects recruitment area distribution") +
  theme(plot.title = element_text(color = "black",size = 16,
                                  face = "bold",vjust = 0.1, hjust = 0.5),
        legend.title = element_blank(),
        legend.position = c(0.2, 0.2),
        panel.grid = element_blank(),
        panel.background = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        axis.title = element_blank())+
  annotation_north_arrow(location = 'tl',which_north = 'false',
                         style = north_arrow_orienteering())

## census 7 
CFPS2018_Area <- ggplot() +
  geom_sf(data = China,aes(fill = factor(colour_cfps2018))) +
  scale_fill_manual(values = c("#FFFFFF", "#C6DBEF","#6BAED6", "#2171B5", "#08306B"),
                    breaks = c("0","1","2", "3", "4"),
                    labels = c("0", "<1%","<5%", "<10%",">=10%"),drop = FALSE) +
  geom_sf(data = gjx) +
  labs(title = "CFPS2018 subjects recruitment area distribution") +
  theme(plot.title = element_text(color = "black",size = 16,
                                  face = "bold",vjust = 0.1, hjust = 0.5),
        legend.position = "none",
        panel.grid = element_blank(),
        panel.background = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        axis.title = element_blank())+
  annotation_north_arrow(location = 'tl',which_north = 'false',
                         style = north_arrow_orienteering())


## CFPS 2018
Census7_Area <- ggplot() +
  geom_sf(data = China,aes(fill = factor(colour_census7))) +
  scale_fill_manual(values = c("#FFFFFF", "#C6DBEF","#6BAED6", "#2171B5", "#08306B"),
                    breaks = c("0","1","2", "3", "4"),
                    labels = c("0", "<1%","<5%", "<10%",">=10%"),drop = FALSE) +
  geom_sf(data = gjx) +
  labs(title = "Census7 population area distribution") +
  theme(plot.title = element_text(color = "black",size = 16,
                                  face = "bold",vjust = 0.1, hjust = 0.5),
        legend.position = "none",
        panel.grid = element_blank(),
        panel.background = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        axis.title = element_blank())+
  annotation_north_arrow(location = 'tl',which_north = 'false',
                         style = north_arrow_orienteering())



H2_Area <- Census7_Area + CFPS2018_Area + Journal_Area + plot_layout(guides = "collect")+
  plot_annotation(tag_levels = 'A', title = "Area distribution",
                  theme = theme(plot.title = element_text(size = 24))) + 
  theme(plot.tag = element_text(size = 20))


ggsave("H2_Area.pdf", H2_Area, device = "pdf", width=18, height = 15)


H2_Area


#table(df_stage2_Journal_Code2$Educational_Attainment_N)
```


```{r}
df_CHN_Journal_Province_count <- df_CHN_Journal_Province_count %>% 
  dplyr::rename(province = 1, population = 2,
                proportion = 3,proportion_bins = 4) %>% 
  dplyr::mutate(Data_Source = "Chinese papers")

df_census7_province <- df_census7_province %>% 
  dplyr::mutate(Data_Source = "Census 7")

## combine three source data
H2_province_bayes <- bind_rows(df_CHN_Journal_Province_count,df_census7_province,df_CFPS2018_province) %>% 
  dplyr::select(1,3,5) %>% 
  tidyr::pivot_wider(names_from = Data_Source, values_from = proportion) %>% 
  dplyr::mutate(across(everything(),~ifelse(is.na(.),1,.)))




BF_H2_Journal_Census7_region <- BayesMultiNomial(dataset = H2_province_bayes,
                                          factor = "province",
                                          observed = "Chinese papers",
                                          expected = "Census 7")



BF_H2_Journal_CFPS2018_region <- BayesMultiNomial(dataset = H2_province_bayes,
                                          factor = "province",
                                          observed = "Chinese papers",
                                          expected = "CFPS 2018")

```



### Educational attainment
Try to process educational attainment data from Chinese journal.
```{r}
df_CHN_edu <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(is.na(Remark1) & !grepl("重复",Remark2_N)) %>% 
  dplyr::filter(Educational_Attainment_N == 1) %>% 
  dplyr::select(Article_IDs,Study_Number,Subjects_Group,Sample_Size,M_age,SD_age,Sample_Type_N,Educational_Attainment_N,Educational_Attainment_info_N)

writexl::write_xlsx(df_CHN_edu,"df_CHN_edu.xlsx")
```


### Ethnicity
Try to analysis ethnicity data from Chinese journal
```{r}
## In informal code stage, Because our code group haveare multiple coders, in order to reduce coding differences between individuals based on criteria and understanding, our coding for ethnic groups does not include information about native minority languages. For example: Tibetan language. I will now supplement this.

df_stage2_Journal_Code2$Ethnicity_info[768] <- "汉族"

### Article_IDs 20181113 
df_stage2_Journal_Code2$Ethnicity[1291:1292] <- 1
df_stage2_Journal_Code2$Ethnicity_info[1291:1292] <- c("维吾尔族","维吾尔族")

### Article_IDs 20211018
df_stage2_Journal_Code2$Ethnicity[1634:1635] <- 1
df_stage2_Journal_Code2$Ethnicity_info[1634:1635] <- c("藏族","藏族")

### Article_IDs 20213168
df_stage2_Journal_Code2$Ethnicity[1603] <- 1
df_stage2_Journal_Code2$Ethnicity_info[1603] <- "汉族;少数民族"

### Article_IDs 20181017
df_stage2_Journal_Code2$Ethnicity[760:761] <- 1
df_stage2_Journal_Code2$Ethnicity_info[760:761] <- "蒙古族"

### Article_IDs 20211013
df_stage2_Journal_Code2$Ethnicity[1587:1588] <- 1
df_stage2_Journal_Code2$Ethnicity_info[1587:1588] <- "锡伯族"

df_CHN_Ethnicity <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(is.na(Remark1) & !grepl("重复",Remark2)) %>% 
  dplyr::select(Article_IDs,Study_Number,Subjects_Group,Sample_Size,
                Ethnicity,Ethnicity_info) %>% 
  dplyr::filter(Ethnicity == 1) %>% 
  tidyr::separate_rows(Ethnicity_info,sep = ";") %>% 
  dplyr::filter(!grepl("少数|汉族|其他",Ethnicity_info))


#table(df_CHN_Ethnicity$Ethnicity) 1507~0, 63~1

table_ethnicity <- data.frame(table(df_CHN_Ethnicity$Ethnicity_info))

ethnicity_add <- c("土家族","回族","蒙古族","畲族","满族","苗族","壮族","黎族","彝族","布依族")

table_ethnicity <- table_ethnicity %>% 
  dplyr::mutate(Freq = ifelse(Var1 %in% ethnicity_add, Freq+1, Freq))


## sample size and different ethnicity
df_CHN_Ethnicity$Sample_Size[2] <- 251
df_CHN_Ethnicity$Sample_Size[3] <- 297
df_CHN_Ethnicity$Sample_Size[4] <- 110
df_CHN_Ethnicity$Sample_Size[5] <- 61

df_CHN_Ethnicity$Sample_Size[6:21] <- c(14,16,18,9,20,10,18,12,19,10,
                                           19,12,17,15,21,13)

df_CHN_Ethnicity$Sample_Size[32:33] <- c(4,0)

df_CHN_Ethnicity$Sample_Size[34:62] <- c(139,108,71,51,50,40,38,31,
                                         27,24,18,16,16,11,9,6,5,4,
                                         3,3,3,2,2,1,1,1,1,1,1)

df_CHN_Ethnicity$Sample_Size[63:64] <- c(30,60)

df_CHN_Ethnicity$Sample_Size[65] <- 1006

df_CHN_Ethnicity$Sample_Size[72] <- 30

## ethnicity sample size
df_CHN_Ethnicity_group <- df_CHN_Ethnicity %>% 
  dplyr::mutate(Sample_Size =as.numeric(Sample_Size)) %>% 
  dplyr::group_by(Ethnicity_info) %>% 
  dplyr::summarise(Sample = sum(Sample_Size)) %>% 
  dplyr::ungroup()


Ethnicity_Article_IDs_number <- df_CHN_Ethnicity %>% 
  dplyr::distinct(Article_IDs)

Code2_Article_IDs_number <-  df_stage2_Journal_Code2 %>% 
  dplyr::distinct(Article_IDs)
  
### 17/997
```


## Test the 3st hypothesis
### Gender
As with the first two hypotheses, I dealt with gender data first. 
```{r}
# gc()

BTS_ALL_gender <- lapply(BTS_gender_list, function(df){
  
  df %>% 
    dplyr::select(ISO3,Data_Source,Gender) 
  
})

BTS_ALL_gender <- do.call(rbind, BTS_ALL_gender) 

## Filter n > 30
BTS_ALL_gender_tab <- BTS_ALL_gender %>%
  dplyr::group_by(ISO3) %>%
  dplyr::summarise(n=n(),.groups = "drop") %>% 
  dplyr::filter(n > 30) %>%
  dplyr::pull(ISO3)

BTS_ALL_gender <- BTS_ALL_gender %>% 
  dplyr::filter(ISO3 %in% BTS_ALL_gender_tab) %>% 
  dplyr::group_by(ISO3,Gender) %>%
  dplyr::summarise(n = n()) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(Data_Source = "BTS")

## Add journal gender data
BTS_ALL_gender <- BTS_ALL_gender %>% 
  dplyr::mutate(n = ifelse(ISO3 == "CHN" & Gender == "Male", 247188+13811,n),
                n = ifelse(ISO3 == "CHN" & Gender == "Female", 286648 + 14171,n))

BTS_ALL_gender_pro <- BTS_ALL_gender %>% 
  dplyr::group_by(ISO3) %>% 
  dplyr::mutate(Proportion = round(n/sum(n),2)*100) %>%
  dplyr::ungroup()
## Set factor levels according to gender proportion
BTS_ALL_gender_factor <- BTS_ALL_gender_pro %>% 
  dplyr::filter(Gender == "Female") %>% 
  dplyr::arrange(Proportion) %>% 
  dplyr::pull(ISO3)


## combine WEIRD data to visualization
WEIRD_code_gender <- WEIRD_code %>% 
  dplyr::filter(!is.na(iso3c)) %>% 
  dplyr::filter(iso3c %in% BTS_ALL_gender_factor)


Journal_BTS_ALL_gender <- BTS_ALL_gender_pro %>% 
  dplyr::left_join(WEIRD_code_gender,by = c("ISO3" = "iso3c")) %>% 
  dplyr::mutate(WEIRD = ifelse(ISO3 == "XKX","WEIRD",WEIRD)) %>% 
  dplyr::mutate(ISO3 = factor(ISO3,levels = BTS_ALL_gender_factor)) %>% 
  dplyr::filter(!is.na(ISO3))
```


and I visualized gender data.
```{r}
H3_Fig_gender <- ggplot(Journal_BTS_ALL_gender, aes(x=Proportion, y=ISO3,fill=Gender)) +
  geom_col(alpha = .75)+
  labs(y="Countries") + 
  scale_fill_discrete(label=c("female","male")) +
  theme_classic()+
  #guides(y="axis_nested") +
  theme(legend.title = element_text(size = 15,family = "serif"),
        axis.title= element_text(size = 15,family = "serif"),
        axis.text = element_text(size = 10,family = "serif"),
        strip.text = element_text(size = 15,family = "serif"),
        strip.background = element_rect(fill = NA,color = NA),
        panel.border = element_rect(fill = NA,color = "black")) +
  scale_x_continuous(breaks = seq(0, 100, by = 10)) +
  facet_wrap(~ WEIRD, scales = "free")


H3_Fig_gender
```


Secondly, I processed age data. Similarity, I processed age data in two classification. The one is PsyStages.
```{r}
BTS_All_Psystages <- BTS_age_PsyStages %>% 
  dplyr::filter(ISO3 %in% BTS_ALL_gender_tab) %>% 
  dplyr::filter(ISO3 != "CHN") %>% ## drop Chinese data
  dplyr::group_by(ISO3,ageBins) %>% 
  dplyr::summarise(n=n()) %>% 
  dplyr::mutate(Proportion = round(n/sum(n)*100,2)) %>% 
  dplyr::ungroup()


## Add Chinese data
Journal_BTS_CHN_PsyStages <- Sim_Journal_age_PsyStages3_prop %>% 
  dplyr::rename(n = 2) %>% 
  dplyr::bind_rows(BTS_CHN_age_PsyStages) %>% 
  dplyr::group_by(ageBins) %>% 
  dplyr::summarise(n=sum(n)) %>% 
  dplyr::mutate(Proportion = round((n/sum(n))*100,2),
                ISO3 = "CHN")

# sum(Journal_BTS_CHN_PsyStages$Proportion)
  

## Combine data
H3_PsyStages <- dplyr::bind_rows(BTS_All_Psystages,Journal_BTS_CHN_PsyStages)


## Set factor
H3_PsyStages_factor <- H3_PsyStages %>% 
  dplyr::filter(ageBins == "18~25") %>% 
  dplyr::arrange(Proportion) %>% 
  dplyr::pull(ISO3)


## Process WEIRD
H3_PsyStages2 <- H3_PsyStages %>% 
  dplyr::left_join(WEIRD_code_gender, by = c("ISO3" = "iso3c")) %>% 
  dplyr::mutate(WEIRD = ifelse(ISO3 == "XKX","WEIRD",WEIRD)) %>%
  dplyr::mutate(ISO3 = factor(ISO3, levels = H3_PsyStages_factor)) %>% 
  dplyr::filter(!is.na(ageBins))
  
  
```


and I visualized age data (PsyStages) for all countries in BTS.
```{r}
H3_Fig_PsyStages <- ggplot(H3_PsyStages2, aes(x=Proportion, y=ISO3, fill=ageBins)) +
  geom_col(alpha = .75)+
  labs(y="Countries") + 
  scale_fill_discrete(label=c("0~17", "18~25", "26~40", "41~59",">=60" )) +
  theme_classic()+
  #guides(y="axis_nested") +
  theme(legend.title = element_text(size = 15,family = "serif"),
        axis.title= element_text(size = 15,family = "serif"),
        axis.text = element_text(size = 10,family = "serif"),
        strip.text = element_text(size = 15,family = "serif"),
        strip.background = element_rect(fill = NA,color = NA),
        panel.border = element_rect(fill = NA,color = "black")) +
  scale_x_continuous(breaks = seq(0, 100, by = 10)) +
  facet_wrap(~ WEIRD, scales = "free") 


H3_Fig_PsyStages
```


The other is 10-year-old.
```{r}
BTS_ALL_interval10 <- BTS_age_interval10 %>% 
  dplyr::filter(ISO3 %in% BTS_ALL_gender_tab) %>% 
  dplyr::filter(ISO3 != "CHN") %>%  ## drop Chinese data
  dplyr::group_by(ISO3,ageBins) %>% 
  dplyr::summarise(n=n()) %>% 
  dplyr::mutate(Proportion = round(n/sum(n)*100,2)) %>% 
  dplyr::ungroup()


## Add Chinese data
Journal_BTS_CHN_interval10 <- Sim_Journal_age_interval103_prop %>% 
  dplyr::rename(n = 2) %>% 
  bind_rows(BTS_CHN_age_interval10_addrow) %>% 
  dplyr::group_by(ageBins) %>% 
  dplyr::summarise(n=sum(n)) %>% 
  dplyr::mutate(Proportion = round((n/sum(n))*100,2),
                ISO3 = "CHN")


## Combine data
H3_interval10 <- bind_rows(BTS_ALL_interval10,Journal_BTS_CHN_interval10)


## Set factor
H3_interval10_factor <- H3_interval10 %>%
  dplyr::add_row(ISO3 = c("CUB","JAM"),ageBins = "11~20",n = 0, Proportion =0) %>%
  ##add data to visualization 
  dplyr::filter(ageBins == "11~20") %>% 
  dplyr::arrange(Proportion) %>% 
  dplyr::pull(ISO3)


## Process WEIRD
H3_interval102 <- H3_interval10 %>% 
  dplyr::left_join(WEIRD_code_gender, by = c("ISO3" = "iso3c")) %>% 
  dplyr::mutate(WEIRD = ifelse(ISO3 == "XKX","WEIRD",WEIRD)) %>%
  dplyr::mutate(ISO3 = factor(ISO3, levels = H3_interval10_factor)) %>% 
  dplyr::filter(!is.na(ageBins) & !is.na(ISO3)) 

```


and I visualized age data (interval10) of all countries in BTS.
```{r}
H3_Fig_interval10 <- ggplot(H3_interval102, aes(x=Proportion, y=ISO3, fill=ageBins)) +
  geom_col(alpha = .75)+
  labs(y="Countries") + 
  scale_fill_discrete(label=c("0~10","11~20","21~30", "31~40", "41~50", "51~60", ">=61")) +
  theme_classic()+
  #guides(y="axis_nested") +
  theme(legend.title = element_text(size = 15,family = "serif"),
        axis.title= element_text(size = 15,family = "serif"),
        axis.text = element_text(size = 10,family = "serif"),
        strip.text = element_text(size = 15,family = "serif"),
        strip.background = element_rect(fill = NA,color = NA),
        panel.border = element_rect(fill = NA,color = "black")) +
  scale_x_continuous(breaks = seq(0, 100, by = 10)) +
  facet_wrap(~ WEIRD, scales = "free") 


H3_Fig_interval10
```


After the visualization of complete, I calculated BF. Firstly I defined a function to calculating BF for multiple countries.
```{r}
# create a new variable to store the BF values
Func_BFpairs <- function(df, countries_order, prop_name){
  
  # create a temp variable for storing 
  BF_mult_tmp <- data.frame(matrix(nrow = 0, ncol = 5))
  colnames(BF_mult_tmp) <- c("Observed", "Expected", "Log(BF10)_NonInform", "BF10_NonInform", "BF01_NonInform")
  
  for (ii in seq(length(countries_order))){
    country <- countries_order[ii]
    if (country != "CHN"){
      df_tmp <- df %>% dplyr::select(prop_name, one_of(country), "CHN")
      
      BF_tmp <- BayesMultiNomial(dataset = df_tmp, 
                                 factor = prop_name, observed = country, expected = "CHN")
      
      BF_mult_tmp[ii,] <- c(as.character(country), "CHN", 
                            BF_tmp$BF$LogBF10, BF_tmp$BF$BF10, BF_tmp$BF$BF01)
    } 
  }
  
  countries_order_age <- BF_mult_tmp %>% 
    tidyr::drop_na() %>%
    dplyr::mutate(`Log(BF10)_NonInform` = as.numeric(`Log(BF10)_NonInform`)) %>%
    dplyr::arrange(`Log(BF10)_NonInform`) %>%
    dplyr::pull(Observed)
  
  BF_mult_p_tmp <- BF_mult_tmp %>%
    tidyr::drop_na() %>%
    dplyr::select(1,2,3) %>%
    dplyr::mutate(Countries = factor(Observed, levels = countries_order_age),
                  `Log(BF10)_NonInform` = as.numeric(`Log(BF10)_NonInform`)) 
  
  return(BF_mult_p_tmp)
}
```


Secondly , I calculated gender BF and visualized gender BF.
```{r}
BF_H3_gender <- Journal_BTS_ALL_gender %>% 
  dplyr::select(ISO3,Gender,Proportion) %>% 
  dplyr::rename(Countries = 1)


BF_H3_gender_factor <- BF_H3_gender %>% 
  dplyr::filter(Gender == "Female") %>% 
  dplyr::arrange(Proportion) %>% 
  dplyr::pull(Countries)


BF_H3_gender_Journal_BTS <- BF_H3_gender  %>% 
  dplyr::mutate(Countries = factor(Countries, levels = BF_H3_gender_factor)) %>% 
  tidyr::pivot_wider(names_from = "Countries",values_from = "Proportion") %>% 
  Func_BFpairs(countries_order = BF_H3_gender_factor,
               prop_name = "Gender")

```


```{r warning=FALSE}
H3_Fig_BF_gender <- ggplot(BF_H3_gender_Journal_BTS, aes( x = `Log(BF10)_NonInform`, y = Countries)) +
  geom_point() +
  scale_color_grey() +
  xlim(-3, 25) +
  scale_y_discrete(limits=rev) +
  geom_vline(xintercept = c(log(1/10), log(1/6), 0, log(6), log(10)), 
             colour = c("red", "tomato", "black", "deepskyblue","blue"), 
             linetype=c("longdash", "longdash", "solid", "longdash","longdash")) + 
  geom_text(aes(x=log(10), label="\nStrong evidence for H1", y = 23), colour="blue", alpha = 0.7, 
            angle=90, text=element_text(size=10)) +
  geom_text(aes(x=log(6), label="Moderate evidence for H1\n", y = 23), colour="deepskyblue", alpha = 0.7, 
            angle=90, text=element_text(size=10)) +
  geom_text(aes(x=log(1/6), label="\nModerate evidence for H0", y = 23), colour="tomato", alpha = 0.7, 
            angle=90, text=element_text(size=10)) +
  geom_text(aes(x=log(1/10), label="Strong evidence for H0\n", y = 23), colour="red", alpha = 0.7, 
            angle=90, text=element_text(size=10)) +
  ggtitle("Gender Proportion") + 
  xlab("Log(BF10)")+
  theme_bw() +
        theme(panel.grid.major = element_blank(),
              panel.grid.minor = element_blank(),
              panel.background = element_blank(),
              panel.border = element_blank(),
              text = element_text(family='Times'),
              axis.text.x = element_text (size = 12, color = 'black',  hjust = 1),
              axis.text.y = element_text (size = 12, color = 'black'),
              plot.title = element_text(lineheight=.8, face="bold", size = 18, margin=margin(0,0,20,0)),
              axis.text = element_text (size = 16, color = 'black'),
              axis.title = element_text (size = 16),
              axis.title.x = element_text (size = 16),
              axis.title.y = element_text( size = 16),
              axis.line.x = element_line(color='black', size = 1),
              axis.line.y = element_line(color='black', size = 1))


H3_Fig_BF_gender
```


Third, I calculted age BF in two classification. In this part, I calculated BF for this two categories.
```{r}
## PsyStages
BF_H3_all_PsyStages <- H3_PsyStages2 %>% 
  dplyr::select(ISO3,ageBins,Proportion) %>% 
  dplyr::rename(Countries = 1)

BF_H3_PsyStages_Journal_BTS <- BF_H3_all_PsyStages  %>% 
  dplyr::mutate(Countries = factor(Countries, levels = BF_H3_gender_factor)) %>% 
  tidyr::pivot_wider(names_from = "Countries",values_from = "Proportion") %>%
  dplyr::mutate(across(2:last_col(), ~ifelse(is.na(.), 0, .))) %>%
  Func_BFpairs(countries_order = BF_H3_gender_factor,
               prop_name = "ageBins")


# sum(BF_H3_PsyStages_Journal_BTS$AGO,na.rm = TRUE)
## interval10
BF_H3_all_interval10 <- H3_interval102 %>% 
  dplyr::select(ISO3,ageBins,Proportion) %>% 
  dplyr::rename(Countries = 1)

BF_H3_interval10_Journal_BTS <- BF_H3_all_interval10  %>% 
  dplyr::mutate(Countries = factor(Countries, levels = BF_H3_gender_factor)) %>% 
  tidyr::pivot_wider(names_from = "Countries",values_from = "Proportion") %>%
  dplyr::mutate(across(2:last_col(), ~ifelse(is.na(.), 1, .))) %>%
  Func_BFpairs(countries_order = BF_H3_gender_factor,
               prop_name = "ageBins")

#write.csv(BF_H3_interval10_Journal_BTS,"BF_H3_interval10_Journal_BTS.csv")

```


and I visualized PsyStages BF at first.
```{r warning=FALSE}
Fig_BF_PsyStages <- ggplot(BF_H3_PsyStages_Journal_BTS, aes( x = `Log(BF10)_NonInform`, y = Countries)) +
  geom_point() +
  scale_color_grey() +
  xlim(-10,200) +
  scale_y_discrete(limits=rev) +
  geom_vline(xintercept = c(log(1/10), log(1/6), 0, log(6), log(10)), 
             colour = c("red", "tomato", "black", "deepskyblue","blue"), 
             linetype=c("longdash", "longdash", "solid", "longdash","longdash")) + 
  geom_text(aes(x=log(10), label="\nStrong evidence for H1", y = 23), colour="blue", alpha = 0.7, 
            angle=90, text=element_text(size=10)) +
  geom_text(aes(x=log(6), label="Moderate evidence for H1\n", y = 23), colour="deepskyblue", alpha = 0.7, 
            angle=90, text=element_text(size=10)) +
  geom_text(aes(x=log(1/6), label="\nModerate evidence for H0", y = 23), colour="tomato", alpha = 0.7, 
            angle=90, text=element_text(size=10)) +
  geom_text(aes(x=log(1/10), label="Strong evidence for H0\n", y = 23), colour="red", alpha = 0.7, 
            angle=90, text=element_text(size=10))  +
  ggtitle("Age distribution") +
  xlab("Log(BF10)")+
  theme_bw() +
        theme(panel.grid.major = element_blank(),
              panel.grid.minor = element_blank(),
              panel.background = element_blank(),
              panel.border = element_blank(),
              text = element_text(family='Times'),
              axis.text.x = element_text (size = 12, color = 'black',  hjust = 1),
              axis.text.y = element_text (size = 12, color = 'black'),
              plot.title = element_text(lineheight=.8, face="bold", size = 18, margin=margin(0,0,20,0)),
              axis.text = element_text (size = 16, color = 'black'),
              axis.title = element_text (size = 16),
              axis.title.x = element_text (size = 16),
              axis.title.y = element_text( size = 16),
              axis.line.x = element_line(color='black', size = 1),    
              axis.line.y = element_line(color='black', size = 1))


Fig_BF_PsyStages
```


Then I visualized another category.
```{r warning=FALSE}
Fig_BF_interval10 <- ggplot(BF_H3_interval10_Journal_BTS, 
                            aes( x = `Log(BF10)_NonInform`, y = Countries)) +
  geom_point() +
  scale_color_grey() +
  xlim(-10,100) +
  scale_y_discrete(limits=rev) +
  geom_vline(xintercept = c(log(1/10), log(1/6), 0, log(6), log(10)), 
             colour = c("red", "tomato", "black", "deepskyblue","blue"), 
             linetype=c("longdash", "longdash", "solid", "longdash","longdash")) + 
  geom_text(aes(x=log(10), label="\nStrong evidence for H1", y = 23), colour="blue", alpha = 0.7, 
            angle=90, text=element_text(size=10)) +
  geom_text(aes(x=log(6), label="Moderate evidence for H1\n", y = 23), colour="deepskyblue", alpha = 0.7, 
            angle=90, text=element_text(size=10)) +
  geom_text(aes(x=log(1/6), label="\nModerate evidence for H0", y = 23), colour="tomato", alpha = 0.7, 
            angle=90, text=element_text(size=10)) +
  geom_text(aes(x=log(1/10), label="Strong evidence for H0\n", y = 23), colour="red", alpha = 0.7, 
            angle=90, text=element_text(size=10))  +
  ggtitle("Age distribution") +
  xlab("Log(BF10)")+
  theme_bw() +
        theme(panel.grid.major = element_blank(),
              panel.grid.minor = element_blank(),
              panel.background = element_blank(),
              panel.border = element_blank(),
              text = element_text(family='Times'),
              axis.text.x = element_text (size = 12, color = 'black',  hjust = 1),
              axis.text.y = element_text (size = 12, color = 'black'),
              plot.title = element_text(lineheight=.8, face="bold", size = 18, margin=margin(0,0,20,0)),
              axis.text = element_text (size = 16, color = 'black'),
              axis.title = element_text (size = 16),
              axis.title.x = element_text (size = 16),
              axis.title.y = element_text( size = 16),
              axis.line.x = element_line(color='black', size = 1),    
              axis.line.y = element_line(color='black', size = 1))


# ggsave("Fig_BF_interval10.pdf", Fig_BF_interval10, device = "pdf", width=18, height = 18)


Fig_BF_interval10
```


Finally, I combined the four figure for gender and age, as well as the figure that suppl document.
```{r warning=FALSE}
H3_Fig_gender_age <- (H3_Fig_BF_gender + Fig_BF_PsyStages) /
   (H3_Fig_gender + H3_Fig_PsyStages) +
  plot_annotation(tag_levels = 'A')  & 
  theme(plot.tag = element_text(size = 18, face = "bold"))


ggsave("H3_Fig_gender_age.pdf", H3_Fig_gender_age, device = "pdf", width=18, height = 18)


H3_Fig_gender_age



## suppl
H3_Fig_gender_age_suppl <- Fig_BF_interval10 + H3_Fig_interval10 +
   plot_annotation(tag_levels =list(c("S1a","S1b")))  & 
  theme(plot.tag = element_text(size = 18, face = "bold"))


ggsave("H3_Fig_gender_age_suppl .pdf", H3_Fig_gender_age_suppl , device = "pdf", width=18, height = 18)


H3_Fig_gender_age_suppl 
```


### Region
In this part, I analysed and visualized all countries in our study. Firstly, I processed region data of BTS. 
```{r}
if(!require("maps")) install.packages("maps")


## creat a world map
world_map <- ggplot2::map_data(map = "world")


world_map2 <- world_map %>% 
  dplyr::mutate(region = iso.alpha(region),
                long = ifelse(long >= -180 & long <= -30, 
                              long + 360, long),
                region = ifelse(region == "TW","CN",region))  


BTS_region <- BTS_Overview2 %>% 
  dplyr::mutate(Proportion = Proportion * 0.01) %>% 
  dplyr::mutate(Proportion_bins = if_else(Proportion >= 0.16, "0.16-1",
                                          if_else(Proportion < 0.16 & Proportion >= 0.08, "0.08-0.16" ,
                                                  if_else(Proportion < 0.08 & Proportion >= 0.04, "0.04-0.08" , 
                                                          if_else(Proportion < 0.04 & Proportion >= 0.02, "0.02-0.04" , 
                                                                  if_else(Proportion < 0.02 & Proportion >= 0.01, "0.01-0.02" , 
                                                                          if_else(Proportion < 0.01 & Proportion >= 0.005, "0.005-0.01" ,         
                                                                                  if_else(Proportion < 0.005 & Proportion >= 0.0025, "0.0025-0.005", "0-0.0025"))))))))

```


And I visualized geographic distribution of BTS.
```{r}
Fig_BTS_region <- ggplot2::ggplot(BTS_region)+
  geom_map(aes(map_id = ISO2, fill = Proportion_bins), map = world_map2,show.legend = TRUE) +
  geom_polygon(data = world_map2, 
               aes(x = long, y = lat, group = group), 
               colour = 'black', size=0.1, fill = NA) + 
  theme_void() + 
  xlim(c(-30, 329)) + 
  ylim(c(-60, 90)) +
  scale_fill_manual(name = "sample proportion",
                    values = c("#CCE5FF","#99CCFF", "#66B2FF","#3399FF","#0080FF" ,"#0066CC","#004C99","#003366"),
                    limits = c("0-0.0025", "0.0025-0.005", "0.005-0.01", "0.01-0.02", "0.02-0.04", "0.04-0.08","0.08-0.16", "0.16-1")) +
ggtitle("Geographical distribution of sample from BTS")+
  theme(plot.title = element_text(hjust = 0.5, size = 15),
        legend.text = element_text(size = 10),  
        legend.title = element_text(size = 12),  
        legend.key.size = unit(3, "pt"),  
        legend.key.height = unit(3, "pt"), 
        legend.key.width = unit(15, "pt")  
        )


Fig_BTS_region
```


Secondly, I processed and visualized geographic distribution of world population.
Note: this data process and plot code from Liu weibiao and Hu chuanpeng, thanks them.
```{r}
wppdata <- read_csv("WPP2022.csv")


wppdata1 <- subset(wppdata, select = c("country_map","continent", "pop"))


wppdata3 <- dplyr::mutate(.data = wppdata1, percentage_pop = pop/7909295.151) 


#wppdata3 <- wppdata2 %>% dplyr::left_join(df_PSA001, by = "country_map")

#Merge data from Taiwan Province with data from mainland China
sum_of_cn <- sum(wppdata3$percentage_pop[wppdata3$country_map %in% c("CN", "TW")])

wppdata3$percentage_pop[wppdata3$country_map %in% c("CN", "TW")] <- sum_of_cn
wppdata3$percentage_pop[wppdata3 $country_map == "GL"] <- NA



wppdata3$n_binned <- 
  if_else(wppdata3$percentage_pop >= 0.16, "0.16-1",
  if_else(wppdata3$percentage_pop < 0.16 & wppdata3$percentage_pop >= 0.08, "0.08-0.16" , 
   if_else(wppdata3$percentage_pop < 0.08 & wppdata3$percentage_pop >= 0.04, "0.04-0.08" , 
  if_else(wppdata3$percentage_pop < 0.04 & wppdata3$percentage_pop >= 0.02, "0.02-0.04" , 
   if_else(wppdata3$percentage_pop < 0.02 & wppdata3$percentage_pop >= 0.01, "0.01-0.02" , 
   if_else(wppdata3$percentage_pop < 0.01 & wppdata3$percentage_pop >= 0.005, "0.005-0.01" ,         
  if_else(wppdata3$percentage_pop < 0.005 & wppdata3$percentage_pop >= 0.0025, "0.0025-0.005",
      "0-0.0025"
    )
  )
 )
))))


wppdata4 <- wppdata3[complete.cases(wppdata3$percentage_pop), ]


# map of World people data 
world_population_map <- ggplot2::ggplot(wppdata4) +
  ggplot2::geom_map(aes(map_id = country_map, fill = n_binned), map = world_map2,show.legend = TRUE) +
  ggplot2::geom_polygon(data = world_map2, 
               aes(x = long, y = lat, group = group), 
               colour = 'black', size=0.1, fill = NA) + 
  theme_void() + 
   xlim(c(-30, 329)) + 
  ylim(c(-60, 90)) + 
  scale_fill_manual(name = "world people proportion",
                    values = c("#CCE5FF","#99CCFF", "#66B2FF","#3399FF","#0080FF" ,"#0066CC","#004C99","#003366"),
                    limits = c("0-0.0025", "0.0025-0.005", "0.005-0.01", "0.01-0.02", "0.02-0.04", "0.04-0.08","0.08-0.16", "0.16-1"),
                    drop = FALSE) +
ggtitle("Geographical distribution of world population")+
  theme(plot.title = element_text(hjust = 0.5, size = 15),
        legend.text = element_text(size = 10),  
        legend.title = element_text(size = 12),  
        legend.key.size = unit(3, "pt"),  
        legend.key.height = unit(3, "pt"),  
        legend.key.width = unit(15, "pt")  
        )


world_population_map


sample_map <- Fig_BTS_region + world_population_map + 
  plot_layout(ncol = 2, heights = c(4,4))+
  patchwork::plot_annotation(tag_levels = 'A')


ggsave("sample_map.pdf", sample_map, device = "pdf", width=18, height = 9)


sample_map 
```


In addition to the above analysis, I also conducted some exploratory analysis of the data.
# Exploratory analysis
## Abstract1 subjects information reported of Chinese journal
Try to process Abstract data.
```{r message=FALSE, warning=FALSE}
### In our coding, different subject groups will make the same article have multiple rows of data, but there is only one abstract and the multi-rows Abstract1 should be consistent. So, first, I check whether Abstract1 is consistent.

Abstract_subj_info_filter <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(is.na(Remark1) & !grepl("重复",Remark2)) %>%
  dplyr::filter(!grepl("2",Subjects_Recruitment_Area)) %>% 
  dplyr::select(Article_IDs,Study_Number,Subjects_Group,Abstract1,Sample_Type_N,Sample_Type_info_N,
                Abstract2)


Abstract1_subj_info_equl <- Abstract_subj_info_filter %>%
  dplyr::group_by(Article_IDs) %>%  
  dplyr::mutate(Same_Abstract1 = n_distinct(Abstract1) == 1) %>%  
  dplyr::ungroup() 

### Article_IDs 20081099
df_stage2_Journal_Code2$Abstract1[17] <- 0

### Article_IDs 20183099
df_stage2_Journal_Code2$Abstract1[382] <- 14

### Article_IDs 20083116
df_stage2_Journal_Code2$Abstract1[1460] <- 14

### Article_IDs 20181236
df_stage2_Journal_Code2$Abstract1[1506] <- 145

### Article_IDs 20081096
df_stage2_Journal_Code2$Abstract1[15] <- 1234

### Article_IDs 20185111
df_stage2_Journal_Code2$Abstract1[1380] <- 0

### Article_IDs 20211025
df_stage2_Journal_Code2$Abstract1[1590:1591] <- "1234b"

### Article_IDs 20213237
df_stage2_Journal_Code2$Abstract1[1641:1642] <- 1

## Then, I check that the encoding of Abstract1 and Abstract2 is exactly the same
Abstract1_Abstract2 <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(is.na(Remark1) & !grepl("重复",Remark2)) %>%
  dplyr::filter(!grepl("2",Subjects_Recruitment_Area)) %>% 
  dplyr::select(Article_IDs,Study_Number,Subjects_Group,Sample_Type_N,Abstract2,Abstract1) %>% 
  dplyr::filter(grepl("1",Sample_Type_N)) %>% 
  dplyr::filter(grepl("1",Abstract1) & Abstract2 != 1)

### Article_IDs 20213252
df_stage2_Journal_Code2$Abstract2[490] <- 1

### Article_IDs 20185009
df_stage2_Journal_Code2$Abstract1[867:868] <- 0

### Article_IDs 20181100
df_stage2_Journal_Code2$Abstract2[1278:1279] <- 1

### Article_IDs 20213184
df_stage2_Journal_Code2$Abstract2[1605] <- 1


### Process demographic information reports for different samples in the Abstract1
Abstract1_subj_info_equl <- Abstract1_subj_info_equl %>% 
  dplyr::filter(Sample_Type_N != 5) %>% 
  dplyr::group_by(Article_IDs) %>% 
  dplyr::mutate(Sample_type3 = ifelse(all(Sample_Type_N == 1),1,
                                          ifelse(any(grepl("1",Sample_Type_N)) & any(Sample_Type_N !=1),2,
                                      3))) %>% 
  dplyr::ungroup()



### Abstract2 (univeristy students report)
Abstract2_report_NA <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(is.na(Remark1) & !grepl("重复",Remark2)) %>%
  dplyr::filter(!grepl("2",Subjects_Recruitment_Area)) %>% 
  dplyr::filter(grepl("1",Sample_Type_N)) %>% 
  dplyr::select(Article_IDs,Study_Number,Subjects_Group,Sample_Type_N,Abstract2,Abstract1) %>% 
  dplyr::filter(is.na(Abstract2))

df_stage2_Journal_Code2 <- df_stage2_Journal_Code2 %>% 
  dplyr::mutate(Abstract2 = ifelse(is.na(Remark1) & !grepl("重复",Remark2) & 
                                     !grepl("2",Subjects_Recruitment_Area) & 
                                     grepl("1",Sample_Type_N) & Abstract1 == 0,0,Abstract2))

### Article_IDs 20183311
df_stage2_Journal_Code2$Abstract2[161] <- 0

### Article_IDs 20182075
df_stage2_Journal_Code2$Abstract2[776] <- 1

### Article_IDs 20082324
df_stage2_Journal_Code2$Abstract2[950] <- 0

### Article_ID 20082024
df_stage2_Journal_Code2$Abstract2[1440] <- 1

### Article_IDs 20082042
df_stage2_Journal_Code2$Abstract1[1451] <- 123
df_stage2_Journal_Code2$Abstract2[1451] <- 1

### Article_IDs 20213168
df_stage2_Journal_Code2$Abstract2[1603] <- 1

### Article_IDs 20213192
df_stage2_Journal_Code2$Abstract2[1611:1612] <- 0
```


Specific abstract reporting data.
```{r message=FALSE, warning=FALSE}
Abstract1_subj_info <- Abstract1_subj_info_equl %>% 
  dplyr::mutate(Abstract1_demo_info = ifelse(Abstract1 == 0,0,1),  
                Abstract1_sample_info = ifelse(grepl("1",Abstract1),1,0)) %>% 
  dplyr::select(Article_IDs,Abstract1_demo_info,Abstract1_sample_info,Sample_type3) %>% 
  dplyr::group_by(Article_IDs) %>% 
  dplyr::slice(1) %>% 
  dplyr::ungroup() ### Abstract1_demo_info means demographic information report, Abstract2_sample_info means sample type report  

### the demographic report of different sample type in Abstract1
Abstract1_demo_info <- Abstract1_subj_info %>% 
  dplyr::group_by(Sample_type3,Abstract1_demo_info) %>% 
  dplyr::summarise(report = n()) %>% 
  dplyr::ungroup() %>% 
  dplyr::mutate(proportion = round(report/sum(report),2))
  
### the sample information report of different sample type in Abstract1
#Abstract1_sample_info <- Abstract1_subj_info %>% 
 # dplyr::group_by(Sample_type3,Abstract1_sample_info) %>% 
  #dplyr::summarise(report = n()) %>% 
  #dplyr::ungroup() %>% 
  #dplyr::mutate(proportion = round(report/sum(report),2))


Abstract2_report <- df_stage2_Journal_Code2 %>% 
  dplyr::filter(is.na(Remark1) & !grepl("重复",Remark2)) %>%
  dplyr::filter(!grepl("2",Subjects_Recruitment_Area)) %>% 
  dplyr::filter(grepl("1",Sample_Type_N)) %>% 
  dplyr::group_by(Article_IDs) %>% 
  dplyr::mutate(Same_Abstract2 = n_distinct(Abstract2) == 1) %>%  ## check multiple subjects group Abstract2 whether is consistent.
  dplyr::slice(1) %>% 
  dplyr::ungroup() %>% 
  dplyr::group_by(Abstract2) %>% 
  dplyr::summarise(report = n()) %>% 
  dplyr::ungroup() %>% 
  dplyr::mutate(proportion = round(report/sum(report),2))

```

