---
title: "Notebook_Exploration_Analysis"
author: "Lei Yue"
date: "2025-05-13"
output: html_document
---



## intall library
```{r}
rm(list = ls())

if (!require("pacman")) install.packages("pacman")

p_load("tidyverse","ggplot2")
```



## Load data
```{r}
load("Journal.Rdata")
```


## Journal report
```{r}
Journal_year2008_report <- Journal %>% 
  dplyr::filter(substr(Article_IDs_N,1,4) == "2008") %>% 
  dplyr::mutate(Subjects_Recruitment_Area = ifelse(Subjects_Recruitment_Area == 0, 0, 1),
                Sampling_Method = ifelse(Sampling_Method == 0, 0 ,1),
                SES_N = ifelse(SES_N == 0, 0, 1),
                Subjects_Recruitment_Method_N = ifelse(Subjects_Recruitment_Method_N == 0, 0, 1)) %>%
  dplyr::group_by(Article_IDs,Study_Number) %>% 
  dplyr::summarise(Age = max(Age) > 0,
                   Gender = max(Gender) > 0,
                   Religious = max(Religious) > 0,
                   Ethnicity = max(Ethnicity) > 0,
                   Sampling_Method = max(Sampling_Method) > 0,
                   Recruitment_Area = max(Subjects_Recruitment_Area) > 0,
                   Recruitment_Method = max(Subjects_Recruitment_Method_N) > 0,
                   SES = max(SES_N) > 0,
                   .groups = "drop") %>% 
  dplyr::select(3:last_col())


report_list <- list()

for (i in names(Journal_year2008_report )){
  
  
  report_table <- data.frame(table(Journal_year2008_report [[i]])) %>% 
    dplyr::mutate(col_names = names(Journal_year2008_report [i]),
                  proportion = round(Freq / sum(Freq),4))
  
  report_list[[i]] <- report_table
  
}

Journal_year2008_report <- do.call(rbind, report_list) %>% 
  dplyr::mutate(Var1 = ifelse(Var1 == "TRUE", "Reported","Unreported")) 


### Calculate reported status of Educational_Attainment and Occupation
Journal_year2008_education_occupation <- Journal %>% 
  dplyr::filter(substr(Article_IDs_N,1,4) == "2008") %>% 
  dplyr::filter(Sample_Type_N %in% c(4,5)) %>% 
  dplyr::group_by(Article_IDs,Study_Number) %>% 
  dplyr::summarise(Educational_Attainment_N = max(Educational_Attainment_N) > 0,
                   Occupation_N = max(Occupation_N) > 0,.groups = "drop") 



# table(Journal_year2008_education_occupation$Educational_Attainment_N) ## FALSE 32 TRUE 30
# table(Journal_year2008_education_occupation$Occupation_N)  ## FALSE 35 TRUE 27


Journal_year2008_education_occupation_table <- data.frame(Var1 = c("Unreported","Reported",
                                                            "Unreported","Reported"),
                                                   Freq = c(32,30,35,27),
                                                   col_names= c("Educational_Attainment",
                                                                "Educational_Attainment",
                                                                "Occupation","Occupation"),
                                                   proportion = c(0.52,0.48,0.56,0.44))

Journal_year2008_report2 <- rbind(Journal_year2008_report,
                                  Journal_year2008_education_occupation_table) %>%
  dplyr::mutate(col_names = factor(col_names, 
                                   labels = c("Gender","Recruitment Method",
                                              "Recruitment Area",
                                              "Age","Educational Attainment",
                                              "Occupation","Sampling Method",
                                              "SES","Ethnicity","Religious"),
                                   levels = c("Gender","Recruitment_Method",
                                              "Recruitment_Area",
                                              "Age","Educational_Attainment",
                                              "Occupation","Sampling_Method",
                                              "SES","Ethnicity","Religious")),
                proportion = proportion *100) %>% 
  dplyr::mutate(Year = "2008")

```


```{r}
Journal_year2018_report <- Journal %>% 
  dplyr::filter(substr(Article_IDs_N,1,4) == "2018") %>% 
  dplyr::mutate(Subjects_Recruitment_Area = ifelse(Subjects_Recruitment_Area == 0, 0, 1),
                Sampling_Method = ifelse(Sampling_Method == 0, 0 ,1),
                SES_N = ifelse(SES_N == 0, 0, 1),
                Subjects_Recruitment_Method_N = ifelse(Subjects_Recruitment_Method_N == 0, 0, 1)) %>%
  dplyr::group_by(Article_IDs,Study_Number) %>% 
  dplyr::summarise(Age = max(Age) > 0,
                   Gender = max(Gender) > 0,
                   Religious = max(Religious) > 0,
                   Ethnicity = max(Ethnicity) > 0,
                   Sampling_Method = max(Sampling_Method) > 0,
                   Recruitment_Area = max(Subjects_Recruitment_Area) > 0,
                   Recruitment_Method = max(Subjects_Recruitment_Method_N) > 0,
                   SES = max(SES_N) > 0,
                   .groups = "drop") %>% 
  dplyr::select(3:last_col())


report_list <- list()

for (i in names(Journal_year2018_report )){
  
  
  report_table <- data.frame(table(Journal_year2018_report [[i]])) %>% 
    dplyr::mutate(col_names = names(Journal_year2018_report [i]),
                  proportion = round(Freq / sum(Freq),4))
  
  report_list[[i]] <- report_table
  
}

Journal_year2018_report <- do.call(rbind, report_list) %>% 
  dplyr::mutate(Var1 = ifelse(Var1 == "TRUE", "Reported","Unreported")) 


### Calculate reported status of Educational_Attainment and Occupation
Journal_year2018_education_occupation <- Journal %>% 
  dplyr::filter(substr(Article_IDs_N,1,4) == "2018") %>% 
  dplyr::filter(Sample_Type_N %in% c(4,5)) %>% 
  dplyr::group_by(Article_IDs,Study_Number) %>% 
  dplyr::summarise(Educational_Attainment_N = max(Educational_Attainment_N) > 0,
                   Occupation_N = max(Occupation_N) > 0,.groups = "drop") 



table(Journal_year2018_education_occupation$Educational_Attainment_N) ## FALSE 73 TRUE 69
table(Journal_year2018_education_occupation$Occupation_N)  ## FALSE 84 TRUE 58


Journal_year2018_education_occupation_table <- data.frame(Var1 = c("Unreported","Reported",
                                                            "Unreported","Reported"),
                                                   Freq = c(73,69,84,58),
                                                   col_names= c("Educational_Attainment",
                                                                "Educational_Attainment",
                                                                "Occupation","Occupation"),
                                                   proportion = c(0.51,0.49,0.59,0.41))

Journal_year2018_report2 <- rbind(Journal_year2018_report,
                                  Journal_year2018_education_occupation_table) %>%
  dplyr::mutate(col_names = factor(col_names, 
                                   labels = c("Gender","Age","Recruitment Method",
                                              "Recruitment Area",
                                              "Educational Attainment",
                                              "Occupation","Sampling Method",
                                              "SES","Ethnicity","Religious"),
                                   levels = c("Gender","Age","Recruitment_Method",
                                              "Recruitment_Area",
                                              "Educational_Attainment",
                                              "Occupation","Sampling_Method",
                                              "SES","Ethnicity","Religious")),
                proportion = proportion *100)%>% 
  dplyr::mutate(Year = "2018")

```


```{r}
Journal_year2021_report <- Journal %>% 
  dplyr::filter(substr(Article_IDs_N,1,4) == "2021") %>% 
  dplyr::mutate(Subjects_Recruitment_Area = ifelse(Subjects_Recruitment_Area == 0, 0, 1),
                Sampling_Method = ifelse(Sampling_Method == 0, 0 ,1),
                SES_N = ifelse(SES_N == 0, 0, 1),
                Subjects_Recruitment_Method_N = ifelse(Subjects_Recruitment_Method_N == 0, 0, 1)) %>%
  dplyr::group_by(Article_IDs,Study_Number) %>% 
  dplyr::summarise(Age = max(Age) > 0,
                   Gender = max(Gender) > 0,
                   Religious = max(Religious) > 0,
                   Ethnicity = max(Ethnicity) > 0,
                   Sampling_Method = max(Sampling_Method) > 0,
                   Recruitment_Area = max(Subjects_Recruitment_Area) > 0,
                   Recruitment_Method = max(Subjects_Recruitment_Method_N) > 0,
                   SES = max(SES_N) > 0,
                   .groups = "drop") %>% 
  dplyr::select(3:last_col())


report_list <- list()

for (i in names(Journal_year2021_report )){
  
  
  report_table <- data.frame(table(Journal_year2021_report [[i]])) %>% 
    dplyr::mutate(col_names = names(Journal_year2021_report [i]),
                  proportion = round(Freq / sum(Freq),4))
  
  report_list[[i]] <- report_table
  
}

Journal_year2021_report <- do.call(rbind, report_list) %>% 
  dplyr::mutate(Var1 = ifelse(Var1 == "TRUE", "Reported","Unreported")) 


### Calculate reported status of Educational_Attainment and Occupation
Journal_year2021_education_occupation <- Journal %>% 
  dplyr::filter(substr(Article_IDs_N,1,4) == "2021") %>% 
  dplyr::filter(Sample_Type_N %in% c(4,5)) %>% 
  dplyr::group_by(Article_IDs,Study_Number) %>% 
  dplyr::summarise(Educational_Attainment_N = max(Educational_Attainment_N) > 0,
                   Occupation_N = max(Occupation_N) > 0,.groups = "drop") 



table(Journal_year2021_education_occupation$Educational_Attainment_N) ## FALSE 55 TRUE 33
table(Journal_year2021_education_occupation$Occupation_N)  ## FALSE 72 TRUE 16


Journal_year2021_education_occupation_table <- data.frame(Var1 = c("Unreported","Reported",
                                                            "Unreported","Reported"),
                                                   Freq = c(55,33,72,16),
                                                   col_names= c("Educational_Attainment",
                                                                "Educational_Attainment",
                                                                "Occupation","Occupation"),
                                                   proportion = c(0.63,0.37,0.82,0.19))

Journal_year2021_report2 <- rbind(Journal_year2021_report,
                                  Journal_year2021_education_occupation_table) %>%
  dplyr::mutate(col_names = factor(col_names, 
                                   labels = c("Gender","Age","Recruitment Method",
                                              "Recruitment Area","Sampling Method",
                                              "Educational Attainment",
                                              "SES","Occupation",
                                              "Ethnicity","Religious"),
                                   levels = c("Gender","Age","Recruitment_Method",
                                              "Recruitment_Area","Sampling_Method",
                                              "Educational_Attainment",
                                              "SES","Occupation",
                                              "Ethnicity","Religious")),
                proportion = proportion *100)%>% 
  dplyr::mutate(Year = "2021")
```


combine three data
```{r}
Journal_report <- bind_rows(Journal_year2008_report2,Journal_year2018_report2,Journal_year2021_report2) %>% 
  dplyr::filter(Var1 == "Reported") %>% 
  dplyr::add_row(data.frame(Var1 = c("Reported","Reported"),
                            Freq = c(0,0),
                            col_names = c("Religious","Religious"),
                            proportion = c(0,0),
                            Year = c("2008","2021"))) %>% 
  dplyr::mutate(col_names = factor(col_names,
                                   levels = c("Gender","Recruitment Method","Recruitment Area",
                                              "Age","Educational Attainment","Occupation",
                                              "Sampling Method","SES","Ethnicity",
                                              "Religious"),
                                   labels = c("Gender","Recruitment Method","Recruitment Area",
                                              "Age","Educational Attainment","Occupation",
                                              "Sampling Method","SES","Ethnicity",
                                              "Religious")))

Journal_report_year <- Journal_report %>% 
  ggplot(aes(x = Year, y = proportion, color = col_names, group = col_names))+
  geom_line(size = 1)+
  geom_point(size = 3)+
  labs(y="Proportion", x = "Year")+
  theme_classic()+
  theme(panel.border =element_rect(fill=NA,color="black"),
        legend.box.spacing = unit(2,"pt"),
        legend.text = element_text(size = 16, family = "serif"),
        legend.title = element_blank(),
        axis.title = element_text(size = 16,family = "serif"),
        axis.text = element_text(size = 16,family = "serif"))

ggsave("Journal_report_year.pdf", Journal_report_year, device = "pdf", width=12, height = 9)


Journal_report_year
```


## Abstract report

Abstract1 subjects information reported of Chinese journal
```{r message=FALSE, warning=FALSE}
## all data
Journal_abstract1_report <- Journal %>% 
  dplyr::select(Article_IDs,Study_Number,Subjects_Group,
                Target_Population_N,Sample_Type_N,Abstract1) %>% 
  dplyr::filter(Sample_Type_N != 5) %>%
  dplyr::group_by(Article_IDs) %>% 
  dplyr::mutate(Study_Type = ifelse(all(Sample_Type_N == 1),"Only college students",ifelse(any(grepl("1",Sample_Type_N)) & any(Sample_Type_N !=1),"College students & other populations","Only sample outside colleges"))) %>% 
  dplyr::ungroup() %>% 
  dplyr::group_by(Article_IDs) %>% 
  dplyr::slice(1) %>% 
  dplyr::ungroup() %>% 
  dplyr::mutate(Sample_Mentioned = ifelse(Abstract1 == "0" ,"Samples mentioned", "Sample not mentioned")) %>% 
  dplyr::group_by(Sample_Mentioned,Study_Type) %>% 
  dplyr::count() %>% 
  dplyr::ungroup() %>% 
  tidyr::pivot_wider(names_from = Sample_Mentioned, values_from = n)


## Chi
matrix_Journal_abstract1_report <- matrix(c(223, 195), nrow = 1)
colnames(matrix_Journal_abstract1_report) <- c("Sample not mentioned", "Samples mentioned")
rownames(matrix_Journal_abstract1_report) <- "Only college students"

matrix_Journal_abstract1_result <- chisq.test(matrix_Journal_abstract1_report)
matrix_Journal_abstract1_result 
```


I would like to explore whether there are differences in specific demographic information.

Mention in sample type
```{r}
## all data
Journal_abstract1_sampletype_report <- Journal %>% 
  dplyr::select(Article_IDs,Study_Number,Subjects_Group,
                Target_Population_N,Sample_Type_N,Abstract1) %>% 
  dplyr::filter(Sample_Type_N != 5) %>%
  dplyr::group_by(Article_IDs) %>% 
  dplyr::mutate(Study_Type = ifelse(all(Sample_Type_N == 1),"Only college students",ifelse(any(grepl("1",Sample_Type_N)) & any(Sample_Type_N !=1),"College students & other populations","Only sample outside colleges"))) %>% 
  dplyr::ungroup() %>% 
  dplyr::group_by(Article_IDs) %>% 
  dplyr::slice(1) %>% 
  dplyr::ungroup() %>% 
  dplyr::mutate(Sample_Mentioned = ifelse(grepl("1", Abstract1),"Samples mentioned", "Sample not mentioned")) %>% 
  dplyr::group_by(Sample_Mentioned,Study_Type) %>% 
  dplyr::count() %>% 
  dplyr::ungroup() %>% 
  tidyr::pivot_wider(names_from = Sample_Mentioned, values_from = n)
```


Chi-sqaure test
```{r}
## sample type mentioned for colleges
matrix_abstract1_sampletype_report <- matrix(c(212, 206), nrow = 1)
colnames(matrix_abstract1_sampletype_report) <- c("Sample not mentioned", "Samples mentioned")
rownames(matrix_abstract1_sampletype_report) <- "Only college students"


matrix_abstract1_sampletype_result <- chisq.test(matrix_abstract1_sampletype_report)
matrix_abstract1_sampletype_result



## I also try to analysis "Only sample outside colleges"
matrix_outside_colleges_report <- matrix(c(43, 401), nrow = 1)
colnames(matrix_outside_colleges_report) <- c("Sample not mentioned", "Samples mentioned")
rownames(matrix_outside_colleges_report) <- "Only sample outside colleges"


matrix_matrix_outside_colleges_result <- chisq.test(matrix_outside_colleges_report)
matrix_matrix_outside_colleges_result


## colleges and others samples
matrix_colleges_andothers_report <- matrix(c(11, 30), nrow = 1)
colnames(matrix_colleges_andothers_report) <- c("Sample not mentioned", "Samples mentioned")
rownames(matrix_colleges_andothers_report) <- "College students & other populations"


matrix_colleges_andothers_result <- chisq.test(matrix_colleges_andothers_report)
matrix_colleges_andothers_result 
```


Filter  2021 article and analysis abstract1 report
```{r} 
## all data
Journal_abstract1_year2021_report <- Journal %>% 
  dplyr::select(Article_IDs,Study_Number,Subjects_Group,
                Target_Population_N,Sample_Type_N,Abstract1) %>% 
  dplyr::filter(substr(Article_IDs,1,4) == "2021") %>% 
  dplyr::filter(Sample_Type_N != 5) %>%
  dplyr::group_by(Article_IDs) %>% 
  dplyr::mutate(Study_Type = ifelse(all(Sample_Type_N == 1),"Only college students",ifelse(any(grepl("1",Sample_Type_N)) & any(Sample_Type_N !=1),"College students & other populations","Only sample outside colleges"))) %>% 
  dplyr::ungroup() %>% 
  dplyr::group_by(Article_IDs) %>% 
  dplyr::slice(1) %>% 
  dplyr::ungroup() %>% 
  dplyr::mutate(Sample_Mentioned = ifelse(Abstract1 == "0" ,"Samples mentioned", "Sample not mentioned")) %>% 
  dplyr::group_by(Sample_Mentioned,Study_Type) %>% 
  dplyr::count() %>% 
  dplyr::ungroup() %>% 
  tidyr::pivot_wider(names_from = Sample_Mentioned, values_from = n)


## sample type
Journal_abstract1_year2021_sampletype_report <- Journal %>% 
  dplyr::select(Article_IDs,Study_Number,Subjects_Group,
                Target_Population_N,Sample_Type_N,Abstract1) %>% 
  dplyr::filter(substr(Article_IDs,1,4) == "2021") %>% 
  dplyr::filter(Sample_Type_N != 5) %>%
  dplyr::group_by(Article_IDs) %>% 
  dplyr::mutate(Study_Type = ifelse(all(Sample_Type_N == 1),"Only college students",ifelse(any(grepl("1",Sample_Type_N)) & any(Sample_Type_N !=1),"College students & other populations","Only sample outside colleges"))) %>% 
  dplyr::ungroup() %>% 
  dplyr::group_by(Article_IDs) %>% 
  dplyr::slice(1) %>% 
  dplyr::ungroup() %>% 
  dplyr::mutate(Sample_Mentioned = ifelse(grepl("1", Abstract1),"Samples mentioned", "Sample not mentioned")) %>% 
  dplyr::group_by(Sample_Mentioned,Study_Type) %>% 
  dplyr::count() %>% 
  dplyr::ungroup() %>% 
  tidyr::pivot_wider(names_from = Sample_Mentioned, values_from = n)
```


```{r}
## sample type mentioned for colleges
matrix_abstract1_sampletype_year2021_report <- matrix(c(62, 42), nrow = 1)
colnames(matrix_abstract1_sampletype_year2021_report) <- c("Sample not mentioned", "Samples mentioned")
rownames(matrix_abstract1_sampletype_year2021_report) <- "Only college students"


matrix_abstract1_sampletype_year2021_result <- chisq.test(matrix_abstract1_sampletype_year2021_report)
matrix_abstract1_sampletype_year2021_result



## I also try to analysis "Only sample outside colleges"
matrix_outside_colleges_year2021_report <- matrix(c(99, 4), nrow = 1)
colnames(matrix_outside_colleges_year2021_report) <- c("Sample not mentioned", "Samples mentioned")
rownames(matrix_outside_colleges_year2021_report) <- "Only sample outside colleges"


matrix_matrix_outside_colleges_year2021_result <- chisq.test(matrix_outside_colleges_year2021_report)
matrix_matrix_outside_colleges_year2021_result


## colleges and others samples
matrix_colleges_andothers_year2021_report <- matrix(c(16, 1), nrow = 1)
colnames(matrix_colleges_andothers_year2021_report) <- c("Sample not mentioned", "Samples mentioned")
rownames(matrix_colleges_andothers_year2021_report) <- "College students & other populations"


matrix_colleges_andothers_year2021_result <- chisq.test(matrix_colleges_andothers_year2021_report)
matrix_colleges_andothers_year2021_result 
```


Abstract2 report
university students reported in abstract when sample type is 1
```{r}
Journal_abstract2_report <- Journal %>% 
  dplyr::filter(grepl("1",Sample_Type_N)) %>% 
  dplyr::group_by(Article_IDs) %>% 
  dplyr::mutate(Abstract2_same = n_distinct(Abstract2) == 1) %>%  ## check multiple subjects group Abstract2 whether is consistent.
  dplyr::slice(1) %>% ## for one articles have multiple rows, only save the first row
  dplyr::ungroup() %>% 
  dplyr::group_by(Abstract2) %>% 
  dplyr::summarise(report = n()) %>% 
  dplyr::ungroup() %>% 
  dplyr::mutate(proportion = round(report/sum(report),2),
                Abstract2 = ifelse(Abstract2 == 0 ,"Unreported","Reported")) %>% 
  dplyr::rename(n = 2)


## Chi
matrix_abstract2_report <- matrix(c(241, 218), nrow = 1)
colnames(matrix_abstract2_report) <- c("Unreported", "Reported")

abstract2_result <- chisq.test(matrix_abstract2_report)
abstract2_result
```



## Reason for current data pattern
```{r}
Journal_subjects_recruitment <- Journal %>% 
  dplyr::select(Article_IDs,Article_Title,Study_Number_N,Subjects_Group_N,
                Target_Population_N,Sample_Type_N,Sampling_Method,Subjects_Recruitment_Method_N,
                Subjects_Recruitment_Method_info_N)

table(Journal_subjects_recruitment$Sampling_Method)  ## 0(1064),1(219),2(284)

table(Journal_subjects_recruitment$Subjects_Recruitment_Method_N)
```


```{r}
Journal_subjects_recruitment2 <- Journal_subjects_recruitment %>% 
  dplyr::filter(Target_Population_N != 1)

table(Journal_subjects_recruitment2$Subjects_Recruitment_Method_N)
```
```

